### 2019-01-20 manuscript/README.Rmd
Set up initial research compendium structure
Add the following directories:
 - /analysis folder with rmarkdown file containing analysis workflow.

 - /data folder for raw, clean, result data, and data from other papers.

 - /man folder for automatically generated function documentation.

 - /manuscript folder with rmarkdown file, will generate final paper.

 - /R folder containing R functions used in the compendium.

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# candidaev

This repository contains the data and code for our paper:

> Authors, (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _Title of paper_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Title of paper'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/csdaw/candidaev/archive/master.zip>

Or you can install this compendium as an R package, candidaev, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("csdaw/candidaev")
```
### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

### 2019-01-20 manuscript/manuscript.Rmd
Set up initial research compendium structure
Add the following directories:
 - /analysis folder with rmarkdown file containing analysis workflow.

 - /data folder for raw, clean, result data, and data from other papers.

 - /man folder for automatically generated function documentation.

 - /manuscript folder with rmarkdown file, will generate final paper.

 - /R folder containing R functions used in the compendium.

---
title: "Title Goes Here"
author:
  - Author One
  - Author Two
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)

library(candidaev) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

# Introduction

Here is a citation [@Marwick2017]

# Background

```{r demo, eval = FALSE}
1 + 1
```

# Methods

# Results

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- readr::read_csv(here::here('analysis', 'data', 'raw_data', 'my_csv_file.csv'))
```

# Discussion

# Conclusion

# Acknowledgements

<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
##### pagebreak

# References 
<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
<div id="refs"></div>

##### pagebreak

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
git2r::repository(here::here())
```

### 2019-01-22 R/README.Rmd
Update each README.md
Update each README.md to describe contents of each directory.

Remove CONDUcT.md and CONTRIBUTION.md.

Add the following:
 - mcp.csl file for correct citation style.

 - pagebreak.lua, a filter to convert LaTeX \newpage command into
   appropriate markup for other formats e.g. html, docx. See:
   https://github.com/pandoc/lua-filters/tree/master/pagebreak

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R

This directory contains R script files used throughout the project.

Each file contains several custom functions which have been
documented using roxygen2 skeletons.

# contents
```
    .
    ├── ...
    ├── /R
    │    ├── file1.R          # Functions for x
    │    ├── file2.R          # Functions for y
    │    ├── file3.R          # Functions for z
    │    ├── README.Rmd       # R markdown file to produce README.md
    │    └── README.md        # Description of /R directory
    └── ...

```

### 2019-01-22 README.Rmd
Update each README.md
Update each README.md to describe contents of each directory.

Remove CONDUcT.md and CONTRIBUTION.md.

Add the following:
 - mcp.csl file for correct citation style.

 - pagebreak.lua, a filter to convert LaTeX \newpage command into
   appropriate markup for other formats e.g. html, docx. See:
   https://github.com/pandoc/lua-filters/tree/master/pagebreak

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# candidaev

This repository contains the research compendium for our paper:

> Authors, (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

The compendium includes all the data, code, and text associated with the publication.
It is structured as an R package to facilitate reproducilibity and distribution.
The principles and motivations behind using research compendiums for academic 
research is detailed in [Marwick et al. (2017)](https://doi.org/10.1080/00031305.2017.1375986).

The R package [rrtools](https://github.com/benmarwick/rrtools) was used in the 
production of this compendium.

### Contents

```
    .
    ├── /R                   # Script files containing reused functions
    ├── /analysis            # Full analysis report and scripts
    ├── /data                # Raw, cleaned, external, and results data
    ├── /manuscript          # Final manuscript and associated files
    ├── .Rbuildignore        # List of files and directories to ignore during R package build
    ├── .gitignore           # List of files to ignore during git commit
    ├── DESCRIPTION          # Research compendium metadata
    ├── LICENSE.md           # MIT License for code
    ├── NAMESPACE            # Auto-generated file for function export
    ├── README.Rmd           # R markdown file to produce README.md
    ├── README.md            # Description of research compendium
    └── candidaev.Rproj      # R project file for compendium

```

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Title of paper'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/csdaw/candidaev/archive/master.zip>

Or you can install this compendium as an R package `candidaev` from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("csdaw/candidaev")
```
### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### 2019-01-22 analysis/README.Rmd
Update each README.md
Update each README.md to describe contents of each directory.

Remove CONDUcT.md and CONTRIBUTION.md.

Add the following:
 - mcp.csl file for correct citation style.

 - pagebreak.lua, a filter to convert LaTeX \newpage command into
   appropriate markup for other formats e.g. html, docx. See:
   https://github.com/pandoc/lua-filters/tree/master/pagebreak

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# analysis

This directory contains the complete data analysis workflow upon which the paper

> Authors, (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

is based upon.

# contents
```
    .
    ├── ...
    ├── /analysis
    │    ├── /figures           # Contains figures generated by analysis R scripts
    │    ├── analysis.Rmd       # R markdown file to produce analysis.html/analysis.md (haven't decided)
    │    ├── analysis.html      # Contains cleaned reference tables
    │    ├── analysis.md        # Contains final results tables
    │    ├── file1.R            # Script for x
    │    ├── README.Rmd         # R markdown file to produce README.md
    │    └── README.md          # Description of /analysis directory
    └── ...

```

### 2019-01-22 manuscript/README.Rmd
Update each README.md
Update each README.md to describe contents of each directory.

Remove CONDUcT.md and CONTRIBUTION.md.

Add the following:
 - mcp.csl file for correct citation style.

 - pagebreak.lua, a filter to convert LaTeX \newpage command into
   appropriate markup for other formats e.g. html, docx. See:
   https://github.com/pandoc/lua-filters/tree/master/pagebreak

@@
 
-# candidaev
+# manuscript
 
-This repository contains the data and code for our paper:
+This directory contains the final manuscript as submitted to Molecular
+and Cellular Proteomics. It also contains templates and other files necessary 
+for producing the `manuscript.pdf` file from the associated `manuscript.Rmd`.
 
-> Authors, (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>
+# contents
+```
+    .
+    ├── ...
+    ├── /manuscript
+    │    ├── /figures            # Contains figures draw by hand
+    │    ├── /templates          # Contains citation and pagebreak templates
+    │    ├── manuscript.Rmd      # R markdown file to produce manuscript.pdf
+    │    ├── manuscript.pdf      # Final submitted manuscript
+    │    ├── references.bib      # BibTex file containing manuscript references
+    │    ├── README.Rmd          # R markdown file to produce README.md
+    │    └── README.md           # Description of /manuscripts directory
+    └── ...
 
-Our pre-print is online here:
-
-> Authors, (YYYY). _Title of paper_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
-
-### How to cite
-
-Please cite this compendium as:
-
-> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Title of paper'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
-
-### How to download or install
-
-You can download the compendium as a zip from from this URL: <https://github.com/csdaw/candidaev/archive/master.zip>
-
-Or you can install this compendium as an R package, candidaev, from GitHub with:
-```{r gh-installation, eval = FALSE}
-# install.packages("devtools")
-devtools::install_github("csdaw/candidaev")
 ```
-### Licenses
-
-**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
-
-**Code :** See the [DESCRIPTION](DESCRIPTION) file
-
-**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
-
-### Contributions
-
-We welcome contributions from everyone.
-Before you get started, please see our [contributor guidelines](CONTRIBUTING.md).
-Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
-By participating in this project you agree to abide by its terms.

### 2019-01-22 manuscript/manuscript.Rmd
Update each README.md
Update each README.md to describe contents of each directory.

Remove CONDUcT.md and CONTRIBUTION.md.

Add the following:
 - mcp.csl file for correct citation style.

 - pagebreak.lua, a filter to convert LaTeX \newpage command into
   appropriate markup for other formats e.g. html, docx. See:
   https://github.com/pandoc/lua-filters/tree/master/pagebreak

@@
 ---
-title: "Title Goes Here"
-author:
-  - Author One
-  - Author Two
-date: "`r format(Sys.time(), '%d %B, %Y')`"
+title: "**Defining protein biomarkers for *Candida albicans* extracellular vesicles**"
+author: "*Charlotte Dawson^a^, Mark Bleackley^a^, Marilyn Anderson^a^*"
+date: "*^a^Department of Biochemistry and Genetics, La Trobe University, Victoria, Australia*"
 output: 
-    bookdown::html_document2:
+    bookdown::word_document2:
+      pandoc_args:
+        '--lua-filter=templates/pagebreak.lua'
+      reference_docx: "templates/draft_template.docx"
       fig_caption: yes
-      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
+    html_notebook: default
+    bookdown::pdf_document2:
+      latex_engine: xelatex
+      fig_caption: yes
+      number_sections: yes
+      toc: no
+      keep_tex: no
 bibliography: references.bib
-csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
-abstract: |
-  Text of abstract
-keywords: |
-  keyword 1; keyword 2; keyword 3
-highlights: |
-  These are the highlights. 
+csl: "templates/molecular-and-cellular-proteomics.csl"
+fontsize: 12pt
+geometry: margin=1in
+classoption: letterpaper
+mainfont: Times New Roman
+linestretch: 1.5
+header-includes:
+  - \usepackage{titling}
+  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
+  - \posttitle{\par\end{center}}
+  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
+  - \postauthor{\par\end{center}}
+  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
+  - \postdate{\par\end{center}}
+  - \usepackage{fancyhdr}
+  - \usepackage{lipsum}
+  - \pagestyle{fancy}
+  - \fancyhead[L]{This is the running title it is rather long}
 ---
+
+**Running title:** Running title goes here
+
+**Corresponding author:**
+
+\newpage
 
@@
 ```
+
+# Abbreviations
+
+EV - extracellular vesicle
+
+\newpage
+
+# Abstract
+
+The abstract goes here.
+
+\newpage
 
@@
 # Note the path that we need to use to access our data files when rendering this document
-my_data <- readr::read_csv(here::here('analysis', 'data', 'raw_data', 'my_csv_file.csv'))
+my_data <- readr::read_csv(here::here('analysis')
 ```
@@
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
-
 # References 
@@
 <div id="refs"></div>
-
-##### pagebreak
-
-### Colophon
-
-This report was generated on `r Sys.time()` using the following computational environment and dependencies:
-
-```{r colophon, cache = FALSE}
-# which R packages and versions?
-devtools::session_info()
-```
-
-The current Git commit details are:
-
-```{r}
-# what commit is this file at? 
-git2r::repository(here::here())
-```

### 2019-01-24 analysis/yeast_analysis.R
Add utility and clean functions
Also:

 - add blank analysis.Rmd and cleaned reference tables
 - add incomplete yeast_analysis script for DAY286 yeast MS analysis
   to eventually be incorporated into analysis.Rmd with analyses of
   the other samples

@@ -1,0 +1,34 @@
+#### Data description ----
+# 1 strain (yeast DAY286), 4 biological replicates, 2 compartments (EV & WCL)
+# (WCL = whole cell lysate)
+# shotgun proteomics data obtained on Thermo Q Exactive HF
+# raw data searched against C. albicans SC5314 UniProt proteome with MaxQuant
+# resulting proteinGroups.txt file used for this analysis, rows = protein groups
+
+#### Load required packages and scripts ----
+library(dplyr)
+source("R/util.R")
+
+#### Import data and reference tables ----
+# load proteinGroups.txt
+pg_orig <- read.table("data/raw/yeast-proteinGroups.txt", sep = "\t", header = TRUE)
+
+# fix headers containing extra `.`
+pg_orig <- colClean(pg_orig)
+
+# load clean UniProt reference table
+unip_table <- read.table(file = "data/clean/unip-table.txt", sep = "\t", header = TRUE,
+                         stringsAsFactors = FALSE)
+
+# load clean CGD reference table
+cgd_table <- read.table(file = "data/clean/cgd-table.txt", sep = "\t", header = TRUE,
+                        stringsAsFactors = FALSE)
+
+#### Initial protein filtering ----
+# remove reversed proteins, contaminant proteins
+pg <- pg_orig %>%
+  filter(Reverse != "+", Potential.contaminant != "+")
+
+# keep only proteins with min 2 unique peptides
+pg <- val_filter(df = pg, pattern = "Unique.peptides", value = 2)
+

### 2019-02-04 manuscript/manuscript.Rmd
Update references.bib

@@
 csl: "templates/molecular-and-cellular-proteomics.csl"
+link-citations: yes
+linkcolor: blue
 fontsize: 12pt
@@
 
-Here is a citation [@Marwick2017]
+Here is a citation [@marwick2017].
 

### 2019-02-13 R/reftable_clean.R
Fix reference tables
Also:
 - Complete yeast_analysis.R script

 - Update bibliography

 - Fix `plot_venn` function

@@ -42,7 +42,7 @@ clean_cgd <- function(file) {
                            "Scerevisiae_orthologs")
 
   # extract orf identifiers (Feature_name) from aliases column
-  cgd_table$Feature_name <- stringr::str_extract(cgd_table$Aliases, "orf19.[0-9]+")
+  cgd_table$Feature_name <- stringr::str_extract(cgd_table$Aliases, "(orf19.[0-9.]+)|(CaalfMp[0-9]{2})")
 
   # replace blank gene names with orf identifiers
   cgd_table <- fill_blank(cgd_table, "Gene_name", "Feature_name")
@@ -154,7 +154,8 @@ clean_unip <- function(file) {
   cgd_table <- read.table(file = "data/clean/cgd-table.txt",
                           header = TRUE,
                           sep = "\t",
-                          stringsAsFactors = FALSE)
+                          stringsAsFactors = FALSE,
+                          check.names = FALSE)
   unip_table$CGDID2 <- as.character(cgd_table$CGDID[match(unip_table$Gene_name_ol,
                                                           cgd_table$Systematic_name)])
 
@@ -168,22 +169,22 @@ clean_unip <- function(file) {
 
   unip_table <- fill_na(unip_table, "CGDID", "CGDID3")
 
-  # remove semicolons in CGDID column
-  unip_table$CGDID <- gsub(";C", "; C", unip_table$CGDID)
+  # remove semicolons if there is only one CGDID in CGDID column
+  unip_table$CGDID <- gsub(";$", "", unip_table$CGDID)
 
-  unip_table$CGDID <- gsub(";", "", unip_table$CGDID)
-
-  # add CGD gene name column (using first UniProt CGDID for crossreference)
-  unip_table$CGD_gene_name <- as.character(cgd_table$Gene_name[match(stringr::str_extract(unip_table$CGDID,
-                                                                                          "[^ ]*"),
-                                                                     cgd_table$CGDID)])
+  # add some CGD columns (using UniProt CGDIDs for crossreference)
+  unip_table$CGD_gene_name <- match_uniprot(unip_table$CGDID, cgd_table, "Gene_name", "CGDID")
+  unip_table$CGD_feature_name <- match_uniprot(unip_table$CGDID, cgd_table, "Feature_name", "CGDID")
[…]

### 2019-02-13 data-raw/README.Rmd
Move raw data
 - Begin restructure of repository to conform to traditional structure
   of an R package.

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# data

This directory contains all of the data files used to generate results
tables and figures.

# contents
```
    .
    ├── ...
    ├── /data
    │    ├── /raw            # Contains raw untouched data files
    │    ├── /external       # Contains data from other papers
    │    ├── /clean          # Contains cleaned reference tables
    │    ├── /results        # Contains final results tables
    │    ├── README.Rmd      # R markdown file to produce README.md
    │    └── README.md       # Description of /data directory
    └── ...

```

### 2019-02-13 data-raw/README.Rmd
Update ./data-raw README

@@
 
-# data
+# /data-raw
 
-This directory contains all of the data files used to generate results
-tables and figures.
+## description
+This directory contains all of the raw data files used in this project. These files are
+*not* included when the package is installed using `devtools::install_github()`. Rather 
+*'clean'* versions of the `.csv` and `.tab` files are provided in the [`/data`](../data) 
+folder as `.rda` files which are accessible once the package has been installed and 
+loaded or attached.
 
-# contents
+To access these raw files:
+
+1. Right click on a desired file and select `Save link as...`.
+
+2. Copy the url for the desired directory, paste into 
+[DownGit](https://minhaskamal.github.io/DownGit/#/home), then download as a `.zip`.
+
+3. Download this entire repository as a `.zip` from this URL: 
+<https://github.com/csdaw/candidaev/archive/master.zip>
+
+4. Clone this repository.
+
+## contents
 ```
@@
     ├── ...
-    ├── /data
-    │    ├── /raw            # Contains raw untouched data files
-    │    ├── /external       # Contains data from other papers
-    │    ├── /clean          # Contains cleaned reference tables
-    │    ├── /results        # Contains final results tables
+    ├── /data-raw
+    │    ├── /external       # Supplementary data tables from other Candida EV proteomics papers
+    │    ├── /lcms           # proteinGroups.txt files output by MaxQuant
+    │    ├── /nta            # Nanosight ns300 .csv summary tables
+    │    ├── /qubit          # Qubit 4 EV protein quantification data 
+    │    ├── /reference      # UniProt and Candida Genome Database reference tables
     │    ├── README.Rmd      # R markdown file to produce README.md
-    │    └── README.md       # Description of /data directory
+    │    └── README.md       # Description of /data-raw directory
     └── ...

### 2019-02-20 R/combine_result.R
Fix plot functions and begin ATCC analysis

@@ -12,6 +12,6 @@
 combine_result <- function(mat, toptab) {
   result <- cbind(mat,
                   toptab[match(rownames(mat), rownames(toptab)), ],
-                  significant = toptab[, "adj.P.Val"] < 0.01)
+                  significant = toptab[match(rownames(mat), rownames(toptab)), "adj.P.Val"] < 0.01)
   return(result)
 }

### 2019-02-20 R/plot_venn.R

@@ -5,9 +5,7 @@
 #'
 #' @param use_uniprot Description
 #'
-#' @param plot Description
-#'
-#' @param file Description
+#' @param type Description
 #'
 #' @param output Description
 #'
@@ -44,8 +42,8 @@
 #'
 #' @importFrom grDevices dev.off png tiff
 #' @export
-plot_venn <- function(vlist, use_uniprot = FALSE, plot = TRUE,
-                      file = NULL, output = c("tiff", "png"), output_dim = c(1000, 1000),
+plot_venn <- function(vlist, use_uniprot = FALSE, type = c("list", "plot", "output"),
+                      output = c("tiff", "png"), output_file = NULL, output_dim = c(1000, 1000),
                       output_res = 300, output_units = "px",
                       output_pts = 14, ...) {
   # supress futile logger message from VennDiagram package
@@ -60,7 +58,7 @@ plot_venn <- function(vlist, use_uniprot = FALSE, plot = TRUE,
   } else {comparison <- vlist}
 
   # plot venn in R, plot venn and save file, or get venn partition lists
-  if(plot == TRUE & is.null(file) == FALSE) {
+  if(type == "save") {
     venn_plot <- VennDiagram::venn.diagram(x = comparison,
                                            filename = NULL, ...)
     if(output == "tiff") {
@@ -87,12 +85,10 @@ plot_venn <- function(vlist, use_uniprot = FALSE, plot = TRUE,
       grid::grid.draw(venn_plot)
       dev.off()
     }
-  } else if(plot == TRUE & is.null(file) == TRUE) {
-    venn_plot <- VennDiagram::venn.diagram(x = comparison,
-                                           filename = NULL, ...)
-    grid::grid.newpage()
-    grid::grid.draw(venn_plot)
-  } else if(plot == FALSE) {
+  } else if(type == "plot") {
+    venn_plot <- VennDiagram::venn.diagram(x = comparison, filename = NULL, ...)
+    return(venn_plot)
+  } else if(type == "list") {
     venn <- VennDiagram::get.venn.partitions(comparison)
     return(venn)
   }

### 2019-03-11 R/get_results.R
Add plots for combined datasets
 - Plot 4-way venn diagram, MDS, heatmap to analyse and compare all
   four datasets at once.

@@ -73,7 +73,7 @@ get_results <- function(efit, mat, p_val = 0.01, lfc = 0, type = c("overall", "i
                CGD_gene_name = match_id(UP_accession, uniprot, "UP_accession", "CGD_gene_name"),
                Protein_name = match_id(UP_accession, uniprot, "UP_accession", "Protein_name")) %>%
         filter(is.na(.[[c1_labels[1]]]) == FALSE | is.na(.[[c2_labels[1]]]) == FALSE) %>%
-        select(UP_accession, CGD_gene_name, Protein_name, everything())
+        select(UP_accession, CGD_gene_name, Protein_name, everything(), -AveExpr)
     }
 
     names(result) <- gsub(" - ", ".vs.", contrasts)

### 2019-03-11 R/match_id.R

@@ -13,6 +13,7 @@
 #' @param new string: column name of character column in reference table with new
 #' information to replace matches
 #' @param concat Description.
+#' @param str_split Description.
 #'
 #' @return A vector with the same length as \code{id} but with the values replaced
 #' with corresponding information from the reference table.
@@ -34,17 +35,22 @@
 #' my_names$last <- match_id(my_names$id, ref_df, "id", "last_name")
 #'
 #' @export
-match_id <- function(id, ref, match, new, concat = TRUE) {
-  if(concat == TRUE) {
+match_id <- function(id, ref, match, new, concat = TRUE, str_split = TRUE) {
+  if(concat == TRUE & str_split == TRUE) {
     stringr::str_extract_all(id, "[^;]+") %>%
       lapply(., function(x) match(x, ref[[match]])) %>%
       Map("[", list(as.character(ref[[new]])), .) %>%
       lapply(., function(x) paste(x, collapse = ";")) %>%
       unlist()
-  } else if(concat == FALSE) {
+  } else if(concat == FALSE & str_split == TRUE) {
     stringr::str_extract_all(id, "[^;]+") %>%
       lapply(., function(x) match(x, ref[[match]])) %>%
       Map("[", list(as.character(ref[[new]])), .) %>%
+      unlist()
+  } else if (concat == TRUE & str_split == FALSE) {
+    lapply(id, function(x) match(x, ref[[match]])) %>%
+      Map("[", list(as.character(ref[[new]])), .) %>%
+      lapply(., function(x) paste(x, collapse = ";")) %>%
       unlist()
   }
 }

### 2019-03-12 R/plot_volcano.R
Add figure 3 to manuscript.Rmd

@@ -15,7 +15,7 @@
 #' #example
 #'
 #' @export
-plot_volcano <- function(data, p_val, lfc, grp, colour = c("red1", "blue1"), label) {
+plot_volcano <- function(data, p_val, lfc, grp, label) {
   p_val <- rlang::enquo(p_val)
   lfc <- rlang::enquo(lfc)
   grp <- rlang::enquo(grp)
@@ -24,12 +24,16 @@ plot_volcano <- function(data, p_val, lfc, grp, colour = c("red1", "blue1"), lab
 
   ggplot(data = dplyr::filter(data, !is.na(!!lfc)),
          mapping = aes(x = !!lfc, y = -log10(!!p_val))) +
-    geom_point(mapping = aes(colour = !!grp)) +
-    scale_colour_manual(values = c(colour, "gray")) +
+    geom_point(mapping = aes(colour = !!grp), size = 0.6) +
+    theme_classic(base_size = 8) +
+    theme(legend.position = "left",
+          legend.title = element_blank(),
+          axis.text = element_text(colour = "black", size = 10)) +
+    guides(colour = guide_legend(override.aes = list(size = 3))) +
     ggrepel::geom_text_repel(data = dplyr::filter(data, !is.na(!!lfc)),
                              mapping = aes(label = !!label),
-                             show.legend = FALSE) +
-    theme_classic() +
-    theme(legend.position = "top",
-          legend.title = element_blank())
+                             show.legend = FALSE,
+                             size = 2) +
+    xlab(expression(log[2]("FC"))) +
+    ylab(expression(-log[10]("Adj. p-value")))
 }

### 2019-03-19 R/plot_mds.R
Refine figure 4

@@ -11,14 +11,18 @@
 #'
 #' @export
 #'
-plot_mds <- function(mat) {
+plot_mds <- function(mat, mat_labels, shape_size = 2) {
   mds <- limma::plotMDS(mat, plot = FALSE)
 
   coord <- data.frame(dim1 = mds[["x"]],
                       dim2 = mds[["y"]]) %>%
     tibble::rownames_to_column(var = "sample") %>%
-    mutate(sample = stringr::str_extract(.[["sample"]], "[^_]+"))
+    mutate(sample = stringr::str_extract(.[["sample"]], "[^_]+"),
+           label = mat_labels)
 
-  ggplot(coord, aes(x = dim1, y = dim2, colour = sample)) +
-    geom_point()
+  ggplot(coord, aes(x = dim1, y = dim2)) +
+    geom_point(aes(colour = sample, shape = sample), size = shape_size) +
+    geom_text(aes(label = mat_labels), hjust = 1.4, vjust = 0.5) +
+    xlab(label = "Dimension 1") +
+    ylab(label = "Dimension 2")
 }

### 2019-03-20 R/plot_go_bar.R
Add GO terms to Figure 4
Also:

 - Change Fig. 5 to a venn diagram
 - Add WCL comparison venn to Fig. 5
 - Adjust venns in Fig. 3A
 - Add x axis labels to Fig. 2C
 - Add unnfinished WCL equivalent to Table 1 in Supplementary

@@ -1,0 +1,32 @@
+#' Title
+#'
+#' Description.
+#'
+#' @param go_table Description.
+#' @param terms_list Description.
+#' @param col_pal Description.
+#'
+#' @return Description.
+#'
+#' @examples
+#' # example
+#'
+#' @export
+plot_go_bar <- function(go_table, terms_list, col_pal) {
+  ggplot(data = go_table[terms_list, ],
+         aes(x = reorder(GO.term, Cat.ratio),
+             y = Cat.ratio*100)) +
+    geom_bar(stat = "identity", aes(fill = GO.type)) +
+    theme_classic(base_size = 8) +
+    scale_y_continuous(limits = c(0,100), expand = expand_scale(mult = c(0, .05))) +
+    labs(x = NULL,
+         y = "Percent GO term coverage",
+         fill = "GO category") +
+    theme(legend.justification = c(1,0),
+          legend.position = "top",
+          axis.text.x = element_text(size = 8),
+          axis.text.y = element_text(size = 6, colour = "black"),
+          panel.grid.major.x = element_line(size = 0.2, colour = "black")) +
+    scale_fill_manual(values = col_pal) +
+    coord_flip()
+}

### 2019-03-22 R/plot_mds.R
Add caption Fig. 4

@@ -12,7 +12,7 @@
 #' @export
 #'
 plot_mds <- function(mat, mat_labels, shape_size = 2) {
-  mds <- limma::plotMDS(mat, plot = FALSE)
+  mds <- limma::plotMDS(mat, top = 500, gene.selection = "common", plot = FALSE)
 
   coord <- data.frame(dim1 = mds[["x"]],
                       dim2 = mds[["y"]]) %>%

### 2019-04-15 R/plot_heatmap2.R
Finalise `plot_heatmap`
 - `plot_heatmap` now returns a plot, a heatmap object, or a data.frame

 - Replace use of ComplexHeatmap::Heatmap in manuscript.Rmd with
   the `plot_heatmap` function

 - Delete redundant `plot_heatmap2` modified function from the DEP
   package.

@@ -1,229 +1,0 @@
-#' Plot a heatmap
-#'
-#' \code{plot_heatmap} generates a heatmap of all significant proteins.
-#'
-#' @param mat SummarizedExperiment,
-#' Data object for which differentially enriched proteins are annotated
-#' (output from \code{test_diff()} and \code{add_rejections()}).
-#' @param exd 'contrast' or 'centered',
-#' The type of data scaling used for plotting.
-#' Either the fold change ('contrast') or
-#' the centered log2-intensity ('centered').
-#' @param unip Description.
-#' @param kmeans Logical(1),
-#' Whether or not to perform k-means clustering.
-#' @param k Integer(1),
-#' Sets the number of k-means clusters.
-#' @param col_limit Integer(1),
-#' Sets the outer limits of the color scale.
-#' @param indicate Character,
-#' Sets additional annotation on the top of the heatmap
-#' based on columns from the experimental design (colData).
-#' Only applicable to type = 'centered'.
-#' @param clustering_distance "euclidean", "maximum", "manhattan", "canberra",
-#' "binary", "minkowski", "pearson", "spearman", "kendall" or "gower",
-#' Function used to calculate clustering distance (for proteins and samples).
-#' Based on \code{\link[ComplexHeatmap]{Heatmap}}
-#' and \code{\link[cluster]{daisy}}.
-#' @param row_font_size Integer(1),
-#' Sets the size of row labels.
-#' @param col_font_size Integer(1),
-#' Sets the size of column labels.
-#' @param plot Logical(1),
-#' If \code{TRUE} (default) the heatmap is produced.
-#' Otherwise (if \code{FALSE}), the data which the
-#' heatmap is based on are returned.
-#' @param ... Additional arguments for Heatmap function as depicted in
-#' \code{\link[ComplexHeatmap]{Heatmap}}
-#' @return A heatmap (generated by \code{\link[ComplexHeatmap]{Heatmap}})
-#' @examples
-#' \dontrun{
-#' # Load example
-#' data <- UbiLength
-#' data <- data[data$Reverse != "+" & data$Potential.contaminant != "+",]
-#' data_unique <- make_unique(data, "Gene.names", "Protein.IDs", delim = ";")
-#'
-#' # Make SummarizedExperiment
-#' columns <- grep("LFQ.", colnames(data_unique))
-#' exp_design <- UbiLength_ExpDesign
-#' se <- make_se(data_unique, columns, exp_design)
-#'
[…]

### 2019-04-15 R/plot_volcano.R
Finalise `plot_volcano`
 - `plot_volcano` now allows slightly more customisation

 - Update `plot_volcano` calls in manuscript.Rmd

 - Delete redundant `plot_volcano2` modified function from the DEP
   package

 - Remove documentation for deleted functions `plot_volcano2` and
   `plot_heatmap2`

 - Closes #1, #7

@@ -4,36 +4,64 @@
 #'
 #' @param data Description.
 #' @param p_val Description.
-#' @param lfc Description.
-#' @param grp Description.
-#' @param colour Description.
-#' @param label Description.
+#' @param log2fc Description.
+#' @param group Description.
+#' @param label_fun Description.
+#' @param point_size Description.
+#' @param label_size Description.
+#' @param x_lim Description.
+#' @param y_lim Description.
+#' @param legend_params Description.
+#' @param axis_params Description.
 #'
 #' @return Description.
 #'
 #' @examples
-#' #example
+#'
+#' # example
 #'
 #' @export
-plot_volcano <- function(data, p_val, lfc, grp, label) {
+plot_volcano <- function(data, p_val, log2fc, group, label_fun,
+                         point_size = 1, label_size = 2,
+                         x_lim = c(-10, 10), y_lim = c(0, 10),
+                         legend_params = c("left", 11, 10),
+                         axis_params = c("black", 10)) {
+
+  # enquo data columns and label function
   p_val <- rlang::enquo(p_val)
-  lfc <- rlang::enquo(lfc)
-  grp <- rlang::enquo(grp)
-  label <- rlang::enquo(label)
+  log2fc <- rlang::enquo(log2fc)
+  group <- rlang::enquo(group)
+  label_fun <- rlang::enquo(label_fun)
 
+  # plot all data that has a valid log2fc value
+  p <- ggplot(data = dplyr::filter(data, !is.na(!!log2fc)),
+              mapping = aes(x = !!log2fc, y = -log10(!!p_val))) +
+    geom_point(mapping = aes(colour = !!group), size = point_size) +
+    theme_classic(base_size = 11)
 
-  ggplot(data = dplyr::filter(data, !is.na(!!lfc)),
-         mapping = aes(x = !!lfc, y = -log10(!!p_val))) +
-    geom_point(mapping = aes(colour = !!grp), size = 0.6) +
-    theme_classic(base_size = 8) +
-    theme(legend.position = "left",
-          legend.title = element_text(size = 11, face = "bold"),
-          axis.text = element_text(colour = "black", size = 10)) +
+  # adjust legend position, text sizes, text colours
+  p <- p +
+    theme(legend.position = legend_params[1],
+          legend.title = element_text(size = legend_params[2], face = "bold"),
+          legend.text = element_text(size = legend_params[3]),
+          axis.text = element_text(colour = axis_params[1], size = axis_params[2]))
+
[…]

### 2019-04-16 R/plot_volcano.R
Reanalyse DAY286 yeast data
Drop WCL replicate 1 instead of replicate 2 in processing of
'yeast' data set.

Explanation:
 - The 'yeast' data set in this package has 4 biological replicates
   (EV and WCL).

 - Previously, during data processing, yeast EV replicate 1 was dropped
   because it did not cluster with the other EV replicates and was
   approximately the same distance away from the other EV samples as
   the WCL samples.

 - WCL replicate 2 was dropped because it had a high number of missing
   values.

 - Change to drop WCL replicate 1. Then the three remaining EV and WCL
   replica

@@ -60,7 +60,7 @@ plot_volcano <- function(data, p_val, log2fc, group, label_fun,
     scale_x_continuous(limits = x_lim, expand = c(0,0)) +
     xlab(expression(log[2]("FC"))) +
     scale_y_continuous(limits = y_lim, expand = c(0,0)) +
-    ylab(expression(-log[10]("Adj. p-value")))
+    ylab(expression(-log[10]("adj. p-val")))
 
   # return plot
   p

### 2019-04-26 R/plot_go_bar.R
Split figure 4
 - Assign GO bar plots figure 4

 - Create new figure 5 with MDS plot and 4 way EV venn diagram

 - Also add new MDS plot and 4 way WCL venn diagram

 - Rename old figure 5 to figure 6 and so on

 - Fix type in NTA metadata in manuscript_supplement.Rmd

 - Finally, add some comments and clean up code a bit

@@ -25,7 +25,7 @@ plot_go_bar <- function(go_table, terms_list, col_pal) {
     theme(legend.justification = c(1,0),
           legend.position = "top",
           axis.text.x = element_text(size = 8),
-          axis.text.y = element_text(size = 6, colour = "black"),
+          axis.text.y = element_text(size = 7, colour = "black"),
           panel.grid.major.x = element_line(size = 0.2, colour = "black")) +
     scale_fill_manual(values = col_pal) +
     coord_flip()

### 2019-04-26 R/plot_mds.R

@@ -11,8 +11,12 @@
 #'
 #' @export
 #'
-plot_mds <- function(mat, mat_labels, shape_size = 2) {
-  mds <- limma::plotMDS(mat, top = 500, gene.selection = "common", plot = FALSE)
+plot_mds <- function(mat, mat_labels, shape_size = 2, ...) {
+  mds <- limma::plotMDS(mat,
+                        top = 500,
+                        gene.selection = "common",
+                        plot = FALSE,
+                        ...)
 
   coord <- data.frame(dim1 = mds[["x"]],
                       dim2 = mds[["y"]]) %>%
@@ -21,7 +25,5 @@ plot_mds <- function(mat, mat_labels, shape_size = 2) {
            label = mat_labels)
 
   ggplot(coord, aes(x = dim1, y = dim2)) +
-    geom_point(aes(fill = sample, shape = label), size = shape_size, colour = "black") +
-    xlab(label = "Dimension 1") +
-    ylab(label = "Dimension 2")
+    geom_point(aes(fill = sample, shape = label), size = shape_size, colour = "black")
 }

### 2019-04-30 R/plot_venn.R
Add EV protein yield to supplement Data
Also:
 - Add missing table reference in manuscript

 - Fix cutoff figure S1 x-axis

@@ -42,7 +42,7 @@
 #'
 #' @importFrom grDevices dev.off png tiff
 #' @export
-plot_venn <- function(vlist, use_uniprot = FALSE, type = c("list", "plot", "output"),
+plot_venn <- function(vlist, use_uniprot = FALSE, type = c("list", "plot", "save"),
                       output = c("tiff", "png"), output_file = NULL, output_dim = c(1000, 1000),
                       output_res = 300, output_units = "px",
                       output_pts = 14, ...) {

### 2019-05-02 R/plot_go_bar.R
Change figure 4 GO bar plot order

@@ -13,8 +13,13 @@
 #'
 #' @export
 plot_go_bar <- function(go_table, terms_list, col_pal) {
-  ggplot(data = go_table[terms_list, ],
-         aes(x = reorder(GO.term, Cat.ratio),
+  df <- go_table[terms_list, ]
+
+  df <- df %>%
+    arrange(adj.p.val)
+
+  ggplot(data = df,
+         aes(x = reorder(GO.term, rev(adj.p.val)),
              y = Cat.ratio*100)) +
     geom_bar(stat = "identity", aes(fill = GO.type)) +
     theme_classic(base_size = 8) +

### 2019-05-05 vignettes/supplement_files/sfile_S1.R
Finalise supplementary files for review

@@ -31,14 +31,23 @@ make_s1 <- function(df) {
            CGDID = match_id(Majority.protein.IDs,
                             uniprot,
                             "UP_accession",
-                            "CGDID")) %>%
+                            "CGDID"),
+           First.protein = stringr::str_extract(Majority.protein.IDs, "[^;]+"),
+           "Mass.(kDa)" = as.numeric(gsub(",", "",
+                                         match_id(First.protein,
+                                                  uniprot,
+                                                  "UP_accession",
+                                                  "Mass_(Da)",
+                                                  concat = FALSE)))/1000) %>%
     select(Majority.protein.IDs,
            CGDID,
            Protein.name,
            Function,
+           "Mass.(kDa)",
            Q.value,
            Score,
-           everything()) %>%
+           everything(),
+           -First.protein) %>%
     rename_all(list(~ stringr::str_replace_all(., "\\.", " ")))
 }
 

### 2019-05-07 R/atcc.R
Add more function documentation

@@ -1,7 +1,7 @@
 #' \emph{C. albicans} (ATCC10231, ATCC90028) extracellular vesicle and
 #' whole cell lysate LC-MS/MS data.
 #'
-#' @description \code{atcc} is a data.frame of a MaxQuant \code{proteinGroups.txt}
+#' @description \code{atcc} is a \code{data.frame} of a MaxQuant \code{proteinGroups.txt}
 #' file generated by \href{https://doi.org}{Dawson et al. (2019)}.
 #'
 #' It contains label free quantification (LFQ) and intensity-based absolute
@@ -66,5 +66,4 @@
 #'
 #' @source Dawson, C. S., Bleackley, M. R., Garcia-Ceron, D., & Anderson, M. A. (2019).
 #' Title. \emph{Journal vol}(issue), 000-000. doi:
-#'
 "atcc"

### 2019-05-07 R/atcc_exp.R

@@ -20,5 +20,4 @@
 #'
 #' @source Dawson, C. S., Bleackley, M. R., Garcia-Ceron, D., & Anderson, M. A. (2019).
 #' Title. \emph{Journal vol}(issue), 000-000. doi:
-#'
 "atcc_exp"

### 2019-05-07 R/biofilm.R

@@ -63,5 +63,4 @@
 #'
 #' @source Dawson, C. S., Bleackley, M. R., Garcia-Ceron, D., & Anderson, M. A. (2019).
 #' Title. \emph{Journal vol}(issue), 000-000. doi:
-#'
 "biofilm"

### 2019-05-07 R/convert_lfq.R

@@ -30,15 +30,14 @@
 #' my_expDesign <- atcc_exp
 #'
 #' # filter for proteins identified with minimum 3 unique peptides
-#' # and convert to numerical matrix
-#' my_proteinGroups_filt <- my_proteinGroups %>%
+#' # and convert to numeric matrix
+#' my_lfq <- my_proteinGroups %>%
 #'   filter(Unique.peptides >= 3) %>%
 #'   convert_lfq(., my_expDesign)
 #'
 #' @import dplyr
 #'
 #' @export
-#'
 convert_lfq <- function(df, exd, log_2 = TRUE) {
   # define vector of labels from experimental design
   lfq_cols <- exd[["label"]]

### 2019-05-07 R/fill_blank.R

@@ -1,6 +1,6 @@
 #' Fill blanks in character column
 #'
-#' \code{fill_blank} fills any empty "" strings in a data.frame character
+#' @description \code{fill_blank} fills any empty "" strings in a data.frame character
 #' column with the corresponding strings from another character column in
 #' the same data.frame.
 #'
@@ -22,7 +22,6 @@
 #' df <- fill_blank(df, "name2", "name1")
 #'
 #' @export
-#'
 fill_blank <- function(df, blank_col, fill_col) {
   df[[blank_col]] <- as.character(ifelse(df[[blank_col]] == "",
                                          df[[fill_col]],

### 2019-05-07 R/filter_na.R

@@ -99,7 +99,6 @@
 #'
 #'
 #' @export
-#'
 filter_na <- function(data, op = c("==", "<=", ">="), pat, val) {
   # refer to operator by name
   op <- as.name(op)

### 2019-05-07 R/filter_na2.R

@@ -128,7 +128,6 @@
 #'   pull(colour)
 #'
 #' @export
-#'
 filter_na2 <- function(data, logic = c("and", "or"), op = c("==", ">=", "<="),
                        pat1, val1, pat2, val2) {
   # refer to operator by name

### 2019-05-07 R/filter_val.R

@@ -98,7 +98,6 @@
 #'
 #'
 #' @export
-#'
 filter_val <- function(data, op = c("==", "<=", ">="), pat, val) {
   # refer to operator by name
   op <- as.name(op)

### 2019-05-07 R/filter_zero.R

@@ -100,7 +100,6 @@
 #'
 #'
 #' @export
-#'
 filter_zero <- function(data, op = c("==", "<=", ">="), pat, val) {
   # refer to operator by name
   op <- as.name(op)

### 2019-05-07 R/filter_zero2.R

@@ -129,7 +129,6 @@
 #'   pull(colour)
 #'
 #' @export
-#'
 filter_zero2 <- function(data, logic = c("and", "or"), op = c("==", "<=", ">="),
                          pat1, val1, pat2, val2) {
   # refer to operator by name

### 2019-05-07 R/get_annotation2.R

@@ -1,67 +1,0 @@
-#' Title
-#'
-#' Internal function to get ComplexHeatmap::HeatmapAnnotation object.
-#'
-#' @param mat Description
-#' @param exd Description
-#' @param indicate Description
-#'
-#' @return Description
-#'
-#' @examples
-#' # example
-#'
-get_annotation2 <- function(mat, exd, indicate) {
-  assertthat::assert_that(
-    is.matrix(mat),
-    is.data.frame(exd),
-    assert_exd(exd),
-    is.character(indicate))
-
-  # Check indicate columns
-  col_data <- exd %>%
-    filter(ID %in% colnames(mat))
-  columns <- colnames(col_data)
-  if(all(!indicate %in% columns)) {
-    stop("'",
-         paste0(indicate, collapse = "' and/or '"),
-         "' column(s) is/are not present in ",
-         deparse(substitute(exd)),
-         ".\nValid columns are: '",
-         paste(columns, collapse = "', '"),
-         "'.",
-         call. = FALSE)
-  }
-  if(any(!indicate %in% columns)) {
-    indicate <- indicate[indicate %in% columns]
-    warning("Only used the following indicate column(s): '",
-            paste0(indicate, collapse = "', '"),
-            "'")
-  }
-
-  # Get annotation
-  anno <- select(col_data, indicate)
-
-  # Annotation color
-  names <- colnames(anno)
-  anno_col <- vector(mode="list", length=length(names))
-  names(anno_col) <- names
-  for(i in names) {
-    var = anno[[i]] %>% unique() %>% sort()
-    if(length(var) == 1)
-      cols <- c("black")
-    if(length(var) == 2)
-      cols <- c("orangered", "cornflowerblue")
-    if(length(var) < 7 & length(var) > 2)
-      cols <- RColorBrewer::brewer.pal(length(var), "Pastel1")
-    if(length(var) > 7)
-      cols <- RColorBrewer::brewer.pal(length(var), "Set3")
-    names(cols) <- var
-    anno_col[[i]] <-  cols
-  }
-
-  # HeatmapAnnotation object
-  ComplexHeatmap::HeatmapAnnotation(df = anno,
-                                    col = anno_col,
-                                    show_annotation_name = TRUE)
-}

### 2019-05-07 R/impute_QRILC.R

@@ -1,14 +1,35 @@
-#' Title
+#' Imputation of left-censored missing data using QRILC method
 #'
-#' @param mat Description
+#' @description This function is a simple wrapper around the
+#' \code{\link[imputeLCMD]{impute.QRILC}}
+#' function from \pkg{imputeLCMD}. See \code{\link[imputeLCMD]{impute.QRILC}} for
+#' more information.
 #'
-#' @return Returns x
+#' @param mat numeric matrix: contains \code{NA} values
 #'
-#' @export
+#' @return Returns a numeric \code{matrix} with missing values imputed.
 #'
 #' @examples
-#' # example
+#' # create a numeric matrix with missing data
+#' my_mat <- matrix(c(NA, NA, 30, NA, 25, NA,
+#'                    NA, 15, 31, 23, 24, NA,
+#'                    NA, NA, 32, 24, 23, NA,
+#'                    23, NA, 29, 22, NA, NA,
+#'                    24, NA, 30, NA, NA, NA,
+#'                    21, 14, 31, 24, NA, 12),
+#'                  nrow = 6,
+#'                  ncol = 6)
+#' colnames(my_mat) <- c("sample_1a",
+#'                       "sample_2a",
+#'                       "sample_3a",
+#'                       "sample_1b",
+#'                       "sample_2b",
+#'                       "sample_3b")
 #'
+#' # impute missing data
+#' my_mat2 <- impute_QRILC(my_mat)
+#'
+#' @export
 impute_QRILC <- function(mat) {
   imp <- imputeLCMD::impute.QRILC(mat)
   imp <- imp[[1]]

### 2019-05-07 R/limma_eBayes.R

@@ -1,29 +1,106 @@
-#' Title
+#' Perform differential protein abundance analysis with empirical Bayes
+#' method from \emph{limma}
 #'
-#' Description.
+#' @description This function performs differential abundance analysis of proteins
+#' using a linear model fit and the empirical Bayes method from the
+#' \pkg{limma}.
 #'
-#' @param mat Description.
+#' The code for this function is slighlty modified from a section of the \code{test_diff} function
+#' from the Bioconductor package \href{http://doi.org/10.18129/B9.bioc.DEP}{DEP}.
+#' \href{http://doi.org/10.18129/B9.bioc.DEP}{DEP} is distributed with the Artistic-2.0 license
+#' which requires any source code modifications to be clearly stated.
 #'
-#' @param design Description.
+#' \code{limma_eBayes} includes the following modifications of \code{test_diff}:
 #'
-#' @param contrasts Description.
+#' \itemize{
+#' \item Names of some objects have been changed.
+#' \item Order of \code{lmFit()} and \code{makeContrasts()} has been swapped.
+#' \item The rest of \code{test_diff} source code has been removed.
+#' }
 #'
-#' @return Description.
+#' The results of this function can be extracted using \code{\link{get_results}}.
+#'
+#' @param mat numeric matrix: typically this will include log2 LFQ intensity data.
+#' \code{NA} values are allowed, however the \code{\link[limma]{eBayes}} function may
+#' produce a warning
+#'
+#' @param design design matrix: created by \code{stats::model.matrix()}. See the
+#' \pkg{limma} user guide for instructions on creating design matrices.
+#'
+#' @param contrasts character vector: names of sample groups you want to contrast separated
+#' by a \code{-} sign. For example: \code{c("A1_EV - A1_W", "A9_EV - A9_W")}. These \strong{must}
+#' refer to column names present in the design matrix.
+#'
+#' @return Returns an object of class \code{MArrayLM}. See \code{\link[limma]{eBayes}} for
+#' more information. This object is required for \code{\link{get_results}}.
 #'
 #' @examples
-#' #example
+#' # load a proteinGroups data.frame supplied with this package
+#' my_proteinGroups <- atcc
+#'
+#' # load its corresponding experimental design
[…]

### 2019-05-07 R/match_id.R

@@ -1,38 +1,111 @@
-#' Replace values based on match
+#' Create a vector based on matching values with a reference table
 #'
-#' \code{match_id} matches a character vector with values (which may or may not be
+#' @description \code{match_id} matches a character vector with values (which may or may not be
 #' separated by semicolons) to a reference table with a character column containing
-#' values (which must not be separated by semicolons) and then replaces those
-#' values with corresponding information from another character column in the
+#' matching values (which may or may not be separated by semicolons) and then produces a
+#' vector with corresponding information from another character column in the
 #' reference table.
 #'
+#' \code{match_id} is  useful for adding single or multiple columns to a \code{data.frame} with
+#' \code{\link[dplyr]{mutate}} based on matching with several different
+#' reference tables.
+#'
+#' If you want to add multiple columns to a \code{data.frame} based on matching to a
+#' single reference table, use \code{\link{match_id_multi}}.
+#'
 #' @param id character vector: the values to be matched
-#' @param ref data frame: reference table with values to be matched against
-#' @param match string: column name of character column in reference table with
+#'
+#' @param ref data.frame: reference table with values to be matched against
+#'
+#' @param match string: name of character column in reference table with
 #' values to be matched against
-#' @param new string: column name of character column in reference table with new
-#' information to replace matches
-#' @param concat Description.
-#' @param str_split Description.
 #'
-#' @return A vector with the same length as \code{id} but with the values replaced
-#' with corresponding information from the reference table.
+#' @param new string: name of character column in reference table with
+#' corresponding information/values of interest
 #'
-#' If there is a value to be matched which is not present in the reference table,
-#' the value will be replaced with the string "NA"
+#' @param concat logical: if \code{TRUE} then if a value in \code{id} has multiple
+#' matches in the \code{ref$match} column, the corresponding values in \code{new}
+#' \strong{will} be concatenated with \code{;}. The default value is \code{TRUE}
+#' because it ensures the output of this function is the same length as \code{id}
+#' which is essential if you want to add the output as a \code{data.frame} column.
+#'
[…]

### 2019-05-07 R/match_id_multi.R

@@ -1,73 +1,92 @@
-#' Title
+#' Create data.frame or list based on matching values with a reference table
 #'
-#' Description.
+#' @description \code{match_id_multi} matches a character column in a \code{data.frame}
+#' with values (which may or may not be
+#' separated by semicolons) to a reference table with a character column containing matching
+#' values (which may or may not be separated by semicolons) and then produces a list of
+#' vectors with corresponding information from other selected columns in the reference
+#' table.
 #'
-#' @param df Description
-#' @param id Description
-#' @param ref Description
-#' @param match Description
-#' @param new Description
-#' @param as_list Description
+#' \code{match_id_multi} is  useful for adding multiple columns to a \code{data.frame}
+#' based on matching with a single reference table.
 #'
-#' @return Description
+#' If you want to add multiple columns to a \code{data.frame} based on matching to multiple
+#' reference tables, see \code{\link{match_id}}.
+#'
+#' @param df data.frame: contains the \code{id} column
+#'
+#' @param id string: name of a character column with values to be matched
+#'
+#' @param ref data.frame: reference table with values to be matched against
+#'
+#' @param match string: name of character column in reference table with
+#' values to be matched against
+#'
+#' @param new vector: name(s) of character column(s) in reference table with
+#' corresponding information/values of interest to append to \code{df}
+#'
+#' @param as_list logical: if \code{TRUE} output is a list of vectors and if
+#' \code{FALSE} output is a data.frame
+#'
+#' @param ... Other arguments passed to \code{\link{match_id}}. Used for specifying
+#' \code{concat = FALSE} or \code{str_split = FALSE} where required. See
+#' \code{\link{match_id}} for examples.
+#'
+#' @return If \code{as_list = TRUE}, returns a list of vectors with the values
+#' from the columns specified by \code{new}. If \code{as_list = FALSE} returns
+#' a \code{data.frame}
+#' with the column specified by \code{new} added to the end.
+#'
+#' If there is a value in \code{id} which is not present in \code{match},
+#' the output for that particular value will be the value \code{NA} or
+#' the string \code{"NA"}.
 #'
 #' @examples
 #' # make a reference table
-#' ref_df <- data.frame(id = c("a1", "a2", "a3"),
-#'                      last_name = c("Smith", "Brown", "Doe"),
-#'                      atr1 = c("Blue", "Brown", "Yellow"),
[…]

### 2019-05-07 R/plot_coverage2.R

@@ -1,66 +1,0 @@
-#' Plot protein coverage
-#'
-#' \code{plot_coverage} generates a barplot
-#' of the protein coverage in all samples.
-#'
-#' @param mat SummarizedExperiment,
-#' Data object for which to plot observation frequency.
-#' @param plot Logical(1),
-#' If \code{TRUE} (default) the barplot is produced.
-#' Otherwise (if \code{FALSE}), the data which the
-#' barplot is based on are returned.
-#' @return Barplot of protein coverage in samples
-#' (generated by \code{\link[ggplot2]{ggplot}})
-#' @examples
-#' \dontrun{
-#' # Load example
-#' data <- UbiLength
-#' data <- data[data$Reverse != "+" & data$Potential.contaminant != "+",]
-#' data_unique <- make_unique(data, "Gene.names", "Protein.IDs", delim = ";")
-#'
-#' # Make SummarizedExperiment
-#' columns <- grep("LFQ.", colnames(data_unique))
-#' exp_design <- UbiLength_ExpDesign
-#' se <- make_se(data_unique, columns, exp_design)
-#'
-#' # Filter and plot coverage
-#' filt <- filter_missval(se, thr = 0)
-#' plot_coverage(filt)
-#' }
-#' @export
-plot_coverage2 <- function(mat, plot = TRUE) {
-  # Show error if input is not the required classes
-  assertthat::assert_that(is.matrix(mat),
-                          is.logical(plot),
-                          length(plot) == 1)
-
-  # Make a binary long data.frame (1 = valid value, 0 = missing value)
-  df <- mat %>%
-    data.frame() %>%
-    tibble::rownames_to_column() %>%
-    tidyr::gather(ID, bin, -rowname) %>%
-    mutate(bin = ifelse(is.na(bin), 0, 1))
-  # Identify the number of experiments a protein was observed
-  stat <- df %>%
-    group_by(rowname) %>%
-    summarise(sum = sum(bin))
-  # Get the frequency of the number of experiments proteins were observerd
-  # and plot the cumulative sum of these numbers
-  table <- table(stat$sum) %>%
-    data.frame()
-  p <- ggplot(table, aes(x = "all", y = Freq, fill = Var1)) +
-    geom_col(col = "white") +
-    scale_fill_grey(start = 0.8, end = 0.2) +
-    labs(title = "Protein coverage",
-         x = "",
-         y = "Number of proteins",
[…]

### 2019-05-07 R/plot_detect2.R

@@ -1,37 +1,64 @@
-#' Visualize intensities of proteins with missing values
+#' Visualise intensities of proteins with missing values
 #'
-#' \code{plot_detect} generates density and CumSum plots
-#' of protein intensities with and without missing values
+#' @description \code{plot_detect2} generates density and cumulative sum plots
+#' of protein intensities for proteins with and without missing values.
 #'
-#' @param mat SummarizedExperiment,
-#' Data object with missing values.
-#' @return Density and CumSum plots of intensities of
+#' This function has been taken directly from the \code{plot_detect} function
+#' in the \href{http://doi.org/10.18129/B9.bioc.DEP}{DEP} package and then
+#' modified for use in this package.
+#'
+#' \href{http://doi.org/10.18129/B9.bioc.DEP}{DEP} is distributed with the Artistic-2.0 license
+#' which requires any source code modifications to be clearly stated.
+#'
+#' \code{plot_detect2} includes the following modifications of \code{plot_detect}:
+#'
+#' \itemize{
+#' \item Dependance on a "SummarizedExperiment" object as input has been removed.
+#' Instead the input has been changed to a numeric matrix.
+#' \item Use of \code{theme_DEP1()} has been replaced with \code{theme_bw()}
+#' \item x axis labels have been changed to "log2 LFQ intensity".
+#' }
+#'
+#' @param mat numeric matrix: must have missing values
+#'
+#' @return Returns density and cumulative sum plots of protein intensities for
 #' proteins with and without missing values
 #' (generated by \code{\link[ggplot2]{ggplot}}).
+#'
 #' @examples
-#' \dontrun{
-#' # Load example
-#' data <- UbiLength
-#' data <- data[data$Reverse != "+" & data$Potential.contaminant != "+",]
-#' data_unique <- make_unique(data, "Gene.names", "Protein.IDs", delim = ";")
+#' # load a proteinGroups data.frame supplied with this package
+#' my_proteinGroups <- atcc
 #'
-#' # Make SummarizedExperiment
-#' columns <- grep("LFQ.", colnames(data_unique))
-#' exp_design <- UbiLength_ExpDesign
-#' se <- make_se(data_unique, columns, exp_design)
+#' # load its corresponding experimental design
+#' my_expDesign <- atcc_exp
 #'
-#' # Filter
[…]

### 2019-05-07 R/plot_frequency2.R

@@ -1,32 +1,52 @@
-#' Plot protein overlap between samples
+#' Plot frequency of protein quantification between samples
 #'
-#' \code{plot_frequency} generates a barplot
-#' of the protein overlap between samples
+#' @description \code{plot_frequency2} generates a bar plot of how many proteins are
+#' quantified in only 1 out of x samples, 2 out of x samples, 3 out of
+#' x samples, etc., i.e. protein quantification frequency.
 #'
-#' @param mat SummarizedExperiment,
-#' Data object for which to plot observation frequency.
-#' @param plot Logical(1),
-#' If \code{TRUE} (default) the barplot is produced.
-#' Otherwise (if \code{FALSE}), the data which the
-#' barplot is based on are returned.
-#' @return Barplot of overlap of protein identifications
-#' between samples (generated by \code{\link[ggplot2]{ggplot}})
-#' @examples
-#' \dontrun{
-#' # Load example
-#' data <- UbiLength
-#' data <- data[data$Reverse != "+" & data$Potential.contaminant != "+",]
-#' data_unique <- make_unique(data, "Gene.names", "Protein.IDs", delim = ";")
+#' This function has been taken directly from the \code{plot_frequency} function
+#' in the \href{http://doi.org/10.18129/B9.bioc.DEP}{DEP} package and then
+#' modified for use in this package.
 #'
-#' # Make SummarizedExperiment
-#' columns <- grep("LFQ.", colnames(data_unique))
-#' exp_design <- UbiLength_ExpDesign
-#' se <- make_se(data_unique, columns, exp_design)
+#' \href{http://doi.org/10.18129/B9.bioc.DEP}{DEP} is distributed with the Artistic-2.0 license
+#' which requires any source code modifications to be clearly stated.
 #'
-#' # Filter and plot frequency
-#' filt <- filter_missval(se, thr = 0)
-#' plot_frequency(filt)
+#' \code{plot_frequency2} includes the following modifications of \code{plot_frequency}:
+#'
+#' \itemize{
+#' \item Dependance on a "SummarizedExperiment" object as input has been removed.
+#' Instead the input has been changed to a numeric matrix.
+#' \item Use of \code{theme_DEP1()} has been replaced with \code{theme_bw()}
+#' \item Plot title has been changed to "Protein quantification frequency".
 #' }
+#'
+#' @param mat numeric matrix: from which to plot protein quantification frequency
[…]

### 2019-05-07 R/plot_heatmap.R

@@ -1,30 +1,179 @@
-#' Title
+#' Plot a protein heatmap
 #'
-#' Description.
+#' @description \code{plot_heatmap} generates a heatmap of proteins
+#' based on either their log2 LFQ intensities across in each sample or
+#' their log2FC between sample groups.
 #'
-#' @param mt Description.
-#' @param plot Description.
-#' @param df Description.
-#' @param data_type Description.
-#' @param clust_fun Description.
-#' @param split_type Description.
-#' @param k Description.
-#' @param cluster_split Description.
-#' @param split_order Description.
-#' @param colour_lims Description.
-#' @param use_cbrewer Description.
-#' @param cbrewer_pal Description.
-#' @param colour_vals Description.
-#' @param legend_pos Description.
-#' @param row_title_fontsize Description.
-#' @param col_name_fontsize Description.
-#' @param ... Description.
+#' This function uses the \code{\link[ComplexHeatmap]{Heatmap}} function from
+#' \pkg{ComplexHeatmap} to generate the heatmap.
+#' If the numeric matrix input does not have missing values, then the clustering
+#' methods built into \code{\link[ComplexHeatmap]{Heatmap}} should be used for
+#' row and column clustering. If there are \code{NA} values in the numeric matrix
+#' input, then \code{clust_fun = "gower"} should be specified, which uses
+#' Gower's formula via the \code{\link[cluster]{daisy}} function from the
+#' package \pkg{cluster} for row and column clustering.
 #'
-#' @return Description.
+#' @param mt numeric matrix: contains either log2 intensities or log2 fold change data.
+#' If \code{NA} values are present, use \code{clust_fun = "gower"}.
+#'
+#' @param plot logical: if \code{TRUE} the heatmap will be plotted using
+#' \code{\link[ComplexHeatmap]{draw}}. If \code{FALSE}, either a
+#' \code{\link[ComplexHeatmap]{Heatmap-class}} object or a \code{data.frame} will be
+#' generated, depending on the value of \code{df}.
+#'
+#' @param df logical: if \code{TRUE} a \code{data.frame} with the data underlying the
+#' heatmap (include the cluster id) is generated, with the proteins in order of
+#' appearance in the heatmap. If \code{FALSE}, a
+#' \code{\link[ComplexHeatmap]{Heatmap-class}} object is generated.
[…]

### 2019-05-10 R/plot_detect2.R
Make figure 2C dots black
Also:
 - Change `plot_detect2` base size to 12

 - Begin fixing up atcc_analysis.Rmd and yeast_analysis.Rmd

@@ -88,11 +88,11 @@ plot_detect2 <- function(mat) {
     geom_density(na.rm = TRUE) +
     labs(x = expression(log[2]~"LFQ intensity"), y = "Density") +
     guides(col = guide_legend(title = "Missing values")) +
-    theme_bw()
+    theme_bw(base_size = 12)
   p2 <- ggplot(cumsum, aes(mean, cs_frac, col = missval)) +
     geom_line() +
     labs(x = expression(log[2]~"LFQ intensity"), y = "Cumulative fraction") +
     guides(col = guide_legend(title = "Missing values")) +
-    theme_bw()
+    theme_bw(base_size = 12)
   gridExtra::grid.arrange(p1, p2, ncol = 1)
 }

### 2019-05-17 R/plot_normalization2.R
Add `process_fungifun` function
Also:
 - Remove `plot_dendro` function
 - Rename `plot_normalization2` x axis
 - Fix typos in some documentation

@@ -101,6 +101,6 @@ plot_normalization2 <- function(exd, mat, ...) {
     geom_boxplot(notch = TRUE, na.rm = TRUE) +
     coord_flip() +
     facet_wrap(~var, ncol = 1) +
-    labs(x = "", y = expression(log[2]~"Intensity")) +
+    labs(x = "", y = expression(log[2]~"LFQ intensity")) +
     theme_bw(base_size = 12)
 }

### 2019-05-17 R/uniprot.R

@@ -72,7 +72,7 @@
 #'
 #' @source The UniProt Consortium (2019). UniProt: a worldwide hub of protein
 #' knowledge. \emph{Nucleic Acids Research, 47}(D1), D506-D515.
-#' \href{https://doi.org/10.1093/nar/gky1049}
+#' \href{https://doi.org/10.1093/nar/gky1049}{doi:10.1093/nar/gky1049}
 #'
 #' Arnaud, M.B., Costanzo, M. C., Skrzypek, M. S., Binkley, G., Lane, C.,
 #' Miyasato, S. R., & Sherlock, G. (2005). The Candida Genome Database (CGD),

### 2019-05-17 R/filter_na2.R
Address some warnings produced by check()

@@ -73,8 +73,8 @@
 #'                       "total")
 #'
 #' # keep rows with maximum 1/3 NA values
-#' in the sample a columns and 1/3 NA values
-#' in the sample b columns
+#' # in the sample a columns and 1/3 NA values
+#' # in the sample b columns
 #' my_mat2 <- filter_na2(my_mat,
 #'                       logic = "or",
 #'                       op = "<=",
@@ -110,6 +110,8 @@
 #' ## note you can also use this function with
 #' ## dplyr functions and magrittr pipes
 #' ## (and other tidyverse functions probably)
+#' # load dplyr
+#' library(dplyr)
 #'
 #' # drop the 'total' column
 #' # keep rows with at least 2/3 NA values in the

### 2019-05-17 R/filter_na4.R

@@ -100,6 +100,8 @@
 #'                       pat4 = "sample.*d", val4 = 0)
 #'
 #' ## example for a data.frame input
+#' # load dplyr
+#' library(dplyr)
 #'
 #' # define a 6x14 data.frame
 #' my_df <- my_mat %>%

### 2019-05-17 R/filter_val.R

@@ -83,6 +83,8 @@
 #' ## note you can also use this function with
 #' ## dplyr functions and magrittr pipes
 #' ## (and other tidyverse functions perhaps)
+#' # load dplyr
+#' library(dplyr)
 #'
 #' # drop the 'total' column
 #' # keep rows where sample columns add up to

### 2019-05-17 R/filter_val2.R

@@ -112,6 +112,8 @@
 #' ## note you can also use this function with
 #' ## dplyr functions and magrittr pipes
 #' ## (and other tidyverse functions probably)
+#' # load dplyr
+#' library(dplyr)
 #'
 #' # drop the 'total' column
 #' # keep rows where the sample a columns add up

### 2019-05-17 R/filter_val4.R

@@ -100,6 +100,8 @@
 #'                        pat4 = "sample.*d", val4 = 20)
 #'
 #' ## example for a data.frame input
+#' # load dplyr
+#' library(dplyr)
 #'
 #' # define a 6x14 data.frame
 #' my_df <- my_mat %>%

### 2019-05-17 R/filter_zero2.R

@@ -74,8 +74,8 @@
 #'                       "total")
 #'
 #' # keep rows with maximum 1/3 zero values
-#' in the sample a columns and 1/3 zero values
-#' in the sample b columns
+#' # in the sample a columns and 1/3 zero values
+#' # in the sample b columns
 #' my_mat2 <- filter_zero2(my_mat,
 #'                         logic = "or",
 #'                         op = "<=",
@@ -111,6 +111,8 @@
 #' ## note you can also use this function with
 #' ## dplyr functions and magrittr pipes
 #' ## (and other tidyverse functions probably)
+#' # load dplyr
+#' library(dplyr)
 #'
 #' # drop the 'total' column
 #' # keep rows with at least 2/3 zero values in the

### 2019-05-17 R/limma_eBayes.R

@@ -35,6 +35,9 @@
 #' more information. This object is required for \code{\link{get_results}}.
 #'
 #' @examples
+#' # load dplyr
+#' library(dplyr)
+#'
 #' # load a proteinGroups data.frame supplied with this package
 #' my_proteinGroups <- atcc
 #'
@@ -50,14 +53,14 @@
 #' # filter for proteins quantified in min 2/3 reps of
 #' # at least 1 sample group
 #' my_filt <- my_lfq %>%
-#'   filter_na4(my_lfq, logic = "or", op = "<=",
+#'   filter_na4(., logic = "or", op = "<=",
 #'              pat1 = "A10231_EV", val1 = 1,
 #'              pat2 = "A10231_W", val2 = 1,
 #'              pat3 = "A90028_EV", val3 = 1,
 #'              pat4 = "A90028_W", val4 = 1)
 #'
 #' # normalise LFQ intensities
-#' my_norm <- normalizeCyclicLoess(my_filt)
+#' my_norm <- limma::normalizeCyclicLoess(my_filt)
 #'
 #' # impute missing values
 #' my_imp <- impute_QRILC(my_norm)
@@ -82,30 +85,34 @@
 #' my_efit <- limma_eBayes(mat = my_imp, design = my_design, contrasts = my_contrasts)
 #'
 #' # extract overall results table
-#' result_overall <- get_results(efit = my_efit, mat = my_imp, p_val = 0.001, lfc = 0, type = "overall")
+#' result_overall <- get_results(my_efit, my_imp,
+#'                               p_val = 0.001, lfc = 0, type = "overall")
 #'
 #' # extract list of results tables for each individual contrast
-#' result_list <- get_results(efit = my_efit, mat = my_imp, p_val = 0.001, lfc = 0, type = "individual")
+#' result_list <- get_results(my_efit, my_imp,
+#'                            p_val = 0.001, lfc = 0, type = "individual")
 #'
 #' # see results table for A9_EV versus A9_W contrast
 #' result_a9 <- result_list[[2]]
 #'
 #' @export
 limma_eBayes <- function(mat, design, contrasts) {
-  cm <- makeContrasts(contrasts = contrasts, levels = design)
-  fit <- lmFit(mat, design = design)
+  cm <- limma::makeContrasts(contrasts = contrasts, levels = design)
+  fit <- limma::lmFit(mat, design = design)
 
[…]

### 2019-05-17 R/match_id.R

@@ -67,25 +67,25 @@
 #' # match the accession column in the reference table and...
 #' # output a vector of gene_names
 #' my_gn <- match_id(id = my_data$id,
-#'                   ref_df = my_ref,
+#'                   ref = my_ref,
 #'                   match = "accession",
 #'                   new = "gene_name")
 #'
 #' # create a new column in my_data with corresponding
 #' # protein names
 #' my_data$pn <- match_id(id = my_data$id,
-#'                        ref_df = my_ref,
+#'                        ref = my_ref,
 #'                        match = "accesssion",
 #'                        new = "protein_name")
 #'
 #' # create several new columns in my_data using dplyr
 #' my_data <- my_data %>%
-#'   mutate(gn = match_id(id, my_df, "accession", "gene_name"),
-#'          pn = match_id(id, my_df, "accession", "protein_name"))
+#'   mutate(gn = match_id(id, my_ref, "accession", "gene_name"),
+#'          pn = match_id(id, my_ref, "accession", "protein_name"))
 #'
 #' # output a vector of gene_names that are not concatenated
 #' my_gn <- match_id(id = my_data$id,
-#'                   ref_df = my_ref,
+#'                   ref = my_ref,
 #'                   match = "accession",
 #'                   new = "gene_name",
 #'                   concat = FALSE)
@@ -102,7 +102,7 @@
 #' # match the accession column in the reference table by not
 #' # splitting the strings in the id column in the data table
 #' my_data2$gn <- match_id(id = my_data2$id,
-#'                         ref_df = my_ref2,
+#'                         ref = my_ref2,
 #'                         match = "accession",
 #'                         new = "gene_name",
 #'                         str_split = FALSE)

### 2019-05-17 R/match_id_multi.R

@@ -74,6 +74,17 @@
 #'                           new = c("protein_name", "gene_name",
 #'                           as_list = TRUE))
 #'
+#' # use with dplyr
+#' library(dplyr)
+#'
+#' my_data3 <- my_data %>%
+#'   select(-sample_B3) %>%
+#'   match_id_multi(.,
+#'                  id = "id",
+#'                  ref = my_ref,
+#'                  match = "accession",
+#'                  new = c("protien_name", "gene_name"))
+#'
 #' @export
 match_id_multi <- function(df, id, ref, match, new, as_list = FALSE, ...) {
   new_columns <- lapply(new, function(x) match_id(id = df[[id]],
@@ -85,7 +96,7 @@ match_id_multi <- function(df, id, ref, match, new, as_list = FALSE, ...) {
   names(new_columns) <- new
 
   if(as_list == FALSE) {
-    new_df <- dplyr::bind_cols(df, new_columns)
+    new_df <- bind_cols(df, new_columns)
 
     new_df
   } else {new_columns}

### 2019-05-17 R/plot_detect2.R

@@ -26,6 +26,9 @@
 #' (generated by \code{\link[ggplot2]{ggplot}}).
 #'
 #' @examples
+#' # load dplyr
+#' library(dplyr)
+#'
 #' # load a proteinGroups data.frame supplied with this package
 #' my_proteinGroups <- atcc
 #'
@@ -41,14 +44,14 @@
 #' # filter for proteins quantified in min 2/3 reps of
 #' # at least 1 sample group
 #' my_filt <- my_lfq %>%
-#'   filter_na4(my_lfq, logic = "or", op = "<=",
+#'   filter_na4(., logic = "or", op = "<=",
 #'              pat1 = "A10231_EV", val1 = 1,
 #'              pat2 = "A10231_W", val2 = 1,
 #'              pat3 = "A90028_EV", val3 = 1,
 #'              pat4 = "A90028_W", val4 = 1)
 #'
 #' # normalise LFQ intensities
-#' my_norm <- normalizeCyclicLoess(my_filt)
+#' my_norm <- limma::normalizeCyclicLoess(my_filt)
 #'
 #' # generate density and cumulative sum plots
 #' plot_detect2(my_norm)

### 2019-05-17 R/plot_frequency2.R

@@ -33,6 +33,9 @@
 #' returns a \code{data.frame} with the data underlying the bar plot.
 #'
 #' @examples
+#' # load dplyr
+#' library(dplyr)
+#'
 #' # load a proteinGroups data.frame supplied with this package
 #' my_proteinGroups <- atcc
 #'

### 2019-05-17 R/plot_go_bar.R

@@ -19,7 +19,7 @@
 #' \code{\link[ggplot2]{ggplot}}).
 #'
 #' @examples
-#' \dontrun{
+#' \donttest{
 #' # import a FungiFun2 output .csv file
 #' go_table <- process_fungifun("./vignettes/figures/f4_GO_DAY_Y.csv")
 #'
@@ -44,7 +44,7 @@ plot_go_bar <- function(go_table, terms_list, col_pal) {
     arrange(adj.p.val)
 
   ggplot(data = df,
-         aes(x = reorder(GO.term, rev(adj.p.val)),
+         aes(x = stats::reorder(GO.term, rev(adj.p.val)),
              y = Cat.ratio*100)) +
     geom_bar(stat = "identity", aes(fill = GO.type)) +
     theme_classic(base_size = 8) +

### 2019-05-17 R/plot_heatmap.R

@@ -74,6 +74,9 @@
 #' returns a \code{data.frame} with the proteins listed in order of appearance in the heatmap.
 #'
 #' @examples
+#' # load dplyr
+#' library(dplyr)
+#'
 #' ## log2 LFQ intensity type heatmap
 #' # load a proteinGroups data.frame supplied with this package
 #' my_proteinGroups <- atcc
@@ -90,14 +93,14 @@
 #' # filter for proteins quantified in min 2/3 reps of
 #' # at least 1 sample group
 #' my_filt <- my_lfq %>%
-#'   filter_na4(my_lfq, logic = "or", op = "<=",
+#'   filter_na4(., logic = "or", op = "<=",
 #'              pat1 = "A10231_EV", val1 = 1,
 #'              pat2 = "A10231_W", val2 = 1,
 #'              pat3 = "A90028_EV", val3 = 1,
 #'              pat4 = "A90028_W", val4 = 1)
 #'
 #' # normalise LFQ intensities
-#' my_norm <- normalizeCyclicLoess(my_filt)
+#' my_norm <- limma::normalizeCyclicLoess(my_filt)
 #'
 #' # impute missing values
 #' my_imp <- impute_QRILC(my_norm)
@@ -122,7 +125,8 @@
 #' my_efit <- limma_eBayes(mat = my_imp, design = my_design, contrasts = my_contrasts)
 #'
 #' # extract overall results table
-#' result_overall <- get_results(efit = my_efit, mat = my_imp, p_val = 0.001, lfc = 0, type = "overall")
+#' result_overall <- get_results(efit = my_efit, mat = my_imp,
+#'                               p_val = 0.001, lfc = 0, type = "overall")
 #'
 #' # plot a log2 LFQ intensity heatmap
 #' htmp_data <- result_overall %>%
@@ -143,7 +147,7 @@
 #'              heatmap_legend_param = list(title = "legend title",
 #'                                          color_bar = "continuous",
 #'                                          direction = "vertical",
-#'                                          legend_width = ggplot2::unit(5, "cm"),
+#'                                          legend_width = grid::unit(5, "cm"),
 #'                                          title_position = "lefttop-rot",
 #'                                          at = seq(-10, 10, 2)))
 #'
@@ -169,7 +173,7 @@
 #'              heatmap_legend_param = list(title = expression(bold(log[2]("FC"))),
[…]

### 2019-05-17 R/plot_missval2.R

@@ -27,6 +27,9 @@
 #' (generated by \code{\link[ComplexHeatmap]{Heatmap}}).
 #'
 #' @examples
+#' # load dplyr
+#' library(dplyr)
+#'
 #' # load a proteinGroups data.frame supplied with this package
 #' my_proteinGroups <- atcc
 #'
@@ -42,7 +45,7 @@
 #' # filter for proteins quantified in min 2/3 reps of
 #' # at least 1 sample group
 #' my_filt <- my_lfq %>%
-#'   filter_na4(my_lfq, logic = "or", op = "<=",
+#'   filter_na4(., logic = "or", op = "<=",
 #'              pat1 = "A10231_EV", val1 = 1,
 #'              pat2 = "A10231_W", val2 = 1,
 #'              pat3 = "A90028_EV", val3 = 1,

### 2019-05-17 R/plot_normalization2.R

@@ -33,6 +33,9 @@
 #' after normalisation (generated by \code{\link[ggplot2]{ggplot}}).
 #'
 #' @examples
+#' # load dplyr
+#' library(dplyr)
+#'
 #' # load a proteinGroups data.frame supplied with this package
 #' my_proteinGroups <- atcc
 #'
@@ -48,24 +51,24 @@
 #' # filter for proteins quantified in min 2/3 reps of
 #' # at least 1 sample group
 #' my_filt <- my_lfq %>%
-#'   filter_na4(my_lfq, logic = "or", op = "<=",
+#'   filter_na4(., logic = "or", op = "<=",
 #'              pat1 = "A10231_EV", val1 = 1,
 #'              pat2 = "A10231_W", val2 = 1,
 #'              pat3 = "A90028_EV", val3 = 1,
 #'              pat4 = "A90028_W", val4 = 1)
 #'
 #' # normalise LFQ intensities using limma
-#' my_norm <- normalizeCyclicLoess(my_filt)
+#' my_norm <- limma::normalizeCyclicLoess(my_filt)
 #'
 #' # normalise LFQ intensities
 #' # using some other function from limma
-#' my_norm2 <- normalizeQuantiles(my_filt)
+#' my_norm2 <- limma::normalizeQuantiles(my_filt)
 #'
 #' # box plots before and after normalisations
-#' plot_normalization(exd = atcc_exp,
-#'                    my_filt,
-#'                    my_norm,
-#'                    my_norm2)
+#' plot_normalization2(exd = atcc_exp,
+#'                     my_filt,
+#'                     my_norm,
+#'                     my_norm2)
 #'
 #' @export
 plot_normalization2 <- function(exd, mat, ...) {

### 2019-05-17 R/plot_numbers2.R

@@ -35,6 +35,9 @@
 #' returns a \code{data.frame} with the data underlying the bar plot.
 #'
 #' @examples
+#' # load dplyr
+#' library(dplyr)
+#'
 #' # load a proteinGroups data.frame supplied with this package
 #' my_proteinGroups <- atcc
 #'
@@ -49,7 +52,7 @@
 #'
 #' # generate bar plot of number of proteins
 #' # quantified per sample
-#' plot_numbers2(my_lfq)
+#' plot_numbers2(my_lfq, my_expDesign)
 #'
 #' @export
 plot_numbers2 <- function(mat, exd, plot = TRUE) {

### 2019-05-17 R/plot_venn.R

@@ -75,19 +75,20 @@
 #' # get the data underlying the Venn
 #' my_venn_data <- plot_venn(vlist = comp,
 #'                           type = "df")
-#'
+#' \donttest{
 #' # plot Venn diagram and save as png
 #' plot_venn(vlist = comp,
 #'           type = "save",
 #'           output = "png",
-#'           output_file = "path/to/save/to/my_venn.png")
+#'           output_file = "./venn/my_venn.png")
 #'
 #' # plot Venn diagram and save as svg
 #' plot_venn(vlist = comp,
 #'           type = "save",
 #'           output = "svg",
-#'           output_file = "path/to/save/to/my_venn.svg",
+#'           output_file = "./venn/my_venn.svg",
 #'           output_dim = c(6, 6))
+#' }
 #'
 #' @importFrom grDevices dev.off png tiff svg
 #' @export
@@ -98,7 +99,8 @@ plot_venn <- function(vlist, use_uniprot = FALSE,
                       output_dim = c(1000, 1000),
                       output_units = "px",
                       output_res = 300,
-                      output_pts = 14, ...) {
+                      output_pts = 14,
+                      ...) {
   # supress futile logger message from VennDiagram package
   futile.logger::flog.threshold(futile.logger::ERROR,
                                 name = "VennDiagramLogger")

### 2019-05-17 R/plot_volcano.R

@@ -60,6 +60,9 @@
 #' \code{label_fun != " "}.
 #'
 #' @examples
+#' # load dplyr
+#' library(dplyr)
+#'
 #' # load a proteinGroups data.frame supplied with this package
 #' my_proteinGroups <- atcc
 #'
@@ -75,14 +78,14 @@
 #' # filter for proteins quantified in min 2/3 reps of
 #' # at least 1 sample group
 #' my_filt <- my_lfq %>%
-#'   filter_na4(my_lfq, logic = "or", op = "<=",
+#'   filter_na4(., logic = "or", op = "<=",
 #'              pat1 = "A10231_EV", val1 = 1,
 #'              pat2 = "A10231_W", val2 = 1,
 #'              pat3 = "A90028_EV", val3 = 1,
 #'              pat4 = "A90028_W", val4 = 1)
 #'
 #' # normalise LFQ intensities
-#' my_norm <- normalizeCyclicLoess(my_filt)
+#' my_norm <- limma::normalizeCyclicLoess(my_filt)
 #'
 #' # impute missing values
 #' my_imp <- impute_QRILC(my_norm)
@@ -147,7 +150,7 @@
 #'                       values = c("red",
 #'                                  "blue",
 #'                                  "grey")
-#'
+#' @importFrom rlang !!
 #' @export
 plot_volcano <- function(data, p_val, log2fc, group,
                          use_labels = FALSE,

### 2019-05-17 R/process_fungifun.R

@@ -19,6 +19,7 @@
 #' enrichment analysis.
 #'
 #' @examples
+#' \donttest{
 #' # write some gene names to the clipboard
 #' # only works with Windows
 #' my_genes <- c("GSC1", "XOG1", "BGL2", "HYR1", "ALS3",
@@ -29,11 +30,13 @@
 #' # paste into FungiFun2 input
 #' # perform GO analysis and save output as CSV
 #' # import GO enrichment analysis results
-#' GO_result <- process_fungifun("./path/to/file")
+#' GO_result <- process_fungifun("./vignettes/figures/f4_GO_DAY_Y.csv")
+#' }
 #'
 #' @export
 process_fungifun <- function(filename) {
-  df <- read.csv(filename, header = TRUE, sep = "\t", stringsAsFactors = FALSE)
+  df <- utils::read.csv(filename, header = TRUE,
+                        sep = "\t", stringsAsFactors = FALSE)
   df$N.prot.found <- as.numeric(gsub(" /.*", "", df$X..genes...category))
   df$N.prot.cat <- as.numeric(gsub(".* / ", "", df$X..genes...category))
   df$N.prot.input <- as.numeric(gsub(".* / ", "", df$X..genes...input))

### 2019-05-17 R/tukey_hsd.R

@@ -11,6 +11,10 @@
 #' adjusted p-values for the comparison of sample means.
 #'
 #' @examples
+#' \donttest{
+#' # load dplyr
+#' library(dplyr)
+#'
 #' # construct data.frame with nta experiment info
 #' nta_metadata <- data.frame(id = c("ATCC10231_1", "ATCC10231_2",
 #'                                   "ATCC10231_3", "ATCC90028_1",
@@ -62,6 +66,7 @@
 #' # ratio across the strains
 #' nta_total_tukey <- aov(part_per_prot ~ Strain, data = nta_total) %>%
 #'   tukey_hsd()
+#' }
 #'
 #' @export
 tukey_hsd <- function(x, ...) {

### 2019-05-20 R/plot_volcano.R
Add volcano plots to atcc_analysis.Rmd

@@ -51,8 +51,9 @@
 #' title text size, and key text size of the legend. For example
 #' \code{c("right", 11, 8)}.
 #'
-#' @param axis_params mixed vector (length = 2): specifies the colour and text
-#' size of the both axes text. For example \code{c("black", 10)}.
+#' @param axis_params mixed vector (length = 3): specifies axis text colour,
+#' axis title text size, and axis text text size for both axes.
+#' For example \code{c("black", 12, 10)}.
 #'
 #' @return Returns a volcano plot with the \code{log2fc} column data on the
 #' x axis and the \code{p_val} data on the y axis and with the points coloured
@@ -144,7 +145,7 @@
 #'                         x_lim = c(-10, 12),
 #'                         y_lim = c(0, 8),
 #'                         legend_params = c("left", 11, 8),
-#'                         axis_params = c("black", 10)) +
+#'                         axis_params = c("black", 11, 8)) +
 #'   scale_colour_manual(labels = c("EV enriched",
 #'                                  "WCL enriched",
 #'                                  "Not significant"),
@@ -160,7 +161,7 @@ plot_volcano <- function(data, p_val, log2fc, group,
                          point_size = 1, label_size = 2,
                          x_lim = c(-10, 10), y_lim = c(0, 10),
                          legend_params = c("left", 11, 10),
-                         axis_params = c("black", 10)) {
+                         axis_params = c("black", 11, 10)) {
 
   # enquo data columns and label function
   p_val <- rlang::enquo(p_val)
@@ -179,8 +180,9 @@ plot_volcano <- function(data, p_val, log2fc, group,
           legend.title = element_text(size = legend_params[2],
                                       face = "bold"),
           legend.text = element_text(size = legend_params[3]),
+          axis.title = element_text(size = axis_params[2]),
           axis.text = element_text(colour = axis_params[1],
-                                   size = axis_params[2]))
+                                   size = axis_params[3]))
 
   # adjust size of dots in legend and
   # add axis limits and axis labels

### 2019-05-20 R/plot_imputation2.R
Add custom facet labels to some plot functions

@@ -25,6 +25,12 @@
 #' examples section of \code{\link{assert_exd}} or \code{\link{atcc_exp}} for
 #' examples of appropriately structured experimental designs.
 #'
+#' @param facet_labels \code{NULL} or a named vector: if\code{NULL} then
+#' the matrix names will be used for the facet labels (aka. strip text). Use a
+#' named vector to customise the facet labels. For example if you are plotting
+#' the following: \code{plot_imputation2(exp, facet_labels = x, mat1, mat2)}
+#' then \code{x} should be \code{c(mat1 = "Matrix 1", mat2 = "Matrix 2")}.
+#'
 #' @param mat numeric matrix: LFQ intensity data before imputation
 #'
 #' @param ... numeric matrix/matrices: LFQ intensity data after imputation.
@@ -73,14 +79,14 @@
 #'                  my_imp,
 #'                  my_imp2)
 #' @export
-plot_imputation2 <- function(exd, mat, ...) {
+plot_imputation2 <- function(exd, facet_labels = NULL, mat, ...) {
   # Get arguments from call
   call <- match.call()
   arglist <- lapply(call[-1], function(x) x)
   var.names <- vapply(arglist, deparse, character(1))
   arglist <- lapply(arglist, eval.parent, n = 2)
   names(arglist) <- var.names
-  arglist <- arglist[-1]
+  arglist <- arglist[c(-1,-2)]
 
   # Show error if inputs are not the required classes
   assertthat::assert_that(is.data.frame(exd),
@@ -102,9 +108,19 @@ plot_imputation2 <- function(exd, mat, ...) {
 
   # Density plots for different conditions with facet_wrap
   # for original and imputed samles
-  ggplot(df, aes(val, col = condition)) +
-    geom_density(na.rm = TRUE) +
-    facet_wrap(~var, ncol = 1) +
-    labs(x = expression(log[2]~"Intensity"), y = "Density") +
-    theme_bw(base_size = 12)
+  if(is.null(facet_labels)) {
+    ggplot(df, aes(val, col = condition)) +
+      geom_density(na.rm = TRUE) +
+      facet_wrap(~var, ncol = 1) +
+      labs(x = expression(log[2]~"Intensity"), y = "Density") +
+      theme_bw(base_size = 12)
+  } else {
+    ggplot(df, aes(val, col = condition)) +
+      geom_density(na.rm = TRUE) +
+      facet_wrap(~var, ncol = 1,
[…]

### 2019-05-20 R/plot_detect2.R
Change plot base sizes to 16
Also reformat `plot_heatmap` examples

@@ -91,11 +91,11 @@ plot_detect2 <- function(mat) {
     geom_density(na.rm = TRUE) +
     labs(x = expression(log[2]~"LFQ intensity"), y = "Density") +
     guides(col = guide_legend(title = "Missing values")) +
-    theme_bw(base_size = 12)
+    theme_bw(base_size = 16)
   p2 <- ggplot(cumsum, aes(mean, cs_frac, col = missval)) +
     geom_line() +
     labs(x = expression(log[2]~"LFQ intensity"), y = "Cumulative fraction") +
     guides(col = guide_legend(title = "Missing values")) +
-    theme_bw(base_size = 12)
+    theme_bw(base_size = 16)
   gridExtra::grid.arrange(p1, p2, ncol = 1)
 }

### 2019-05-20 R/plot_frequency2.R

@@ -79,7 +79,7 @@ plot_frequency2 <- function(mat, plot = TRUE) {
     labs(title = "Protein quantification frequency",
          x = "Identified in number of samples",
          y = "Number of proteins") +
-    theme_bw(base_size = 12) +
+    theme_bw(base_size = 16) +
     theme(legend.position="none")
   if(plot) {
     return(p)

### 2019-05-20 R/plot_heatmap.R

@@ -136,6 +136,14 @@
 #'   select(-significant) %>%
 #'   as.matrix()
 #'
+#' # define legend parameters
+#' htmp_params <- list(title = "legend title",
+#'                              color_bar = "continuous",
+#'                              direction = "vertical",
+#'                              legend_width = grid::unit(5, "cm"),
+#'                              title_position = "lefttop-rot",
+#'                              at = seq(-10, 10, 2)))
+#'
 #' plot_heatmap(htmp_data,
 #'              plot = TRUE,
 #'              df = FALSE,
@@ -144,12 +152,7 @@
 #'              split_type = "kmeans",
 #'              k = 5,
 #'              legend_pos = "right",
-#'              heatmap_legend_param = list(title = "legend title",
-#'                                          color_bar = "continuous",
-#'                                          direction = "vertical",
-#'                                          legend_width = grid::unit(5, "cm"),
-#'                                          title_position = "lefttop-rot",
-#'                                          at = seq(-10, 10, 2)))
+#'              heatmap_legend_param = htmp_params)
 #'
 #'
 #' ## log2FC type heatmap
@@ -161,6 +164,16 @@
 #'   select(-significant) %>%
 #'   as.matrix()
 #'
+#' # define legend parameters
+#' htmp_params2 <- list(title = expression(bold(log[2]("FC"))),
+#'                      color_bar = "continuous",
+#'                      direction = "vertical",
+#'                      legend_height = grid::unit(5, "cm"),
+#'                      title_position = "lefttop-rot",
+#'                      title_gp = grid::gpar(colour = "black", fontsize = 8),
+#'                      labels_gp = grid::gpar(colour = "black", fontsize = 8),
+#'                      at = seq(-10, 10, 2)))
+#'
 #' plot_heatmap(htmp_data2,
 #'              plot = TRUE,
 #'              df = FALSE,
@@ -170,14 +183,7 @@
 #'              k = 5,
 #'              legend_pos = "right",
 #'              split_order = c(2, 5, 1, 4, 3),
-#'              heatmap_legend_param = list(title = expression(bold(log[2]("FC"))),
-#'              color_bar = "continuous",
-#'              direction = "vertical",
-#'              legend_width = grid::unit(5, "cm"),
-#'              title_position = "lefttop-rot",
-#'              title_gp = grid::gpar(colour = "black", fontsize = 8),
[…]

### 2019-05-20 R/plot_imputation2.R

@@ -113,14 +113,14 @@ plot_imputation2 <- function(exd, facet_labels = NULL, mat, ...) {
       geom_density(na.rm = TRUE) +
       facet_wrap(~var, ncol = 1) +
       labs(x = expression(log[2]~"Intensity"), y = "Density") +
-      theme_bw(base_size = 12)
+      theme_bw(base_size = 16)
   } else {
     ggplot(df, aes(val, col = condition)) +
       geom_density(na.rm = TRUE) +
       facet_wrap(~var, ncol = 1,
                  labeller = labeller(var = facet_labels)) +
       labs(x = expression(log[2]~"Intensity"), y = "Density") +
-      theme_bw(base_size = 12)
+      theme_bw(base_size = 16)
   }
 
 }

### 2019-05-20 R/plot_missval2.R

@@ -74,7 +74,9 @@ plot_missval2 <- function(mat) {
   # Define heatmap legend parameters
   legend_param <- list(at = c(0, 1),
                        labels = c("Missing value",
-                                  "Valid value"))
+                                  "Valid value"),
+                       title_gp = grid::gpar(fontsize = 16),
+                       labels_gp = grid::gpar(fontsize = 14))
 
   # Plot binary heatmap
   ht2 = ComplexHeatmap::Heatmap(missval,

### 2019-05-20 R/plot_normalization2.R

@@ -112,13 +112,13 @@ plot_normalization2 <- function(exd, facet_labels = NULL, mat, ...) {
       coord_flip() +
       facet_wrap(~var, ncol = 1) +
       labs(x = "", y = expression(log[2]~"LFQ intensity")) +
-      theme_bw(base_size = 12)
+      theme_bw(base_size = 16)
   } else {
     ggplot(df, aes(x = ID, y = val, fill = condition)) +
       geom_boxplot(notch = TRUE, na.rm = TRUE) +
       coord_flip() +
       facet_wrap(~var, ncol = 1, labeller = labeller(var = facet_labels)) +
       labs(x = "", y = expression(log[2]~"LFQ intensity")) +
-      theme_bw(base_size = 12)
+      theme_bw(base_size = 16)
   }
 }

### 2019-05-20 R/plot_numbers2.R

@@ -81,7 +81,7 @@ plot_numbers2 <- function(mat, exd, plot = TRUE) {
     geom_hline(yintercept = unique(stat$n)) +
     labs(title = "Proteins per sample", x = "",
          y = "Number of proteins") +
-    theme_bw(base_size = 12)
+    theme_bw(base_size = 16)
   if(plot) {
     return(p)
   } else {

### 2019-05-24 R/plot_imputation2.R
Finalise atcc_analysis.Rmd vignette

@@ -112,14 +112,14 @@ plot_imputation2 <- function(exd, facet_labels = NULL, mat, ...) {
     ggplot(df, aes(val, col = condition)) +
       geom_density(na.rm = TRUE) +
       facet_wrap(~var, ncol = 1) +
-      labs(x = expression(log[2]~"Intensity"), y = "Density") +
+      labs(x = expression(log[2]~"LFQ intensity"), y = "Density") +
       theme_bw(base_size = 16)
   } else {
     ggplot(df, aes(val, col = condition)) +
       geom_density(na.rm = TRUE) +
       facet_wrap(~var, ncol = 1,
                  labeller = labeller(var = facet_labels)) +
-      labs(x = expression(log[2]~"Intensity"), y = "Density") +
+      labs(x = expression(log[2]~"LFQ intensity"), y = "Density") +
       theme_bw(base_size = 16)
   }
 

### 2019-05-28 vignettes/components/protein_funs.R
Wrap manuscript code to 80 characters
Also:
 - Prepare manuscript.Rmd and manuscript supplement.Rmd files to be
   moved out of ./vignettes and into ./manuscript.
 - Cut protein function description vectors out of manuscript.Rmd and
   manuscipt_supplement.Rmd and paste into external R script to be
   referenced using read_chunk().

@@ -1,0 +1,148 @@
+# Function descriptions for Table 1 and Table S2
+
+
+## @knitr fun_list1
+function_desc1 <- c("1,3-beta-glucanosyltransferase",
+                    "Rho family GTPase",
+                    "Multidrug transporter of ABC superfamily",
+                    "Major chitin synthase of yeast and hyphae",
+                    "GPI-anchored cell wall transglycosylase",
+                    "GPI-anchored cell wall protein",
+                    paste0("Predicted P-type ATPase sodium pump",
+                           footnote_marker_alphabet(1)),
+                    "ER oxidoreductin",
+                    paste0("Long-chain fatty acid-CoA ligase",
+                           footnote_marker_alphabet(1)),
+                    "Multicopper feroxidase",
+                    "High-affinity S-adenosylmethionine permease",
+                    "1,3-beta-glucan synthase",
+                    "High-affinity MFS glucose transporter",
+                    "Putative high-affinity MFS glucose transporter",
+                    paste0("Putative mitochondrial phosphate transporter",
+                           footnote_marker_alphabet(1)),
+                    paste0("Glycolipid 2-alpha-mannosyltransferase",
+                           footnote_marker_alphabet(1)),
+                    "Cell surface mannoprotein",
+                    "Mucin family adhesin-like protein",
+                    "Sphingolipid C9-methyltransferase",
+                    paste0("\\textit{S. cerevisiae} ortholog is POM33, transmembrane nucleoporin",
+                           footnote_marker_alphabet(2)),
+                    paste0("\\textit{S. cerevisiae} ortholog is RTN1, reticulon protein",
+                           footnote_marker_alphabet(2)),
+                    paste0("Hexadecenal dehydrogenase",
+                           footnote_marker_alphabet(2)),
+                    paste0("\\textit{S. cerevisiae} ortholog is PUN1, plasma membrane protein",
+                           footnote_marker_alphabet(2)),
+                    "1,3-beta-glucanosyltransferase",
+                    "GPI-anchored cell surface protein of unknown function",
+                    "Putative ion transporter",
+                    "Cell surface glycosidase",
+                    "Glycosidase",
+                    "Phospholipase B",
+                    "Plasma membrane ATPase",
+                    paste0("Mitochondrial outer membrane porin",
+                           footnote_marker_alphabet(1)),
+                    "G-protein of RAC subfamily",
+                    "Rho family GTPase",
+                    "Rho family GTPase",
[…]

### 2019-06-04 R/biofilm.R
Add section 2.1-2.7 in yeast_analysis.Rmd
Also:
 - Fix various typos and formatting errors in biofilm_analysis.Rmd
   and atcc_analysis.Rmd.
 - Fix column name errors in documentation for yeast and biofilm
   data sets.
 - Add information about yeast C3 samples.

@@ -12,13 +12,13 @@
 #' There are 10 samples total in this data set:
 #'
 #' \itemize{
-#' \item DAY286 biofilm EV1, EV2, EV3, EV4, EV5
-#' \item DAY286 biofilm W1, W2, W3, W4, W5
+#' \item DAY286 biofilm bEV3, bEV4, bEV5, bEV6, bEV7
+#' \item DAY286 biofilm bW3, bW4, bW5, bW6, bW7
 #' }
 #'
 #' The EV and WCL biological replicates are paired as they are derived from
-#' the same biofilm, i.e. \code{EV1} EVs were isolated from the culture medium
-#' used to grow the biofilm from cells were lysed to obtain \code{W1} WCL.
+#' the same biofilm, i.e. \code{bEV3} EVs were isolated from the culture medium
+#' used to grow the biofilm from cells were lysed to obtain \code{bW3} WCL.
 #'
 #' See \href{https://doi.org}{Dawson et al. (2019)} for more information about the
 #' generation of this data set. The raw \code{proteinGroups.txt} file and the

### 2019-06-04 R/yeast.R

@@ -7,18 +7,22 @@
 #' It contains label free quantification (LFQ) and intensity-based absolute
 #' quantification (iBAQ) proteomics data for extracellular vesicles (EV) and whole
 #' cell lysates (WCL or W) obtained from the \emph{Candida albicans} strain DAY286
-#' yeast liquid cultures (n = 4).
+#' yeast liquid cultures (n = 3 (C6-C8) and n = 1 (C3)).
 #'
 #' There are 8 samples total in this data set:
 #'
 #' \itemize{
-#' \item DAY286 yeast EV1, EV2, EV3, EV4
-#' \item DAY286 yeast W1, W2, W3, W4
+#' \item DAY286 yeast C3.EV, C6.EV, C7.EV, C8.EV
+#' \item DAY286 yeast C3.WCL, C6.WCL, C7.WCL, C8.WCL
 #' }
 #'
 #' The EV and WCL biological replicates are paired as they are derived from
-#' the same liquid culture, i.e. \code{EV1} EVs were isolated from the culture medium
-#' used to grow the cells which were lysed to obtain \code{W1} WCL.
+#' the same liquid culture, i.e. \code{C7} EVs were isolated from the culture medium
+#' used to grow the cells which were lysed to obtain \code{C7} WCL.
+#'
+#' \strong{NOTE: the EVs used for the C3.EV sample were isolated using a
+#' different protocol to the other samples. Hence the C3.EV and C3.WCL samples
+#' should be removed prior to analysis of the other biological replicates.}
 #'
 #' See \href{https://doi.org}{Dawson et al. (2019)} for more information about the
 #' generation of this data set. The raw \code{proteinGroups.txt} file and the

### 2019-06-05 inst/manuscript/README.Rmd
Move manuscript directory to inst/

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# /vignettes

## description
This directory contains the submitted manuscript (see `manuscript.pdf`) 
for this paper :

> Authors, (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

It also contains a more detailed analysis of the LC-MS/MS data, upon which the manuscript 
is based (see `analysis.md` or `analysis.html`). The 
Rmarkdown (`.Rmd`) files used to generate these documents are provided.

Both the manuscript and the analysis documents *are* included as vignettes in this 
package so they can be easily viewed (or regenerated completely from the raw data) if 
the package is installed. Alternatively, one can download these documents directly 
from this GitHub repository.

## how to access the manuscript

## how to access the analysis

## contents
```
    .
    ├── ...
    ├── /vignettes
    │    ├── /figures            # Contains figures
    │    ├── /components         # Contains required components for knitting manuscript and analysis
    │    ├── analysis.Rmd        # R markdown file to produce analysis.md or analysis.html
    │    ├── analysis.html       # Full analysis upon which the manuscript is based.
    │    ├── analysis.md         # Full analysis upon which the manuscript is based.
    │    ├── manuscript.Rmd      # R markdown file to produce manuscript.pdf or manuscript.docx
    │    ├── manuscript.pdf      # Final submitted manuscript
    │    ├── README.Rmd          # R markdown file to produce README.md
    │    └── README.md           # Description of /vignettes directory
    └── ...

```

### 2019-06-05 inst/manuscript/manuscript.Rmd
Move manuscript directory to inst/

---
title: | 
   **Defining protein markers for *Candida albicans* extracellular vesicles**
author: | 
   *Charlotte Dawson^a^, Mark Bleackley^a^, Donovan Garcia Ceron^a^, 
   Marilyn Anderson^a^*
date: | 
   *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
   Molecular Science, La Trobe University, Victoria, 3086, Australia*
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
    bookdown::word_document2:
      pandoc_args:
        '--lua-filter=components/pagebreak.lua'
      reference_docx: "components/draft_template.docx"
      fig_caption: yes
bibliography: "components/references.bib" 
csl: "components/molecular-and-cellular-proteomics.csl"
link-citations: yes
linkcolor: black
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \usepackage{lipsum}
  - \pagestyle{fancy}
  - \fancyhead[L]{This is the running title it is rather long}
  - \setlength{\headheight}{15pt}
  - \usepackage{float}
  - \let\origfigure\figure
  - \let\endorigfigure\endfigure
  - \renewenvironment{figure}[1][2]{\expandafter\origfigure\expandafter[H]}
    {\endorigfigure}
  - \usepackage{caption}
  - \captionsetup{font={normalsize,stretch=1.3},labelfont=bf}
  - \usepackage{threeparttable}
---

**Running title:** Running title goes here

**Corresponding author:**

\newpage

```{r setup, include=FALSE}
# set knit options
knitr::opts_knit$set(progress = TRUE, 
                     verbose = TRUE)

# set chunk options
knitr::opts_chunk$set(collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      echo = FALSE,
                      comment = "#>")

# load packages
library(candidaev)
library(tidyNano)
library(limma)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(kableExtra)

# set seed for random number generation
set.seed(1)

# reference external R script with protein function lists
knitr::read_chunk('components/protein_funs.R')

# define colour palette to distinguish between strains
# colours = yellow, blue, green, pink
# levels = yeast, ATCC90028, ATCC10231, biofilm
st_pal <- c("#E69F00", "#56B4E9", "#009E73", "#CC79A7")

# define colour palette to distinguish between EVs and whole cell lysate (WCL)
# colours = grey, red, blue
# levels = not significant, EV, WCL
ev_pal <- c("#999999", "#D55E00", "#0072B2")
```

```{r yeast, include=FALSE}
# filter out reverse, contaminant proteins, proteins with <2 unique peptides
# extract LFQ intensity columns and UniProt accessions 
# log2 transform LFQ intensities
yeast_lfq <- yeast %>% 
  filter(Reverse != "+", 
         Potential.contaminant != "+", 
         Unique.peptides >= 2) %>% 
  convert_lfq(., yeast_exp)

# drop EV_1 and WCL_1 samples
yeast_lfq2 <- yeast_lfq[, !colnames(yeast_lfq) %in% c("EV_1", "WCL_1")]

# filter for proteins quantified in min 2/3 reps of EV or WCL
yeast_filt2 <- filter_na2(yeast_lfq2, logic = "or", op = "<=", 
                          pat1 = "EV", val1 = 1, 
                          pat2 = "W", val2 = 1)

# normalise LFQ intensities
yeast_norm2 <- normalizeCyclicLoess(yeast_filt2)

# filter for proteins identified in min 1/3 reps of EV
# define 'EV proteins'
y_ev <- filter_na(yeast_norm2, op = "<=", 
                  pat = "EV", val = 2)

# filter for proteins identified in min 1/3 reps of WCL
# define 'WCL proteins'
y_wcl <- filter_na(yeast_norm2, op = "<=", 
                   pat = "W", val = 2)

# can't impute with so many missing values
# separate EV/WCL exclusive proteins (don't impute) from 
# EV/WCL common proteins (impute)
yeast_excl <- filter_na2(yeast_norm2, logic = "or", op = "==", 
                         pat1 = "EV", val1 = 3, 
                         pat2 = "W", val2 = 3)

yeast_both <- filter_na2(yeast_norm2, logic = "and", op = "<=", 
                         pat1 = "EV", val1 = 2, 
                         pat2 = "W", val2 = 2)

# proteins with missing values tend to have lower intensity
# therefore proteins are MNAR, close to detection limit
# use left censored imputation method
yeast_imp <- impute_QRILC(yeast_both)

# recombine imputed proteins and non-imputed proteins in matrix
yeast_de <- rbind(yeast_excl, yeast_imp)

# see limma user guide section 9.2 for more info about DE
# create design matrix
y_samp <- data.frame(T = rep(c("EV", "WCL"), each = 3))

y_design <- stats::model.matrix(~ 0 + T, data = y_samp)
colnames(y_design) <- c("EV", "WCL")

# define sample comparisons of interest
y_contrasts <- c("EV - WCL")

# make all pair-wise comparisons between EV and WCL
# and perform limma::eBayes()
y_efit <- limma_eBayes(yeast_de, design = y_design, contrasts = y_contrasts)

# extract DE results
yeast_res <- get_results(efit = y_efit, 
                         mat = yeast_de, 
                         p_val = 0.01, 
                         lfc = 0, 
                         type = "individual")[[1]]
```

```{r biofilm, include=FALSE}
# filter out reverse, contaminant proteins, proteins with <2 unique peptides
# extract LFQ intensity columns and UniProt accessions 
# log2 transform LFQ intensities
biofilm_lfq <- biofilm %>% 
  filter(Reverse != "+", 
         Potential.contaminant != "+", 
         Unique.peptides >= 2) %>% 
  convert_lfq(., biofilm_exp)

# filter for proteins quantified in min 4/5 reps of EV or WCL
biofilm_filt <- filter_na2(biofilm_lfq, logic = "or", op = "<=", 
                           pat1 = "EV", val1 = 1, 
                           pat2 = "W", val2 = 1)

# normalise LFQ intensities
biofilm_norm <- normalizeCyclicLoess(biofilm_filt)

# filter for proteins identified in min 1/5 reps of EV
# define 'EV proteins'
b_ev <- filter_na(biofilm_norm, op = "<=", 
                  pat = "EV", val = 4)

# filter for proteins identified in min 1/5 reps of WCL
# define 'WCL proteins'
b_wcl <- filter_na(biofilm_norm, op = "<=", 
                   pat = "W", val = 4)

# can't impute with so many missing values
# filter for proteins with 4-5 NA values in EV or WCL (don't impute)
biofilm_excl <- filter_na2(biofilm_norm, logic = "or", op = ">=", 
                         pat1 = "EV", val1 = 4, 
                         pat2 = "W", val2 = 4)

# filter for proteins with min 3 valid values in EV and WCL (impute)
biofilm_both <- filter_na2(biofilm_norm, logic = "and", op = "<=", 
                         pat1 = "EV", val1 = 3, 
                         pat2 = "W", val2 = 3)

# proteins with missing values tend to have lower intensity
# therefore proteins are MNAR, close to detection limit
# use left censored imputation method
biofilm_imp <- impute_QRILC(biofilm_both)

# recombine imputed proteins and non-imputed proteins in matrix
biofilm_de <- rbind(biofilm_excl, biofilm_imp)

# see limma user guide section 9.2 for more info about DE
# create design matrix
b_samp <- data.frame(T = rep(c("EV", "WCL"), each = 5))

b_design <- stats::model.matrix(~ 0 + T, data = b_samp)
colnames(b_design) <- c("EV", "WCL")

# define sample comparisons of interest
b_contrasts <- c("EV - WCL")

# make all pair-wise comparisons between EV and WCL
# and perform limma::eBayes()
b_efit <- limma_eBayes(biofilm_de, design = b_design, contrasts = b_contrasts)

# extract DE results
biofilm_res <- get_results(efit = b_efit, 
                           mat = biofilm_de, 
                           p_val = 0.01, 
                           lfc = 0, 
                           type = "individual")[[1]]
```

```{r atcc, include=FALSE}
# filter out reverse, contaminant proteins, proteins with <2 unique peptides
# extract LFQ intensity columns and UniProt accessions 
# log2 transform LFQ intensities
atcc_lfq <- atcc %>% 
  filter(Reverse != "+", 
         Potential.contaminant != "+", 
         Unique.peptides >= 2) %>% 
  convert_lfq(., atcc_exp)

# filter for proteins quantified in min 2/3 reps of: 
# A1 EV or A1 WCL or A9 EV or A9 WCL
atcc_filt <- filter_na4(atcc_lfq, "or", "<=", 
                        pat1 = "A10231_EV", 1, 
                        pat2 = "A10231_W", 1, 
                        pat3 = "A90028_EV", 1, 
                        pat4 = "A90028_W", 1)

# normalise LFQ intensities
atcc_norm <- normalizeCyclicLoess(atcc_filt)

# filter for proteins identified in min 1/3 reps of 10231 EV
# define 'ATCC10231 EV proteins'
atcc1_ev <- filter_na(atcc_norm, op = "<=", 
                      pat = "A10231_EV", val = 2)

# filter for proteins identified in min 1/3 reps of 10231 WCL
# define 'ATCC10231 WCL proteins'
atcc1_w <- filter_na(atcc_norm, op = "<=", 
                     pat = "A10231_W", val = 2)

# filter for proteins identified in min 1/3 reps of 90028 EV
# define 'ATCC90028 EV proteins'
atcc9_ev <- filter_na(atcc_norm, op = "<=", 
                      pat = "A90028_EV", val = 2)

# filter for proteins identified in min 1/3 reps of 90028 WCL
# define 'ATCC90028 WCL proteins'
atcc9_w <- filter_na(atcc_norm, op = "<=", 
                      pat = "A90028_W", val = 2)

# can't impute with so many missing values
# filter for exclusive to 10231 EV or WCL or 90028 EV or WCL (don't impute)
atcc_excl <- filter_na4(atcc_norm, logic = "or", op = "==", 
                        pat1 = "A10231_EV", val1 = 3, 
                        pat2 = "A10231_W", val2 = 3, 
                        pat3 = "A90028_EV", val3 = 3, 
                        pat4 = "A90028_W", val4 = 3)

# filter for proteins with min 1 valid value in all 4 sample types (impute)
atcc_both <- filter_na4(atcc_norm, logic = "and", op = "<=", 
                        pat1 = "A10231_EV", val1 = 2, 
                        pat2 = "A10231_W", val2 = 2, 
                        pat3 = "A90028_EV", val3 = 2, 
                        pat4 = "A90028_W", val4 = 2)

# proteins with missing values tend to have lower intensity
# therefore proteins are MNAR, close to detection limit
# use left censored imputation method
atcc_imp <- impute_QRILC(atcc_both)

# recombine imputed proteins and non-imputed proteins in matrix
atcc_de <- rbind(atcc_excl, atcc_imp)
colnames(atcc_de) <- stringi::stri_replace_all_regex(colnames(atcc_de), 
                                                     c("A10231_", "A90028_"), 
                                                     c("A1_", "A9_"), 
                                                     vectorize_all = FALSE)

# see limma user guide section 9.2 for more info about DE
# create design matrix
atcc_samp <- data.frame(T = rep(c("A1_EV", "A1_WCL", 
                                  "A9_EV", "A9_WCL"), each = 3))

atcc_design <- stats::model.matrix(~ 0 + T, data = atcc_samp)
colnames(atcc_design) <- c("A1_EV", "A1_W", "A9_EV", "A9_W")

# define sample comparisons of interest
atcc_contrasts <- c("A1_EV - A1_W", "A9_EV - A9_W")

# make all pair-wise comparisons for specified contrasts
# and perform limma::eBayes()
atcc_efit <- limma_eBayes(atcc_de, atcc_design, atcc_contrasts)

# extract overall results
atcc_overall <- get_results(efit = atcc_efit, mat = atcc_de, 
                            p_val = 0.01, lfc = 0, type = "overall")

# extract results for ATCC strains
a1_res <- get_results(efit = atcc_efit, 
                      mat = atcc_de, 
                      p_val = 0.01, 
                      lfc = 0, 
                      type = "individual")[[1]]

a9_res <- get_results(efit = atcc_efit, 
                      mat = atcc_de, 
                      p_val = 0.01, 
                      lfc = 0, 
                      type = "individual")[[2]]
```

# Abbreviations

EV - extracellular vesicle

\newpage

# Abstract

The abstract goes here. Here is a citation [@liao2012].

Here is another citation [@gil-bona2015].

And another [@lin2014].

\newpage

# Introduction

Here is a citation [@marwick2017].

# Experimental procedures

## Subsection 1

## Subsection 2

# Results

# Discussion

# Acknowledgements

# Data availability

# Acknowledgements

\newpage
# References 
<div id="refs"></div>

\newpage

# Tables

```{r table1Data, include=FALSE}
# make list of EV sig. enriched and exclusive proteins for each strain
marker_comp <- list("DAY Y" = yeast_res %>% 
                      filter(group == "EV up" | group == "EV ex") %>% 
                      pull(CGD_gene_name), 
                    "DAY B" = biofilm_res %>% 
                      filter(group == "EV up" | group == "EV ex") %>% 
                      pull(CGD_gene_name), 
                    "ATCC90028" = a9_res %>% 
                      filter(group == "A9_EV up" | group == "A9_EV ex") %>% 
                      pull(CGD_gene_name), 
                    "ATCC10231" = a1_res %>% 
                      filter(group == "A1_EV up" | group == "A1_EV ex") %>% 
                      pull(CGD_gene_name))

# get venn segments
marker_comp_tab <- plot_venn(vlist = marker_comp, 
                             use_uniprot = FALSE, 
                             type = "df")

# extract protein names from venn overlap
marker_candidates <- marker_comp_tab %>% 
  filter(apply(.[, 1:4], 1, sum) == 4) %>% 
  pull(..values..) %>% 
  unlist() %>% 
  as.data.frame(stringsAsFactors = FALSE) %>% 
  rename(Name = 1)

# construct table 1
marker_longlist <- marker_candidates %>% 
  mutate(Function = match_id(Name, uniprot, "CGD_gene_name", "Protein_name"),
         DAY.Y = match_id(Name, yeast_res, "CGD_gene_name", "logFC", 
                          str_split = FALSE), 
         A9 = match_id(Name, a9_res, "CGD_gene_name", "logFC", 
                       str_split = FALSE), 
         A1 = match_id(Name, a1_res, "CGD_gene_name", "logFC", 
                       str_split = FALSE), 
         DAY.B = match_id(Name, biofilm_res, "CGD_gene_name", "logFC", 
                          str_split = FALSE), 
         TM = match_id(Name, uniprot, "CGD_gene_name", "Transmembrane"), 
         SP = match_id(Name, uniprot, "CGD_gene_name", "Signal_peptide")) %>% 
  mutate_at(.vars = vars(DAY.Y, DAY.B, A1, A9), 
            .funs = list(~ sprintf(as.numeric(.), fmt = "%#.2f"))) %>% 
  mutate_at(.vars = vars(DAY.Y, DAY.B, A1, A9), 
            .funs = list(~ case_when(. == "NA" ~ "ex", 
                                     TRUE ~ as.character(.)))) %>% 
  mutate(TM = stringr::str_count(TM, "Helical"), 
         SP = case_when(grepl("SIGNAL", SP) ~ "Y", 
                        TRUE ~ ""), 
         TM = case_when(TM == 0 ~ "", 
                        TRUE ~ as.character(TM))) %>% 
  rename("DAY Y" = DAY.Y, "DAY B" = DAY.B) %>% 
  arrange(Name)

# load vector of protein functions from external R script
<<fun_list1>>

# add proper protein functions to table 1
# also add vesicle depleted supernatant info and 
# group proteins according to localisation
marker_longlist <- marker_longlist %>% 
  mutate(Function = function_desc1, 
         VDM = c("Y", rep("",3), rep("Y", 2), "", "Y", rep("", 8), rep("Y", 2), 
                 rep("", 4), rep("Y", 3), rep("", 2), rep("Y", 2), rep("", 5), 
                 "Y", rep("", 7), "Y"), 
         pack_row = c(5, rep(1,3), rep(5,2), 1, 2, rep(1,3), rep(1,3), 4, 2, 
                      rep(5,2), 1, rep(2,2), 4, 1, rep(5,2), 1, rep(5,3), 1, 
                      4, rep(1,3), 5, 1, 1, 3, 1, 3, 2, 3, 5)) %>% 
  arrange(pack_row)

# fix number of TM domains for CDR1;CDR2
marker_longlist[2, 7] <- "12;12"

# UniProt says SUR7 has 3 TM domains and a signal peptide
# much of literature says SUR7 has 4 TM domains
# TOPCONS2 predicts SUR7 has 4 TM domains and no signal peptide
# fix SUR7 entries
marker_longlist[19, 7] <- "4"
marker_longlist[19, 8] <- ""
```

<!-- assign markdown references for table caption -->
(ref:table1) [@gil-bona2015]
(ref:footnote1) [@skrzypek2017]
(ref:footnote2) [@almagroarmenteros2017]
(ref:footnote3) [@tsirigos2015]

```{r table1}
tab1_cap <- "\\textbf{Candidate positive protein markers for 
             \\textit{C. albicans} EVs.} This list of proteins consists of 
             those that were found to be exclusive to EVs or significantly 
             enriched in EVs across the four \\textit{C. albicans} strains 
             examined in this study. Proteins are grouped according to their 
             subcellular localisation as annotated in the Candida Genome 
             Database (candidagenome.org) (ref:footnote1). 
             The log\\textsubscript{2} ratio of the abundance (mean MaxQuant 
             LFQ intensity) of each protein in EVs compared to whole cell 
             lysate (WCL) for each strain is listed. \`\`ex\" indicates where 
             a protein was only quantified in the EV fraction and not the WCL 
             for that strain. The \`\`TM\" column indicates the number of 
             transmembrane domains for each protein as annotated in UniProtKB. 
             \`\`SP\" indicates whether a protein is annotated as having a 
             signal peptide according to UniProtKB. \`\`VDM\" shows whether a 
             protein has previously been detected in vesicle-depleted culture 
             media (i.e. the proteins may also be in the soluble secretome) 
             (ref:table1). Underlined proteins are those identified as the 
             best candidates for positive EV markers according to the 
             criteria depicted in Figure \\ref{fig:figure1}."

# draw table 1
knitr::kable(marker_longlist[ ,-10],
             caption = tab1_cap, 
             format = "latex", 
             booktabs = TRUE, 
             longtable = TRUE, 
             linesep = "", 
             escape = FALSE)  %>% 
  row_spec(row = c(1, 5, 6, 11, 12, 15:20, 22:27, 39), underline = TRUE) %>% 
  add_header_above(c(" " = 2, 
                     "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
                     " " = 2), escape = FALSE) %>% 
  kable_styling(font_size = 8) %>% 
  pack_rows("Plasma membrane", 1, 20) %>% 
  pack_rows("Golgi, ER, secretory pathway", 21, 25) %>% 
  pack_rows("Vacuole", 26, 28) %>% 
  pack_rows("Mitochondria", 29, 31) %>% 
  pack_rows("Cell wall, cell surface", 32, 43) %>% 
  footnote(alphabet = c("Protein localisation was inferred from sequence 
                         similarity with \\\\textit{S. cerevisiae} ortholog as 
                         annotated in the Candida Genome Database 
                        (ref:footnote1)", 
                        "Protein localisation was predicted using DeepLoc-1.0 
                        (ref:footnote2)", 
                        "Presence of transmembrane domains and absense of a 
                        signal peptide was predicted using TOPCONS2 
                        (ref:footnote3)"), 
           escape = FALSE, 
           threeparttable = TRUE)
```

\newpage

# Figures

```{r figure1, fig.cap=f1_cap, fig.width=5.45, fig.height=6}
# construct figure 1
f1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
           proteomic analysis of \\textit{C. albicans} EVs and the selection 
           of EV protein markers.} Steps 1 to 6 were performed for each of the 
           four strains examined in this study: DAY286 yeast, ATCC90028 yeast, 
           ATCC10231 yeast, and DAY286 biofilm. The results from the four 
           seperate analyses were combined (step 7) to identify proteins which 
           commonly appeared as EV marker candidates. The MISEV2018 criteria 
           for protein content-based EV characterisation and other 
           considerations were used to select the best \\textit{C. albicans} 
           EV marker proteins."

f1 <- png::readPNG("figures/figure1.png")

# draw figure 1
ggplot() + 
  background_image(f1)
```

\newpage

```{r figure2Data, include=FALSE}
# construct data.frame with nta experiment info
nta_metadata <- data.frame(id = c("ATCC10231_1", "ATCC10231_2", "ATCC10231_3", 
                                  "ATCC90028_1", "ATCC90028_2", "ATCC90028_3", 
                                  "Biofilm_1", "Biofilm_2", "Biofilm_3", 
                                  "Biofilm_4", "Biofilm_5", 
                                  "DAY286_1", "DAY286_2", "DAY286_3"), 
                           protein_conc = c(0.192, 0.282, 0.287, 
                                            0.424, 0.716, 0.584, 
                                            0.204, 0.198, 0.297, 0.193, 0.416, 
                                            0.437, 0.360, 0.447), 
                           stringsAsFactors = FALSE)

# average the nta technical replicate data
nta_techavg <- nta %>% 
  nanolyze(particle_size, Strain, Bio_rep, Dilution, 
           name = "Tech_rep", 
           param_var = True_count)

# average the nta biological replicate data
nta_bioavg <- nta_techavg %>% 
  nanolyze(particle_size, Strain,
           name = "Bio_rep", 
           param_var = Tech_rep_mean) %>% 
  mutate(facet = case_when(Strain == "Biofilm" ~ "second", TRUE ~ "first"))

# determine the total particle concentration for each biological replicate
nta_total <- nta_techavg %>% 
  nanocount(Strain, Bio_rep, Dilution, 
            param_var = Tech_rep_mean) %>% 
  tidyr::unite("id", Strain, Bio_rep) %>% 
  mutate(protein_conc = as.numeric(match_id(id, nta_metadata, 
                                            "id", "protein_conc")), 
         od = match_id(id, nta_metadata, "id", "OD600"), 
         part_per_prot = Particle_count / protein_conc / 1000) %>% 
  tidyr::separate(col = id, into = c("Strain", "Bio_rep"), sep = "_", 
                  remove = TRUE)

# use ANOVA with Tukey HSD to compare mean particle per ug protein 
# ratio across the strains
nta_total_tukey <- aov(part_per_prot ~ Strain, data = nta_total) %>% 
  tukey_hsd()
```

```{r figure2plots, include=FALSE}
# construct figure 2a
f2a_img <- png::readPNG("figures/figure2a.png")

f2a <- ggplot() + 
  background_image(f2a_img) + 
  theme(plot.margin = margin(t = 0.3, l = 0, r = 0, b = 0, unit = "inches"))

# construct figure 2b
f2b <- nta_bioavg %>% 
  ggplot(aes(x = particle_size, y = Bio_rep_mean, colour = Strain)) + 
  scale_colour_manual(values = st_pal[c(3, 2, 4, 1)], 
                      breaks = c("DAY286", "ATCC90028", 
                                 "ATCC10231", "Biofilm"), 
                      labels = c("DAY286 Y", "ATCC90028", 
                                 "ATCC10231", "DAY286 B")) + 
  geom_vline(xintercept = 100, colour = "#999999", linetype = "dashed") +
  geom_line(size = 0.5) + 
  facet_wrap(~ facet, scales = "free", ncol = 2, nrow = 1) + 
  theme_classic() + 
  theme(strip.background = element_blank(), 
        strip.text = element_blank(), 
        legend.position = c(0.88, 0.6), 
        legend.title = element_blank(), 
        plot.margin = margin(t = 0.2, l = 0, r = 0.2, b = 0, unit = "inches"), 
        axis.text.x = element_text(colour = "black")) + 
  xlab(label = "Particle size (nm)") + 
  ylab(label = "Particles / mL")

# construct figure 2c
nta_total$Strain <- factor(nta_total$Strain, 
                           levels = c("DAY286", "ATCC90028", 
                                      "ATCC10231", "Biofilm"))

f2c <- nta_total %>% 
  ggboxplot(x = "Strain", y = "part_per_prot", 
            color = "Strain", palette = st_pal, add = "jitter", 
            add.params = list(color = "black"), 
            shape = 15,
            ylab = expression("Particles /"~paste(mu,g)~"protein"))
f2c <- ggpar(f2c, 
             yscale = "log10", 
             format.scale = TRUE, 
             ylim = c(8e8, 8e10),
             font.y = 10, 
             legend = "none") + 
  stat_pvalue_manual(nta_total_tukey[c(2,4,6), ], label = "p.adj", 
                     y.position = c(10.45, 10.65, 10.85), 
                     tip.length = 1e-2, 
                     label.size = 3) + 
  theme(axis.title.x = element_blank(), 
        plot.margin = margin(t = 0.2, l = 0.2, r = 0, b = 0.15, 
                             unit = "inches")) + 
  scale_x_discrete(labels = c("ATCC90028" = "A9", 
                              "ATCC10231" = "A1", 
                              "Biofilm" = "B", 
                              "DAY286" = "Y"))
```

```{r figure2, fig.cap=f2_cap, fig.width=7.1, fig.height=4}
# draw figure 2
ggarrange(f2a, 
          ggarrange(f2b, f2c, 
                    labels = c("B", "C"), 
                    ncol = 2,
                    nrow = 1, 
                    widths = c(1.8,1)), 
          labels = c("A", ""), 
          nrow = 2, 
          ncol = 1, 
          heights = c(1,1))

f2_cap <- "\\textbf{Characterisation and quantification of EVs from different 
           \\textit{C. albicans} strains.} \\textit{(A)} Representative TEM 
           images of EVs isolated from 4 different \\textit{C. albicans} 
           strains. Scale bar indicates 0.5 $\\mu$m. \\textit{(B)} Size 
           distribution of DAY286 yeast (n = 3), ATCC90028 yeast (n = 3), 
           ATCC10231 yeast (n = 3), and DAY286 biofilm (n = 5) EVs as measured 
           by nanoparticle tracking analysis. Line plots shown are the average 
           of the biological replicates and the dashed grey line indicates 100 
           nm. Plots for the individual biological replicates are presented in 
           supplemental Figure S1. \\textit{(C)} Comparison of the ratio of 
           particle concentration to protein concentration of the EV fraction, 
           (particles/mL) $\\div$ ($\\mu$g protein/mL), across the four EV 
           sources. Each dot represents one biological replicate. Sample means 
           were compared using ANOVA followed by Tukey's HSD \\textit{post-hoc} 
           test. P-values indicating significant differences are shown. The 
           particle and protein concentrations for each biological replicate 
           are provided in supplemental Table S1."
```

\newpage

```{r figure3Yeast, include=FALSE}
# compare DAY286 yeast EV WCL proteins
f3a1 <- plot_venn(list("EV" = y_ev, "WCL" = y_wcl), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans", 
                  cex = 0.8,
                  cat.fontfamily = "sans", 
                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
                  margin = 0.05)

# DAY286 yeast venn
f3a1 <- as_ggplot(f3a1) + 
  theme(plot.margin = unit(c(1,0.5,1,0.5), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, 
           label = "bold('DAY286 yeast')", parse = TRUE)

# generate volcano plot
f3b1 <- plot_volcano(data = yeast_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched", 
                                 "WCL enriched", 
                                 "Not significant"), 
                      values = unname(ev_pal[c(2,1,3)]), 
                      breaks = c("EV up", "WCL up", "not sig"), 
                      name = element_blank()) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 Y')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('88')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('88')", parse = TRUE, 
           colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('318')", parse = TRUE, 
           colour = unname(ev_pal[1]))
```

```{r figure3A9, include=FALSE}
# compare ATCC90028 EV WCL proteins
f3a2 <- plot_venn(list("EV" = atcc9_ev, "WCL" = atcc9_w), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans",
                  cex = 0.8,
                  cat.fontfamily = "sans", 
                  cat.just = list(c(0.5,1.7), c(0.5,1.55)), 
                  ext.percent = c(30,10,0),
                  ext.pos = c(45,315),
                  ext.dist = -0.05,
                  ext.length = 0.5,
                  margin = 0.05)

# ATCC90028 venn
f3a2 <- as_ggplot(f3a2) + 
  theme(plot.margin = unit(c(1,0,1,0.5), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, label = "bold('ATCC90028')", parse = TRUE)

# generate volcano plot
f3b2 <- plot_volcano(data = a9_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (99)", "WCL enriched (130)", 
                                 "Not significant (744)"),
                      values = unname(ev_pal[c(2,3,1)])) + 
  annotate("text", x = 8, y = 0.5, label = "bold('ATCC90028')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('99')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('130')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('744')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure3A1, include=FALSE}
# compare ATCC10231 EV WCL proteins
f3a3 <- plot_venn(list("EV" = atcc1_ev, "WCL" = atcc1_w), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans", 
                  cex = 0.8,
                  cat.fontfamily = "sans",
                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
                  ext.percent = c(0,20,0),
                  ext.pos = 45,
                  ext.dist = -0.05,
                  ext.length = 0.5,
                  margin = 0.05)

# ATCC10231 venn
f3a3 <- as_ggplot(f3a3) + 
  theme(plot.margin = unit(c(1,0.5,1,0.5), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, label = "bold('ATCC10231')", parse = TRUE)

# generate volcano plot
f3b3 <- plot_volcano(data = a1_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (108)", "WCL enriched (142)", 
                                 "Not significant (435)"),
                      values = unname(ev_pal[c(2,3,1)])) + 
  annotate("text", x = 8, y = 0.5, label = "bold('ATCC10231')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('106')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('134')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('445')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure3Biofilm, include=FALSE}
# compare DAY286 biofilm EV WCL proteins
f3a4 <- plot_venn(list("EV" = b_ev, "WCL" = b_wcl), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans", 
                  cex = 0.8, 
                  cat.fontfamily = "sans", 
                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
                  ext.text = TRUE,
                  ext.percent = c(20,10,0),
                  ext.pos = c(45,315),
                  ext.dist = -0.1,
                  ext.length = 0.5,
                  margin = 0.05)
# DAY286 biofilm venn
f3a4 <- as_ggplot(f3a4) + 
  theme(plot.margin = unit(c(1,0,1,0), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, label = "bold('DAY286 biofilm')", 
           parse = TRUE)

# generate volcano plot
f3b4 <- plot_volcano(data = biofilm_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (95)", "WCL enriched (79)", 
                                 "Not significant (484)"), 
                      values = unname(ev_pal[c(2,1,3)]), 
                      breaks = c("EV up", "WCL up", "not sig")) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 B')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('95')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('79')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('484')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure3, fig.cap=f3_cap, fig.width=7.1, fig.height=6}
# draw figure 3
ggarrange(ggarrange(f3a1, f3a2, f3a3, f3a4, 
                    labels = c("A", "", "", ""), 
                    ncol = 4, 
                    nrow = 1, 
                    align = "v"), 
          ggarrange(f3b1, f3b2,
                    f3b3, f3b4, 
                    labels = c("B", rep("", 3)), 
                    ncol = 2, 
                    nrow = 2, 
                    align = "hv", 
                    common.legend = TRUE, 
                    legend = "right", 
                    widths = c(1,1), 
                    vjust = 1), 
          ncol = 1,
          nrow = 2, 
          heights = c(1,2))

f3_cap <- "\\textbf{Differential abundance analysis of proteins identified in 
           \\textit{C. albicans} EVs and whole cell lysates (WCL).} 
           \\textit{(A)} Venn diagrams comparing the EV and WCL proteomes from 
           four \\textit{C. albicans} strains; DAY286 yeast (n = 3), ATCC90028 
           yeast (n = 3), ATCC10231 yeast (n = 3), and DAY286 biofilm (n = 5). 
           Whole cell lysates were prepared from the EV source cells. Proteins 
           were quantified (MaxQuant LFQ intensity) in minimum 2/3 (yeast) and 
           4/5 (biofilm) biological replicates of EV or WCL. \\textit{(B)} 
           Volcano plots depicting significantly enriched EV or WCL proteins. 
           Differential abundance analysis was performed by comparing the mean 
           normalised LFQ intensities of proteins identified in both EV and 
           WCL (i.e. proteins in the venn overlap) using the Bioconductor 
           package \\textit{limma} [@cox2014; @ritchie2015]. Significantly 
           enriched proteins were identified using a Benjamini-Hochberg 
           adjusted p-value cut off of 0.01. Counts of significant and 
           non-significant proteins are indicated on each graph. Proteins with 
           a log\\textsubscript{2}(FC) greater than 8 are labelled. Data tables 
           underlying the venn diagrams and volcano plots are provided in 
           supplemental File S2."
```

\newpage

```{r figure4Data, include=FALSE}
# get list of DAY286 yeast EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f4_y_go <- marker_comp[1] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  gsub("CHS3", "CaO19.4937", .) %>% 
  gsub("PEP1", "CaO19.3767", .)

# get list of DAY286 biofilm EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f4_b_go <- marker_comp[2] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  stringi::stri_replace_all_regex(., 
                                  c("CHS3", "PEP1", "ALS3", 
                                    "PLB3", "PLB4.5"), 
                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
                                    "CaO19.6594", "CaO19.9017"), 
                                  vectorize_all = FALSE)

# get list of ATCC90028 EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f4_a9_go <- marker_comp[3] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  stringi::stri_replace_all_regex(., 
                                  c("CHS3", "PEP1", "ALS3", 
                                    "PLB3", "PLB4.5", "^MNN2$", 
                                    "MNN22", "MNN24", "ECM331", 
                                    "CAM1-1", "FCY21"), 
                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
                                    "CaO19.6594", "CaO19.9017", "CaO19.2347", 
                                    "CaO19.3803", "CaO19.1995", "CaO19.4255", 
                                    "CaO19.2651", "CaO19.8937"), 
                                  vectorize_all = FALSE)
f4_a9_go <- f4_a9_go[!f4_a9_go %in% c("orf19.7397.1", "orf19.7398")]

# get list of ATCC10231 EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f4_a1_go <- marker_comp[4] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  stringi::stri_replace_all_regex(., 
                                  c("CHS3", "PEP1", "ALS3", 
                                    "PLB3", "PLB4.5", "^MNN2$", 
                                    "MNN22", "MNN24", "ECM331", 
                                    "CAM1-1"), 
                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
                                    "CaO19.6594", "CaO19.9017", "CaO19.2347", 
                                    "CaO19.3803", "CaO19.1995", "CaO19.4255", 
                                    "CaO19.2651"), 
                                  vectorize_all = FALSE)
```

```{r figure4Plots, include=FALSE}
# import FungiFun2 GO enrichment results
f4_y_go_table <- process_fungifun("figures/f4_GO_DAY_Y.csv")
f4_b_go_table <- process_fungifun("figures/f4_GO_DAY_B.csv")
f4_a1_go_table <- process_fungifun("figures/f4_GO_ATCC10231.csv")
f4_a9_go_table <- process_fungifun("figures/f4_GO_ATCC90028.csv")

# define the colour palette
f4_pal <- c("#6D2077", "#E4002B", "#FFB81C")

# GO term bar plots
f4_y <- plot_go_bar(f4_y_go_table, c(1:4, 49,52:53,55, 77,79:81), f4_pal) + 
  annotate("text", x = 12, y = 65, label = "bold('DAY286 Y')", parse = TRUE) + 
  labs(fill = "GO domain") + 
  theme(legend.text = element_text(size = 10), 
        legend.title = element_text(size = 10))

f4_b <- plot_go_bar(f4_b_go_table, c(1:4, 69,71:73, 96:97, 100, 102), f4_pal) + 
  annotate("text", x = 12, y = 60, label = "bold('DAY286 B')", parse = TRUE)

f4_a9 <- plot_go_bar(f4_a9_go_table, c(1:4, 35,37:38,42, 55:56,58:59), f4_pal) + 
  annotate("text", x = 12, y = 70, label = "bold('ATCC90028')", parse = TRUE)

f4_a1 <- plot_go_bar(f4_a1_go_table, c(1:4, 63,65:67, 88:91), f4_pal) + 
  annotate("text", x = 12, y = 70, label = "bold('ATCC10231')", parse = TRUE)
```

```{r figure4, fig.cap=f4_cap, fig.width=7.2, fig.height=5}
# draw figure 4
ggarrange(f4_y, f4_a9, 
          f4_a1, f4_b, 
          labels = NULL, 
          ncol = 2, 
          nrow = 2, 
          common.legend = TRUE, 
          legend = "bottom", 
          align = "hv")

f4_cap <- "\\textbf{Functional enrichment analyses of the significantly 
           enriched and exclusive \\textit{C. albicans} EV proteins.} The 
           online tool FungiFun2 (elbe.hki-jena.de/fungifun) was used to 
           identify enriched biological process (BP), cellular component (CC), 
           and molecular function (MF) GO terms [@priebe2015]. A selection of 
           the most significantly enriched terms for each GO domain are shown. 
           They are presented top to bottom in order of increasing 
           Benjamini-Hochberg adjusted p-value. Full lists of enriched GO 
           terms can be found in supplemental File S3."
```

\newpage

```{r figure5Data, include=FALSE}
# figure 5a EV venn
f5a_comp <- list("DAY Y" = rownames(y_ev), 
                 "DAY B" = rownames(b_ev),
                 "ATCC90028" = rownames(atcc9_ev), 
                 "ATCC10231" = rownames(atcc1_ev))
f5a_comp <- lapply(f5a_comp, function(x) match_id(x, ref = uniprot, 
                                                  match = "UP_accession", 
                                                  new = "CGD_gene_name"))

f5a_venn <- plot_venn(vlist = f5a_comp, use_uniprot = FALSE, type = "plot", 
                      fontfamily = "sans", 
                      cat.fontfamily = "sans", 
                      cex = 1, 
                      cat.cex = 0.8, 
                      fill = st_pal[c(1,4,2,3)], 
                      alpha = c(0.3, 0.3, 0.3, 0.3))

f5a <- as_ggplot(f5a_venn) + 
  theme(plot.margin = unit(c(0,2,0,2), "lines"))

f5a_overlap <- plot_venn(vlist = f5a_comp, 
                         use_uniprot = FALSE, type = "df") %>% 
  filter(..count.. == 403) %>% 
  pull(..values..) %>% 
  unlist()

# figure 5b WCL venn
f5b_comp <- list("DAY Y" = rownames(y_wcl), 
                 "DAY B" = rownames(b_wcl),
                 "ATCC90028" = rownames(atcc9_w), 
                 "ATCC10231" = rownames(atcc1_w))
f5b_comp <- lapply(f5b_comp, function(x) match_id(x, ref = uniprot, 
                                                  match = "UP_accession", 
                                                  new = "CGD_gene_name"))

f5b_venn <- plot_venn(vlist = f5b_comp, use_uniprot = FALSE, type = "plot", 
                      fontfamily = "sans", 
                      cat.fontfamily = "sans", 
                      cex = 1, 
                      cat.cex = 0.8, 
                      fill = st_pal[c(1,4,2,3)], 
                      alpha = c(0.3, 0.3, 0.3, 0.3))

f5b <- as_ggplot(f5b_venn) + 
  theme(plot.margin = unit(c(0,2,0,2), "lines"))

# MDS data table
mds_data <- cbind(atcc_de, 
                  biofilm_de[match(rownames(atcc_de), rownames(biofilm_de)), ])

mds_data <- cbind(mds_data, 
                  yeast_de[match(rownames(mds_data), rownames(yeast_de)), ])

colnames(mds_data)[13:28] <- c("B_EV1", "B_EV2", "B_EV3", "B_EV4", "B_EV5", 
                               "B_W1", "B_W2", "B_W3", "B_W4", "B_W5", 
                               "Y_EV1", "Y_EV2", "Y_EV3", 
                               "Y_W1", "Y_W2", "Y_W3")

mds_labels <- c(rep("EV", 3), rep("WCL", 3), 
                rep("EV", 3), rep("WCL", 3), 
                rep("EV", 5), rep("WCL", 5), 
                rep("EV", 3), rep("WCL", 3))

# figure 5c MDS [dim1, dim2]
f5c <- plot_mds(mds_data, mat_labels = mds_labels, 
                shape_size = 3, dim.plot = c(1,2)) + 
  scale_x_continuous(limits = c(-1.5, 2.5), 
                     expand = c(0,0)) + 
  scale_y_continuous(limits = c(-1.5, 2.5), 
                     expand = c(0,0)) + 
  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
                    values = st_pal[c(3, 2, 4, 1)], 
                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
                    guide = "legend") + 
  scale_shape_manual(values = c(22,24)) + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        legend.position = "right", 
        legend.text = element_text(size = 8), 
        legend.direction = "vertical") + 
  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
  xlab(label = "Dimension 1") + 
  ylab(label = "Dimension 2")

# figure 5d MDS [dim3, dim2]
f5d <- plot_mds(mds_data, mat_labels = mds_labels, 
                shape_size = 3, dim.plot = c(3,2)) + 
  scale_x_continuous(limits = c(-1.5, 2.5), 
                     expand = c(0,0)) + 
  scale_y_continuous(limits = c(-1.5, 2.5), 
                     expand = c(0,0)) + 
  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
                    values = st_pal[c(3, 2, 4, 1)], 
                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
                    guide = "legend") + 
  scale_shape_manual(values = c(22,24)) + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        legend.position = "right", 
        legend.text = element_text(size = 8), 
        legend.direction = "vertical", 
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0.1), 
        legend.box.margin = margin(t = -10, r = -6, b = -10, l = -10)) + 
  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
  xlab(label = "Dimension 3") + 
  ylab(label = "Dimension 2")
```

```{r figure5, fig.cap=f5_cap, fig.width=7.1, fig.height=5}
ggarrange(ggarrange(f5a, f5b,
                    labels = c("A", "B"),
                    ncol = 2,
                    nrow = 1),
          ggarrange(f5c, f5d,
                    labels = c("C", "D"),
                    ncol = 2,
                    nrow = 1, 
                    common.legend = TRUE,
                    legend = "right", 
                    align = "hv"),
          labels = NULL,
          ncol = 1,
          nrow = 2,
          heights = c(2, 3))

f5_cap <- "\\textbf{Combined comparison of \\textit{C. albicans} proteomes.} 
           \\textit{(A)} Venn diagram comparing four \\textit{C. albicans} EV 
           proteomes. Lists of proteins present in the centre and right 
           partitions of each venn diagram in Figure \\@ref(fig:figure3)A were 
           compared to identify proteins present in all four datasets. 
           \\textit{(B)} Venn diagram comparing four \\textit{C. albicans} WCL 
           proteomes. Lists of proteins present in the centre and left 
           partitions of each venn diagram in Figure \\@ref(fig:figure3)A were 
           compared to identify proteins present in all four datasets. The data 
           tables underlying Figures \\@ref(fig:figure5)A and 
           \\@ref(fig:figure5)B are provided in supplemental File S4. 
           \\textit{(C)} Multidimensional scaling (MDS) plot of each LC-MS/MS 
           biological replicate sample with the first 2 dimensions shown. 
           Pairwise distance between samples approximately indicates the 
           log\\textsubscript{2}(FC) between samples. \\textit{limma} was used 
           to generate the MDS plots [@ritchie2015]. \\textit{(D)} MDS plot of 
           each LC-MS/MS biological replicate sample with the second and third 
           dimensions shown."
```

\newpage

```{r figure6Heatmap, include=FALSE}
# figure 6 heatmap
f6_table <- a9_res %>% 
  select(logFC, CGD_gene_name) %>% 
  full_join(., select(a1_res, logFC, CGD_gene_name), 
            by = "CGD_gene_name") %>% 
  full_join(., select(yeast_res, logFC, CGD_gene_name), 
            by = "CGD_gene_name") %>% 
  full_join(., select(biofilm_res, logFC, CGD_gene_name), 
            by = "CGD_gene_name") %>% 
  rename(a9_lfc = logFC.x, 
         a1_lfc = logFC.y, 
         y_lfc = logFC.x.x, 
         b_lfc = logFC.y.y) %>% 
  select(CGD_gene_name, everything()) %>% 
  filter(CGD_gene_name %in% f5a_overlap)

# filter for rows with min 1/4 valid values
# otherwise clustering will not work
f6_table_filt <- f6_table %>% 
  filter_at(.vars = vars(contains("lfc")), 
            any_vars(!is.na(.))) %>% 
  tibble::column_to_rownames(var = "CGD_gene_name") %>% 
  as.matrix()

# excluded proteins
f6_table_excl <- f6_table %>% 
  filter_at(.vars = vars(contains("lfc")), 
            all_vars(is.na(.))) %>% 
  tibble::column_to_rownames(var = "CGD_gene_name") %>% 
  as.matrix()

# heatmap legend parameters
f6_params <- list(color_bar = "continuous", 
                  title = expression(bold(log[2]("FC"))), 
                  direction = "horizontal", 
                  legend_width = unit(2, "cm"), 
                  title_position = "lefttop", 
                  title_gp = grid::gpar(colour = "black", 
                                        fontsize = 5), 
                  labels_gp = grid::gpar(colour = "black", 
                                         fontsize = 5), 
                  at = seq(-6, 6, 2))

# plot heatmap
f6_htmp <- plot_heatmap(mt = f6_table_filt, 
                        plot = FALSE,
                        df = FALSE, 
                        data_type = "log2fc", 
                        clust_fun = "gower", 
                        split_type = "cutree", 
                        k = 5, 
                        cluster_split = FALSE, 
                        split_order = c(3, 1, 4, 2, 5), 
                        colour_lims = c(-4, 4),
                        column_labels = c("ATCC90028", "ATCC10231", 
                                          "DAY286 Y", "DAY286 B"), 
                        col_name_fontsize = 6, 
                        column_names_rot = 45, 
                        row_title_fontsize = 6, 
                        row_title_rot = 0, 
                        row_title = c("1", "2", "3", "4", "5"), 
                        heatmap_legend_param = f6_params)

# save heatmap as pdf file for editing in inkscape
# not run in rmarkdown but manually in console
# pdf(file = "figures/figure5_unf.pdf", width = 1.7, height = 4)
# ComplexHeatmap::draw(f5_htmp, heatmap_legend_side = "bottom")
# dev.off()
```

```{r figure6Table, include=FALSE}
#  list of proteins for heatmap table in order of appearance in heatmap
f6_clusters <- plot_heatmap(mt = f6_table_filt, 
                            plot = FALSE,
                            df = TRUE, 
                            data_type = "log2fc", 
                            clust_fun = "gower", 
                            split_type = "cutree", 
                            k = 5, 
                            cluster_split = FALSE) %>% 
  mutate(cluster = recode(cluster, 
                          "1" = 2, "2" = 4, "3" = 1, "4" = 3, "5" = 5)) %>% 
  arrange(cluster)

# extract identifiers from each cluster
f6_clust1 <- f6_clusters %>% 
  filter(cluster == 1) %>% 
  mutate(id = gsub("CHS3", "CaO19.4937", id)) %>% 
  pull(id)

f6_clust2 <- f6_clusters %>% 
  filter(cluster == 2) %>% 
  mutate(id = gsub("PEP1", "CaO19.3767", id)) %>% 
  pull(id) %>% 
  stringr::str_extract_all(., "[^;]+") %>% 
  unlist()

f6_clust3 <- f6_clusters %>% 
  filter(cluster == 3) %>% 
  pull(id)

f6_clust4 <- f6_clusters %>% 
  filter(cluster == 4) %>% 
  pull(id)

# cluster 5 has too many proteins to fit in table
# but GO enrichment still possible
f6_clust5 <- f6_clusters %>% 
  filter(cluster == 5) %>% 
  mutate(id = gsub("ALA1", "CaO19.5746", id), 
         id = gsub("MDH1", "CaO19.7481", id), 
         id = gsub("RPS1", "CaO19.3002", id), 
         id = gsub("TSA1", "CaO19.7417", id)) %>% 
  pull(id) %>% 
  stringr::str_extract_all(., "[^;]+") %>% 
  unlist() %>% 
  unique()

# cluster 6 is proteins that could not be clustered
# because all 4 log2FCs = NA
f6_clust6 <- sort(rownames(f6_table_excl))

# import FungiFun2 results
f6_go1 <- process_fungifun("figures/f6_GO_clust1.csv") %>% 
  mutate(Prot.found = gsub("CaO19.4937", "CHS3", Prot.found))

# issue with PEP1, ambiguous ID in FungiFun, used CaO19.3767 as identifier
f6_go2 <- process_fungifun("figures/f6_GO_clust2.csv") %>% 
  mutate(Prot.found = gsub("CaO19.3767", "PEP1", Prot.found))

f6_go3 <- process_fungifun("figures/f6_GO_clust3.csv")

# issue with CHS3, ambiguous ID in FungiFun, used CaO19.4937 as identifier
f6_go4 <- process_fungifun("figures/f6_GO_clust4.csv")

# issue with ALA1, MDH1, used CaO19.5746 and CaO19.7481 as identifiers
f6_go5 <- process_fungifun("figures/f6_GO_clust5.csv") %>% 
  mutate(Prot.found = gsub("CaO19.5746", "ALA1", Prot.found), 
         Prot.found = gsub("CaO19.7481", "MDH1", Prot.found), 
         Prot.found = gsub("CaO19.3002", "RPS1", Prot.found), 
         Prot.found = gsub("CaO19.7417", "TSA1", Prot.found))

f6_go6 <- process_fungifun("figures/f6_GO_clust6.csv")
```

```{r figure6, fig.cap=f6_cap, fig.height=6}
f6 <- png::readPNG("figures/figure6.png")

# draw figure 6
ggplot() + 
  background_image(f6) + 
  theme(plot.margin = margin(t = 0.1, l = 0.1, r = 0.1, b = 0.1, 
                             unit = "inches"))

f6_cap <- "\\textbf{Identification of commonly enriched EV proteins across 
           different \\textit{C. albicans} strains.} Heatmap of proteins 
           (n = 403) identified in all four EV samples (venn overlap in Figure 
           \\@ref(fig:figure5)A). Each column represents a 
           \\textit{C. albicans} strain and each row represents a protein. The 
           colours indicate the log\\textsubscript{2}(FC) of the protein for 
           that particular strain; red is EV enriched, blue is EV depleted, and 
           black is EV exclusive. Unsupervised clustering of rows and columns 
           was performed using Gower's formula via the daisy function from the 
           R package \\textit{cluster} [@maechler2019]. Proteins which were 
           exclusive to EVs from all four strains could not be clustered and 
           were seperated prior to clustering, in the group designated 
           \`\`cluster 6\". Functional enrichment analyses were performed on 
           the heatmap protein clusters using the online tool FungiFun2 
           [@priebe2015]. A selection of significantly enriched GO terms are 
           presented in the table inset. Lists of the proteins identified in 
           each cluster are shown and are also available in supplemental 
           File S5."
```

\newpage

```{r figure7Data, include=FALSE}
f7a_venn <- plot_venn(vlist = marker_comp, use_uniprot = FALSE, type = "plot", 
                      fontfamily = "sans", 
                      cat.fontfamily = "sans", 
                      cex = 0.9, 
                      cat.cex = 0.8, 
                      fill = st_pal[c(1,4,2,3)], 
                      alpha = c(0.3, 0.3, 0.3, 0.3), 
                      sub = "EV exclusive + sig. enriched", 
                      sub.fontfamily = "sans", 
                      sub.pos = c(0.5, 1.05), 
                      margin = 0.05)

f7a <- as_ggplot(f7a_venn) + 
  theme(plot.margin = unit(c(1.2,0,0,0), "lines"))

wcl_comp <- list("DAY Y" = yeast_res %>% 
                   filter(group == "WCL up" | group == "WCL ex") %>% 
                   pull(CGD_gene_name), 
                 "DAY B" = biofilm_res %>% 
                   filter(group == "WCL up" | group == "WCL ex") %>% 
                   pull(CGD_gene_name),
                 "ATCC90028" = a9_res %>% 
                   filter(group == "A9_W up" | group == "A9_W ex") %>% 
                   pull(CGD_gene_name), 
                 "ATCC10231" = a1_res %>% 
                   filter(group == "A1_W up" | group == "A1_W ex") %>% 
                   pull(CGD_gene_name))

f7b_venn <- plot_venn(vlist = wcl_comp, use_uniprot = FALSE, type = "plot", 
                      fontfamily = "sans", 
                      cat.fontfamily = "sans", 
                      cex = 0.9, 
                      cat.cex = 0.8, 
                      fill = st_pal[c(1,4,2,3)], 
                      alpha = c(0.3, 0.3, 0.3, 0.3), 
                      sub = "WCL exclusive + sig. enriched", 
                      sub.fontfamily = "sans", 
                      sub.pos = c(0.5, 1.05), 
                      margin = 0.05)

f7b <- as_ggplot(f7b_venn) + 
  theme(plot.margin = unit(c(1.2,0,0,0), "lines"))
```

```{r figure7, fig.cap=f7_cap, fig.width=2.5, fig.height=4}
ggarrange(f7a, f7b, 
          labels = c("A", "B"), 
          ncol = 1,
          nrow = 2)

f7_cap <- "\\textbf{Identification of common signficantly enriched or exclusive 
           \\textit{C. albicans} EV and WCL proteins.} Proteins identified as 
           significantly enriched or exclusive to EVs in Figure 
           \\@ref(fig:figure3) were compared to select those which were common 
           to all 4 datasets. 43 proteins were identified as potential positive 
           EV protein markers and 52 proteins as potential negative EV protein 
           markers. The data tables underlying Figure 
           \\@ref(fig:figure7) are provided in supplemental File S4. Details of 
           the 43 positive EV protein marker candidates and 52 negative 
           candidates can be found in Table \\@ref(tab:table1) and supplemental 
           Table S2 respectively."
```

\newpage

```{r figure8, fig.cap=f8_cap, fig.width=3.5, fig.height=2.8}
f8_cap <- "\\textbf{Eighteen best potential \\textit{C. albicans} positive EV 
           protein markers.} These proteins are those underlined in Table 
           \\@ref(tab:table1). They are are enriched or exclusive to EVs 
           isolated from all of the \\textit{C. albicans} strains investigated 
           in this study. The proteins fit within the EV biomarker categories 
           1a, 2a, and 2b from MISEV2018 which includes transmembrane, 
           GPI-anchored, and cytosolic proteins that are EV enriched 
           [@thery2018]."

f8 <- png::readPNG("figures/figure8.png")

ggplot() + 
  background_image(f8)
```

\newpage

```{r figure9, fig.cap=f9_cap, fig.width=7.2, fig.height=6}
f9_cap <- "\\textbf{Predicted topology and palmitoylation sites of 
           \\textit{C. albicans} MCC/eisosome proteins SUR7 and orf19.6741 
           compared to the human tetraspanin CD81.} The presence of 
           transmembrane (TM) domains and palmitoylation sites shown on the 
           left side of the figure were predicted using the online tools 
           TOPCONS2 (topcons.cbr.su.se) [@tsirigos2015] and CSS-PALM 4.0 
           (csspalm.biocuckoo.org) [@ren2008] respectively. For CD81, 
           palmitoylation sites experimentally determined in previous 
           literature are shown [@delandre2009]. The right side of the figure 
           shows a cartoon representation of the TOPCONS2 consensus topology 
           prediction for the three proteins as well as the crystal structure 
           of CD81 (PDB: 5TCX) [@zimmerman2016]."

f9 <- png::readPNG("figures/figure9.png")

ggplot() + 
  background_image(f9)
```

### 2019-06-05 inst/manuscript/manuscript.Rmd
Remove .docx output option from manuscript.Rmd
Also:
 - Remove associated components with .docx output

@@
       keep_tex: no
-    bookdown::word_document2:
-      pandoc_args:
-        '--lua-filter=components/pagebreak.lua'
-      reference_docx: "components/draft_template.docx"
-      fig_caption: yes
 bibliography: "components/references.bib" 

### 2019-06-10 inst/manuscript/manuscript.Rmd
Combine golgi, ER, vacuole proteins in table 1
Also:
 - Fix protein names in figure 8 so they are not in all
   capitals.
 - Separate Vac8 and Ykt6 in figure 8

@@
                  "Y", rep("", 7), "Y"), 
-         pack_row = c(5, rep(1,3), rep(5,2), 1, 2, rep(1,3), rep(1,3), 4, 2, 
-                      rep(5,2), 1, rep(2,2), 4, 1, rep(5,2), 1, rep(5,3), 1, 
-                      4, rep(1,3), 5, 1, 1, 3, 1, 3, 2, 3, 5)) %>% 
+         pack_row = c(4, rep(1,3), rep(4,2), 1, 2, rep(1,3), rep(1,3), 3, 2, 
+                      rep(4,2), 1, rep(2,2), 3, 1, rep(4,2), 1, rep(4,3), 1, 
+                      3, rep(1,3), 4, 1, 1, 2, 1, 2, 2, 2, 4)) %>% 
   arrange(pack_row)
@@
   pack_rows("Plasma membrane", 1, 20) %>% 
-  pack_rows("Golgi, ER, secretory pathway", 21, 25) %>% 
-  pack_rows("Vacuole", 26, 28) %>% 
+  pack_rows("Golgi, ER, vacuole", 21, 28) %>% 
   pack_rows("Mitochondria", 29, 31) %>% 

### 2019-06-18 inst/manuscript/manuscript_supplement.Rmd
Add ribosome section to supplemental Table S2

--- 2019-06-10 inst/manuscript/manuscript.Rmd
@@
     {\endorigfigure}
+  - \newcommand{\beginsupplement}{
+      \setcounter{table}{0} 
+      \renewcommand{\thetable}{S\arabic{table}} 
+      \setcounter{figure}{0} 
+      \renewcommand{\thefigure}{S\arabic{figure}}
+    }
   - \usepackage{caption}
@@
 
-# load packages
+# load libraries
 library(candidaev)
@@
 knitr::read_chunk('components/protein_funs.R')
-
-# define colour palette to distinguish between strains
-# colours = yellow, blue, green, pink
-# levels = yeast, ATCC90028, ATCC10231, biofilm
-st_pal <- c("#E69F00", "#56B4E9", "#009E73", "#CC79A7")
-
-# define colour palette to distinguish between EVs and whole cell lysate (WCL)
-# colours = grey, red, blue
-# levels = not significant, EV, WCL
-ev_pal <- c("#999999", "#D55E00", "#0072B2")
 ```
@@
 
-# drop EV_1 and WCL_1 samples
+# drop EV_1 and WCL_1
 yeast_lfq2 <- yeast_lfq[, !colnames(yeast_lfq) %in% c("EV_1", "WCL_1")]
@@
 # create design matrix
-y_samp <- data.frame(T = rep(c("EV", "WCL"), each = 3))
+y_samp <- data.frame(T = (rep(c("EV", "WCL"), each = 3)))
 
@@
 # create design matrix
-b_samp <- data.frame(T = rep(c("EV", "WCL"), each = 5))
+b_samp <- data.frame(T = (rep(c("EV", "WCL"), each = 5)))
 
@@
 # create design matrix
-atcc_samp <- data.frame(T = rep(c("A1_EV", "A1_WCL", 
-                                  "A9_EV", "A9_WCL"), each = 3))
+atcc_samp <- data.frame(T = (rep(c("A1_EV", "A1_WCL", 
+                                   "A9_EV", "A9_WCL"), each = 3)))
 
@@
 
-# extract results for ATCC strains
+# extract DE results
 a1_res <- get_results(efit = atcc_efit, 
@@
 
-# Abbreviations
+# Supplementary data
 
-EV - extracellular vesicle
+\beginsupplement
+
+```{r figureS1, fig.cap=fS1_cap, fig.height=5, fig.width=5}
+fS1_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 
+              determined by nanoparticle tracking analysis (NTA).} A line plot 
+              for each EV biological replicate from each strain is shown. Each 
+              line plots represents the average of three technical replicates 
+              and the dashed grey lines indicate 100 nm.")
+
+figS1_labels <- c("ATCC10231", 
+                  "ATCC90028", 
+                  "DAY286 biofilm", 
+                  "DAY286 yeast")
+
+names(figS1_labels) <- c("ATCC10231", 
+                         "ATCC90028", 
+                         "Biofilm", 
+                         "DAY286")
+
+# average the nta technical replicate data
+nta_techavg <- nta %>% 
+  nanolyze(particle_size, Strain, Bio_rep, Dilution, 
+           name = "Tech_rep", 
+           param_var = True_count)
+
+nta_techavg$Strain <- factor(nta_techavg$Strain, levels = c("DAY286",
+                                                            "ATCC90028", 
+                                                            "ATCC10231", 
+                                                            "Biofilm"))
+
+# plot nta distribution for each bio rep
+nta_techavg %>% 
+  ggplot(aes(x = particle_size, y = Tech_rep_mean, colour = Bio_rep)) + 
+  geom_line(size = 0.5) + 
+  geom_vline(xintercept = 100, colour = "#999999", linetype = "dashed") +
+  facet_wrap(~ Strain, scales = "free", ncol = 2, nrow = 2, 
+             labeller = labeller(Strain = figS1_labels)) + 
+  theme_classic() + 
+  theme(strip.background = element_blank(), 
+        legend.position = "bottom", 
+        plot.margin = margin(t = 0, l = 0, r = 0.1, b = 0, unit = "inches")) + 
+  xlab(label = "Particle size (nm)") + 
+  ylab(label = "Particles / mL") + 
+  labs(colour = "Biological replicate")
+```
 
@@
 
-# Abstract
+```{r tableS1Data}
+# construct data.frame with nta experiment info
+nta_metadata <- data.frame(id = c("ATCC10231_1", "ATCC10231_2", "ATCC10231_3", 
+                                  "ATCC90028_1", "ATCC90028_2", "ATCC90028_3", 
+                                  "Biofilm_1", "Biofilm_2", "Biofilm_3", 
+                                  "Biofilm_4", "Biofilm_5", 
+                                  "DAY286_1", "DAY286_2", "DAY286_3"), 
+                           strain = c(rep("ATCC10231", 3), 
+                                      rep("ATCC90028", 3), 
+                                      rep("Biofilm", 5), 
+                                      rep("DAY286", 3)), 
+                           replicate = c(seq(1, 3), seq(1, 3), 
+                                         seq(1, 5), seq(1, 3)), 
+                           OD600 = c(0.455*20, 0.557*20, 0.615*20, 
+                                     0.310*50, 0.337*50, 0.297*50, 
+                                     rep(NA, 5), 
+                                     36.2, 39.7, 34.0),
+                           culture_vol = c(rep(150, 3),
+                                           rep(150, 3), 
+                                           rep(1000, 5), 
+                                           rep(300, 3)), 
+                           protein_yield = c(19.2, 28.2, 28.7, 
+                                             42.4, 71.6, 58.4, 
+                                             20.4, 19.8, 29.7, 19.3, 41.6, 
+                                             21.9, 18.0, 22.4), 
+                           protein_conc = c(0.192, 0.282, 0.287, 
+                                            0.424, 0.716, 0.584, 
+                                            0.204, 0.198, 0.297, 0.193, 0.416, 
+                                            0.437, 0.360, 0.447), 
+                           df = c(250, 750, 750, 
+                                  1500, 3000, 3000, 
+                                  3000, 2000, 2000, 3000, 6000, 
+                                  1500, 1500, 1500), 
+                           mean = c(248.5, 218.7, 217.9, 
+                                    197.1, 233.1, 191.0, 
+                                    119.4, 142.1, 143.3, 133.3, 120.9, 
+                                    182.8, 174.5, 164.5), 
+                           mode = c(171.9, 155.5, 140.2, 
+                                    135.4, 156.7, 138.0, 
+                                    100.5, 94.7, 103.1, 103.1, 97.5, 
+                                    106.4, 99.2, 100.2), 
+                           sd = c(120.1, 112.1, 110.0, 
+                                  87.1, 90.7, 68.4, 
+                                  47.4, 64.3, 70.2, 60.7, 47.4, 
+                                  93.4, 93.9, 83.1), 
+                           d10 = c(139.1, 110.2, 118.1, 
+                                   122.4, 141.9, 126.0, 
+                                   90.2, 88.8, 96.4, 93.2, 89.7, 
+                                   97.8, 93.8, 93.0), 
+                           d50 = c(211.9, 188.2, 180.3, 
+                                   169.4, 209.3, 170.7, 
+                                   105.6, 115.0, 110.9, 108.1, 105.9, 
+                                   152.8, 147.3, 136.2),
+                           d90 = c(393.0, 354, 354.4, 
+                                   301.4, 381.1, 285.8, 
+                                   151.5, 239.7, 240.8, 210.2, 171.2, 
+                                   320.4, 308.0, 290.9),
+                           sort_order = c(rep(3, 3), rep(2, 3), 
+                                          rep(4, 5), rep(1, 3)), 
+                           stringsAsFactors = FALSE)
 
-The abstract goes here. Here is a citation [@liao2012].
+# determine the total particle concentration for each biological replicate
+nta_total <- nta_techavg %>% 
+  nanocount(Strain, Bio_rep, Dilution, 
+            param_var = Tech_rep_mean) %>% 
+  tidyr::unite("id", Strain, Bio_rep) %>% 
+  inner_join(., nta_metadata, by = "id") %>% 
+  arrange(sort_order) %>% 
+  select(strain, replicate, OD600, culture_vol, protein_yield, protein_conc, 
+         Particle_count, mean, mode, sd) %>% 
+  mutate(OD600 = case_when(is.na(OD600) == TRUE ~ "NA", 
+                           TRUE ~ as.character(OD600)), 
+         Particle_count = signif(Particle_count, digits = 3))
+```
 
-Here is another citation [@gil-bona2015].
+```{r tableS1}
+tabS1_labs <- c("Biological\nreplicate", 
+                "OD600", 
+                "Culture vol.\n(mL)", 
+                "Protein yield\n($\\mu$g)", 
+                "Protein conc.\n($\\mu$g/mL)", 
+                "Particle conc.\n(particles/mL)", 
+                "Mean", 
+                "Mode", 
+                "SD")
 
-And another [@lin2014].
+tabS1_cap <- "\\textbf{Metadata for each EV isolation analysed in this study.} 
+              The optical density (at 600 nm) and volume of each culture from 
+              which the EVs were isolated is given. The protein and particle 
+              concentration of the EVs along with the NTA size distribution 
+              results for each biological replicate are also shown."
+
+# construct a table of metadata for each EV biological replicate
+nta_total %>% 
+  select(-strain) %>% 
+  mutate_all(linebreak) %>% 
+  knitr::kable(caption = tabS1_cap, 
+               format = "latex", 
+               booktabs = TRUE, 
+               linesep = "", 
+               col.names = linebreak(tabS1_labs), 
+               escape = FALSE, 
+               align = "l") %>% 
+  kable_styling(latex_options = c("scale_down", 
+                                  "HOLD_position")) %>% 
+  add_header_above(c(" " = 6, "Particle diameter (nm)" = 3)) %>% 
+  pack_rows("DAY286 yeast", 1, 3) %>% 
+  pack_rows("ATCC90028", 4, 6) %>% 
+  pack_rows("ATCC10231", 7, 9) %>% 
+  pack_rows("DAY286 biofilm", 10, 14)
+```
 
@@
 
-# Introduction
-
-Here is a citation [@marwick2017].
-
-# Experimental procedures
-
-## Subsection 1
-
-## Subsection 2
-
-# Results
-
-# Discussion
-
-# Acknowledgements
-
-# Data availability
-
-# Acknowledgements
-
-\newpage
-# References 
-<div id="refs"></div>
-
-\newpage
-
-# Tables
-
-```{r table1Data, include=FALSE}
-# make list of EV sig. enriched and exclusive proteins for each strain
-marker_comp <- list("DAY Y" = yeast_res %>% 
-                      filter(group == "EV up" | group == "EV ex") %>% 
+```{r tableS2Data}
+# make list of WCL sig. enriched and exclusive proteins for each strain
+wcl_comp <- list("yeast" = yeast_res %>% 
+                   filter(group == "WCL up" | group == "WCL ex") %>% 
                    pull(CGD_gene_name), 
-                    "DAY B" = biofilm_res %>% 
-                      filter(group == "EV up" | group == "EV ex") %>% 
+                 "biofilm" = biofilm_res %>% 
+                   filter(group == "WCL up" | group == "WCL ex") %>% 
+                   pull(CGD_gene_name), 
+                 "ATCC10231" = a1_res %>% 
+                   filter(group == "A1_W up" | group == "A1_W ex") %>% 
                    pull(CGD_gene_name), 
                  "ATCC90028" = a9_res %>% 
-                      filter(group == "A9_EV up" | group == "A9_EV ex") %>% 
-                      pull(CGD_gene_name), 
-                    "ATCC10231" = a1_res %>% 
-                      filter(group == "A1_EV up" | group == "A1_EV ex") %>% 
+                   filter(group == "A9_W up" | group == "A9_W ex") %>% 
                    pull(CGD_gene_name))
@@
 # get venn segments
-marker_comp_tab <- plot_venn(vlist = marker_comp, 
+wcl_comp_tab <- plot_venn(vlist = wcl_comp, 
                           use_uniprot = FALSE, 
@@
 # extract protein names from venn overlap
-marker_candidates <- marker_comp_tab %>% 
+wcl_candidates <- wcl_comp_tab %>% 
   filter(apply(.[, 1:4], 1, sum) == 4) %>% 
@@
 
-# construct table 1
-marker_longlist <- marker_candidates %>% 
-  mutate(Function = match_id(Name, uniprot, "CGD_gene_name", "Protein_name"),
-         DAY.Y = match_id(Name, yeast_res, "CGD_gene_name", "logFC", 
-                          str_split = FALSE), 
-         A9 = match_id(Name, a9_res, "CGD_gene_name", "logFC", 
-                       str_split = FALSE), 
-         A1 = match_id(Name, a1_res, "CGD_gene_name", "logFC", 
-                       str_split = FALSE), 
-         DAY.B = match_id(Name, biofilm_res, "CGD_gene_name", "logFC", 
-                          str_split = FALSE), 
+# construct table S2
+wcl_longlist <- wcl_candidates %>% 
+  mutate(Function = match_id(Name, uniprot, "CGD_gene_name", 
+                             "Protein_name", concat = TRUE, str_split = FALSE),
+         DAY.Y = match_id(Name, yeast_res, "CGD_gene_name", 
+                          "logFC", concat = TRUE, str_split = FALSE), 
+         A9 = match_id(Name, a9_res, "CGD_gene_name", 
+                       "logFC", concat = TRUE, str_split = FALSE), 
+         A1 = match_id(Name, a1_res, "CGD_gene_name", 
+                       "logFC", concat = TRUE, str_split = FALSE), 
+         DAY.B = match_id(Name, biofilm_res, "CGD_gene_name", 
+                          "logFC", concat = TRUE, str_split = FALSE), 
          TM = match_id(Name, uniprot, "CGD_gene_name", "Transmembrane"), 
@@
 # load vector of protein functions from external R script
-<<fun_list1>>
+<<fun_list2>>
 
@@
 # group proteins according to localisation
-marker_longlist <- marker_longlist %>% 
-  mutate(Function = function_desc1, 
-         VDM = c("Y", rep("",3), rep("Y", 2), "", "Y", rep("", 8), rep("Y", 2), 
-                 rep("", 4), rep("Y", 3), rep("", 2), rep("Y", 2), rep("", 5), 
-                 "Y", rep("", 7), "Y"), 
-         pack_row = c(4, rep(1,3), rep(4,2), 1, 2, rep(1,3), rep(1,3), 3, 2, 
-                      rep(4,2), 1, rep(2,2), 3, 1, rep(4,2), 1, rep(4,3), 1, 
-                      3, rep(1,3), 4, 1, 1, 2, 1, 2, 2, 2, 4)) %>% 
+wcl_longlist <- wcl_longlist %>% 
+  mutate(Function = function_desc2, 
+         VDM = c(rep("", 52)), 
+         pack_row = c(8, rep(4, 2), 3, rep(2, 2), 7, rep(1, 2), rep(7, 3), 1, 
+                      rep(2, 3), 7, 2, 4, rep(2, 2), 7, 3, 2, 5, rep(1, 2), 6, 
+                      2, 7, 6, 2, 1, 7, rep(1, 3), 2, 1, 5, 2, 1, 6, 
+                      1, 6, 2, 1, 9, 9, rep(1, 3))) %>% 
   arrange(pack_row)
-
-# fix number of TM domains for CDR1;CDR2
-marker_longlist[2, 7] <- "12;12"
-
-# UniProt says SUR7 has 3 TM domains and a signal peptide
-# much of literature says SUR7 has 4 TM domains
-# TOPCONS2 predicts SUR7 has 4 TM domains and no signal peptide
-# fix SUR7 entries
-marker_longlist[19, 7] <- "4"
-marker_longlist[19, 8] <- ""
 ```
 
-<!-- assign markdown references for table caption -->
 (ref:table1) [@gil-bona2015]
+
 (ref:footnote1) [@skrzypek2017]
+
 (ref:footnote2) [@almagroarmenteros2017]
-(ref:footnote3) [@tsirigos2015]
 
-```{r table1}
-tab1_cap <- "\\textbf{Candidate positive protein markers for 
+(ref:footnote3) [@savojardo2018]
+
+```{r tableS2}
+tabs2_cap <- "\\textbf{Candidate negative protein markers for 
               \\textit{C. albicans} EVs.} This list of proteins consists of 
-             those that were found to be exclusive to EVs or significantly 
-             enriched in EVs across the four \\textit{C. albicans} strains 
-             examined in this study. Proteins are grouped according to their 
-             subcellular localisation as annotated in the Candida Genome 
-             Database (candidagenome.org) (ref:footnote1). 
-             The log\\textsubscript{2} ratio of the abundance (mean MaxQuant 
-             LFQ intensity) of each protein in EVs compared to whole cell 
-             lysate (WCL) for each strain is listed. \`\`ex\" indicates where 
-             a protein was only quantified in the EV fraction and not the WCL 
-             for that strain. The \`\`TM\" column indicates the number of 
-             transmembrane domains for each protein as annotated in UniProtKB. 
-             \`\`SP\" indicates whether a protein is annotated as having a 
-             signal peptide according to UniProtKB. \`\`VDM\" shows whether a 
-             protein has previously been detected in vesicle-depleted culture 
-             media (i.e. the proteins may also be in the soluble secretome) 
-             (ref:table1). Underlined proteins are those identified as the 
-             best candidates for positive EV markers according to the 
-             criteria depicted in Figure \\ref{fig:figure1}."
+              those that were found to be exclusive to whole cell lysate (WCL) 
+              or significantly enriched in WCL across the four 
+              \\textit{C. albicans} strains examined in this study. Proteins 
+              are grouped according to their subcellular localisation as 
+              annotated in the Candida Genome Database (candidagenome.org) 
+              (ref:footnote1). The log\\textsubscript{2} ratio of the abundance 
+              (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
+              WCL for each strain is listed. A negative value indicates that a 
+              protein was enriched in WCL compared to EV. \`\`ex\" indicates 
+              where a protein was only quantified in the WCL fraction and not 
+              in EVs for that strain. The \`\`TM\" column indicates the number 
+              of transmembrane domains for each protein as annotated in 
+              UniProtKB. \`\`SP\" indicates whether a protein is annotated as 
+              having a signal peptide according to UniProtKB. \`\`VDM\" shows 
+              whether a protein has previously been detected in 
+              vesicle-depleted culture media (i.e. the proteins may also be in 
+              the soluble secretome) (ref:table1). Underlined proteins are 
+              those identified as the best candidates for negative
+              EV markers according to the criteria depicted in Figure 1."
 
-# draw table 1
-knitr::kable(marker_longlist[ ,-10],
-             caption = tab1_cap, 
+# draw table S2
+knitr::kable(wcl_longlist[, -10], 
+             caption = tabs2_cap, 
              format = "latex", 
@@
              escape = FALSE) %>% 
-  row_spec(row = c(1, 5, 6, 11, 12, 15:20, 22:27, 39), underline = TRUE) %>% 
+  row_spec(row = c(23, 30, 34, 35, 44, 50), underline = TRUE) %>% 
   add_header_above(c(" " = 2, 
                      "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
-                     " " = 2), escape = FALSE) %>% 
-  kable_styling(font_size = 8) %>% 
-  pack_rows("Plasma membrane", 1, 20) %>% 
-  pack_rows("Golgi, ER, vacuole", 21, 28) %>% 
-  pack_rows("Mitochondria", 29, 31) %>% 
-  pack_rows("Cell wall, cell surface", 32, 43) %>% 
+                     " " = 3), escape = FALSE) %>% 
+  kable_styling(font_size = 8, 
+                latex_options = c("HOLD_position")) %>% 
+  pack_rows("Cytoplasm", 1, 16) %>% 
+  pack_rows("Mitochondria", 17, 30) %>% 
+  pack_rows("Nucleus", 31, 32) %>% 
+  pack_rows("Vacuole", 33, 35) %>% 
+  pack_rows("Peroxisome", 36, 37) %>% 
+  pack_rows("Proteasome", 38, 41) %>% 
+  pack_rows("Cell wall, cell surface, fungal biofilm matrix", 42, 49) %>% 
+  pack_rows("Cytoskeleton", 50, 50) %>% 
+  pack_rows("Ribosome", 51, 52) %>% 
   footnote(alphabet = c("Protein localisation was inferred from sequence 
@@
                          (ref:footnote2)", 
-                        "Presence of transmembrane domains and absense of a 
-                        signal peptide was predicted using TOPCONS2 
+                        "Protein localisation was predicted using BUSCA 
                          (ref:footnote3)"), 
@@
 
-# Figures
+# References
 
-```{r figure1, fig.cap=f1_cap, fig.width=5.45, fig.height=6}
-# construct figure 1
-f1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
-           proteomic analysis of \\textit{C. albicans} EVs and the selection 
-           of EV protein markers.} Steps 1 to 6 were performed for each of the 
-           four strains examined in this study: DAY286 yeast, ATCC90028 yeast, 
-           ATCC10231 yeast, and DAY286 biofilm. The results from the four 
-           seperate analyses were combined (step 7) to identify proteins which 
-           commonly appeared as EV marker candidates. The MISEV2018 criteria 
-           for protein content-based EV characterisation and other 
-           considerations were used to select the best \\textit{C. albicans} 
-           EV marker proteins."
-
-f1 <- png::readPNG("figures/figure1.png")
-
-# draw figure 1
-ggplot() + 
-  background_image(f1)
-```
-
-\newpage
-
-```{r figure2Data, include=FALSE}
-# construct data.frame with nta experiment info
-nta_metadata <- data.frame(id = c("ATCC10231_1", "ATCC10231_2", "ATCC10231_3", 
-                                  "ATCC90028_1", "ATCC90028_2", "ATCC90028_3", 
-                                  "Biofilm_1", "Biofilm_2", "Biofilm_3", 
-                                  "Biofilm_4", "Biofilm_5", 
-                                  "DAY286_1", "DAY286_2", "DAY286_3"), 
-                           protein_conc = c(0.192, 0.282, 0.287, 
-                                            0.424, 0.716, 0.584, 
-                                            0.204, 0.198, 0.297, 0.193, 0.416, 
-                                            0.437, 0.360, 0.447), 
-                           stringsAsFactors = FALSE)
-
-# average the nta technical replicate data
-nta_techavg <- nta %>% 
-  nanolyze(particle_size, Strain, Bio_rep, Dilution, 
-           name = "Tech_rep", 
-           param_var = True_count)
-
-# average the nta biological replicate data
-nta_bioavg <- nta_techavg %>% 
-  nanolyze(particle_size, Strain,
-           name = "Bio_rep", 
-           param_var = Tech_rep_mean) %>% 
-  mutate(facet = case_when(Strain == "Biofilm" ~ "second", TRUE ~ "first"))
-
-# determine the total particle concentration for each biological replicate
-nta_total <- nta_techavg %>% 
-  nanocount(Strain, Bio_rep, Dilution, 
-            param_var = Tech_rep_mean) %>% 
-  tidyr::unite("id", Strain, Bio_rep) %>% 
-  mutate(protein_conc = as.numeric(match_id(id, nta_metadata, 
-                                            "id", "protein_conc")), 
-         od = match_id(id, nta_metadata, "id", "OD600"), 
-         part_per_prot = Particle_count / protein_conc / 1000) %>% 
-  tidyr::separate(col = id, into = c("Strain", "Bio_rep"), sep = "_", 
-                  remove = TRUE)
-
-# use ANOVA with Tukey HSD to compare mean particle per ug protein 
-# ratio across the strains
-nta_total_tukey <- aov(part_per_prot ~ Strain, data = nta_total) %>% 
-  tukey_hsd()
-```
-
-```{r figure2plots, include=FALSE}
-# construct figure 2a
-f2a_img <- png::readPNG("figures/figure2a.png")
-
-f2a <- ggplot() + 
-  background_image(f2a_img) + 
-  theme(plot.margin = margin(t = 0.3, l = 0, r = 0, b = 0, unit = "inches"))
-
-# construct figure 2b
-f2b <- nta_bioavg %>% 
-  ggplot(aes(x = particle_size, y = Bio_rep_mean, colour = Strain)) + 
-  scale_colour_manual(values = st_pal[c(3, 2, 4, 1)], 
-                      breaks = c("DAY286", "ATCC90028", 
-                                 "ATCC10231", "Biofilm"), 
-                      labels = c("DAY286 Y", "ATCC90028", 
-                                 "ATCC10231", "DAY286 B")) + 
-  geom_vline(xintercept = 100, colour = "#999999", linetype = "dashed") +
-  geom_line(size = 0.5) + 
-  facet_wrap(~ facet, scales = "free", ncol = 2, nrow = 1) + 
-  theme_classic() + 
-  theme(strip.background = element_blank(), 
-        strip.text = element_blank(), 
-        legend.position = c(0.88, 0.6), 
-        legend.title = element_blank(), 
-        plot.margin = margin(t = 0.2, l = 0, r = 0.2, b = 0, unit = "inches"), 
-        axis.text.x = element_text(colour = "black")) + 
-  xlab(label = "Particle size (nm)") + 
-  ylab(label = "Particles / mL")
-
-# construct figure 2c
-nta_total$Strain <- factor(nta_total$Strain, 
-                           levels = c("DAY286", "ATCC90028", 
-                                      "ATCC10231", "Biofilm"))
-
-f2c <- nta_total %>% 
-  ggboxplot(x = "Strain", y = "part_per_prot", 
-            color = "Strain", palette = st_pal, add = "jitter", 
-            add.params = list(color = "black"), 
-            shape = 15,
-            ylab = expression("Particles /"~paste(mu,g)~"protein"))
-f2c <- ggpar(f2c, 
-             yscale = "log10", 
-             format.scale = TRUE, 
-             ylim = c(8e8, 8e10),
-             font.y = 10, 
-             legend = "none") + 
-  stat_pvalue_manual(nta_total_tukey[c(2,4,6), ], label = "p.adj", 
-                     y.position = c(10.45, 10.65, 10.85), 
-                     tip.length = 1e-2, 
-                     label.size = 3) + 
-  theme(axis.title.x = element_blank(), 
-        plot.margin = margin(t = 0.2, l = 0.2, r = 0, b = 0.15, 
-                             unit = "inches")) + 
-  scale_x_discrete(labels = c("ATCC90028" = "A9", 
-                              "ATCC10231" = "A1", 
-                              "Biofilm" = "B", 
-                              "DAY286" = "Y"))
-```
-
-```{r figure2, fig.cap=f2_cap, fig.width=7.1, fig.height=4}
-# draw figure 2
-ggarrange(f2a, 
-          ggarrange(f2b, f2c, 
-                    labels = c("B", "C"), 
-                    ncol = 2,
-                    nrow = 1, 
-                    widths = c(1.8,1)), 
-          labels = c("A", ""), 
-          nrow = 2, 
-          ncol = 1, 
-          heights = c(1,1))
-
-f2_cap <- "\\textbf{Characterisation and quantification of EVs from different 
-           \\textit{C. albicans} strains.} \\textit{(A)} Representative TEM 
-           images of EVs isolated from 4 different \\textit{C. albicans} 
-           strains. Scale bar indicates 0.5 $\\mu$m. \\textit{(B)} Size 
-           distribution of DAY286 yeast (n = 3), ATCC90028 yeast (n = 3), 
-           ATCC10231 yeast (n = 3), and DAY286 biofilm (n = 5) EVs as measured 
-           by nanoparticle tracking analysis. Line plots shown are the average 
-           of the biological replicates and the dashed grey line indicates 100 
-           nm. Plots for the individual biological replicates are presented in 
-           supplemental Figure S1. \\textit{(C)} Comparison of the ratio of 
-           particle concentration to protein concentration of the EV fraction, 
-           (particles/mL) $\\div$ ($\\mu$g protein/mL), across the four EV 
-           sources. Each dot represents one biological replicate. Sample means 
-           were compared using ANOVA followed by Tukey's HSD \\textit{post-hoc} 
-           test. P-values indicating significant differences are shown. The 
-           particle and protein concentrations for each biological replicate 
-           are provided in supplemental Table S1."
-```
-
-\newpage
-
-```{r figure3Yeast, include=FALSE}
-# compare DAY286 yeast EV WCL proteins
-f3a1 <- plot_venn(list("EV" = y_ev, "WCL" = y_wcl), 
-                  use_uniprot = TRUE, type = "plot", 
-                  fontfamily = "sans", 
-                  cex = 0.8,
-                  cat.fontfamily = "sans", 
-                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
-                  margin = 0.05)
-
-# DAY286 yeast venn
-f3a1 <- as_ggplot(f3a1) + 
-  theme(plot.margin = unit(c(1,0.5,1,0.5), "lines")) + 
-  annotate("text", x = 0.5, y = 0.92, 
-           label = "bold('DAY286 yeast')", parse = TRUE)
-
-# generate volcano plot
-f3b1 <- plot_volcano(data = yeast_res, 
-                     p_val = adj.P.Val, 
-                     log2fc = logFC,
-                     group = group, 
-                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
-                     point_size = 0.6, 
-                     label_size = 2, 
-                     x_lim = c(-10, 12), 
-                     y_lim = c(0, 8), 
-                     legend_params = c("left", 11, 8), 
-                     axis_params = c("black", 10)) + 
-  scale_colour_manual(labels = c("EV enriched", 
-                                 "WCL enriched", 
-                                 "Not significant"), 
-                      values = unname(ev_pal[c(2,1,3)]), 
-                      breaks = c("EV up", "WCL up", "not sig"), 
-                      name = element_blank()) + 
-  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 Y')", parse = TRUE) + 
-  annotate("text", x = 3.5, y = 7, label = "bold('88')", 
-           parse = TRUE, colour = unname(ev_pal[2])) + 
-  annotate("text", x = -3.5, y = 7, label = "bold('88')", parse = TRUE, 
-           colour = unname(ev_pal[3])) + 
-  annotate("text", x = 0, y = 6, label = "bold('318')", parse = TRUE, 
-           colour = unname(ev_pal[1]))
-```
-
-```{r figure3A9, include=FALSE}
-# compare ATCC90028 EV WCL proteins
-f3a2 <- plot_venn(list("EV" = atcc9_ev, "WCL" = atcc9_w), 
-                  use_uniprot = TRUE, type = "plot", 
-                  fontfamily = "sans",
-                  cex = 0.8,
-                  cat.fontfamily = "sans", 
-                  cat.just = list(c(0.5,1.7), c(0.5,1.55)), 
-                  ext.percent = c(30,10,0),
-                  ext.pos = c(45,315),
-                  ext.dist = -0.05,
-                  ext.length = 0.5,
-                  margin = 0.05)
-
-# ATCC90028 venn
-f3a2 <- as_ggplot(f3a2) + 
-  theme(plot.margin = unit(c(1,0,1,0.5), "lines")) + 
-  annotate("text", x = 0.5, y = 0.92, label = "bold('ATCC90028')", parse = TRUE)
-
-# generate volcano plot
-f3b2 <- plot_volcano(data = a9_res, 
-                     p_val = adj.P.Val, 
-                     log2fc = logFC,
-                     group = group, 
-                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
-                     point_size = 0.6, 
-                     label_size = 2, 
-                     x_lim = c(-10, 12), 
-                     y_lim = c(0, 8), 
-                     legend_params = c("left", 11, 8), 
-                     axis_params = c("black", 10)) + 
-  scale_colour_manual(labels = c("EV enriched (99)", "WCL enriched (130)", 
-                                 "Not significant (744)"),
-                      values = unname(ev_pal[c(2,3,1)])) + 
-  annotate("text", x = 8, y = 0.5, label = "bold('ATCC90028')", parse = TRUE) + 
-  annotate("text", x = 3.5, y = 7, label = "bold('99')", 
-           parse = TRUE, colour = unname(ev_pal[2])) + 
-  annotate("text", x = -3.5, y = 7, label = "bold('130')", 
-           parse = TRUE, colour = unname(ev_pal[3])) + 
-  annotate("text", x = 0, y = 6, label = "bold('744')", 
-           parse = TRUE, colour = unname(ev_pal[1]))
-```
-
-```{r figure3A1, include=FALSE}
-# compare ATCC10231 EV WCL proteins
-f3a3 <- plot_venn(list("EV" = atcc1_ev, "WCL" = atcc1_w), 
-                  use_uniprot = TRUE, type = "plot", 
-                  fontfamily = "sans", 
-                  cex = 0.8,
-                  cat.fontfamily = "sans",
-                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
-                  ext.percent = c(0,20,0),
-                  ext.pos = 45,
-                  ext.dist = -0.05,
-                  ext.length = 0.5,
-                  margin = 0.05)
-
-# ATCC10231 venn
-f3a3 <- as_ggplot(f3a3) + 
-  theme(plot.margin = unit(c(1,0.5,1,0.5), "lines")) + 
-  annotate("text", x = 0.5, y = 0.92, label = "bold('ATCC10231')", parse = TRUE)
-
-# generate volcano plot
-f3b3 <- plot_volcano(data = a1_res, 
-                     p_val = adj.P.Val, 
-                     log2fc = logFC,
-                     group = group, 
-                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
-                     point_size = 0.6, 
-                     label_size = 2, 
-                     x_lim = c(-10, 12), 
-                     y_lim = c(0, 8), 
-                     legend_params = c("left", 11, 8), 
-                     axis_params = c("black", 10)) + 
-  scale_colour_manual(labels = c("EV enriched (108)", "WCL enriched (142)", 
-                                 "Not significant (435)"),
-                      values = unname(ev_pal[c(2,3,1)])) + 
-  annotate("text", x = 8, y = 0.5, label = "bold('ATCC10231')", parse = TRUE) + 
-  annotate("text", x = 3.5, y = 7, label = "bold('106')", 
-           parse = TRUE, colour = unname(ev_pal[2])) + 
-  annotate("text", x = -3.5, y = 7, label = "bold('134')", 
-           parse = TRUE, colour = unname(ev_pal[3])) + 
-  annotate("text", x = 0, y = 6, label = "bold('445')", 
-           parse = TRUE, colour = unname(ev_pal[1]))
-```
-
-```{r figure3Biofilm, include=FALSE}
-# compare DAY286 biofilm EV WCL proteins
-f3a4 <- plot_venn(list("EV" = b_ev, "WCL" = b_wcl), 
-                  use_uniprot = TRUE, type = "plot", 
-                  fontfamily = "sans", 
-                  cex = 0.8, 
-                  cat.fontfamily = "sans", 
-                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
-                  ext.text = TRUE,
-                  ext.percent = c(20,10,0),
-                  ext.pos = c(45,315),
-                  ext.dist = -0.1,
-                  ext.length = 0.5,
-                  margin = 0.05)
-# DAY286 biofilm venn
-f3a4 <- as_ggplot(f3a4) + 
-  theme(plot.margin = unit(c(1,0,1,0), "lines")) + 
-  annotate("text", x = 0.5, y = 0.92, label = "bold('DAY286 biofilm')", 
-           parse = TRUE)
-
-# generate volcano plot
-f3b4 <- plot_volcano(data = biofilm_res, 
-                     p_val = adj.P.Val, 
-                     log2fc = logFC,
-                     group = group, 
-                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
-                     point_size = 0.6, 
-                     label_size = 2, 
-                     x_lim = c(-10, 12), 
-                     y_lim = c(0, 8), 
-                     legend_params = c("left", 11, 8), 
-                     axis_params = c("black", 10)) + 
-  scale_colour_manual(labels = c("EV enriched (95)", "WCL enriched (79)", 
-                                 "Not significant (484)"), 
-                      values = unname(ev_pal[c(2,1,3)]), 
-                      breaks = c("EV up", "WCL up", "not sig")) + 
-  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 B')", parse = TRUE) + 
-  annotate("text", x = 3.5, y = 7, label = "bold('95')", 
-           parse = TRUE, colour = unname(ev_pal[2])) + 
-  annotate("text", x = -3.5, y = 7, label = "bold('79')", 
-           parse = TRUE, colour = unname(ev_pal[3])) + 
-  annotate("text", x = 0, y = 6, label = "bold('484')", 
-           parse = TRUE, colour = unname(ev_pal[1]))
-```
-
-```{r figure3, fig.cap=f3_cap, fig.width=7.1, fig.height=6}
-# draw figure 3
-ggarrange(ggarrange(f3a1, f3a2, f3a3, f3a4, 
-                    labels = c("A", "", "", ""), 
-                    ncol = 4, 
-                    nrow = 1, 
-                    align = "v"), 
-          ggarrange(f3b1, f3b2,
-                    f3b3, f3b4, 
-                    labels = c("B", rep("", 3)), 
-                    ncol = 2, 
-                    nrow = 2, 
-                    align = "hv", 
-                    common.legend = TRUE, 
-                    legend = "right", 
-                    widths = c(1,1), 
-                    vjust = 1), 
-          ncol = 1,
-          nrow = 2, 
-          heights = c(1,2))
-
-f3_cap <- "\\textbf{Differential abundance analysis of proteins identified in 
-           \\textit{C. albicans} EVs and whole cell lysates (WCL).} 
-           \\textit{(A)} Venn diagrams comparing the EV and WCL proteomes from 
-           four \\textit{C. albicans} strains; DAY286 yeast (n = 3), ATCC90028 
-           yeast (n = 3), ATCC10231 yeast (n = 3), and DAY286 biofilm (n = 5). 
-           Whole cell lysates were prepared from the EV source cells. Proteins 
-           were quantified (MaxQuant LFQ intensity) in minimum 2/3 (yeast) and 
-           4/5 (biofilm) biological replicates of EV or WCL. \\textit{(B)} 
-           Volcano plots depicting significantly enriched EV or WCL proteins. 
-           Differential abundance analysis was performed by comparing the mean 
-           normalised LFQ intensities of proteins identified in both EV and 
-           WCL (i.e. proteins in the venn overlap) using the Bioconductor 
-           package \\textit{limma} [@cox2014; @ritchie2015]. Significantly 
-           enriched proteins were identified using a Benjamini-Hochberg 
-           adjusted p-value cut off of 0.01. Counts of significant and 
-           non-significant proteins are indicated on each graph. Proteins with 
-           a log\\textsubscript{2}(FC) greater than 8 are labelled. Data tables 
-           underlying the venn diagrams and volcano plots are provided in 
-           supplemental File S2."
-```
-
-\newpage
-
-```{r figure4Data, include=FALSE}
-# get list of DAY286 yeast EV proteins exclusive and sig. enriched
-# substitute protein names that don't work with FungiFun2
-f4_y_go <- marker_comp[1] %>% 
-  unlist() %>% 
-  strsplit(., ";") %>% 
-  unlist() %>% 
-  gsub("CHS3", "CaO19.4937", .) %>% 
-  gsub("PEP1", "CaO19.3767", .)
-
-# get list of DAY286 biofilm EV proteins exclusive and sig. enriched
-# substitute protein names that don't work with FungiFun2
-f4_b_go <- marker_comp[2] %>% 
-  unlist() %>% 
-  strsplit(., ";") %>% 
-  unlist() %>% 
-  stringi::stri_replace_all_regex(., 
-                                  c("CHS3", "PEP1", "ALS3", 
-                                    "PLB3", "PLB4.5"), 
-                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
-                                    "CaO19.6594", "CaO19.9017"), 
-                                  vectorize_all = FALSE)
-
-# get list of ATCC90028 EV proteins exclusive and sig. enriched
-# substitute protein names that don't work with FungiFun2
-f4_a9_go <- marker_comp[3] %>% 
-  unlist() %>% 
-  strsplit(., ";") %>% 
-  unlist() %>% 
-  stringi::stri_replace_all_regex(., 
-                                  c("CHS3", "PEP1", "ALS3", 
-                                    "PLB3", "PLB4.5", "^MNN2$", 
-                                    "MNN22", "MNN24", "ECM331", 
-                                    "CAM1-1", "FCY21"), 
-                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
-                                    "CaO19.6594", "CaO19.9017", "CaO19.2347", 
-                                    "CaO19.3803", "CaO19.1995", "CaO19.4255", 
-                                    "CaO19.2651", "CaO19.8937"), 
-                                  vectorize_all = FALSE)
-f4_a9_go <- f4_a9_go[!f4_a9_go %in% c("orf19.7397.1", "orf19.7398")]
-
-# get list of ATCC10231 EV proteins exclusive and sig. enriched
-# substitute protein names that don't work with FungiFun2
-f4_a1_go <- marker_comp[4] %>% 
-  unlist() %>% 
-  strsplit(., ";") %>% 
-  unlist() %>% 
-  stringi::stri_replace_all_regex(., 
-                                  c("CHS3", "PEP1", "ALS3", 
-                                    "PLB3", "PLB4.5", "^MNN2$", 
-                                    "MNN22", "MNN24", "ECM331", 
-                                    "CAM1-1"), 
-                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
-                                    "CaO19.6594", "CaO19.9017", "CaO19.2347", 
-                                    "CaO19.3803", "CaO19.1995", "CaO19.4255", 
-                                    "CaO19.2651"), 
-                                  vectorize_all = FALSE)
-```
-
-```{r figure4Plots, include=FALSE}
-# import FungiFun2 GO enrichment results
-f4_y_go_table <- process_fungifun("figures/f4_GO_DAY_Y.csv")
-f4_b_go_table <- process_fungifun("figures/f4_GO_DAY_B.csv")
-f4_a1_go_table <- process_fungifun("figures/f4_GO_ATCC10231.csv")
-f4_a9_go_table <- process_fungifun("figures/f4_GO_ATCC90028.csv")
-
-# define the colour palette
-f4_pal <- c("#6D2077", "#E4002B", "#FFB81C")
-
-# GO term bar plots
-f4_y <- plot_go_bar(f4_y_go_table, c(1:4, 49,52:53,55, 77,79:81), f4_pal) + 
-  annotate("text", x = 12, y = 65, label = "bold('DAY286 Y')", parse = TRUE) + 
-  labs(fill = "GO domain") + 
-  theme(legend.text = element_text(size = 10), 
-        legend.title = element_text(size = 10))
-
-f4_b <- plot_go_bar(f4_b_go_table, c(1:4, 69,71:73, 96:97, 100, 102), f4_pal) + 
-  annotate("text", x = 12, y = 60, label = "bold('DAY286 B')", parse = TRUE)
-
-f4_a9 <- plot_go_bar(f4_a9_go_table, c(1:4, 35,37:38,42, 55:56,58:59), f4_pal) + 
-  annotate("text", x = 12, y = 70, label = "bold('ATCC90028')", parse = TRUE)
-
-f4_a1 <- plot_go_bar(f4_a1_go_table, c(1:4, 63,65:67, 88:91), f4_pal) + 
-  annotate("text", x = 12, y = 70, label = "bold('ATCC10231')", parse = TRUE)
-```
-
-```{r figure4, fig.cap=f4_cap, fig.width=7.2, fig.height=5}
-# draw figure 4
-ggarrange(f4_y, f4_a9, 
-          f4_a1, f4_b, 
-          labels = NULL, 
-          ncol = 2, 
-          nrow = 2, 
-          common.legend = TRUE, 
-          legend = "bottom", 
-          align = "hv")
-
-f4_cap <- "\\textbf{Functional enrichment analyses of the significantly 
-           enriched and exclusive \\textit{C. albicans} EV proteins.} The 
-           online tool FungiFun2 (elbe.hki-jena.de/fungifun) was used to 
-           identify enriched biological process (BP), cellular component (CC), 
-           and molecular function (MF) GO terms [@priebe2015]. A selection of 
-           the most significantly enriched terms for each GO domain are shown. 
-           They are presented top to bottom in order of increasing 
-           Benjamini-Hochberg adjusted p-value. Full lists of enriched GO 
-           terms can be found in supplemental File S3."
-```
-
-\newpage
-
-```{r figure5Data, include=FALSE}
-# figure 5a EV venn
-f5a_comp <- list("DAY Y" = rownames(y_ev), 
-                 "DAY B" = rownames(b_ev),
-                 "ATCC90028" = rownames(atcc9_ev), 
-                 "ATCC10231" = rownames(atcc1_ev))
-f5a_comp <- lapply(f5a_comp, function(x) match_id(x, ref = uniprot, 
-                                                  match = "UP_accession", 
-                                                  new = "CGD_gene_name"))
-
-f5a_venn <- plot_venn(vlist = f5a_comp, use_uniprot = FALSE, type = "plot", 
-                      fontfamily = "sans", 
-                      cat.fontfamily = "sans", 
-                      cex = 1, 
-                      cat.cex = 0.8, 
-                      fill = st_pal[c(1,4,2,3)], 
-                      alpha = c(0.3, 0.3, 0.3, 0.3))
-
-f5a <- as_ggplot(f5a_venn) + 
-  theme(plot.margin = unit(c(0,2,0,2), "lines"))
-
-f5a_overlap <- plot_venn(vlist = f5a_comp, 
-                         use_uniprot = FALSE, type = "df") %>% 
-  filter(..count.. == 403) %>% 
-  pull(..values..) %>% 
-  unlist()
-
-# figure 5b WCL venn
-f5b_comp <- list("DAY Y" = rownames(y_wcl), 
-                 "DAY B" = rownames(b_wcl),
-                 "ATCC90028" = rownames(atcc9_w), 
-                 "ATCC10231" = rownames(atcc1_w))
-f5b_comp <- lapply(f5b_comp, function(x) match_id(x, ref = uniprot, 
-                                                  match = "UP_accession", 
-                                                  new = "CGD_gene_name"))
-
-f5b_venn <- plot_venn(vlist = f5b_comp, use_uniprot = FALSE, type = "plot", 
-                      fontfamily = "sans", 
-                      cat.fontfamily = "sans", 
-                      cex = 1, 
-                      cat.cex = 0.8, 
-                      fill = st_pal[c(1,4,2,3)], 
-                      alpha = c(0.3, 0.3, 0.3, 0.3))
-
-f5b <- as_ggplot(f5b_venn) + 
-  theme(plot.margin = unit(c(0,2,0,2), "lines"))
-
-# MDS data table
-mds_data <- cbind(atcc_de, 
-                  biofilm_de[match(rownames(atcc_de), rownames(biofilm_de)), ])
-
-mds_data <- cbind(mds_data, 
-                  yeast_de[match(rownames(mds_data), rownames(yeast_de)), ])
-
-colnames(mds_data)[13:28] <- c("B_EV1", "B_EV2", "B_EV3", "B_EV4", "B_EV5", 
-                               "B_W1", "B_W2", "B_W3", "B_W4", "B_W5", 
-                               "Y_EV1", "Y_EV2", "Y_EV3", 
-                               "Y_W1", "Y_W2", "Y_W3")
-
-mds_labels <- c(rep("EV", 3), rep("WCL", 3), 
-                rep("EV", 3), rep("WCL", 3), 
-                rep("EV", 5), rep("WCL", 5), 
-                rep("EV", 3), rep("WCL", 3))
-
-# figure 5c MDS [dim1, dim2]
-f5c <- plot_mds(mds_data, mat_labels = mds_labels, 
-                shape_size = 3, dim.plot = c(1,2)) + 
-  scale_x_continuous(limits = c(-1.5, 2.5), 
-                     expand = c(0,0)) + 
-  scale_y_continuous(limits = c(-1.5, 2.5), 
-                     expand = c(0,0)) + 
-  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
-                    values = st_pal[c(3, 2, 4, 1)], 
-                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
-                    guide = "legend") + 
-  scale_shape_manual(values = c(22,24)) + 
-  theme_bw() + 
-  theme(legend.title = element_blank(),
-        legend.position = "right", 
-        legend.text = element_text(size = 8), 
-        legend.direction = "vertical") + 
-  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
-  xlab(label = "Dimension 1") + 
-  ylab(label = "Dimension 2")
-
-# figure 5d MDS [dim3, dim2]
-f5d <- plot_mds(mds_data, mat_labels = mds_labels, 
-                shape_size = 3, dim.plot = c(3,2)) + 
-  scale_x_continuous(limits = c(-1.5, 2.5), 
-                     expand = c(0,0)) + 
-  scale_y_continuous(limits = c(-1.5, 2.5), 
-                     expand = c(0,0)) + 
-  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
-                    values = st_pal[c(3, 2, 4, 1)], 
-                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
-                    guide = "legend") + 
-  scale_shape_manual(values = c(22,24)) + 
-  theme_bw() + 
-  theme(legend.title = element_blank(),
-        legend.position = "right", 
-        legend.text = element_text(size = 8), 
-        legend.direction = "vertical", 
-        legend.margin = margin(t = 0, r = 0, b = 0, l = 0.1), 
-        legend.box.margin = margin(t = -10, r = -6, b = -10, l = -10)) + 
-  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
-  xlab(label = "Dimension 3") + 
-  ylab(label = "Dimension 2")
-```
-
-```{r figure5, fig.cap=f5_cap, fig.width=7.1, fig.height=5}
-ggarrange(ggarrange(f5a, f5b,
-                    labels = c("A", "B"),
-                    ncol = 2,
-                    nrow = 1),
-          ggarrange(f5c, f5d,
-                    labels = c("C", "D"),
-                    ncol = 2,
-                    nrow = 1, 
-                    common.legend = TRUE,
-                    legend = "right", 
-                    align = "hv"),
-          labels = NULL,
-          ncol = 1,
-          nrow = 2,
-          heights = c(2, 3))
-
-f5_cap <- "\\textbf{Combined comparison of \\textit{C. albicans} proteomes.} 
-           \\textit{(A)} Venn diagram comparing four \\textit{C. albicans} EV 
-           proteomes. Lists of proteins present in the centre and right 
-           partitions of each venn diagram in Figure \\@ref(fig:figure3)A were 
-           compared to identify proteins present in all four datasets. 
-           \\textit{(B)} Venn diagram comparing four \\textit{C. albicans} WCL 
-           proteomes. Lists of proteins present in the centre and left 
-           partitions of each venn diagram in Figure \\@ref(fig:figure3)A were 
-           compared to identify proteins present in all four datasets. The data 
-           tables underlying Figures \\@ref(fig:figure5)A and 
-           \\@ref(fig:figure5)B are provided in supplemental File S4. 
-           \\textit{(C)} Multidimensional scaling (MDS) plot of each LC-MS/MS 
-           biological replicate sample with the first 2 dimensions shown. 
-           Pairwise distance between samples approximately indicates the 
-           log\\textsubscript{2}(FC) between samples. \\textit{limma} was used 
-           to generate the MDS plots [@ritchie2015]. \\textit{(D)} MDS plot of 
-           each LC-MS/MS biological replicate sample with the second and third 
-           dimensions shown."
-```
-
-\newpage
-
-```{r figure6Heatmap, include=FALSE}
-# figure 6 heatmap
-f6_table <- a9_res %>% 
-  select(logFC, CGD_gene_name) %>% 
-  full_join(., select(a1_res, logFC, CGD_gene_name), 
-            by = "CGD_gene_name") %>% 
-  full_join(., select(yeast_res, logFC, CGD_gene_name), 
-            by = "CGD_gene_name") %>% 
-  full_join(., select(biofilm_res, logFC, CGD_gene_name), 
-            by = "CGD_gene_name") %>% 
-  rename(a9_lfc = logFC.x, 
-         a1_lfc = logFC.y, 
-         y_lfc = logFC.x.x, 
-         b_lfc = logFC.y.y) %>% 
-  select(CGD_gene_name, everything()) %>% 
-  filter(CGD_gene_name %in% f5a_overlap)
-
-# filter for rows with min 1/4 valid values
-# otherwise clustering will not work
-f6_table_filt <- f6_table %>% 
-  filter_at(.vars = vars(contains("lfc")), 
-            any_vars(!is.na(.))) %>% 
-  tibble::column_to_rownames(var = "CGD_gene_name") %>% 
-  as.matrix()
-
-# excluded proteins
-f6_table_excl <- f6_table %>% 
-  filter_at(.vars = vars(contains("lfc")), 
-            all_vars(is.na(.))) %>% 
-  tibble::column_to_rownames(var = "CGD_gene_name") %>% 
-  as.matrix()
-
-# heatmap legend parameters
-f6_params <- list(color_bar = "continuous", 
-                  title = expression(bold(log[2]("FC"))), 
-                  direction = "horizontal", 
-                  legend_width = unit(2, "cm"), 
-                  title_position = "lefttop", 
-                  title_gp = grid::gpar(colour = "black", 
-                                        fontsize = 5), 
-                  labels_gp = grid::gpar(colour = "black", 
-                                         fontsize = 5), 
-                  at = seq(-6, 6, 2))
-
-# plot heatmap
-f6_htmp <- plot_heatmap(mt = f6_table_filt, 
-                        plot = FALSE,
-                        df = FALSE, 
-                        data_type = "log2fc", 
-                        clust_fun = "gower", 
-                        split_type = "cutree", 
-                        k = 5, 
-                        cluster_split = FALSE, 
-                        split_order = c(3, 1, 4, 2, 5), 
-                        colour_lims = c(-4, 4),
-                        column_labels = c("ATCC90028", "ATCC10231", 
-                                          "DAY286 Y", "DAY286 B"), 
-                        col_name_fontsize = 6, 
-                        column_names_rot = 45, 
-                        row_title_fontsize = 6, 
-                        row_title_rot = 0, 
-                        row_title = c("1", "2", "3", "4", "5"), 
-                        heatmap_legend_param = f6_params)
-
-# save heatmap as pdf file for editing in inkscape
-# not run in rmarkdown but manually in console
-# pdf(file = "figures/figure5_unf.pdf", width = 1.7, height = 4)
-# ComplexHeatmap::draw(f5_htmp, heatmap_legend_side = "bottom")
-# dev.off()
-```
-
-```{r figure6Table, include=FALSE}
-#  list of proteins for heatmap table in order of appearance in heatmap
-f6_clusters <- plot_heatmap(mt = f6_table_filt, 
-                            plot = FALSE,
-                            df = TRUE, 
-                            data_type = "log2fc", 
-                            clust_fun = "gower", 
-                            split_type = "cutree", 
-                            k = 5, 
-                            cluster_split = FALSE) %>% 
-  mutate(cluster = recode(cluster, 
-                          "1" = 2, "2" = 4, "3" = 1, "4" = 3, "5" = 5)) %>% 
-  arrange(cluster)
-
-# extract identifiers from each cluster
-f6_clust1 <- f6_clusters %>% 
-  filter(cluster == 1) %>% 
-  mutate(id = gsub("CHS3", "CaO19.4937", id)) %>% 
-  pull(id)
-
-f6_clust2 <- f6_clusters %>% 
-  filter(cluster == 2) %>% 
-  mutate(id = gsub("PEP1", "CaO19.3767", id)) %>% 
-  pull(id) %>% 
-  stringr::str_extract_all(., "[^;]+") %>% 
-  unlist()
-
-f6_clust3 <- f6_clusters %>% 
-  filter(cluster == 3) %>% 
-  pull(id)
-
-f6_clust4 <- f6_clusters %>% 
-  filter(cluster == 4) %>% 
-  pull(id)
-
-# cluster 5 has too many proteins to fit in table
-# but GO enrichment still possible
-f6_clust5 <- f6_clusters %>% 
-  filter(cluster == 5) %>% 
-  mutate(id = gsub("ALA1", "CaO19.5746", id), 
-         id = gsub("MDH1", "CaO19.7481", id), 
-         id = gsub("RPS1", "CaO19.3002", id), 
-         id = gsub("TSA1", "CaO19.7417", id)) %>% 
-  pull(id) %>% 
-  stringr::str_extract_all(., "[^;]+") %>% 
-  unlist() %>% 
-  unique()
-
-# cluster 6 is proteins that could not be clustered
-# because all 4 log2FCs = NA
-f6_clust6 <- sort(rownames(f6_table_excl))
-
-# import FungiFun2 results
-f6_go1 <- process_fungifun("figures/f6_GO_clust1.csv") %>% 
-  mutate(Prot.found = gsub("CaO19.4937", "CHS3", Prot.found))
-
-# issue with PEP1, ambiguous ID in FungiFun, used CaO19.3767 as identifier
-f6_go2 <- process_fungifun("figures/f6_GO_clust2.csv") %>% 
-  mutate(Prot.found = gsub("CaO19.3767", "PEP1", Prot.found))
-
-f6_go3 <- process_fungifun("figures/f6_GO_clust3.csv")
-
-# issue with CHS3, ambiguous ID in FungiFun, used CaO19.4937 as identifier
-f6_go4 <- process_fungifun("figures/f6_GO_clust4.csv")
-
-# issue with ALA1, MDH1, used CaO19.5746 and CaO19.7481 as identifiers
-f6_go5 <- process_fungifun("figures/f6_GO_clust5.csv") %>% 
-  mutate(Prot.found = gsub("CaO19.5746", "ALA1", Prot.found), 
-         Prot.found = gsub("CaO19.7481", "MDH1", Prot.found), 
-         Prot.found = gsub("CaO19.3002", "RPS1", Prot.found), 
-         Prot.found = gsub("CaO19.7417", "TSA1", Prot.found))
-
-f6_go6 <- process_fungifun("figures/f6_GO_clust6.csv")
-```
-
-```{r figure6, fig.cap=f6_cap, fig.height=6}
-f6 <- png::readPNG("figures/figure6.png")
-
-# draw figure 6
-ggplot() + 
-  background_image(f6) + 
-  theme(plot.margin = margin(t = 0.1, l = 0.1, r = 0.1, b = 0.1, 
-                             unit = "inches"))
-
-f6_cap <- "\\textbf{Identification of commonly enriched EV proteins across 
-           different \\textit{C. albicans} strains.} Heatmap of proteins 
-           (n = 403) identified in all four EV samples (venn overlap in Figure 
-           \\@ref(fig:figure5)A). Each column represents a 
-           \\textit{C. albicans} strain and each row represents a protein. The 
-           colours indicate the log\\textsubscript{2}(FC) of the protein for 
-           that particular strain; red is EV enriched, blue is EV depleted, and 
-           black is EV exclusive. Unsupervised clustering of rows and columns 
-           was performed using Gower's formula via the daisy function from the 
-           R package \\textit{cluster} [@maechler2019]. Proteins which were 
-           exclusive to EVs from all four strains could not be clustered and 
-           were seperated prior to clustering, in the group designated 
-           \`\`cluster 6\". Functional enrichment analyses were performed on 
-           the heatmap protein clusters using the online tool FungiFun2 
-           [@priebe2015]. A selection of significantly enriched GO terms are 
-           presented in the table inset. Lists of the proteins identified in 
-           each cluster are shown and are also available in supplemental 
-           File S5."
-```
-
-\newpage
-
-```{r figure7Data, include=FALSE}
-f7a_venn <- plot_venn(vlist = marker_comp, use_uniprot = FALSE, type = "plot", 
-                      fontfamily = "sans", 
-                      cat.fontfamily = "sans", 
-                      cex = 0.9, 
-                      cat.cex = 0.8, 
-                      fill = st_pal[c(1,4,2,3)], 
-                      alpha = c(0.3, 0.3, 0.3, 0.3), 
-                      sub = "EV exclusive + sig. enriched", 
-                      sub.fontfamily = "sans", 
-                      sub.pos = c(0.5, 1.05), 
-                      margin = 0.05)
-
-f7a <- as_ggplot(f7a_venn) + 
-  theme(plot.margin = unit(c(1.2,0,0,0), "lines"))
-
-wcl_comp <- list("DAY Y" = yeast_res %>% 
-                   filter(group == "WCL up" | group == "WCL ex") %>% 
-                   pull(CGD_gene_name), 
-                 "DAY B" = biofilm_res %>% 
-                   filter(group == "WCL up" | group == "WCL ex") %>% 
-                   pull(CGD_gene_name),
-                 "ATCC90028" = a9_res %>% 
-                   filter(group == "A9_W up" | group == "A9_W ex") %>% 
-                   pull(CGD_gene_name), 
-                 "ATCC10231" = a1_res %>% 
-                   filter(group == "A1_W up" | group == "A1_W ex") %>% 
-                   pull(CGD_gene_name))
-
-f7b_venn <- plot_venn(vlist = wcl_comp, use_uniprot = FALSE, type = "plot", 
-                      fontfamily = "sans", 
-                      cat.fontfamily = "sans", 
-                      cex = 0.9, 
-                      cat.cex = 0.8, 
-                      fill = st_pal[c(1,4,2,3)], 
-                      alpha = c(0.3, 0.3, 0.3, 0.3), 
-                      sub = "WCL exclusive + sig. enriched", 
-                      sub.fontfamily = "sans", 
-                      sub.pos = c(0.5, 1.05), 
-                      margin = 0.05)
-
-f7b <- as_ggplot(f7b_venn) + 
-  theme(plot.margin = unit(c(1.2,0,0,0), "lines"))
-```
-
-```{r figure7, fig.cap=f7_cap, fig.width=2.5, fig.height=4}
-ggarrange(f7a, f7b, 
-          labels = c("A", "B"), 
-          ncol = 1,
-          nrow = 2)
-
-f7_cap <- "\\textbf{Identification of common signficantly enriched or exclusive 
-           \\textit{C. albicans} EV and WCL proteins.} Proteins identified as 
-           significantly enriched or exclusive to EVs in Figure 
-           \\@ref(fig:figure3) were compared to select those which were common 
-           to all 4 datasets. 43 proteins were identified as potential positive 
-           EV protein markers and 52 proteins as potential negative EV protein 
-           markers. The data tables underlying Figure 
-           \\@ref(fig:figure7) are provided in supplemental File S4. Details of 
-           the 43 positive EV protein marker candidates and 52 negative 
-           candidates can be found in Table \\@ref(tab:table1) and supplemental 
-           Table S2 respectively."
-```
-
-\newpage
-
-```{r figure8, fig.cap=f8_cap, fig.width=3.5, fig.height=2.8}
-f8_cap <- "\\textbf{Eighteen best potential \\textit{C. albicans} positive EV 
-           protein markers.} These proteins are those underlined in Table 
-           \\@ref(tab:table1). They are are enriched or exclusive to EVs 
-           isolated from all of the \\textit{C. albicans} strains investigated 
-           in this study. The proteins fit within the EV biomarker categories 
-           1a, 2a, and 2b from MISEV2018 which includes transmembrane, 
-           GPI-anchored, and cytosolic proteins that are EV enriched 
-           [@thery2018]."
-
-f8 <- png::readPNG("figures/figure8.png")
-
-ggplot() + 
-  background_image(f8)
-```
-
-\newpage
-
-```{r figure9, fig.cap=f9_cap, fig.width=7.2, fig.height=6}
-f9_cap <- "\\textbf{Predicted topology and palmitoylation sites of 
-           \\textit{C. albicans} MCC/eisosome proteins SUR7 and orf19.6741 
-           compared to the human tetraspanin CD81.} The presence of 
-           transmembrane (TM) domains and palmitoylation sites shown on the 
-           left side of the figure were predicted using the online tools 
-           TOPCONS2 (topcons.cbr.su.se) [@tsirigos2015] and CSS-PALM 4.0 
-           (csspalm.biocuckoo.org) [@ren2008] respectively. For CD81, 
-           palmitoylation sites experimentally determined in previous 
-           literature are shown [@delandre2009]. The right side of the figure 
-           shows a cartoon representation of the TOPCONS2 consensus topology 
-           prediction for the three proteins as well as the crystal structure 
-           of CD81 (PDB: 5TCX) [@zimmerman2016]."
-
-f9 <- png::readPNG("figures/figure9.png")
-
-ggplot() + 
-  background_image(f9)
-```
+<div id="refs"></div>

### 2019-06-18 README.Rmd
Fix reference tables
Also:
 - Complete yeast_analysis.R script

 - Update bibliography

 - Fix `plot_venn` function
Adjust main README.md

@@
 ```{r, echo = FALSE}
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  comment = "#>",
-  fig.path = "README-"
-)
+knitr::opts_chunk$set(collapse = TRUE,
+                      comment = "#>")
 ```
@@
 
+![GitHub last commit](https://img.shields.io/github/last-commit/csdaw/candidaev.svg?style=popout)
+
 This repository contains the research compendium for our paper:
 
-> Authors, (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>
+> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Anderson, M. A., 
+Bleackley, M. R. (2019) Sur7 family proteins are putative markers for
+_Candida albicans_ extracellular vesicles. Mol. Cell. Proteomics, submitted.
 
-The compendium includes all the data, code, and text associated with the publication.
-It is structured as an R package to facilitate reproducilibity and distribution.
-The principles and motivations behind using research compendiums for academic 
-research is detailed in [Marwick et al. (2017)](https://doi.org/10.1080/00031305.2017.1375986).
+It has been permanently archived at Zenodo with the DOI shown above.
+
+The compendium includes all the data, code, and text associated with the 
+publication. It is structured as an R package to facilitate reproducilibity and 
+distribution. The principles and motivations behind using research compendiums 
+for academic research is detailed in 
+[Marwick et al. (2018)](https://doi.org/10.1080/00031305.2017.1375986).
 
@@
 production of this compendium.
+
+### Citation
+
+Please cite this compendium as:
+
+> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Anderson, M. A., 
+Bleackley, M. R. (2019) Research compendium for: _Sur7 family proteins are_
+_putative markers for_ Candida albicans _extracellular vesicles_, 2019. 
+Version x.x.x. Zenodo. URL.
 
@@
     .
-    ├── /R                   # Script files containing reused functions
-    ├── /analysis            # Full analysis report and scripts
-    ├── /data                # Raw, cleaned, external, and results data
-    ├── /manuscript          # Final manuscript and associated files
+    ├── /R                   # Script files for functions and included data
+    ├── /data-raw            # Raw data used (but not modified) in analyses
+    ├── /data                # Data tables installed with package
+    ├── /inst/manuscript     # Final submitted manuscript and supplemental files
+    ├── /man                 # Auto-generated documentation for functions and included data
+    ├── /vignettes           # Detailed examples of how analyses were performed
     ├── .Rbuildignore        # List of files and directories to ignore during R package build
+    ├── .gitattributes       # List of files for github/linguist to ignore
     ├── .gitignore           # List of files to ignore during git commit
@@
 
-### How to cite
+### Accessing the compendium
 
-Please cite this compendium as:
+#### 1. Downloading directly from GitHub
+You can download the compendium as a zip from from this URL: 
+<https://github.com/csdaw/candidaev/archive/master.zip>. 
+Note that the contents of `/data-raw` is not installed when the package is 
+installed but instructions for downloaded just these files is provided
+[here](https://github.com/csdaw/candidaev/tree/master/data-raw).
 
-> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Title of paper'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+#### 2. Cloning via `git`
 
-### How to download or install
+#### 3. Installing the package using R and `devtools`
 
-You can download the compendium as a zip from from this URL: <https://github.com/csdaw/candidaev/archive/master.zip>
-
-Or you can install this compendium as an R package `candidaev` from GitHub with:
-```{r gh-installation, eval = FALSE}
+This research compendium can be installed as an R package `candidaev` from 
+GitHub using `devtools`:
+```{r gh-install, eval = FALSE}
 # install.packages("devtools")
@@
 ```
-### Licenses
 
-**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
+### Using the `candidaev` package
 
-**Code :** See the [DESCRIPTION](DESCRIPTION) file
+### R session information
 
-**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
+The system on which this document was compiled was running 
+pandoc v`r rmarkdown::pandoc_version()`. Here is output of 
+`sessionInfo()`.
+
+```{r sessionInfo, echo=FALSE}
+sessionInfo()
+```

### 2019-06-27 inst/manuscript/manuscript.Rmd
Fix yeast sample labels in manuscript
Change figure 1 to figure S1
Also:
 - Update title, running title, authors, affiliations, corresponding
   author

@@
 title: | 
-   **Defining protein markers for *Candida albicans* extracellular vesicles**
+   **Protein markers for *Candida albicans* EVs include claudin-like Sur7 
+   family proteins and GTPases**
 author: | 
-   *Charlotte Dawson^a^, Mark Bleackley^a^, Donovan Garcia Ceron^a^, 
-   Marilyn Anderson^a^*
+   | Charlotte Dawson^a^, Donovan Garcia Ceron^a^, Harinda Rajapaksha^b^, 
+     Pierre Faou^b^,
+   | Marilyn Anderson^a^, Mark Bleackley^a^
 date: | 
-   *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
-   Molecular Science, La Trobe University, Victoria, 3086, Australia*
+   | *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
+     Molecular Science, La Trobe University, 
+     Melbourne, 3086, Victoria, Australia*
+   | *^b^La Trobe Comprehensive Proteomics Platform, La Trobe Institute for 
+     Molecular Science, La Trobe University, Melbourne, 
+     3086, Victoria, Australia*
 output: 
@@
   - \pagestyle{fancy}
-  - \fancyhead[L]{This is the running title it is rather long}
+  - \fancyhead[L]{Defining \textit{Candida albicans} EV protein markers}
   - \setlength{\headheight}{15pt}
@@
 
-**Running title:** Running title goes here
-
-**Corresponding author:**
+**Corresponding author:** Mark Bleackley, m.bleackley@latrobe.edu.au
+
+**Running title:** Defining _Candida albicans_ EV protein markers
 
@@
 # drop EV_1 and WCL_1 samples
-yeast_lfq2 <- yeast_lfq[, !colnames(yeast_lfq) %in% c("EV_1", "WCL_1")]
+yeast_lfq2 <- yeast_lfq[, !colnames(yeast_lfq) %in% c("EV_0", "WCL_0")]
 
@@
              best candidates for positive EV markers according to the 
-             criteria depicted in Figure \\ref{fig:figure1}."
+             criteria depicted in supplemental Figure S1."
 
@@
 
-```{r figure1, fig.cap=f1_cap, fig.width=5.45, fig.height=6}
-# construct figure 1
-f1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
-           proteomic analysis of \\textit{C. albicans} EVs and the selection 
-           of EV protein markers.} Steps 1 to 6 were performed for each of the 
-           four strains examined in this study: DAY286 yeast, ATCC90028 yeast, 
-           ATCC10231 yeast, and DAY286 biofilm. The results from the four 
-           seperate analyses were combined (step 7) to identify proteins which 
-           commonly appeared as EV marker candidates. The MISEV2018 criteria 
-           for protein content-based EV characterisation and other 
-           considerations were used to select the best \\textit{C. albicans} 
-           EV marker proteins."
-
-f1 <- png::readPNG("figures/figure1.png")
-
-# draw figure 1
-ggplot() + 
-  background_image(f1)
-```
-
-\newpage
-
-```{r figure2Data, include=FALSE}
+```{r figure1Data, include=FALSE}
 # construct data.frame with nta experiment info
@@
 
-```{r figure2plots, include=FALSE}
-# construct figure 2a
-f2a_img <- png::readPNG("figures/figure2a.png")
-
-f2a <- ggplot() + 
-  background_image(f2a_img) + 
+```{r figure1plots, include=FALSE}
+# construct figure 1a
+f1a_img <- png::readPNG("figures/figure1a.png")
+
+f1a <- ggplot() + 
+  background_image(f1a_img) + 
   theme(plot.margin = margin(t = 0.3, l = 0, r = 0, b = 0, unit = "inches"))
 
-# construct figure 2b
-f2b <- nta_bioavg %>% 
+# construct figure 1b
+f1b <- nta_bioavg %>% 
   ggplot(aes(x = particle_size, y = Bio_rep_mean, colour = Strain)) + 
@@
 
-f2c <- nta_total %>% 
+f1c <- nta_total %>% 
   ggboxplot(x = "Strain", y = "part_per_prot", 
@@
             ylab = expression("Particles /"~paste(mu,g)~"protein"))
-f2c <- ggpar(f2c, 
+f1c <- ggpar(f1c, 
              yscale = "log10", 
@@
 
-```{r figure2, fig.cap=f2_cap, fig.width=7.1, fig.height=4}
-# draw figure 2
-ggarrange(f2a, 
-          ggarrange(f2b, f2c, 
+```{r figure1, fig.cap=f1_cap, fig.width=7.1, fig.height=4}
+# draw figure 1
+ggarrange(f1a, 
+          ggarrange(f1b, f1c, 
                     labels = c("B", "C"), 
@@
 
-f2_cap <- "\\textbf{Characterisation and quantification of EVs from different 
+f1_cap <- "\\textbf{Characterisation and quantification of EVs from different 
            \\textit{C. albicans} strains.} \\textit{(A)} Representative TEM 
@@
            nm. Plots for the individual biological replicates are presented in 
-           supplemental Figure S1. \\textit{(C)} Comparison of the ratio of 
+           supplemental Figure S2. \\textit{(C)} Comparison of the ratio of 
            particle concentration to protein concentration of the EV fraction, 
@@
 
-```{r figure3Yeast, include=FALSE}
+```{r figure2Yeast, include=FALSE}
 # compare DAY286 yeast EV WCL proteins
-f3a1 <- plot_venn(list("EV" = y_ev, "WCL" = y_wcl), 
+f2a1 <- plot_venn(list("EV" = y_ev, "WCL" = y_wcl), 
                   use_uniprot = TRUE, type = "plot", 
@@
 # DAY286 yeast venn
-f3a1 <- as_ggplot(f3a1) + 
+f2a1 <- as_ggplot(f2a1) + 
   theme(plot.margin = unit(c(1,0.5,1,0.5), "lines")) + 
@@
 # generate volcano plot
-f3b1 <- plot_volcano(data = yeast_res, 
+f2b1 <- plot_volcano(data = yeast_res, 
                      p_val = adj.P.Val, 
@@
 
-```{r figure3A9, include=FALSE}
+```{r figure2A9, include=FALSE}
 # compare ATCC90028 EV WCL proteins
-f3a2 <- plot_venn(list("EV" = atcc9_ev, "WCL" = atcc9_w), 
+f2a2 <- plot_venn(list("EV" = atcc9_ev, "WCL" = atcc9_w), 
                   use_uniprot = TRUE, type = "plot", 
@@
 # ATCC90028 venn
-f3a2 <- as_ggplot(f3a2) + 
+f2a2 <- as_ggplot(f2a2) + 
   theme(plot.margin = unit(c(1,0,1,0.5), "lines")) + 
@@
 # generate volcano plot
-f3b2 <- plot_volcano(data = a9_res, 
+f2b2 <- plot_volcano(data = a9_res, 
                      p_val = adj.P.Val, 
@@
 
-```{r figure3A1, include=FALSE}
+```{r figure2A1, include=FALSE}
 # compare ATCC10231 EV WCL proteins
-f3a3 <- plot_venn(list("EV" = atcc1_ev, "WCL" = atcc1_w), 
+f2a3 <- plot_venn(list("EV" = atcc1_ev, "WCL" = atcc1_w), 
                   use_uniprot = TRUE, type = "plot", 
@@
 # ATCC10231 venn
-f3a3 <- as_ggplot(f3a3) + 
+f2a3 <- as_ggplot(f2a3) + 
   theme(plot.margin = unit(c(1,0.5,1,0.5), "lines")) + 
@@
 # generate volcano plot
-f3b3 <- plot_volcano(data = a1_res, 
+f2b3 <- plot_volcano(data = a1_res, 
                      p_val = adj.P.Val, 
@@
 
-```{r figure3Biofilm, include=FALSE}
+```{r figure2Biofilm, include=FALSE}
 # compare DAY286 biofilm EV WCL proteins
-f3a4 <- plot_venn(list("EV" = b_ev, "WCL" = b_wcl), 
+f2a4 <- plot_venn(list("EV" = b_ev, "WCL" = b_wcl), 
                   use_uniprot = TRUE, type = "plot", 
@@
 # DAY286 biofilm venn
-f3a4 <- as_ggplot(f3a4) + 
+f2a4 <- as_ggplot(f2a4) + 
   theme(plot.margin = unit(c(1,0,1,0), "lines")) + 
@@
 # generate volcano plot
-f3b4 <- plot_volcano(data = biofilm_res, 
+f2b4 <- plot_volcano(data = biofilm_res, 
                      p_val = adj.P.Val, 
@@
 
-```{r figure3, fig.cap=f3_cap, fig.width=7.1, fig.height=6}
-# draw figure 3
-ggarrange(ggarrange(f3a1, f3a2, f3a3, f3a4, 
+```{r figure2, fig.cap=f2_cap, fig.width=7.1, fig.height=6}
+# draw figure 2
+ggarrange(ggarrange(f2a1, f2a2, f2a3, f2a4, 
                     labels = c("A", "", "", ""), 
@@
                     align = "v"), 
-          ggarrange(f3b1, f3b2,
-                    f3b3, f3b4, 
+          ggarrange(f2b1, f2b2,
+                    f2b3, f2b4, 
                     labels = c("B", rep("", 3)), 
@@
 
-f3_cap <- "\\textbf{Differential abundance analysis of proteins identified in 
+f2_cap <- "\\textbf{Differential abundance analysis of proteins identified in 
            \\textit{C. albicans} EVs and whole cell lysates (WCL).} 
@@
 
-```{r figure4Data, include=FALSE}
+```{r figure3Data, include=FALSE}
 # get list of DAY286 yeast EV proteins exclusive and sig. enriched
 # substitute protein names that don't work with FungiFun2
-f4_y_go <- marker_comp[1] %>% 
+f3_y_go <- marker_comp[1] %>% 
   unlist() %>% 
@@
 # substitute protein names that don't work with FungiFun2
-f4_b_go <- marker_comp[2] %>% 
+f3_b_go <- marker_comp[2] %>% 
   unlist() %>% 
@@
 # substitute protein names that don't work with FungiFun2
-f4_a9_go <- marker_comp[3] %>% 
+f3_a9_go <- marker_comp[3] %>% 
   unlist() %>% 
@@
                                   vectorize_all = FALSE)
-f4_a9_go <- f4_a9_go[!f4_a9_go %in% c("orf19.7397.1", "orf19.7398")]
+f3_a9_go <- f3_a9_go[!f3_a9_go %in% c("orf19.7397.1", "orf19.7398")]
 
@@
 # substitute protein names that don't work with FungiFun2
-f4_a1_go <- marker_comp[4] %>% 
+f3_a1_go <- marker_comp[4] %>% 
   unlist() %>% 
@@
 # import FungiFun2 GO enrichment results
-f4_y_go_table <- process_fungifun("figures/f4_GO_DAY_Y.csv")
-f4_b_go_table <- process_fungifun("figures/f4_GO_DAY_B.csv")
-f4_a1_go_table <- process_fungifun("figures/f4_GO_ATCC10231.csv")
-f4_a9_go_table <- process_fungifun("figures/f4_GO_ATCC90028.csv")
+f3_y_go_table <- process_fungifun("figures/f3_GO_DAY_Y.csv")
+f3_b_go_table <- process_fungifun("figures/f3_GO_DAY_B.csv")
+f3_a1_go_table <- process_fungifun("figures/f3_GO_ATCC10231.csv")
+f3_a9_go_table <- process_fungifun("figures/f3_GO_ATCC90028.csv")
 
 # define the colour palette
-f4_pal <- c("#6D2077", "#E4002B", "#FFB81C")
+f3_pal <- c("#6D2077", "#E4002B", "#FFB81C")
 
 # GO term bar plots
-f4_y <- plot_go_bar(f4_y_go_table, c(1:4, 49,52:53,55, 77,79:81), f4_pal) + 
+f3_y <- plot_go_bar(f3_y_go_table, c(1:4, 49,52:53,55, 77,79:81), f3_pal) + 
   annotate("text", x = 12, y = 65, label = "bold('DAY286 Y')", parse = TRUE) + 
@@
 
-f4_b <- plot_go_bar(f4_b_go_table, c(1:4, 69,71:73, 96:97, 100, 102), f4_pal) + 
+f3_b <- plot_go_bar(f3_b_go_table, c(1:4, 69,71:73, 96:97, 100, 102), f3_pal) + 
   annotate("text", x = 12, y = 60, label = "bold('DAY286 B')", parse = TRUE)
 
-f4_a9 <- plot_go_bar(f4_a9_go_table, c(1:4, 35,37:38,42, 55:56,58:59), f4_pal) + 
+f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:4, 35,37:38,42, 55:56,58:59), f3_pal) + 
   annotate("text", x = 12, y = 70, label = "bold('ATCC90028')", parse = TRUE)
 
-f4_a1 <- plot_go_bar(f4_a1_go_table, c(1:4, 63,65:67, 88:91), f4_pal) + 
+f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4, 63,65:67, 88:91), f3_pal) + 
   annotate("text", x = 12, y = 70, label = "bold('ATCC10231')", parse = TRUE)
@@
 
-```{r figure4, fig.cap=f4_cap, fig.width=7.2, fig.height=5}
+```{r figure3, fig.cap=f3_cap, fig.width=7.2, fig.height=5}
 # draw figure 4
-ggarrange(f4_y, f4_a9, 
-          f4_a1, f4_b, 
+ggarrange(f3_y, f3_a9, 
+          f3_a1, f3_b, 
           labels = NULL, 
@@
 
-f4_cap <- "\\textbf{Functional enrichment analyses of the significantly 
+f3_cap <- "\\textbf{Functional enrichment analyses of the significantly 
            enriched and exclusive \\textit{C. albicans} EV proteins.} The 
@@
 
-```{r figure5Data, include=FALSE}
-# figure 5a EV venn
-f5a_comp <- list("DAY Y" = rownames(y_ev), 
+```{r figure4Data, include=FALSE}
+# figure 4a EV venn
+f4a_comp <- list("DAY Y" = rownames(y_ev), 
                  "DAY B" = rownames(b_ev),
@@
                  "ATCC10231" = rownames(atcc1_ev))
-f5a_comp <- lapply(f5a_comp, function(x) match_id(x, ref = uniprot, 
+f4a_comp <- lapply(f4a_comp, function(x) match_id(x, ref = uniprot, 
                                                   match = "UP_accession", 
@@
 
-f5a_venn <- plot_venn(vlist = f5a_comp, use_uniprot = FALSE, type = "plot", 
+f4a_venn <- plot_venn(vlist = f4a_comp, use_uniprot = FALSE, type = "plot", 
                       fontfamily = "sans", 
@@
 
-f5a <- as_ggplot(f5a_venn) + 
+f4a <- as_ggplot(f4a_venn) + 
   theme(plot.margin = unit(c(0,2,0,2), "lines"))
 
-f5a_overlap <- plot_venn(vlist = f5a_comp, 
+f4a_overlap <- plot_venn(vlist = f4a_comp, 
                          use_uniprot = FALSE, type = "df") %>% 
@@
 
-# figure 5b WCL venn
-f5b_comp <- list("DAY Y" = rownames(y_wcl), 
+# figure 4b WCL venn
+f4b_comp <- list("DAY Y" = rownames(y_wcl), 
                  "DAY B" = rownames(b_wcl),
@@
                  "ATCC10231" = rownames(atcc1_w))
-f5b_comp <- lapply(f5b_comp, function(x) match_id(x, ref = uniprot, 
+f4b_comp <- lapply(f4b_comp, function(x) match_id(x, ref = uniprot, 
                                                   match = "UP_accession", 
@@
 
-f5b_venn <- plot_venn(vlist = f5b_comp, use_uniprot = FALSE, type = "plot", 
+f4b_venn <- plot_venn(vlist = f4b_comp, use_uniprot = FALSE, type = "plot", 
                       fontfamily = "sans", 
@@
 
-f5b <- as_ggplot(f5b_venn) + 
+f4b <- as_ggplot(f4b_venn) + 
   theme(plot.margin = unit(c(0,2,0,2), "lines"))
@@
 
-# figure 5c MDS [dim1, dim2]
-f5c <- plot_mds(mds_data, mat_labels = mds_labels, 
+# figure 4c MDS [dim1, dim2]
+f4c <- plot_mds(mds_data, mat_labels = mds_labels, 
                 shape_size = 3, dim.plot = c(1,2)) + 
@@
 
-# figure 5d MDS [dim3, dim2]
-f5d <- plot_mds(mds_data, mat_labels = mds_labels, 
+# figure 4d MDS [dim3, dim2]
+f4d <- plot_mds(mds_data, mat_labels = mds_labels, 
                 shape_size = 3, dim.plot = c(3,2)) + 
@@
 
-```{r figure5, fig.cap=f5_cap, fig.width=7.1, fig.height=5}
-ggarrange(ggarrange(f5a, f5b,
+```{r figure4, fig.cap=f4_cap, fig.width=7.1, fig.height=5}
+ggarrange(ggarrange(f4a, f4b,
                     labels = c("A", "B"),
@@
                     nrow = 1),
-          ggarrange(f5c, f5d,
+          ggarrange(f4c, f4d,
                     labels = c("C", "D"),
@@
 
-f5_cap <- "\\textbf{Combined comparison of \\textit{C. albicans} proteomes.} 
+f4_cap <- "\\textbf{Combined comparison of \\textit{C. albicans} proteomes.} 
            \\textit{(A)} Venn diagram comparing four \\textit{C. albicans} EV 
            proteomes. Lists of proteins present in the centre and right 
-           partitions of each venn diagram in Figure \\@ref(fig:figure3)A were 
+           partitions of each venn diagram in Figure \\@ref(fig:figure2)A were 
            compared to identify proteins present in all four datasets. 
@@
            proteomes. Lists of proteins present in the centre and left 
-           partitions of each venn diagram in Figure \\@ref(fig:figure3)A were 
+           partitions of each venn diagram in Figure \\@ref(fig:figure2)A were 
            compared to identify proteins present in all four datasets. The data 
-           tables underlying Figures \\@ref(fig:figure5)A and 
-           \\@ref(fig:figure5)B are provided in supplemental File S4. 
+           tables underlying Figures \\@ref(fig:figure4)A and 
+           \\@ref(fig:figure4)B are provided in supplemental File S4. 
            \\textit{(C)} Multidimensional scaling (MDS) plot of each LC-MS/MS 
@@
 
-```{r figure6Heatmap, include=FALSE}
-# figure 6 heatmap
-f6_table <- a9_res %>% 
+```{r figure5Heatmap, include=FALSE}
+# figure 5 heatmap
+f5_table <- a9_res %>% 
   select(logFC, CGD_gene_name) %>% 
@@
   select(CGD_gene_name, everything()) %>% 
-  filter(CGD_gene_name %in% f5a_overlap)
+  filter(CGD_gene_name %in% f4a_overlap)
 
@@
 # otherwise clustering will not work
-f6_table_filt <- f6_table %>% 
+f5_table_filt <- f5_table %>% 
   filter_at(.vars = vars(contains("lfc")), 
@@
 # excluded proteins
-f6_table_excl <- f6_table %>% 
+f5_table_excl <- f5_table %>% 
   filter_at(.vars = vars(contains("lfc")), 
@@
 # heatmap legend parameters
-f6_params <- list(color_bar = "continuous", 
+f5_params <- list(color_bar = "continuous", 
                   title = expression(bold(log[2]("FC"))), 
@@
 # plot heatmap
-f6_htmp <- plot_heatmap(mt = f6_table_filt, 
+f5_htmp <- plot_heatmap(mt = f5_table_filt, 
                         plot = FALSE,
@@
                         row_title = c("1", "2", "3", "4", "5"), 
-                        heatmap_legend_param = f6_params)
+                        heatmap_legend_param = f5_params)
 
@@
 # not run in rmarkdown but manually in console
-# pdf(file = "figures/figure5_unf.pdf", width = 1.7, height = 4)
+# pdf(file = "figures/figure5_htmp.pdf", width = 1.7, height = 4)
 # ComplexHeatmap::draw(f5_htmp, heatmap_legend_side = "bottom")
@@
 
-```{r figure6Table, include=FALSE}
+```{r figure5Table, include=FALSE}
 #  list of proteins for heatmap table in order of appearance in heatmap
-f6_clusters <- plot_heatmap(mt = f6_table_filt, 
+f5_clusters <- plot_heatmap(mt = f5_table_filt, 
                             plot = FALSE,
@@
 # extract identifiers from each cluster
-f6_clust1 <- f6_clusters %>% 
+f5_clust1 <- f5_clusters %>% 
   filter(cluster == 1) %>% 
@@
 
-f6_clust2 <- f6_clusters %>% 
+f5_clust2 <- f5_clusters %>% 
   filter(cluster == 2) %>% 
@@
 
-f6_clust3 <- f6_clusters %>% 
+f5_clust3 <- f5_clusters %>% 
   filter(cluster == 3) %>% 
@@
 
-f6_clust4 <- f6_clusters %>% 
+f5_clust4 <- f5_clusters %>% 
   filter(cluster == 4) %>% 
@@
 # but GO enrichment still possible
-f6_clust5 <- f6_clusters %>% 
+f5_clust5 <- f5_clusters %>% 
   filter(cluster == 5) %>% 
@@
 # because all 4 log2FCs = NA
-f6_clust6 <- sort(rownames(f6_table_excl))
+f5_clust6 <- sort(rownames(f5_table_excl))
 
 # import FungiFun2 results
-f6_go1 <- process_fungifun("figures/f6_GO_clust1.csv") %>% 
+f5_go1 <- process_fungifun("figures/f5_GO_clust1.csv") %>% 
   mutate(Prot.found = gsub("CaO19.4937", "CHS3", Prot.found))
@@
 # issue with PEP1, ambiguous ID in FungiFun, used CaO19.3767 as identifier
-f6_go2 <- process_fungifun("figures/f6_GO_clust2.csv") %>% 
+f5_go2 <- process_fungifun("figures/f5_GO_clust2.csv") %>% 
   mutate(Prot.found = gsub("CaO19.3767", "PEP1", Prot.found))
 
-f6_go3 <- process_fungifun("figures/f6_GO_clust3.csv")
+f5_go3 <- process_fungifun("figures/f5_GO_clust3.csv")
 
 # issue with CHS3, ambiguous ID in FungiFun, used CaO19.4937 as identifier
-f6_go4 <- process_fungifun("figures/f6_GO_clust4.csv")
+f5_go4 <- process_fungifun("figures/f5_GO_clust4.csv")
 
 # issue with ALA1, MDH1, used CaO19.5746 and CaO19.7481 as identifiers
-f6_go5 <- process_fungifun("figures/f6_GO_clust5.csv") %>% 
+f5_go5 <- process_fungifun("figures/f5_GO_clust5.csv") %>% 
   mutate(Prot.found = gsub("CaO19.5746", "ALA1", Prot.found), 
@@
 
-f6_go6 <- process_fungifun("figures/f6_GO_clust6.csv")
-```
-
-```{r figure6, fig.cap=f6_cap, fig.height=6}
-f6 <- png::readPNG("figures/figure6.png")
-
-# draw figure 6
+f5_go6 <- process_fungifun("figures/f5_GO_clust6.csv")
+```
+
+```{r figure5, fig.cap=f5_cap, fig.height=6}
+f5 <- png::readPNG("figures/figure5.png")
+
+# draw figure 5
 ggplot() + 
-  background_image(f6) + 
+  background_image(f5) + 
   theme(plot.margin = margin(t = 0.1, l = 0.1, r = 0.1, b = 0.1, 
@@
 
-f6_cap <- "\\textbf{Identification of commonly enriched EV proteins across 
+f5_cap <- "\\textbf{Identification of commonly enriched EV proteins across 
            different \\textit{C. albicans} strains.} Heatmap of proteins 
            (n = 403) identified in all four EV samples (venn overlap in Figure 
-           \\@ref(fig:figure5)A). Each column represents a 
+           \\@ref(fig:figure4)A). Each column represents a 
            \\textit{C. albicans} strain and each row represents a protein. The 
@@
 
-```{r figure7Data, include=FALSE}
-f7a_venn <- plot_venn(vlist = marker_comp, use_uniprot = FALSE, type = "plot", 
+```{r figure6Data, include=FALSE}
+f6a_venn <- plot_venn(vlist = marker_comp, use_uniprot = FALSE, type = "plot", 
                       fontfamily = "sans", 
@@
 
-f7a <- as_ggplot(f7a_venn) + 
+f6a <- as_ggplot(f6a_venn) + 
   theme(plot.margin = unit(c(1.2,0,0,0), "lines"))
@@
 
-f7b_venn <- plot_venn(vlist = wcl_comp, use_uniprot = FALSE, type = "plot", 
+f6b_venn <- plot_venn(vlist = wcl_comp, use_uniprot = FALSE, type = "plot", 
                       fontfamily = "sans", 
@@
 
-f7b <- as_ggplot(f7b_venn) + 
+f6b <- as_ggplot(f6b_venn) + 
   theme(plot.margin = unit(c(1.2,0,0,0), "lines"))
@@
 
-```{r figure7, fig.cap=f7_cap, fig.width=2.5, fig.height=4}
-ggarrange(f7a, f7b, 
+```{r figure6, fig.cap=f6_cap, fig.width=2.5, fig.height=4}
+ggarrange(f6a, f6b, 
           labels = c("A", "B"), 
@@
 
-f7_cap <- "\\textbf{Identification of common signficantly enriched or exclusive 
+f6_cap <- "\\textbf{Identification of common signficantly enriched or exclusive 
            \\textit{C. albicans} EV and WCL proteins.} Proteins identified as 
            significantly enriched or exclusive to EVs in Figure 
-           \\@ref(fig:figure3) were compared to select those which were common 
+           \\@ref(fig:figure2) were compared to select those which were common 
            to all 4 datasets. 43 proteins were identified as potential positive 
@@
            markers. The data tables underlying Figure 
-           \\@ref(fig:figure7) are provided in supplemental File S4. Details of 
+           \\@ref(fig:figure6) are provided in supplemental File S4. Details of 
            the 43 positive EV protein marker candidates and 52 negative 
@@
 
-```{r figure8, fig.cap=f8_cap, fig.width=3.5, fig.height=2.8}
-f8_cap <- "\\textbf{Eighteen best potential \\textit{C. albicans} positive EV 
+```{r figure7, fig.cap=f7_cap, fig.width=3.5, fig.height=2.8}
+f7_cap <- "\\textbf{Eighteen best potential \\textit{C. albicans} positive EV 
            protein markers.} These proteins are those underlined in Table 
@@
            in this study. The proteins fit within the EV biomarker categories 
-           1a, 2a, and 2b from MISEV2018 which includes transmembrane, 
+           1 and 2 from MISEV2018 which includes transmembrane, 
            GPI-anchored, and cytosolic proteins that are EV enriched 
@@
 
-f8 <- png::readPNG("figures/figure8.png")
+f7 <- png::readPNG("figures/figure7.png")
 
 ggplot() + 
-  background_image(f8)
+  background_image(f7)
 ```
@@
 
-```{r figure9, fig.cap=f9_cap, fig.width=7.2, fig.height=6}
-f9_cap <- "\\textbf{Predicted topology and palmitoylation sites of 
+```{r figure8, fig.cap=f8_cap, fig.width=7.2, fig.height=6}
+f8_cap <- "\\textbf{Predicted topology and palmitoylation sites of 
            \\textit{C. albicans} MCC/eisosome proteins SUR7 and orf19.6741 
@@
 
-f9 <- png::readPNG("figures/figure9.png")
+f8 <- png::readPNG("figures/figure8.png")
 
 ggplot() + 
-  background_image(f9)
-```
+  background_image(f8)
+```

### 2019-06-27 inst/manuscript/manuscript_supplement.Rmd
Fix yeast sample labels in manuscript
Change figure 1 to figure S1
Also:
 - Update title, running title, authors, affiliations, corresponding
   author

@@
 
-**Running title:** Running title goes here
+**Corresponding author:** Mark Bleackley, m.bleackley@latrobe.edu.au
 
-**Corresponding author:**
+**Running title:** Defining _Candida albicans_ EV protein markers
 
@@
 # drop EV_1 and WCL_1
-yeast_lfq2 <- yeast_lfq[, !colnames(yeast_lfq) %in% c("EV_1", "WCL_1")]
+yeast_lfq2 <- yeast_lfq[, !colnames(yeast_lfq) %in% c("EV_0", "WCL_0")]
 
@@
 
-```{r figureS1, fig.cap=fS1_cap, fig.height=5, fig.width=5}
-fS1_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 
+```{r figureS1, fig.cap=f1_cap, fig.width=5.45, fig.height=6}
+# construct figure 1
+fs1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
+           proteomic analysis of \\textit{C. albicans} EVs and the selection 
+           of EV protein markers.} Steps 1 to 6 were performed for each of the 
+           four strains examined in this study: DAY286 yeast, ATCC90028 yeast, 
+           ATCC10231 yeast, and DAY286 biofilm. The results from the four 
+           seperate analyses were combined (step 7) to identify proteins which 
+           commonly appeared as EV marker candidates. The MISEV2018 criteria 
+           for protein content-based EV characterisation and other 
+           considerations were used to select the best \\textit{C. albicans} 
+           EV marker proteins."
+
+fs1 <- png::readPNG("figures/figure1.png")
+
+# draw figure S1
+ggplot() + 
+  background_image(fs1)
+```
+
+```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5}
+fS2_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 
               determined by nanoparticle tracking analysis (NTA).} A line plot 
@@
 
-figS1_labels <- c("ATCC10231", 
+figS2_labels <- c("ATCC10231", 
                   "ATCC90028", 
@@
 
-names(figS1_labels) <- c("ATCC10231", 
+names(figS2_labels) <- c("ATCC10231", 
                          "ATCC90028", 

### 2019-06-28 inst/manuscript/manuscript.Rmd
Fix atcc analysis in manuscript.Rmd
Also:
 - Update figures affected by this fix

Issue:
 - Error in atcc analysis section
 - The proteins depicted in the 4 venn diagrams in Fig. 2A should
   include only proteins quantified in min 2/3 replicates of EV or WCL.
   However, some ATCC90028 and ATCC10231 proteins do not pass this
   statement.
 - Yeast and biofilm results unaffected.

Solution:
 - Change atcc analysis workflow from this method:
    - Filter, normalise, impute, split into ATCC90028 and ATCC10231,
      then perform separate DE analyses.
   to this method:
    - Filter, normalise, s

@@
 
-# filter for proteins identified in min 1/3 reps of EV
+# filter for proteins quantified in min 1/3 reps of EV
 # define 'EV proteins'
@@
 
-# filter for proteins identified in min 1/3 reps of WCL
+# filter for proteins quantified in min 1/3 reps of WCL
 # define 'WCL proteins'
@@
 
-# filter for proteins identified in min 1/5 reps of EV
+# filter for proteins quantified in min 1/5 reps of EV
 # define 'EV proteins'
@@
 
-# filter for proteins identified in min 1/5 reps of WCL
+# filter for proteins quantified in min 1/5 reps of WCL
 # define 'WCL proteins'
@@
 
-```{r atcc, include=FALSE}
+```{r atccBoth, include=FALSE}
 # filter out reverse, contaminant proteins, proteins with <2 unique peptides
@@
 atcc_norm <- normalizeCyclicLoess(atcc_filt)
-
-# filter for proteins identified in min 1/3 reps of 10231 EV
-# define 'ATCC10231 EV proteins'
-atcc1_ev <- filter_na(atcc_norm, op = "<=", 
-                      pat = "A10231_EV", val = 2)
-
-# filter for proteins identified in min 1/3 reps of 10231 WCL
-# define 'ATCC10231 WCL proteins'
-atcc1_w <- filter_na(atcc_norm, op = "<=", 
-                     pat = "A10231_W", val = 2)
-
-# filter for proteins identified in min 1/3 reps of 90028 EV
-# define 'ATCC90028 EV proteins'
-atcc9_ev <- filter_na(atcc_norm, op = "<=", 
-                      pat = "A90028_EV", val = 2)
-
-# filter for proteins identified in min 1/3 reps of 90028 WCL
-# define 'ATCC90028 WCL proteins'
-atcc9_w <- filter_na(atcc_norm, op = "<=", 
-                      pat = "A90028_W", val = 2)
+```
+
+```{r atcc1, include=FALSE}
+# filter for proteins quantified in min 2/3 reps of EV or WCL
+a1_norm <- filter_na2(atcc_norm, logic = "or", op = "<=", 
+                      pat1 = "A10231_EV", val1 = 1, 
+                      pat2 = "A10231_W", val2 = 1)
+a1_norm <- a1_norm[, -c(7:12)]
+
+# filter for proteins quantified in min 1/3 reps of EV
+# define 'EV proteins'
+a1_ev <- filter_na(a1_norm, op = "<=", pat = "EV", val = 2)
+
+# filter for proteins quantified in min 1/3 reps of WCL
+# define 'WCL proteins'
+a1_wcl <- filter_na(a1_norm, op = "<=", pat = "W", val = 2)
 
 # can't impute with so many missing values
-# filter for exclusive to 10231 EV or WCL or 90028 EV or WCL (don't impute)
-atcc_excl <- filter_na4(atcc_norm, logic = "or", op = "==", 
-                        pat1 = "A10231_EV", val1 = 3, 
-                        pat2 = "A10231_W", val2 = 3, 
-                        pat3 = "A90028_EV", val3 = 3, 
-                        pat4 = "A90028_W", val4 = 3)
-
-# filter for proteins with min 1 valid value in all 4 sample types (impute)
-atcc_both <- filter_na4(atcc_norm, logic = "and", op = "<=", 
-                        pat1 = "A10231_EV", val1 = 2, 
-                        pat2 = "A10231_W", val2 = 2, 
-                        pat3 = "A90028_EV", val3 = 2, 
-                        pat4 = "A90028_W", val4 = 2)
+# separate EV/WCL exclusive proteins (don't impute) from
+# EV/WCL common proteins (impute)
+a1_excl <- filter_na2(a1_norm, logic = "or", op = "==",
+                      pat1 = "EV", val1 = 3,
+                      pat2 = "W", val2 = 3)
+
+a1_both <- filter_na2(a1_norm, logic = "and", op = "<=",
+                      pat1 = "EV", val1 = 2,
+                      pat2 = "W", val2 = 2)
 
@@
 # use left censored imputation method
-atcc_imp <- impute_QRILC(atcc_both)
+a1_imp <- impute_QRILC(a1_both)
 
 # recombine imputed proteins and non-imputed proteins in matrix
-atcc_de <- rbind(atcc_excl, atcc_imp)
-colnames(atcc_de) <- stringi::stri_replace_all_regex(colnames(atcc_de), 
-                                                     c("A10231_", "A90028_"), 
-                                                     c("A1_", "A9_"), 
-                                                     vectorize_all = FALSE)
+a1_de <- rbind(a1_excl, a1_imp)
+colnames(a1_de) <- gsub("A10231", "A1", colnames(a1_de))
 
@@
 # create design matrix
-atcc_samp <- data.frame(T = rep(c("A1_EV", "A1_WCL", 
-                                  "A9_EV", "A9_WCL"), each = 3))
-
-atcc_design <- stats::model.matrix(~ 0 + T, data = atcc_samp)
-colnames(atcc_design) <- c("A1_EV", "A1_W", "A9_EV", "A9_W")
+a1_samp <- data.frame(T = (rep(c("EV", "WCL"), each = 3)))
+
+a1_design <- stats::model.matrix(~ 0 + T, data = a1_samp)
+colnames(a1_design) <- c("A1_EV", "A1_W")
 
 # define sample comparisons of interest
-atcc_contrasts <- c("A1_EV - A1_W", "A9_EV - A9_W")
-
-# make all pair-wise comparisons for specified contrasts
+a1_contrasts <- c("A1_EV - A1_W")
+
+# make all pair-wise comparisons between EV and WCL
 # and perform limma::eBayes()
-atcc_efit <- limma_eBayes(atcc_de, atcc_design, atcc_contrasts)
-
-# extract overall results
-atcc_overall <- get_results(efit = atcc_efit, mat = atcc_de, 
-                            p_val = 0.01, lfc = 0, type = "overall")
-
-# extract results for ATCC strains
-a1_res <- get_results(efit = atcc_efit, 
-                      mat = atcc_de, 
+a1_efit <- limma_eBayes(a1_de, design = a1_design, contrasts = a1_contrasts)
+
+# extract DE results
+a1_res <- get_results(efit = a1_efit,
+                      mat = a1_de,
                       p_val = 0.01,
@@
                       type = "individual")[[1]]
-
-a9_res <- get_results(efit = atcc_efit, 
-                      mat = atcc_de, 
+```
+
+```{r atcc9, include=FALSE}
+# filter for proteins quantified in min 2/3 reps of EV or WCL
+a9_norm <- filter_na2(atcc_norm, logic = "or", op = "<=",
+                      pat1 = "A90028_EV", val1 = 1,
+                      pat2 = "A90028_W", val2 = 1)
+a9_norm <- a9_norm[, -c(1:6)]
+
+# filter for proteins quantified in min 1/3 reps of EV
+# define 'EV proteins'
+a9_ev <- filter_na(a9_norm, op = "<=", pat = "EV", val = 2)
+
+# filter for proteins quantified in min 1/3 reps of WCL
+# define 'WCL proteins'
+a9_wcl <- filter_na(a9_norm, op = "<=", pat = "W", val = 2)
+
+# can't impute with so many missing values
+# separate EV/WCL exclusive proteins (don't impute) from
+# EV/WCL common proteins (impute)
+a9_excl <- filter_na2(a9_norm, logic = "or", op = "==",
+                      pat1 = "EV", val1 = 3,
+                      pat2 = "W", val2 = 3)
+
+a9_both <- filter_na2(a9_norm, logic = "and", op = "<=",
+                      pat1 = "EV", val1 = 2,
+                      pat2 = "W", val2 = 2)
+
+# proteins with missing values tend to have lower intensity
+# therefore proteins are MNAR, close to detection limit
+# use left censored imputation method
+a9_imp <- impute_QRILC(a9_both)
+
+# recombine imputed proteins and non-imputed proteins in matrix
+a9_de <- rbind(a9_excl, a9_imp)
+colnames(a9_de) <- gsub("A90028", "A9", colnames(a9_de))
+
+# see limma user guide section 9.2 for more info about DE
+# create design matrix
+a9_samp <- data.frame(T = (rep(c("EV", "WCL"), each = 3)))
+
+a9_design <- stats::model.matrix(~ 0 + T, data = a9_samp)
+colnames(a9_design) <- c("A9_EV", "A9_W")
+
+# define sample comparisons of interest
+a9_contrasts <- c("A9_EV - A9_W")
+
+# make all pair-wise comparisons between EV and WCL
+# and perform limma::eBayes()
+a9_efit <- limma_eBayes(a9_de, design = a9_design, contrasts = a9_contrasts)
+
+# extract DE results
+a9_res <- get_results(efit = a9_efit,
+                      mat = a9_de,
                       p_val = 0.01,
                       lfc = 0,
-                      type = "individual")[[2]]
+                      type = "individual")[[1]]
 ```
@@
 # group proteins according to localisation
-marker_longlist <- marker_longlist %>% 
+marker_longlist2 <- marker_longlist %>% 
   mutate(Function = function_desc1, 
-         VDM = c("Y", rep("",3), rep("Y", 2), "", "Y", rep("", 8), rep("Y", 2), 
-                 rep("", 4), rep("Y", 3), rep("", 2), rep("Y", 2), rep("", 5), 
-                 "Y", rep("", 7), "Y"), 
-         pack_row = c(4, rep(1,3), rep(4,2), 1, 2, rep(1,3), rep(1,3), 3, 2, 
-                      rep(4,2), 1, rep(2,2), 3, 1, rep(4,2), 1, rep(4,3), 1, 
-                      3, rep(1,3), 4, 1, 1, 2, 1, 2, 2, 2, 4)) %>% 
-  arrange(pack_row)
+         pack_row = c(4, rep(1, 3), rep(4, 2), 1, 2, rep(1, 6), 3, rep(4, 2),
+                      1, rep(2, 3), 1, rep(4, 2), 1, rep(4, 3), 1, 3, 
+                      rep(1, 3), 4, 1, 2, 1, 2, 4)) %>% 
+  arrange(pack_row) %>% 
+  mutate(VDS = c(rep("", 11), "Y", rep("", 7), "Y", rep("", 7), 
+                 rep("Y", 7), "", rep("Y", 4)))
 
 # fix number of TM domains for CDR1;CDR2
-marker_longlist[2, 7] <- "12;12"
+marker_longlist2[2, 7] <- "12;12"
 
@@
 # fix SUR7 entries
-marker_longlist[19, 7] <- "4"
-marker_longlist[19, 8] <- ""
+marker_longlist2[18, 7] <- "4"
+marker_longlist2[18, 8] <- ""
+
+# Change name of orf19.6741 to Evp1
+marker_longlist2[12, 1] <- paste0("EVP1",
+                                  footnote_marker_alphabet(4))
 ```
@@
 # draw table 1
-knitr::kable(marker_longlist[ ,-10],
+knitr::kable(marker_longlist2[ ,-9],
              caption = tab1_cap, 
@@
              escape = FALSE)  %>% 
-  row_spec(row = c(1, 5, 6, 11, 12, 15:20, 22:27, 39), underline = TRUE) %>% 
+  row_spec(row = c(1, 5, 11, 12, 15:19, 21:25, 35), underline = TRUE) %>% 
   add_header_above(c(" " = 2, 
@@
   kable_styling(font_size = 8) %>% 
-  pack_rows("Plasma membrane", 1, 20) %>% 
-  pack_rows("Golgi, ER, vacuole", 21, 28) %>% 
-  pack_rows("Mitochondria", 29, 31) %>% 
-  pack_rows("Cell wall, cell surface", 32, 43) %>% 
+  pack_rows("Plasma membrane", 1, 19) %>% 
+  pack_rows("Golgi, ER, vacuole", 20, 25) %>% 
+  pack_rows("Mitochondria", 26, 27) %>% 
+  pack_rows("Cell wall, cell surface", 28, 39) %>% 
   footnote(alphabet = c("Protein localisation was inferred from sequence 
@@
                          annotated in the Candida Genome Database 
-                        (ref:footnote1)", 
+                        (ref:footnote1).", 
                         "Protein localisation was predicted using DeepLoc-1.0 
-                        (ref:footnote2)", 
+                        (ref:footnote2).", 
                         "Presence of transmembrane domains and absense of a 
                         signal peptide was predicted using TOPCONS2 
-                        (ref:footnote3)"), 
+                        (ref:footnote3).",
+                        "The name Evp1 for the protein encoded by orf19.6741 
+                        was proposed in the present study."), 
            escape = FALSE, 
@@
 # compare ATCC90028 EV WCL proteins
-f2a2 <- plot_venn(list("EV" = atcc9_ev, "WCL" = atcc9_w), 
+f2a2 <- plot_venn(list("EV" = a9_ev, "WCL" = a9_wcl), 
                   use_uniprot = TRUE, type = "plot", 
@@
                      axis_params = c("black", 10)) + 
-  scale_colour_manual(labels = c("EV enriched (99)", "WCL enriched (130)", 
-                                 "Not significant (744)"),
+  scale_colour_manual(labels = c("EV enriched (86)", "WCL enriched (122)", 
+                                 "Not significant (761)"),
                       values = unname(ev_pal[c(2,3,1)])) + 
   annotate("text", x = 8, y = 0.5, label = "bold('ATCC90028')", parse = TRUE) + 
-  annotate("text", x = 3.5, y = 7, label = "bold('99')", 
+  annotate("text", x = 3.5, y = 7, label = "bold('86')", 
            parse = TRUE, colour = unname(ev_pal[2])) + 
-  annotate("text", x = -3.5, y = 7, label = "bold('130')", 
+  annotate("text", x = -3.5, y = 7, label = "bold('122')", 
            parse = TRUE, colour = unname(ev_pal[3])) + 
-  annotate("text", x = 0, y = 6, label = "bold('744')", 
+  annotate("text", x = 0, y = 6, label = "bold('761')", 
            parse = TRUE, colour = unname(ev_pal[1]))
@@
 # compare ATCC10231 EV WCL proteins
-f2a3 <- plot_venn(list("EV" = atcc1_ev, "WCL" = atcc1_w), 
+f2a3 <- plot_venn(list("EV" = a1_ev, "WCL" = a1_wcl), 
                   use_uniprot = TRUE, type = "plot", 
@@
                      axis_params = c("black", 10)) + 
-  scale_colour_manual(labels = c("EV enriched (108)", "WCL enriched (142)", 
-                                 "Not significant (435)"),
+  scale_colour_manual(labels = c("EV enriched (55)", "WCL enriched (52)", 
+                                 "Not significant (567)"),
                       values = unname(ev_pal[c(2,3,1)])) + 
   annotate("text", x = 8, y = 0.5, label = "bold('ATCC10231')", parse = TRUE) + 
-  annotate("text", x = 3.5, y = 7, label = "bold('106')", 
+  annotate("text", x = 3.5, y = 7, label = "bold('55')", 
            parse = TRUE, colour = unname(ev_pal[2])) + 
-  annotate("text", x = -3.5, y = 7, label = "bold('134')", 
+  annotate("text", x = -3.5, y = 7, label = "bold('52')", 
            parse = TRUE, colour = unname(ev_pal[3])) + 
-  annotate("text", x = 0, y = 6, label = "bold('445')", 
+  annotate("text", x = 0, y = 6, label = "bold('567')", 
            parse = TRUE, colour = unname(ev_pal[1]))
@@
   gsub("PEP1", "CaO19.3767", .)
+# paste into FungiFun2 and download results .csv
 
@@
                                   vectorize_all = FALSE)
+# paste into FungiFun2 and download results .csv
 
@@
 f3_a9_go <- f3_a9_go[!f3_a9_go %in% c("orf19.7397.1", "orf19.7398")]
+# paste into FungiFun2 and download results .csv
 
@@
                                   vectorize_all = FALSE)
+# paste into FungiFun2 and download results .csv
 ```
@@
 
-f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:4, 35,37:38,42, 55:56,58:59), f3_pal) + 
+f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:3,6, 27,29,32:33, 46,49,51:52), f3_pal) + 
   annotate("text", x = 12, y = 70, label = "bold('ATCC90028')", parse = TRUE)
 
-f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4, 63,65:67, 88:91), f3_pal) + 
+f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4, 62,64:66, 86:89), f3_pal) + 
   annotate("text", x = 12, y = 70, label = "bold('ATCC10231')", parse = TRUE)
@@
                  "DAY B" = rownames(b_ev),
-                 "ATCC90028" = rownames(atcc9_ev), 
-                 "ATCC10231" = rownames(atcc1_ev))
+                 "ATCC90028" = rownames(a9_ev), 
+                 "ATCC10231" = rownames(a1_ev))
 f4a_comp <- lapply(f4a_comp, function(x) match_id(x, ref = uniprot, 
@@
                          use_uniprot = FALSE, type = "df") %>% 
-  filter(..count.. == 403) %>% 
+  filter(..count.. == 396) %>% 
   pull(..values..) %>% 
@@
                  "DAY B" = rownames(b_wcl),
-                 "ATCC90028" = rownames(atcc9_w), 
-                 "ATCC10231" = rownames(atcc1_w))
+                 "ATCC90028" = rownames(a9_wcl), 
+                 "ATCC10231" = rownames(a1_wcl))
 f4b_comp <- lapply(f4b_comp, function(x) match_id(x, ref = uniprot, 
@@
 # MDS data table
-mds_data <- cbind(atcc_de, 
-                  biofilm_de[match(rownames(atcc_de), rownames(biofilm_de)), ])
-
-mds_data <- cbind(mds_data, 
-                  yeast_de[match(rownames(mds_data), rownames(yeast_de)), ])
+mds_a9 <- a9_de %>% 
+  as.data.frame() %>% 
+  tibble::rownames_to_column(var = "id")
+
+mds_a1 <- a1_de %>% 
+  as.data.frame() %>% 
+  tibble::rownames_to_column(var = "id")
+
+mds_biofilm <- biofilm_de%>% 
+  as.data.frame() %>% 
+  tibble::rownames_to_column(var = "id")
+
+mds_yeast <- yeast_de%>% 
+  as.data.frame() %>% 
+  tibble::rownames_to_column(var = "id")
+
+mds_data <- full_join(mds_a9, mds_a1, by = "id") %>% 
+  full_join(., mds_biofilm, by = "id") %>% 
+  full_join(., mds_yeast, by = "id") %>% 
+  tibble::column_to_rownames(var = "id")
 
@@
                      expand = c(0,0)) + 
-  scale_y_continuous(limits = c(-1.5, 2.5), 
+  scale_y_continuous(limits = c(-2.5, 1.5), 
                      expand = c(0,0)) + 
@@
                         cluster_split = FALSE, 
-                        split_order = c(3, 1, 4, 2, 5), 
+                        split_order = c(2, 5, 1, 4, 3), 
                         colour_lims = c(-4, 4),
@@
 # not run in rmarkdown but manually in console
-# pdf(file = "figures/figure5_htmp.pdf", width = 1.7, height = 4)
+# pdf(file = "inst/manuscript/figures/figure5_htmp.pdf", width = 1.7, height = 4)
 # ComplexHeatmap::draw(f5_htmp, heatmap_legend_side = "bottom")
@@
   mutate(cluster = recode(cluster, 
-                          "1" = 2, "2" = 4, "3" = 1, "4" = 3, "5" = 5)) %>% 
+                          "1" = 4, "2" = 1, "3" = 5, "4" = 2, "5" = 3)) %>% 
   arrange(cluster)
@@
   filter(cluster == 1) %>% 
-  mutate(id = gsub("CHS3", "CaO19.4937", id)) %>% 
-  pull(id)
-
-f5_clust2 <- f5_clusters %>% 
-  filter(cluster == 2) %>% 
   mutate(id = gsub("PEP1", "CaO19.3767", id)) %>% 
@@
 
+f5_clust2 <- f5_clusters %>% 
+  filter(cluster == 2) %>% 
+  pull(id)
+
 f5_clust3 <- f5_clusters %>% 
   filter(cluster == 3) %>% 
+  mutate(id = gsub("CHS3", "CaO19.4937", id)) %>% 
   pull(id)
@@
 f5_go1 <- process_fungifun("figures/f5_GO_clust1.csv") %>% 
+  mutate(Prot.found = gsub("CaO19.3767", "PEP1", Prot.found))
+
+# issue with PEP1, ambiguous ID in FungiFun, used CaO19.3767 as identifier
+f5_go2 <- process_fungifun("figures/f5_GO_clust2.csv")
+
+f5_go3 <- process_fungifun("figures/f5_GO_clust3.csv") %>% 
   mutate(Prot.found = gsub("CaO19.4937", "CHS3", Prot.found))
-
-# issue with PEP1, ambiguous ID in FungiFun, used CaO19.3767 as identifier
-f5_go2 <- process_fungifun("figures/f5_GO_clust2.csv") %>% 
-  mutate(Prot.found = gsub("CaO19.3767", "PEP1", Prot.found))
-
-f5_go3 <- process_fungifun("figures/f5_GO_clust3.csv")
 
@@
            different \\textit{C. albicans} strains.} Heatmap of proteins 
-           (n = 403) identified in all four EV samples (venn overlap in Figure 
+           (n = 396) identified in all four EV samples (venn overlap in Figure 
            \\@ref(fig:figure4)A). Each column represents a 
@@
            each cluster are shown and are also available in supplemental 
-           File S5."
+           File S5. \\textsuperscript{a} indicates where all proteins from 
+           each protein group in the cluster were used for the GO analysis."
 ```
@@
            \\@ref(fig:figure2) were compared to select those which were common 
-           to all 4 datasets. 43 proteins were identified as potential positive 
-           EV protein markers and 52 proteins as potential negative EV protein 
+           to all 4 datasets. 39 proteins were identified as potential positive 
+           EV protein markers and 40 proteins as potential negative EV protein 
            markers. The data tables underlying Figure 
            \\@ref(fig:figure6) are provided in supplemental File S4. Details of 
-           the 43 positive EV protein marker candidates and 52 negative 
+           the 39 positive EV protein marker candidates and 40 negative 
            candidates can be found in Table \\@ref(tab:table1) and supplemental 
@@
 f8_cap <- "\\textbf{Predicted topology and palmitoylation sites of 
-           \\textit{C. albicans} MCC/eisosome proteins SUR7 and orf19.6741 
+           \\textit{C. albicans} MCC/eisosome proteins Sur7 and Evp1 
+           (orf19.6741) 
            compared to the human tetraspanin CD81.} The presence of 

### 2019-06-28 inst/manuscript/components/protein_funs.R

@@ -11,27 +11,24 @@ function_desc1 <- c("1,3-beta-glucanosyltransferase",
                     paste0("Predicted P-type ATPase sodium pump",
                            footnote_marker_alphabet(1)),
                     "ER oxidoreductin",
-                    paste0("Long-chain fatty acid-CoA ligase",
-                           footnote_marker_alphabet(1)),
                     "Multicopper feroxidase",
                     "High-affinity S-adenosylmethionine permease",
                     "1,3-beta-glucan synthase",
                     "High-affinity MFS glucose transporter",
                     "Putative high-affinity MFS glucose transporter",
+                    "Putative MFS glucose transporter",
                     paste0("Putative mitochondrial phosphate transporter",
-                           footnote_marker_alphabet(1)),
-                    paste0("Glycolipid 2-alpha-mannosyltransferase",
                            footnote_marker_alphabet(1)),
                     "Cell surface mannoprotein",
                     "Mucin family adhesin-like protein",
                     "Sphingolipid C9-methyltransferase",
-                    paste0("\\textit{S. cerevisiae} ortholog is POM33, transmembrane nucleoporin",
+                    paste0("\\textit{S. cerevisiae} ortholog is Pom33, transmembrane nucleoporin",
                            footnote_marker_alphabet(2)),
-                    paste0("\\textit{S. cerevisiae} ortholog is RTN1, reticulon protein",
+                    paste0("\\textit{S. cerevisiae} ortholog is Yop1, reticulon-interacting protein",
                            footnote_marker_alphabet(2)),
-                    paste0("Hexadecenal dehydrogenase",
+                    paste0("\\textit{S. cerevisiae} ortholog is Rtn1, reticulon protein",
                            footnote_marker_alphabet(2)),
-                    paste0("\\textit{S. cerevisiae} ortholog is PUN1, plasma membrane protein",
+                    paste0("\\textit{S. cerevisiae} ortholog is Pun1, plasma membrane protein",
                            footnote_marker_alphabet(2)),
                     "1,3-beta-glucanosyltransferase",
                     "GPI-anchored cell surface protein of unknown function",
@@ -46,22 +43,17 @@ function_desc1 <- c("1,3-beta-glucanosyltransferase",
                     "Rho family GTPase",
                     "Rho family GTPase",
                     "Secreted aspartyl protease",
-                    "Plasma membrane t-SNARE",
[…]

### 2019-06-28 inst/manuscript/manuscript_supplement.Rmd
Fix atcc analysis in manuscript_supplement.Rmd

@@
 atcc_norm <- normalizeCyclicLoess(atcc_filt)
+```
 
-# filter for proteins identified in min 1/3 reps of 10231 EV
-# define 'ATCC10231 EV proteins'
-atcc1_ev <- filter_na(atcc_norm, op = "<=", 
-                      pat = "A10231_EV", val = 2)
+```{r atcc1, include=FALSE}
+# filter for proteins quantified in min 2/3 reps of EV or WCL
+a1_norm <- filter_na2(atcc_norm, logic = "or", op = "<=", 
+                      pat1 = "A10231_EV", val1 = 1, 
+                      pat2 = "A10231_W", val2 = 1)
+a1_norm <- a1_norm[, -c(7:12)]
 
-# filter for proteins identified in min 1/3 reps of 10231 WCL
-# define 'ATCC10231 WCL proteins'
-atcc1_w <- filter_na(atcc_norm, op = "<=", 
-                     pat = "A10231_W", val = 2)
+# filter for proteins quantified in min 1/3 reps of EV
+# define 'EV proteins'
+a1_ev <- filter_na(a1_norm, op = "<=", pat = "EV", val = 2)
 
-# filter for proteins identified in min 1/3 reps of 90028 EV
-# define 'ATCC90028 EV proteins'
-atcc9_ev <- filter_na(atcc_norm, op = "<=", 
-                      pat = "A90028_EV", val = 2)
-
-# filter for proteins identified in min 1/3 reps of 90028 WCL
-# define 'ATCC90028 WCL proteins'
-atcc9_w <- filter_na(atcc_norm, op = "<=", 
-                      pat = "A90028_W", val = 2)
+# filter for proteins quantified in min 1/3 reps of WCL
+# define 'WCL proteins'
+a1_wcl <- filter_na(a1_norm, op = "<=", pat = "W", val = 2)
 
 # can't impute with so many missing values
-# filter for exclusive to 10231 EV or WCL or 90028 EV or WCL (don't impute)
-atcc_excl <- filter_na4(atcc_norm, logic = "or", op = "==", 
-                        pat1 = "A10231_EV", val1 = 3, 
-                        pat2 = "A10231_W", val2 = 3, 
-                        pat3 = "A90028_EV", val3 = 3, 
-                        pat4 = "A90028_W", val4 = 3)
+# separate EV/WCL exclusive proteins (don't impute) from
+# EV/WCL common proteins (impute)
+a1_excl <- filter_na2(a1_norm, logic = "or", op = "==",
+                      pat1 = "EV", val1 = 3,
+                      pat2 = "W", val2 = 3)
 
-# filter for proteins with min 1 valid value in all 4 sample types (impute)
-atcc_both <- filter_na4(atcc_norm, logic = "and", op = "<=", 
-                        pat1 = "A10231_EV", val1 = 2, 
-                        pat2 = "A10231_W", val2 = 2, 
-                        pat3 = "A90028_EV", val3 = 2, 
-                        pat4 = "A90028_W", val4 = 2)
+a1_both <- filter_na2(a1_norm, logic = "and", op = "<=",
+                      pat1 = "EV", val1 = 2,
+                      pat2 = "W", val2 = 2)
 
@@
 # create design matrix
-atcc_samp <- data.frame(T = (rep(c("A1_EV", "A1_WCL", 
-                                   "A9_EV", "A9_WCL"), each = 3)))
+a1_samp <- data.frame(T = (rep(c("EV", "WCL"), each = 3)))
 
-atcc_design <- stats::model.matrix(~ 0 + T, data = atcc_samp)
-colnames(atcc_design) <- c("A1_EV", "A1_W", "A9_EV", "A9_W")
+a1_design <- stats::model.matrix(~ 0 + T, data = a1_samp)
+colnames(a1_design) <- c("A1_EV", "A1_W")
 
 # define sample comparisons of interest
-atcc_contrasts <- c("A1_EV - A1_W", "A9_EV - A9_W")
+a1_contrasts <- c("A1_EV - A1_W")
 
-# make all pair-wise comparisons for specified contrasts
+# make all pair-wise comparisons between EV and WCL
 # and perform limma::eBayes()
-atcc_efit <- limma_eBayes(atcc_de, atcc_design, atcc_contrasts)
-
-# extract overall results
-atcc_overall <- get_results(efit = atcc_efit, mat = atcc_de, 
-                            p_val = 0.01, lfc = 0, type = "overall")
+a1_efit <- limma_eBayes(a1_de, design = a1_design, contrasts = a1_contrasts)
 
 # extract DE results
-a1_res <- get_results(efit = atcc_efit, 
-                      mat = atcc_de, 
+a1_res <- get_results(efit = a1_efit,
+                      mat = a1_de,
                       p_val = 0.01,
@@
                       type = "individual")[[1]]
+```
 
-a9_res <- get_results(efit = atcc_efit, 
-                      mat = atcc_de, 
+```{r atcc9, include=FALSE}
+# filter for proteins quantified in min 2/3 reps of EV or WCL
+a9_norm <- filter_na2(atcc_norm, logic = "or", op = "<=",
+                      pat1 = "A90028_EV", val1 = 1,
+                      pat2 = "A90028_W", val2 = 1)
+a9_norm <- a9_norm[, -c(1:6)]
+
+# filter for proteins quantified in min 1/3 reps of EV
+# define 'EV proteins'
+a9_ev <- filter_na(a9_norm, op = "<=", pat = "EV", val = 2)
+
+# filter for proteins quantified in min 1/3 reps of WCL
+# define 'WCL proteins'
+a9_wcl <- filter_na(a9_norm, op = "<=", pat = "W", val = 2)
+
+# can't impute with so many missing values
+# separate EV/WCL exclusive proteins (don't impute) from
+# EV/WCL common proteins (impute)
+a9_excl <- filter_na2(a9_norm, logic = "or", op = "==",
+                      pat1 = "EV", val1 = 3,
+                      pat2 = "W", val2 = 3)
+
+a9_both <- filter_na2(a9_norm, logic = "and", op = "<=",
+                      pat1 = "EV", val1 = 2,
+                      pat2 = "W", val2 = 2)
+
+# proteins with missing values tend to have lower intensity
+# therefore proteins are MNAR, close to detection limit
+# use left censored imputation method
+a9_imp <- impute_QRILC(a9_both)
+
+# recombine imputed proteins and non-imputed proteins in matrix
+a9_de <- rbind(a9_excl, a9_imp)
+colnames(a9_de) <- gsub("A90028", "A9", colnames(a9_de))
+
+# see limma user guide section 9.2 for more info about DE
+# create design matrix
+a9_samp <- data.frame(T = (rep(c("EV", "WCL"), each = 3)))
+
+a9_design <- stats::model.matrix(~ 0 + T, data = a9_samp)
+colnames(a9_design) <- c("A9_EV", "A9_W")
+
+# define sample comparisons of interest
+a9_contrasts <- c("A9_EV - A9_W")
+
+# make all pair-wise comparisons between EV and WCL
+# and perform limma::eBayes()
+a9_efit <- limma_eBayes(a9_de, design = a9_design, contrasts = a9_contrasts)
+
+# extract DE results
+a9_res <- get_results(efit = a9_efit,
+                      mat = a9_de,
                       p_val = 0.01,
                       lfc = 0,
-                      type = "individual")[[2]]
+                      type = "individual")[[1]]
 ```
@@
 
-```{r figureS1, fig.cap=f1_cap, fig.width=5.45, fig.height=6}
+```{r figureS1, fig.cap=fs1_cap, fig.width=5.45, fig.height=6}
 # construct figure 1
@@
 
-fs1 <- png::readPNG("figures/figure1.png")
+fs1 <- png::readPNG("figures/figures1.png")
 
@@
   facet_wrap(~ Strain, scales = "free", ncol = 2, nrow = 2, 
-             labeller = labeller(Strain = figS1_labels)) + 
+             labeller = labeller(Strain = figS2_labels)) + 
   theme_classic() + 
@@
 # group proteins according to localisation
-wcl_longlist <- wcl_longlist %>% 
+wcl_longlist2 <- wcl_longlist %>% 
   mutate(Function = function_desc2, 
-         VDM = c(rep("", 52)), 
-         pack_row = c(8, rep(4, 2), 3, rep(2, 2), 7, rep(1, 2), rep(7, 3), 1, 
-                      rep(2, 3), 7, 2, 4, rep(2, 2), 7, 3, 2, 5, rep(1, 2), 6, 
-                      2, 7, 6, 2, 1, 7, rep(1, 3), 2, 1, 5, 2, 1, 6, 
-                      1, 6, 2, 1, 9, 9, rep(1, 3))) %>% 
+         VDM = c(rep("", 40)), 
+         pack_row = c(rep(4, 2), 3, rep(2, 2), 7, rep(1, 2), rep(7, 2), 1, 
+                      rep(2, 4), 7, 3, 2, 5, 1, 
+                      2, 6, 2, 1, 7, rep(1, 2), 2, 1, 5, 1, 
+                      1, 6, 2, 1, rep(8, 2), rep(1, 3))) %>% 
   arrange(pack_row)
@@
 # draw table S2
-knitr::kable(wcl_longlist[, -10], 
+knitr::kable(wcl_longlist2[, -10], 
              caption = tabs2_cap, 
@@
              escape = FALSE) %>% 
-  row_spec(row = c(23, 30, 34, 35, 44, 50), underline = TRUE) %>% 
+  row_spec(row = c(20, 25, 29, 36), underline = TRUE) %>% 
   add_header_above(c(" " = 2, 
@@
                 latex_options = c("HOLD_position")) %>% 
-  pack_rows("Cytoplasm", 1, 16) %>% 
-  pack_rows("Mitochondria", 17, 30) %>% 
-  pack_rows("Nucleus", 31, 32) %>% 
-  pack_rows("Vacuole", 33, 35) %>% 
-  pack_rows("Peroxisome", 36, 37) %>% 
-  pack_rows("Proteasome", 38, 41) %>% 
-  pack_rows("Cell wall, cell surface, fungal biofilm matrix", 42, 49) %>% 
-  pack_rows("Cytoskeleton", 50, 50) %>% 
-  pack_rows("Ribosome", 51, 52) %>% 
+  pack_rows("Cytoplasm", 1, 14) %>% 
+  pack_rows("Mitochondria", 15, 25) %>% 
+  pack_rows("Nucleus", 26, 27) %>% 
+  pack_rows("Vacuole", 28, 29) %>% 
+  pack_rows("Peroxisome", 30, 31) %>% 
+  pack_rows("Proteasome", 32, 33) %>% 
+  pack_rows("Cell wall, cell surface, fungal biofilm matrix", 34, 38) %>% 
+  pack_rows("Ribosome", 39, 40) %>% 
   footnote(alphabet = c("Protein localisation was inferred from sequence 

### 2019-06-30 inst/manuscript/manuscript.Rmd
Fix missing volcano plot labels

@@
                      group = group, 
+                     use_labels = TRUE,
                      label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
@@
                      group = group, 
+                     use_labels = TRUE, 
                      label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
@@
 
-```{r figure4Plots, include=FALSE}
+```{r figure3Plots, include=FALSE}
 # import FungiFun2 GO enrichment results

### 2019-07-01 README.Rmd
Update title and authors in documentation

@@
 ---
-output: github_document
+output:
+  github_document:
+    toc: TRUE
+    toc_depth: 4
 ---
@@
 
-> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Anderson, M. A., 
-Bleackley, M. R. (2019) Sur7 family proteins are putative markers for
-_Candida albicans_ extracellular vesicles. Mol. Cell. Proteomics, submitted.
+> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
+Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
+claudin-like Sur7 family proteins and Rho GTPases. Mol. Cell. Proteomics, 
+submitted.
 
@@
 > Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Anderson, M. A., 
-Bleackley, M. R. (2019) Research compendium for: _Sur7 family proteins are_
-_putative markers for_ Candida albicans _extracellular vesicles_, 2019. 
-Version x.x.x. Zenodo. URL.
+Bleackley, M. R. (2019) _Protein markers for_ Candida albicans _EVs include_ 
+_claudin-like Sur7 family proteins and Rho GTPases_, version x.x.x. Zenodo. URL.
 

### 2019-07-01 inst/manuscript/manuscript.Rmd
Update title and authors in documentation

@@
    **Protein markers for *Candida albicans* EVs include claudin-like Sur7 
-   family proteins and GTPases**
+   family proteins and Rho GTPases**
 author: | 

### 2019-07-01 R/atcc_exp.R

@@ -18,7 +18,8 @@
 #'   \item{\strong{replicate}}{Biological replicate.}
 #' }
 #'
-#' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A.,
-#' Bleackley, M. R. (2019) Sur7 family proteins are putative markers for
-#' \emph{Candida albicans} extracellular vesicles. Mol. Cell. Proteomics, submitted.
+#' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
+#' M. A., Bleackley, M. R. (2019) Protein markers for \emph{Candida albicans}
+#' EVs include claudin-like Sur7 family proteins and Rho GTPases.
+#' Mol. Cell. Proteomics, submitted.
 "atcc_exp"

### 2019-07-01 R/biofilm_exp.R

@@ -18,7 +18,8 @@
 #'   \item{\strong{replicate}}{Biological replicate.}
 #' }
 #'
-#' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A.,
-#' Bleackley, M. R. (2019) Sur7 family proteins are putative markers for
-#' \emph{Candida albicans} extracellular vesicles. Mol. Cell. Proteomics, submitted.
+#' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
+#' M. A., Bleackley, M. R. (2019) Protein markers for \emph{Candida albicans}
+#' EVs include claudin-like Sur7 family proteins and Rho GTPases.
+#' Mol. Cell. Proteomics, submitted.
 "biofilm_exp"

### 2019-07-01 R/nta.R

@@ -41,7 +41,8 @@
 #'
 #' @format An object of class \code{data.frame} with 42,000 observations (rows) and 7 variables (columns).
 #'
-#' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A.,
-#' Bleackley, M. R. (2019) Sur7 family proteins are putative markers for
-#' \emph{Candida albicans} extracellular vesicles. Mol. Cell. Proteomics, submitted.
+#' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
+#' M. A., Bleackley, M. R. (2019) Protein markers for \emph{Candida albicans}
+#' EVs include claudin-like Sur7 family proteins and Rho GTPases.
+#' Mol. Cell. Proteomics, submitted.
 "nta"

### 2019-07-01 R/yeast.R

@@ -65,7 +65,8 @@
 #'
 #' @format An object of class \code{data.frame} with 1997 observations (rows) and 97 variables (columns).
 #'
-#' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A.,
-#' Bleackley, M. R. (2019) Sur7 family proteins are putative markers for
-#' \emph{Candida albicans} extracellular vesicles. Mol. Cell. Proteomics, submitted.
+#' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
+#' M. A., Bleackley, M. R. (2019) Protein markers for \emph{Candida albicans}
+#' EVs include claudin-like Sur7 family proteins and Rho GTPases.
+#' Mol. Cell. Proteomics, submitted.
 "yeast"

### 2019-07-01 inst/manuscript/manuscript.Rmd
Minor fixes to manuscript and supplement

@@
 
-f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:3,6, 27,29,32:33, 46,49,51:52), f3_pal) + 
+f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:3,6, 27,29,33,40, 46,49,51:52), f3_pal) + 
   annotate("text", x = 12, y = 70, label = "bold('ATCC90028')", parse = TRUE)
 
-f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4, 62,64:66, 86:89), f3_pal) + 
+f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4, 62,65:66,76, 86:89), f3_pal) + 
   annotate("text", x = 12, y = 70, label = "bold('ATCC10231')", parse = TRUE)

### 2019-07-01 inst/manuscript/manuscript_supplement.Rmd
Minor fixes to manuscript and supplement

--- 2019-06-28 inst/manuscript/manuscript_supplement.Rmd
@@
 title: | 
-   **Protein markers for *Candida albicans* EVs include claudin-like Sur7 
-   family proteins and GTPases**
+   **Supplement to: Protein markers for *Candida albicans* EVs include
+   claudin-like Sur7 family proteins and Rho GTPases**
 author: | 
@@
               those identified as the best candidates for negative
-              EV markers according to the criteria depicted in Figure 1."
+              EV markers according to the criteria depicted in Figure S1."
 

### 2019-07-01 inst/manuscript/supplement_files/sfile_S2_S4_S5.R

@@ -577,7 +577,7 @@ s5 <- plot_heatmap(mt = s5_table_filt,
                    k = 5,
                    cluster_split = FALSE) %>%
   mutate(cluster = recode(cluster,
-                          "1" = 4, "2" = 1, "3" = 5, "4" = 2, "5" = 3)) %>%
+                          "1" = 3, "2" = 1, "3" = 5, "4" = 4, "5" = 2)) %>%
   arrange(cluster) %>%
   select(-order) %>%
   bind_rows(s5_table_excl) %>%
@@ -588,15 +588,16 @@ s5 <- plot_heatmap(mt = s5_table_filt,
          Feature_name = match_id(id, uniprot,
                                  "CGD_gene_name", "CGD_feature_name")) %>%
   select(Accession, CGDID, Feature_name, id, Function,
-         y_lfc, a9_lfc, a1_lfc, b_lfc, cluster) %>%
+         b_lfc, a1_lfc, a9_lfc, y_lfc, cluster) %>%
   rename("Protein name" = id,
          "Feature name" = Feature_name,
-         "DAY286 yeast log2FC" = y_lfc,
-         "ATCC90028 log2FC" = a9_lfc,
-         "ATCC10231 log2FC" = a1_lfc,
          "DAY286 biofilm log2FC" = b_lfc,
+         "ATCC10231 log2FC" = a1_lfc,
+         "ATCC90028 log2FC" = a9_lfc,
+         "DAY286 yeast log2FC" = y_lfc,
          "Cluster" = cluster)
 s5[390, 4] <- "EVP1"
 
 #### export ####
-writexl::write_xlsx(s5, "inst/manuscript/supplement_files/sfile_S5.xlsx")
+writexl::write_xlsx(list("Fig. 5 Heatmap clusters" = s5),
+                    "inst/manuscript/supplement_files/sfile_S5.xlsx")

### 2019-07-03 README.Rmd
Update root README.md

@@
 
-```{r, echo = FALSE}
+```{r, echo=FALSE}
 knitr::opts_chunk$set(collapse = TRUE,
@@
 
-It has been permanently archived at Zenodo with the DOI shown above.
+It has been permanently archived at Zenodo with the DOI shown above. The raw 
+MS data has been deposited in the ProteomeXchange Consortium database via 
+the PRIDE partner repository with the data set identifiers PXD014367, 
+PXD014388, and PXD014389.
 
@@
 > Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Anderson, M. A., 
-Bleackley, M. R. (2019) _Protein markers for_ Candida albicans _EVs include_ 
-_claudin-like Sur7 family proteins and Rho GTPases_, version x.x.x. Zenodo. URL.
+Bleackley, M. R. (2019) Research compendium for "Protein markers for 
+_Candida albicans_ EVs include claudin-like Sur7 family proteins and Rho 
+GTPases". version x.x.x. Zenodo. URL.
 
@@
     ├── NAMESPACE            # Auto-generated file for function export
-    ├── README.Rmd           # R markdown file to produce README.md
+    ├── README.Rmd           # Rmarkdown file to produce README.md
     ├── README.md            # Description of research compendium
@@
 
-#### 1. Downloading directly from GitHub
-You can download the compendium as a zip from from this URL: 
-<https://github.com/csdaw/candidaev/archive/master.zip>. 
-Note that the contents of `/data-raw` is not installed when the package is 
-installed but instructions for downloaded just these files is provided
-[here](https://github.com/csdaw/candidaev/tree/master/data-raw).
+#### 1. Installing the package using R and `devtools`
+
+This research compendium can be installed as an R package `candidaev` from 
+GitHub using `devtools`. A full installation will include all the functions and 
+data included in the package as well as some HTML vignettes,
+and the manuscript `.Rmd` file which can be used to reproduce the manuscript as
+it was submitted.
+
+A partial installation will only install functions and data, which can be
+used to analyse other MaxQuant `.txt` files.
+
+```{r gh-install, eval=FALSE}
+# install the devtools package from CRAN if not already installed
+# install.packages("devtools")
+
+# install partial compendium (functions, data)
+devtools::install_github("csdaw/candidaev", 
+                         INSTALL_opts = "--no-inst")
+
+# install full compendium (functions, data, vignettes, manuscript) 
+# and other packages required to build vignettes and manuscript
+devtools::install_github("csdaw/candidaev", 
+                         build_opts = c("--no-resave-data", "--no-manual"), 
+                         dependencies = TRUE)
+```
+
+**Note:** the contents of `/data-raw` and `/inst/manuscript/supplement_files` 
+are not installed when the package is 
+installed using `install_github`. Instead, `/data-raw` can be manually 
+downloaded from 
+[here](https://github.com/csdaw/candidaev/tree/master/data-raw) and 
+`/inst/manuscript/supplement_files` can be manually downloaded from 
+[here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).
 
@@
 
-#### 3. Installing the package using R and `devtools`
+The research compendium can be downloaded from GitHub as is using `git`. 
+First install git from [here](https://git-scm.com/), navigate to a directory of 
+choice then execute this line at a Bash prompt:
 
-This research compendium can be installed as an R package `candidaev` from 
-GitHub using `devtools`:
-```{r gh-install, eval = FALSE}
-# install.packages("devtools")
-devtools::install_github("csdaw/candidaev")
+```
+git clone https://github.com/csdaw/candidaev.git
 ```
 
-### Using the `candidaev` package
+**Note:** the `candidaev` package must be installed to function.
+
+#### 3. Downloading directly from GitHub
+
+The research compendium can be downloaded from GitHub as a zip using this URL:
+<https://github.com/csdaw/candidaev/archive/master.zip>.
+
+**Note:** the `candidaev` package must be installed to function.
+
+### Using the `candidaev` package after installation
+
+#### Accessing included MS data
+
+The MaxQuant `proteinsGroups.txt` files on which the analyses in this 
+compendium are based is available from the PRIDE data sets mentioned above. 
+They are also included when the `candidaev` package is installed, 
+and can be accessed with:
+
+```{r, eval=FALSE}
+library(candidaev)
+
+data(atcc)
+
+data(biofilm)
+
+data(yeast)
+```
+
+#### Viewing the vignettes
+
+Three HTML vignettes detailing the analysis procedures used in the manuscript 
+are included in this research compendium. These 
+vignettes can be viewed with:
+
+```{r, eval=FALSE}
+# if full compendium package was installed with devtools::install_github
+browseVignettes("candidaev")
+
+# if the partial compendium package was installed 
+# the vignettes are not included. Please install the full compendium.
+```
+
+#### Building the manuscript
+
+To generate the reproducible manuscript, an installation of LaTeX is required. 
+TinyTex is a good option for this and can be installed using:
+
+```{r, eval=FALSE}
+# install TinyTex R package
+install.packages("tinytex")
+
+# install TinyTex LaTex distribution
+tinytex::install_tinytex()
+```
+
+Then the manuscript (and supplement) can be built using:
+
+```{r, eval=FALSE}
+# requires LaTeX installation and full compendium installation
+rmarkdown::render(system.file("manuscript", "manuscript.Rmd", 
+                              package = "candidaev"))
+rmarkdown::render(system.file("manuscript", "manuscript_supplement.Rmd", 
+                              package = "candidaev"))
+```
 

### 2019-07-03 R/README.Rmd
Update other README.md

@@
 
-```{r, echo = FALSE}
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  comment = "#>",
-  fig.path = "README-"
-)
+```{r, echo=FALSE}
+knitr::opts_chunk$set(collapse = TRUE,
+                      comment = "#>")
 ```
@@
 
-This directory contains R script files used throughout the project.
+## Description
 
-Each file contains several custom functions which have been
-documented using roxygen2 skeletons.
+This directory contains R script files used throughout the project. Each file 
+contains one custom function or one data.frame which has been
+documented using an roxygen2 skeleton.
 
-# contents
+After installing `candidaev`, an index of all the included 
+functions/data.frames can be viewed in R using:
+
+```{r, eval=FALSE}
+help(package = "candidaev")
 ```
-    .
-    ├── ...
-    ├── /R
-    │    ├── file1.R          # Functions for x
-    │    ├── file2.R          # Functions for y
-    │    ├── file3.R          # Functions for z
-    │    ├── README.Rmd       # R markdown file to produce README.md
-    │    └── README.md        # Description of /R directory
-    └── ...
-
-```

### 2019-07-03 data-raw/README.Rmd
Update other README.md

@@
 
-## description
-This directory contains all of the raw data files used in this project. These files are
-*not* included when the package is installed using `devtools::install_github()`. Rather 
-*'clean'* versions of the `.csv` and `.tab` files are provided in the [`/data`](../data) 
-folder as `.rda` files which are accessible once the package has been installed and 
-loaded or attached.
+## Description
+This directory contains all of the raw data files used in this project. 
+These files are *not* included when the package is installed using 
+`devtools::install_github()`. Rather *'clean'* versions of the `.csv` and 
+`.tab` files are provided in the [`/data`](../data) folder as `.rda` files 
+which are accessible once the package has been installed and loaded or attached.
 
-To access these raw files:
+Some different ways to access these raw files include:
 
@@
 2. Copy the url for the desired directory, paste into 
-[DownGit](https://minhaskamal.github.io/DownGit/#/home), then download as a `.zip`.
+[DownGit](https://minhaskamal.github.io/DownGit/#/home), then 
+download as a `.zip`.
 
@@
 
-4. Clone this repository.
+4. Clone this repository using `git`.
 
-## contents
+## Contents
 ```
@@
     ├── /data-raw
-    │    ├── /external       # Supplementary data tables from other Candida EV proteomics papers
     │    ├── /lcms           # proteinGroups.txt files output by MaxQuant
-    │    ├── /nta            # Nanosight ns300 .csv summary tables
-    │    ├── /qubit          # Qubit 4 EV protein quantification data 
+    │    ├── /nta            # Nanosight NS300 .csv summary tables
     │    ├── /reference      # UniProt and Candida Genome Database reference tables

### 2019-07-03 inst/manuscript/README.Rmd
Update other README.md

@@
 
-```{r, echo = FALSE}
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  comment = "#>",
-  fig.path = "README-"
-)
+```{r, echo=FALSE}
+knitr::opts_chunk$set(collapse = TRUE,
+                      comment = "#>")
 ```
 
-# /vignettes
+# /inst/manuscript
 
-## description
-This directory contains the submitted manuscript (see `manuscript.pdf`) 
-for this paper :
+## Description
 
-> Authors, (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>
+This directory contains the submitted manuscript, supplemental figures and 
+tables, and supplemental files for our paper:
 
-It also contains a more detailed analysis of the LC-MS/MS data, upon which the manuscript 
-is based (see `analysis.md` or `analysis.html`). The 
-Rmarkdown (`.Rmd`) files used to generate these documents are provided.
+> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
+Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
+claudin-like Sur7 family proteins and Rho GTPases. Mol. Cell. Proteomics, 
+submitted.
 
-Both the manuscript and the analysis documents *are* included as vignettes in this 
-package so they can be easily viewed (or regenerated completely from the raw data) if 
-the package is installed. Alternatively, one can download these documents directly 
-from this GitHub repository.
+The Rmarkdown (`.Rmd`), `.svg`, and `.R` files used to generate these 
+documents are provided along with the derived `.pdf` and `.csv` files.
 
-## how to access the manuscript
-
-## how to access the analysis
-
-## contents
+## Contents
 ```
@@
     ├── ...
-    ├── /vignettes
-    │    ├── /figures            # Contains figures
-    │    ├── /components         # Contains required components for knitting manuscript and analysis
-    │    ├── analysis.Rmd        # R markdown file to produce analysis.md or analysis.html
-    │    ├── analysis.html       # Full analysis upon which the manuscript is based.
-    │    ├── analysis.md         # Full analysis upon which the manuscript is based.
-    │    ├── manuscript.Rmd      # R markdown file to produce manuscript.pdf or manuscript.docx
+    ├── /inst
+    │    ├── /manuscript
+    │         ├── /components                 # Contains required components for building the manuscript
+    │         ├── /figures                    # Contains .svg and .csv files used to make some figures
+    │         ├── /supplement_files           # Contains .R scripts used to generate supplemental files
+    │         ├── manuscript.Rmd              # R markdown file to produce manuscript.pdf
     │         ├── manuscript.pdf              # Final submitted manuscript
+    │         ├── manuscript_supplement.Rmd   # R markdown file to produce manuscript_supplement.pdf
+    │         ├── manuscript_supplement.pdf   # Final submitted supplemental figures and tables
     │         ├── README.Rmd                  # R markdown file to produce README.md
-    │    └── README.md           # Description of /vignettes directory
+    │         └── README.md                   # Description of /inst/manuscript directory
     └── ...

### 2019-07-04 inst/manuscript/manuscript.Rmd
Add introduction

@@
 mainfont: Times New Roman
-linestretch: 1.5
+linestretch: 2
 header-includes:
@@
 
-The abstract goes here. Here is a citation [@liao2012].
-
-Here is another citation [@gil-bona2015].
-
-And another [@lin2014].
-
 \newpage
@@
 
-Here is a citation [@marwick2017].
+Fungal infections are ubiquitous and are estimated to affect over 20% of the 
+world’s population [@havlickova2008]. These infections range from 
+non-life-threatening mycoses of the skin and nails, to deadly systemic 
+infections. They represent a significant burden to healthcare systems, with the 
+direct medical cost of fungal disease in the United States in 2017 estimated to 
+be \$7.2 billion [@benedict2018]. The fungi responsible for most fungal 
+infections worldwide are the various species of _Candida_ [@pfaller2007]. 
+_Candida_ is primarily associated with relatively harmless superficial infections 
+[@brown2012], but infections of the bloodstream or internal organs are 
+associated with mortality rates as high as 75% [@guinea2014; @kullberg2015]. 
+Over 12,000 people were hospitalised for invasive candidiasis in the US in 2017 
+alone, at a cost of almost \$1.2 billion [@benedict2018]. The species 
+responsible for the majority of _Candida_ infections is _Candida albicans_ 
+[@guinea2014]. _C. albicans_ infections are most often treated with two classes 
+of antifungals, the azoles which target biosynthesis of the fungal-specific 
+sterol ergosterol, and the echinocandins, which target biosynthesis of the major
+cell wall polysaccharide 1,3-β-glucan [@pappas2016]. Resistance to these and 
+other antifungals has begun to emerge 
+[@fisher2018; @perlin2015; @perlin2017; @whaley2017] making the development of 
+new antifungals with novel mechanisms of action paramount. Understanding the 
+interface between the host and pathogen will help to identify new targets for 
+controlling _C. albicans_ infections.
 
@@
 \newpage
+
 # References 
+\setstretch{1.5}
 <div id="refs"></div>
@@
 
-```{r figure1Data, include=FALSE}
+```{r figure1Data, include=FALSE, cache=TRUE}
 # construct data.frame with nta experiment info

### 2019-07-04 inst/manuscript/manuscript.Rmd
Add full introduction

@@
 
+Extracellular vesicles (EVs) are key factors in the progression of many diseases 
+ranging from cancer [@xu2018] to neurodegenerative diseases [@quek2017] and 
+bacterial infections [@pathirana2016]. EVs are defined as “particles naturally 
+released from the cell that are delimited by a lipid bilayer and cannot 
+replicate” [@thery2018]. Packaging of cargo into EVs is a method for the 
+coordinated release of biological molecules via a non-classic method of 
+secretion.  This facilitates intercellular communication both within an 
+organism [@maas2017] and between organisms [@schorey2015].
+
+Recently, EVs have 
+been proposed to function in the pathogenesis of fungal disease, particularly 
+in yeast infections including those from the genera _Cryptococcus_ 
+[@bielska2018; @oliveira2010b; @rodrigues2008], _Paracoccidioides_ 
+[@dasilva2015a; @vallejo2011], and _Candida_ 
+[@joffe2016; @vargas2015; @wolf2015]. The cargo of fungal EVs comprises 
+proteins [@bleackley2019], nucleic acids [@dasilva2015], lipids 
+[@oliveira2009; @rodrigues2007; @vargas2015; @wolf2015] and carbohydrates 
+[@dasilva2015a; @rodrigues2007]. Fungal EVs activate innate immune cells in 
+vitro [@dasilva2016; @oliveira2010b; @vargas2015; @wolf2015] and are responsible 
+for the hypervirulence of a _Cryptococcus gattii_ strain that caused disease in 
+immunocompetent individuals [@bielska2018]. Given the potential roles for EVs in 
+host-pathogen interactions, there is significant motivation to better understand 
+the biology of fungal EVs.
+
+_C. albicans_ EVs are typical of fungal EVs. They contain proteins, lipids, 
+nucleic acids and carbohydrates 
+[@dasilva2015; @gil-bona2015b; @vargas2015; @wolf2015; @zarnowski2018]. 
+Activation of murine macrophages and dendritic cells by EVs from _C. albicans_ 
+indicates a potential role for EVs in modulating the innate immune response to 
+the fungus [@vargas2015; @wolf2015]. Formation of biofilms is a critical 
+component of _C. albicans_ pathogenesis [@nobile2015] and the biofilm matrix 
+provides a protective layer for the fungus against antifungal drugs [@taff2012]. 
+The cargo of EVs produced by _C. albicans_ biofilms includes key proteins and 
+carbohydrates for biofilm biogenesis, making EVs crucial contributors to the 
+establishment of biofilms [@zarnowski2018]. Furthermore, “add-back” of EVs from 
+wildtype biofilms restored the loss of azole resistance in biofilms formed by 
+strains with deletions in genes encoding important enzymes for matrix 
+generation [@zarnowski2018]. That is, EVs also function in antifungal drug 
+resistance.
+
+The tools and techniques for the study of fungal EVs have been adapted from 
+those established for mammalian systems, where EVs are most intensively 
+studied. Many of the cutting-edge experimental techniques for isolation, 
+tracking, and analysis of mammalian EVs are dependent on protein markers 
+[@lotvall2014]. They include identifying fractions containing EVs after density 
+gradient centrifugation [@greening2015] or size exclusion chromatography 
+[@gamez-valero2016], purification of EVs via immunoaffinity capture [@oksvold2015], 
+and imaging of EV release and uptake [@suetsugu2013]. Unfortunately, proteomic 
+analyses of fungal EVs have revealed that the markers that have been so useful 
+for the isolation and study of mammalian EVs are not present in fungal EVs 
+[@bleackley2019]. Thus, there are differences in the protein cargo and possibly 
+the biogenesis of EVs from fungi and mammalian cells, and _de novo_ 
+identification of fungal EV markers is essential. Inconsistencies between 
+published data sets on the protein content of fungal EVs [@bleackley2019] means 
+that a robust proteomic analysis of EVs from a particular species is required 
+to provide an adequate data set for EV marker identification. In this study, we 
+have addressed this problem by performing in-depth proteomic analyses on 
+multiple _C. albicans_ strains to define a set of broadly applicable 
+_C. albicans_ EV markers.
+
+We employed label-free quantitative proteomics to generate EV and whole cell 
+lysate (WCL) proteomes for a selection of different _C. albicans_ strains and 
+morphologies; DAY286 yeast, DAY286 biofilm, ATCC90028 yeast, and ATCC10231 
+yeast. By comparing the EV versus WCL data across all four strains we 
+identified 39 putative EV markers which are enriched in _C. albicans_ EVs 
+regardless of source, cell strain, or morphology. These candidate protein 
+markers include GTPases, enzymes crucial for cell wall synthesis, and 
+plasma membrane proteins resembling mammalian tetraspanins or claudins. 
+The “minimal information for studies of EVs” (MISEV) 2018 position statement 
+indicates that, in addition to demonstrating the enrichment of EV marker 
+proteins in EV preparations, a deficiency of non-EV proteins should also be 
+shown [@thery2018]. With this in mind, we identified 40 proteins that were 
+depleted in _C. albicans_ EVs compared to the WCL from the four strains. 
+Validation of these putative EV markers in vitro will allow future _C. albicans_ 
+EV research to align better with the recommendations set out in MISEV2018. 
+Furthermore, robust _C. albicans_ EV markers will allow adaptation of mammalian 
+EV analysis techniques for use in the study of EVs in _C. albicans_ pathogenesis 
+and will provide potential new targets for the development of novel antifungals.
+
 # Experimental procedures

### 2019-07-05 inst/manuscript/manuscript.Rmd
Add abbreviations
Also:
 - Fix typo in table 1

@@
 
+A1 - ATCC10231
+
+A9 - ATCC90028
+
+DAY B - DAY286 biofilm
+
+DAY Y - DAY286 yeast
+
 EV - extracellular vesicle
+
+Evp1 - extracellular vesicle protein 1 (orf19.6741)
+
+Log<sub>2</sub>(FC) - log<sub>2</sub> fold change
+
+MCC - membrane compartment of Can1
+
+MDS - multidimensional scaling
+
+MISEV - minimal information for studies of EVs
+
+sEVs - small EVs
+
+SP - signal peptide
+
+TEMs - tetraspanin enriched microdomains
+
+TM - transmembrane domain
+
+VDM - vesicle depleted medium
+
+WCL - whole cell lysate
 
@@
   arrange(pack_row) %>% 
-  mutate(VDS = c(rep("", 11), "Y", rep("", 7), "Y", rep("", 7), 
+  mutate(VDM = c(rep("", 11), "Y", rep("", 7), "Y", rep("", 7), 
                  rep("Y", 7), "", rep("Y", 4)))

### 2019-07-05 inst/manuscript/manuscript.Rmd
Add experimental procedures

@@
 
-## Subsection 1
-
-## Subsection 2
+## _C. albicans_ strains and maintenance
+
+_C. albicans_ strains used in this study were DAY286 [@davis2002], ATCC90028, 
+and ATCC10231. All strains were maintained on YPD Agar plates (1% yeast extract, 
+2% peptone, 2% dextrose, 2% agar). Liquid starter cultures were grown overnight 
+in YPD medium (1% yeast extract, 2% peptone, 2% dextrose) at 30°C and 300 rpm.
+
+## Yeast culture conditions
+
+For isolation of EVs from yeast form _C. albicans_ (DAY286, ATCC90028, 
+ATCC10231), YPD starter cultures were used to inoculate 150 or 300 mL YPD at an 
+OD~600~ = 0.2 in a baffled flask. Cultures were incubated at 30°C overnight 
+(approximately 20h). The culture OD~600~ was measured immediately prior to EV 
+isolation.
+
+## Biofilm culture conditions
+
+Biofilms (DAY286) were generated based on the method described in [@ramage2002] 
+with modifications. Briefly, 500 mL pre-warmed ½ strength RPMI (250 mL RPMI 
+1640 (Sigma), 0.165 M MOPS (Sigma) and 250 mL 3.6% dextrose) was inoculated 
+using a liquid starter culture to 1.0 x 10^6^ cells/mL. Five 25 x 25 
+cm non-treated bioassay dishes (Thermo Fisher Scientific) were each filled with 
+100 mL of inoculated ½ RPMI and incubated statically for 4 h at 37°C to allow 
+for adhesion of cells to the dish. Following cell adhesion, the culture medium 
+and any non-adherent cells was decanted and replaced with 200 mL pre-warmed 
+full strength RPMI. Biofilms were formed by incubating the dishes for 54 h at 
+37°C with agitation at 28 rpm in an Incu-Shaker Mini (Benchmark Scientific).
+
+## EV isolation
+
+EVs were isolated according to the method described in [@rodrigues2007] with 
+minor modifications. In brief, yeast cells or biofilm fragments were separated 
+from the culture supernatants by centrifugation at 4,000 x g for 15 min 
+(75003607 rotor, Thermo Scientific), then 15,000 x g for 30 min 
+(JLA 16.250 rotor, Beckman Coulter). Supernatants were 0.45 μm (Millipore) 
+filtered then centrifuged twice at 100,000 x g for 1 h (45Ti rotor, 
+Beckman Coulter) to pellet EVs which were resuspended in phosphate buffered 
+saline (137 mM NaCl, 2.7 mM KCl, 10 mM Na~2~HPO~4~, 1.8 mM KH~2~PO~4~) (PBS). 
+An aliquot of yeast cells (250 µL) was reserved for preparation of yeast whole 
+cell lysate. Similarly, 250 μL of biofilm scrapings were resuspended in PBS for 
+preparation of biofilm lysate.
+
+## Preparation of whole cell lysate and protein quantification
+
+Samples were washed three times with PBS prior to the addition of approximately 
+400 µL of acid washed glass beads (Sigma). Cells were lysed using a TissueLyser 
+(Qiagen) at 30 bps for 3 x 1 min bursts with 1 min incubations on ice between 
+bursts. Debris and beads were pelleted by centrifugation for 5 min at 
+23,000 x g at 4 °C. The supernatant was retained as the respective lysate 
+sample. Protein concentration of EVs and whole cell lysates (WCL) was 
+determined using a Qubit^TM^ 4 fluorimeter (Life Technologies) and the 
+Qubit^TM^ protein assay kit according to the manufacturer’s instructions.
+
+## Nanoparticle tracking analysis
+
+The particle size and concentration of EV samples was determined using a 
+NanoSight NS300 equipped with a 405 nm (blue) laser (Malvern Instruments).  
+Immediately prior to injection, EVs were diluted between 1:250 and 1:6000 
+in 0.22 μm (Millipore) filtered PBS to bring the particle concentration within 
+the manufacturer’s recommended range (10^7^ – 10^9^ particles/mL). NTA software 
+version 3.2 was used to record data in 60 s reads in triplicate. Instrument 
+settings included: a syringe infusion rate of 70, temperature held at 25°C, 
+a camera level of 11, and a detection threshold of 6. The particle 
+concentrations and particle size parameters were recorded. Dilution 
+factor correction and averaging of data across biological replicates was 
+performed using the R package _tidyNano_ [@nguyen2019].
+
+## Transmission electron microscopy
+
+Carbon-coated 400-mesh copper grids (ProSciTech) were glow discharged for 1 
+min in a K950X turbo evaporator coupled to a K350 glow discharge unit 
+(Quorum Technologies Ltd). EVs (5 µL) were deposited onto the grid and 
+incubated for 1 min. Grids were then washed once with ultrapure water and 
+negatively stained three times with 2% (v/v) uranyl acetate (Agar Scientific). 
+Excess solution was blotted off and the grids were dried overnight. A JEM 2100 
+electron microscope (JEOL Ltd) operated at 200 kV was used for imaging.
+
+## Experimental design and statistical rationale
+
+A total of 14 EV and WCL samples from four different _C. albicans_ strains were 
+used for proteomics and NTA analyses; DAY286 yeast (n = 3), ATCC90028 yeast 
+(n = 3), ATCC10231 yeast (n = 3), and DAY286 biofilm (n = 5). The EV and WCL 
+samples from an individual biological replicate were paired as they were derived 
+from cells in the same culture or biofilm. Biofilm EVs and WCLs were obtained 
+from 5 independent biofilms on different days. Yeast EVs and WCLs were obtained 
+from 3 independent yeast cultures in parallel on different days for each strain. 
+Preparation of EV and WCL proteomics samples and MS data acquisition was 
+performed in three separate batches; DAY286 yeast, DAY286 biofilm, and then 
+both ATCC strains. Proteomics samples were randomised prior to injection and 
+each biological replicate was injected twice. The raw data from both injections 
+was combined into one sample during protein identification and quantification. 
+All proteomics statistical and data analyses were performed using R version 
+3.6.0 [@rcoreteam2018], Statistical tests, multiple comparison corrections and 
+important individual R and Bioconductor packages are referenced where they have 
+been used.
+
+## Sample preparation for mass spectrometry
+
+EVs or WCLs (15 μg protein) were boiled in LDS sample buffer (Life Technologies) 
+and TCEP (Thermo Fisher Scientific), then separated by short-range SDS-PAGE 
+[@greening2016]. The gel was fixed in 50% (v/v) methanol, 7% (v/v) acetic acid 
+for 30 min, and the samples were excised. The proteins were reduced (2 mM TCEP, 
+1 h) and alkylated (40 mM iodoacetamide, 30 min in the dark) before digestion 
+(1 μg trypsin, 18 h at 37°C). Peptides were then extracted from the gel pieces 
+with 85% (v/v) ACN, 0.5% (v/v) TFA, lyophilised and resuspended in 5% (v/v) 
+ACN, 0.5% (v/v) TFA.
+
+## Mass spectrometry (ESI-LC-MS/MS) of EVs and WCL proteins
+
+Peptides were analysed as described previously [@fingerhut2018] with 
+modifications. Using a nanoflow UPLC instrument (Scientific^TM^ 
+UltiMate^TM^ 3000 RSLCnano, Thermo Fisher Scientific), the 
+reconstituted peptides were loaded onto a precolumn (C18 PepMap 300 μm ID x 2 cm 
+trapping column, Thermo Fisher Scientific) and washed prior to separation using 
+a 90 min linear ACN gradient on an analytical column (BEH C18, 1.7 μm, 130 Å 
+and 75 μm ID x 25 cm, Waters). The nanoflow UPLC was coupled on-line to a 
+Q Exactive HF mass spectrometer (Thermo Fisher Scientific) with a 
+nanoelectrospray ion source (Thermo Fisher Scientific). The Orbitrap of the Q 
+Exactive HF was used for MS and the linear trap was used for MS/MS.
+
+Data were collected in data-dependent acquisition mode using an MS scan range 
+of m/z 350 – 1500 and resolution of 60,000. HCD MS/MS spectra were collected 
+for the 15 most intense ions per MS scan at 15,000 resolution with a normalised 
+collision energy of 28% and an isolation window of 1.4 m/z. Dynamic exclusion 
+parameters were set as follows: exclude isotope on, duration 30 sec and peptide 
+match preferred. Other Orbitrap instrument parameters included an MS maximum 
+injection time of 30 ms with AGC target 3 x 10^6^, for a maximum 
+injection time of 25 ms with an AGT target of 1 x 10^5^.
+
+## Database search and protein identification
+
+Tandem MS data collected for EVs and WCLs were processed in MaxQuant 
+version 1.6.0.16 [@tyanova2016]. Andromeda was used to search the data against 
+the UniProt _C. albicans_ reference proteome (UP000000559; downloaded 
+16/06/2018; 6035 entries) and the common contaminants and decoys list [@cox2011]. 
+Trypsin was selected as the digestion enzyme and up to 2 missed cleavages were 
+allowed. Carbamidomethylation of cysteine was set as a fixed modification and 
+oxidation of methionine and N-terminal acetylation were set as variable 
+modifications. Peptide mass tolerances were 20 ppm (first search) and 4.5 ppm 
+(main search), and false discovery rate (FDR) cut offs were 0.01 for both 
+proteins and peptides. Minimum and maximum peptide lengths were set to 8 and 25 
+respectively and match between runs was not selected. Label-free quantification 
+(LFQ) of protein abundances was performed using the MaxLFQ algorithm [@cox2014]. 
+Fast LFQ was selected and normalisation was skipped. The proteinGroups.txt 
+MaxQuant output was used for further analyses. Metadata for identified proteins 
+(localisation, topology, function) were obtained from the UniProt _C. albicans_ 
+reference proteome was well as the _C. albicans_ SC5314 Assembly 22 chromosomal 
+feature file available from the Candida Genome Database 
+(candidagenome.org/download/chromosomal_feature_files) 
+[@arnaud2005; @skrzypek2017].
+
+## Protein filtering and proteomics analysis
+
+Data processing and statistical analyses were all performed using R 
+version 3.6.0 and RStudio version 1.2.1335 [@rcoreteam2018; @rstudioinc]. 
+The DAY286 yeast, DAY286 biofilm, and ATCC proteinGroups.txt files were 
+initially processed and analysed separately. Analysis methodology and some 
+modified functions were derived from the Bioconductor package _DEP_ [@zhang2018]. 
+First, reversed and contaminant proteins as well as proteins identified by less 
+than 2 unique peptides were removed. The resulting proteins were filtered for 
+those quantified (LFQ intensity > 0) in minimum 2/3 yeast or 4/5 biofilm EV or 
+WCL biological replicates. The raw LFQ intensities, sequence coverage, 
+number of unique peptides, and MS/MS counts for these proteins can be found in 
+supplemental File S1. LFQ intensities were log~2~ transformed, then 
+normalised using the default cyclic loess normalisation method from the 
+Bioconductor package _limma_ [@ritchie2015]. Proteins were then separated into 
+two groups: those exclusive to EVs or WCL, and those quantified in both samples. 
+Missing LFQ values in the latter group were imputed using the QRILC method from 
+the R package _imputeLCMD_ [@lazar2015], while exclusive proteins were left 
+untouched. Finally, differential abundance analysis of proteins in EV versus 
+WCL was performed using empirical Bayes method from _limma_ 
+[@phipson2016; @ritchie2015]. Protein log~2~(fold changes) indicated 
+the difference in average log~2~ LFQ intensity values between EVs and 
+WCLs, this value is referred to as the log~2~(FC). The resulting 
+p-values were adjusted using the Benjamini-Hochberg approach [@benjamini1995] 
+and the significance threshold was set at an adjusted p-value of 0.01. Proteins 
+were considered significantly enriched or depleted in EVs if they had a p-value 
+less than 0.01 and a positive or negative log~2~(FC) respectively. 
+Results of the differential abundance analyses are available in supplemental 
+File S2.
+
+## Functional enrichment analysis and clustering
+
+The online tool FungiFun2 version 2.2.8 (sbi.hki-jena.de/fungifun) was used for 
+all GO term enrichment analyses [@priebe2015]. Enriched GO terms were those 
+with a Benjamini-Hochberg adjusted p-value less than 0.05. Multidimensional 
+scaling (MDS) plots were constructed using the plotMDS function from _limma_ 
+[@ritchie2015]. The top 500 proteins with the largest standard deviations 
+between the proteomics samples were used for the distance calculation. To 
+construct the heatmap in Figure 5, unsupervised clustering of log~2~(FC) 
+values for the proteins common to EVs from all strains was performed using 
+Gower’s formula via the daisy function from the R package _cluster_ [@maechler2019].
+
+## Protein localisation and attribute prediction
+
+Location information of proteins was obtained from the Candida Genome Database 
+(candidagenome.org) [@arnaud2005; @skrzypek2017]. When this information was not 
+available DeepLoc-1.0 (cbs.dtu.dk/services/DeepLoc) was used to predict 
+subcellular location [@almagroarmenteros2017]. Signal peptide and transmembrane 
+domain annotations for each protein were obtained from UniProtKB or were 
+predicted using TOPCONS2 (topcons.cbr.su.se) 
+[@theuniprotconsortium2019; @tsirigos2015]. Prediction of protein palmitoylation 
+sites was performed using CSS-PALM 4.0 (csspalm.biocuckoo.org) [@ren2008].
+
+## _C. albicans_ EV marker definition
+
+Lists of proteins significantly enriched and exclusive in EVs from each strain 
+were compared using the R package _VennDiagram_ [@chen2011]. Proteins common to 
+all four strains were selected as potential EV positive protein markers. This 
+was repeated for significantly enriched and exclusive proteins in WCL to define 
+potential EV negative protein markers. Initial candidate EV marker proteins 
+were refined using the following criteria to obtain a shortlist of the best 
+potential markers. Ideal positive EV markers were proteins that satisfied 
+MISEV2018 marker categories 1 and 2 [@thery2018] and had less than 5 transmembrane 
+domains, no recognisable signal peptide, and were not detected in 
+vesicle-depleted media [@gil-bona2015b]. Ideal negative EV marker proteins were 
+selected based on prior tagging with fluorescent proteins in literature, prior 
+detection via Western blot, and adherence to MISEV2018 marker categories
+3 or 4 [@thery2018].
+
+## Data availability
+
+The proteomics data have been deposited in the ProteomeXchange Consortium 
+database via the PRIDE partner repository [@deutsch2017; @perez-riverol2019] 
+with the data set identifiers PXD014367 (DAY286 yeast), PXD014388 (ATCC90028 
+and ATCC10231), and PXD014389 (DAY286 biofilm). These data include ‘RAW’ files, 
+peak list files, MaxQuant search engine txt output, and the UniProt C. albicans 
+reference proteome FASTA file. The proteinGroups.txt files and source code used 
+in this study is freely available in an online research compendium available at 
+github.com/csdaw/candidaev. It was constructed using the R package 
+_rrtools_ [@marwick2018] and is structured as an R package which can be used to 
+reproduce the results and manuscript as submitted. The compendium has also been 
+permanently archived at zenodo (url).
 

### 2019-07-09 README.Rmd
Update other README.md
Fix some documentation references

@@
 Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
-claudin-like Sur7 family proteins and Rho GTPases. Mol. Cell. Proteomics, 
-submitted.
+claudin-like Sur7 family proteins and Rho GTPases. _Molecular and Cellular_ 
+_Proteomics_, submitted.
 
@@
 the PRIDE partner repository with the data set identifiers PXD014367, 
-PXD014388, and PXD014389.
+PXD014388, and PXD014389. The analysis techniques and workflow used in this 
+compendium were derived from the _Bioconductor_ package 
+**[DEP](https://doi.org/10.18129/B9.bioc.DEP)**^1^.
 
@@
 [Marwick et al. (2018)](https://doi.org/10.1080/00031305.2017.1375986). 
-
-The R package [rrtools](https://github.com/benmarwick/rrtools) was used in the 
-production of this compendium.
+The R package **[rrtools](https://github.com/benmarwick/rrtools)**^2^ was used 
+in the production of this compendium.
 
@@
 
+### References
+
+1. Zhang, X., Smits, A., van Tilburg, G., Ovaa, H., Huber, W., Vermeulen, 
+   M. (2018). Proteome-wide identification of ubiquitin interactions using UbIA-MS. 
+   _Nature Protocols_, **13**, 530-550. 
+   [doi:10.1038/nprot.2017.147](https://doi.org/10.1038/nprot.2017.147)
+
+2. Marwick, B., Boettiger, C., Mullen, L. (2018). Packaging data analytical 
+   work reproducibly using R (and friends). _The American Statistician_, 
+   **72**(1), 80-88. 
+   [doi:10.1080/00031305.2017.1375986](https://doi.org/10.1080/00031305.2017.1375986)
+
 ### Accessing the compendium
@@
                          build_opts = c("--no-resave-data", "--no-manual"), 
-                         dependencies = TRUE)
+                         dependencies = TRUE, build_vignettes = TRUE)
 ```
@@
 Three HTML vignettes detailing the analysis procedures used in the manuscript 
-are included in this research compendium. These 
+are included in this research compendium. They are automatically built from 
+scratch when the full research compendium is installed with `devtools`. These 
 vignettes can be viewed with:
@@
 
-#### Building the manuscript
+#### Viewing the manuscript
+
+The manuscript `.pdf` file, as submitted, can be downloaded 
+[here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).
+
+#### Building the manuscript from scratch
 

### 2019-07-09 R/atcc_exp.R

@@ -21,5 +21,5 @@
 #' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
 #' M. A., Bleackley, M. R. (2019) Protein markers for \emph{Candida albicans}
 #' EVs include claudin-like Sur7 family proteins and Rho GTPases.
-#' Mol. Cell. Proteomics, submitted.
+#' \emph{Molecular and Cellular Proteomics}, submitted.
 "atcc_exp"

### 2019-07-09 R/biofilm.R

@@ -64,5 +64,5 @@
 #' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
 #' M. A., Bleackley, M. R. (2019) Protein markers for \emph{Candida albicans}
 #' EVs include claudin-like Sur7 family proteins and Rho GTPases.
-#' Mol. Cell. Proteomics, submitted.
+#' \emph{Molecular and Cellular Proteomics}, submitted.
 "biofilm"

### 2019-07-09 R/cgd.R

@@ -49,11 +49,11 @@
 #' }
 #' @source Arnaud, M.B., Costanzo, M. C., Skrzypek, M. S., Binkley, G., Lane, C., Miyasato, S. R., & Sherlock, G.
 #' (2005). The Candida Genome Database (CGD), a community resource for \emph{Candida albicans} gene and
-#' protein information. \emph{Nucleic Acids Research, 33}(suppl_1), D358-D363.
+#' protein information. \emph{Nucleic Acids Research}, \strong{33}(suppl_1), D358-D363.
 #' \href{https://doi.org/10.1093/nar/gki003}{doi:10.1093/nar/gki003}
 #'
 #' Skrzypek, M. S., Binkley, J., Binkley, G., Miyasato, S. R., Simison, M., & Sherlock, G. (2017).
 #' The Candida Genome Database (CGD): incorporation of Assembly 22, systematic identifiers and visualization of
-#' high throughput sequencing data. \emph{Nucleic Acids Research, 45}(D1), D592-D596.
+#' high throughput sequencing data. \emph{Nucleic Acids Research}, \strong{45}(D1), D592-D596.
 #' \href{https://doi.org/10.1093/nar/gkw924}{doi:10.1093/nar/gkw924}
 "cgd"

### 2019-07-09 R/limma_eBayes.R

@@ -34,6 +34,11 @@
 #' @return Returns an object of class \code{MArrayLM}. See \code{\link[limma]{eBayes}} for
 #' more information. This object is required for \code{\link{get_results}}.
 #'
+#' @references Zhang, X., Smits, A., van Tilburg, G., Ovaa, H., Huber, W., Vermeulen,
+#' M. (2018). Proteome-wide identification of ubiquitin interactions using UbIA-MS.
+#' \emph{Nature Protocols}, \strong{13}, 530-550.
+#' \href{https://doi.org/10.1038/nprot.2017.147}{doi:10.1038/nprot.2017.147}
+#'
 #' @examples
 #' # load dplyr
 #' library(dplyr)

### 2019-07-09 R/nta.R

@@ -44,5 +44,5 @@
 #' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
 #' M. A., Bleackley, M. R. (2019) Protein markers for \emph{Candida albicans}
 #' EVs include claudin-like Sur7 family proteins and Rho GTPases.
-#' Mol. Cell. Proteomics, submitted.
+#' \emph{Molecular and Cellular Proteomics}, submitted.
 "nta"

### 2019-07-09 R/plot_detect2.R

@@ -25,6 +25,11 @@
 #' proteins with and without missing values
 #' (generated by \code{\link[ggplot2]{ggplot}}).
 #'
+#' @references Zhang, X., Smits, A., van Tilburg, G., Ovaa, H., Huber, W., Vermeulen,
+#' M. (2018). Proteome-wide identification of ubiquitin interactions using UbIA-MS.
+#' \emph{Nature Protocols}, \strong{13}, 530-550.
+#' \href{https://doi.org/10.1038/nprot.2017.147}{doi:10.1038/nprot.2017.147}
+#'
 #' @examples
 #' # load dplyr
 #' library(dplyr)

### 2019-07-09 R/plot_imputation2.R

@@ -40,6 +40,11 @@
 #' @return Returns density plots of all input matrices, e.g. before and
 #' after imputation (generated by \code{\link[ggplot2]{ggplot}}).
 #'
+#' @references Zhang, X., Smits, A., van Tilburg, G., Ovaa, H., Huber, W., Vermeulen,
+#' M. (2018). Proteome-wide identification of ubiquitin interactions using UbIA-MS.
+#' \emph{Nature Protocols}, \strong{13}, 530-550.
+#' \href{https://doi.org/10.1038/nprot.2017.147}{doi:10.1038/nprot.2017.147}
+#'
 #' @examples
 #' # load dplyr
 #' library(dplyr)

### 2019-07-09 R/plot_normalization2.R

@@ -38,6 +38,11 @@
 #' @return Returns box plots of all input matrices, e.g. before and
 #' after normalisation (generated by \code{\link[ggplot2]{ggplot}}).
 #'
+#' @references Zhang, X., Smits, A., van Tilburg, G., Ovaa, H., Huber, W., Vermeulen,
+#' M. (2018). Proteome-wide identification of ubiquitin interactions using UbIA-MS.
+#' \emph{Nature Protocols}, \strong{13}, 530-550.
+#' \href{https://doi.org/10.1038/nprot.2017.147}{doi:10.1038/nprot.2017.147}
+#'
 #' @examples
 #' # load dplyr
 #' library(dplyr)

### 2019-07-09 R/yeast_exp.R

@@ -23,5 +23,5 @@
 #' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
 #' M. A., Bleackley, M. R. (2019) Protein markers for \emph{Candida albicans}
 #' EVs include claudin-like Sur7 family proteins and Rho GTPases.
-#' Mol. Cell. Proteomics, submitted.
+#' \emph{Molecular and Cellular Proteomics}, submitted.
 "yeast_exp"

### 2019-07-09 R/filter_na4.R
Add block argument to limma_eBayes function
Also:
 - Fix some documentation typos

@@ -152,7 +152,7 @@ filter_na4 <- function(data, logic = c("and", "or"), op = c("==", ">=", "<="),
   # get number of NA in fourth group of columns
   n_na4 <- apply(is.na(data[, c(grep(pat4, colnames(data)))]), 1, sum)
 
-  # subset data based on number of NA in two column groups
+  # subset data based on number of NA in all column groups
   if(logic == "and") {
     subset(data, sapply(n_na1, op, val1) &
              sapply(n_na2, op, val2) &

### 2019-07-09 R/limma_eBayes.R

@@ -101,9 +101,9 @@
 #' result_a9 <- result_list[[2]]
 #'
 #' @export
-limma_eBayes <- function(mat, design, contrasts) {
+limma_eBayes <- function(mat, design, contrasts, block = NULL) {
   cm <- limma::makeContrasts(contrasts = contrasts, levels = design)
-  fit <- limma::lmFit(mat, design = design)
+  fit <- limma::lmFit(mat, design = design, block = block)
 
   result <- limma::contrasts.fit(fit = fit, contrasts = cm)
 

### 2019-07-15 inst/manuscript/manuscript.Rmd
Change imputation method to bpca
Change from QRILC from limma package,
to bpca from pcaMethods package.

@@
 
-# set seed for random number generation
-set.seed(1)
-
-# reference external R script with protein function lists
-knitr::read_chunk('components/protein_funs.R')
-
 # define colour palette to distinguish between strains
@@
 
-# can't impute with so many missing values
+# won't impute with so many missing values
 # separate EV/WCL exclusive proteins (don't impute) from 
@@
 
-# proteins with missing values tend to have lower intensity
-# therefore proteins are MNAR, close to detection limit
-# use left censored imputation method
-yeast_imp <- impute_QRILC(yeast_both)
+# use bpca method from pcaMethods for missing value imputation
+yeast_imp <- pcaMethods::pca(yeast_both, method = "bpca")
+yeast_imp <- pcaMethods::completeObs(yeast_imp)
 
@@
 # extract DE results
+# adj.p.val cutoff is 0.01, log2FC cutoff is 1
 yeast_res <- get_results(efit = y_efit, 
@@
                          p_val = 0.01, 
-                         lfc = 0, 
+                         lfc = 1, 
                          type = "individual")[[1]]
@@
 
-# can't impute with so many missing values
+# won't impute with so many missing values
 # filter for proteins with 4-5 NA values in EV or WCL (don't impute)
@@
 
-# proteins with missing values tend to have lower intensity
-# therefore proteins are MNAR, close to detection limit
-# use left censored imputation method
-biofilm_imp <- impute_QRILC(biofilm_both)
+# use bpca method from pcaMethods for missing value imputation
+biofilm_imp <- pcaMethods::pca(biofilm_both, method = "bpca")
+biofilm_imp <- pcaMethods::completeObs(biofilm_imp)
 
@@
 # extract DE results
+# adj.p.val cutoff is 0.01, log2FC cutoff is 1
 biofilm_res <- get_results(efit = b_efit, 
@@
                            p_val = 0.01, 
-                           lfc = 0, 
+                           lfc = 1, 
                            type = "individual")[[1]]
@@
 ```{r atcc1, include=FALSE}
-# filter for proteins quantified in min 2/3 reps of EV or WCL
+# filter for proteins quantified in min 2/3 reps of ATCC10231 EV or WCL
 a1_norm <- filter_na2(atcc_norm, logic = "or", op = "<=", 
@@
 
-# can't impute with so many missing values
+# won't impute with so many missing values
 # separate EV/WCL exclusive proteins (don't impute) from
@@
 
-# proteins with missing values tend to have lower intensity
-# therefore proteins are MNAR, close to detection limit
-# use left censored imputation method
-a1_imp <- impute_QRILC(a1_both)
+# use bpca method from pcaMethods for missing value imputation
+a1_imp <- pcaMethods::pca(a1_both, method = "bpca")
+a1_imp <- pcaMethods::completeObs(a1_imp)
 
@@
 # extract DE results
+# adj.p.val cutoff is 0.01, log2FC cutoff is 1
 a1_res <- get_results(efit = a1_efit,
@@
                       p_val = 0.01,
-                      lfc = 0,
+                      lfc = 1,
                       type = "individual")[[1]]
@@
 ```{r atcc9, include=FALSE}
-# filter for proteins quantified in min 2/3 reps of EV or WCL
+# filter for proteins quantified in min 2/3 reps of ATCC90028 EV or WCL
 a9_norm <- filter_na2(atcc_norm, logic = "or", op = "<=",
@@
 
-# proteins with missing values tend to have lower intensity
-# therefore proteins are MNAR, close to detection limit
-# use left censored imputation method
-a9_imp <- impute_QRILC(a9_both)
+# use bpca method from pcaMethods for missing value imputation
+a9_imp <- pcaMethods::pca(a9_both, method = "bpca")
+a9_imp <- pcaMethods::completeObs(a9_imp)
 
@@
 # extract DE results
+# adj.p.val cutoff is 0.01, log2FC cutoff is 1
 a9_res <- get_results(efit = a9_efit,
@@
 marker_longlist <- marker_candidates %>% 
-  mutate(Function = match_id(Name, uniprot, "CGD_gene_name", "Protein_name"),
-         DAY.Y = match_id(Name, yeast_res, "CGD_gene_name", "logFC", 
+  mutate(DAY.Y = match_id(Name, yeast_res, "CGD_gene_name", "logFC", 
                           str_split = FALSE), 
@@
 
-# load vector of protein functions from external R script
-<<fun_list1>>
+# load .csv file with table 1 labels
+marker_labels <- read.csv("components/table1.csv", stringsAsFactors = FALSE) %>% 
+  mutate(Function = case_when(Superscript == "a" ~ paste0(Function, footnote_marker_alphabet(1)), 
+                              Superscript == "b"~ paste0(Function, footnote_marker_alphabet(2)), 
+                              Superscript == "c" ~ paste0(Function, footnote_marker_alphabet(3)), 
+                              TRUE ~ as.character(Function)))
 
@@
 # group proteins according to localisation
-marker_longlist2 <- marker_longlist %>% 
-  mutate(Function = function_desc1, 
-         pack_row = c(4, rep(1, 3), rep(4, 2), 1, 2, rep(1, 6), 3, rep(4, 2),
-                      1, rep(2, 3), 1, rep(4, 2), 1, rep(4, 3), 1, 3, 
-                      rep(1, 3), 4, 1, 2, 1, 2, 4)) %>% 
-  arrange(pack_row) %>% 
-  mutate(VDM = c(rep("", 11), "Y", rep("", 7), "Y", rep("", 7), 
-                 rep("Y", 7), "", rep("Y", 4)))
+marker_longlist2 <- match_id_multi(df = marker_longlist, 
+                                   id = "Name", 
+                                   ref = marker_labels, 
+                                   match = "Name", 
+                                   new = c("Function", "Loc_num", "VDM"), 
+                                   str_split = FALSE) %>% 
+  select(Name, Function, everything()) %>% 
+  arrange(Loc_num)
 
 # fix number of TM domains for CDR1;CDR2
-marker_longlist2[2, 7] <- "12;12"
+marker_longlist2[3, 7] <- "12;12"
 
@@
 # fix SUR7 entries
-marker_longlist2[18, 7] <- "4"
-marker_longlist2[18, 8] <- ""
+marker_longlist2[22, 7] <- "4"
+marker_longlist2[22, 8] <- ""
 
 # Change name of orf19.6741 to Evp1
-marker_longlist2[12, 1] <- paste0("EVP1",
+marker_longlist2[15, 1] <- paste0("EVP1",
                                   footnote_marker_alphabet(4))
@@
 (ref:footnote1) [@skrzypek2017]
-(ref:footnote2) [@almagroarmenteros2017]
+(ref:footnote2) [@theuniprotconsortium2019]
 (ref:footnote3) [@tsirigos2015]
@@
              subcellular localisation as annotated in the Candida Genome 
-             Database (candidagenome.org) (ref:footnote1). 
-             The log\\textsubscript{2} ratio of the abundance (mean MaxQuant 
-             LFQ intensity) of each protein in EVs compared to whole cell 
-             lysate (WCL) for each strain is listed. \`\`ex\" indicates where 
-             a protein was only quantified in the EV fraction and not the WCL 
-             for that strain. The \`\`TM\" column indicates the number of 
-             transmembrane domains for each protein as annotated in UniProtKB. 
-             \`\`SP\" indicates whether a protein is annotated as having a 
-             signal peptide according to UniProtKB. \`\`VDM\" shows whether a 
-             protein has previously been detected in vesicle-depleted culture 
-             media (i.e. the proteins may also be in the soluble secretome) 
+             Database (candidagenome.org) (ref:footnote1) or in the 
+             \\textit{C. albicans} UniProt reference proteome (UP000000559) 
+             (ref:footnote2). The log\\textsubscript{2} ratio of the abundance 
+             (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
+             whole cell lysate (WCL) for each strain is listed. \`\`ex\" 
+             indicates where a protein was only quantified in the EV fraction 
+             and not the WCL for that strain. The \`\`TM\" column indicates the 
+             number of transmembrane domains for each protein as annotated in 
+             UniProt. \`\`SP\" indicates whether a protein is annotated as 
+             having a signal peptide according to UniProt. \`\`VDM\" shows 
+             whether a protein has previously been detected in vesicle-depleted 
+             culture media (i.e. the proteins may also be in the soluble secretome) 
              (ref:table1). Underlined proteins are those identified as the 
@@
              escape = FALSE)  %>% 
-  row_spec(row = c(1, 5, 11, 12, 15:19, 21:25, 35), underline = TRUE) %>% 
+  row_spec(row = c(1,2, 6,7, 13,14,15, 18,19,20,21,22,23, 27, 32, 
+                   38,39,40, 42,43,44,45), underline = TRUE) %>% 
   add_header_above(c(" " = 2, 
@@
   kable_styling(font_size = 8) %>% 
-  pack_rows("Plasma membrane", 1, 19) %>% 
-  pack_rows("Golgi, ER, vacuole", 20, 25) %>% 
-  pack_rows("Mitochondria", 26, 27) %>% 
-  pack_rows("Cell wall, cell surface", 28, 39) %>% 
+  pack_rows("Plasma membrane", 1, 23) %>% 
+  pack_rows("Cell wall, cell surface", 24, 36) %>% 
+  pack_rows("Endoplasmic reticulum", 37, 41) %>% 
+  pack_rows("Endosome, Golgi, transport vesicle", 42, 44) %>% 
+  pack_rows("Vacuole", 45, 45) %>% 
+  pack_rows("Mitochondrion", 46, 47) %>% 
   footnote(alphabet = c("Protein localisation was inferred from sequence 
@@
                         (ref:footnote1).", 
-                        "Protein localisation was predicted using DeepLoc-1.0 
-                        (ref:footnote2).", 
-                        "Presence of transmembrane domains and absense of a 
+                        "Protein localisation was obtained from the GO Cellular
+                        Component annotation in UniProt (ref:footnote2).", 
+                        "Presence of transmembrane domains and absence of a 
                         signal peptide was predicted using TOPCONS2 
@@
   annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 Y')", parse = TRUE) + 
-  annotate("text", x = 3.5, y = 7, label = "bold('88')", 
+  annotate("text", x = 3.5, y = 7, label = "bold('101')", 
            parse = TRUE, colour = unname(ev_pal[2])) + 
-  annotate("text", x = -3.5, y = 7, label = "bold('88')", parse = TRUE, 
+  annotate("text", x = -3.5, y = 7, label = "bold('117')", parse = TRUE, 
            colour = unname(ev_pal[3])) + 
-  annotate("text", x = 0, y = 6, label = "bold('318')", parse = TRUE, 
+  annotate("text", x = 0, y = 6, label = "bold('276')", parse = TRUE, 
            colour = unname(ev_pal[1]))
@@
                      axis_params = c("black", 10)) + 
-  scale_colour_manual(labels = c("EV enriched (86)", "WCL enriched (122)", 
-                                 "Not significant (761)"),
+  scale_colour_manual(labels = c("EV enriched", "WCL enriched", 
+                                 "Not significant"),
                       values = unname(ev_pal[c(2,3,1)])) + 
   annotate("text", x = 8, y = 0.5, label = "bold('ATCC90028')", parse = TRUE) + 
-  annotate("text", x = 3.5, y = 7, label = "bold('86')", 
+  annotate("text", x = 3.5, y = 7, label = "bold('121')", 
            parse = TRUE, colour = unname(ev_pal[2])) + 
-  annotate("text", x = -3.5, y = 7, label = "bold('122')", 
+  annotate("text", x = -3.5, y = 7, label = "bold('176')", 
            parse = TRUE, colour = unname(ev_pal[3])) + 
-  annotate("text", x = 0, y = 6, label = "bold('761')", 
+  annotate("text", x = 0, y = 6, label = "bold('672')", 
            parse = TRUE, colour = unname(ev_pal[1]))
@@
                      axis_params = c("black", 10)) + 
-  scale_colour_manual(labels = c("EV enriched (55)", "WCL enriched (52)", 
-                                 "Not significant (567)"),
+  scale_colour_manual(labels = c("EV enriched", "WCL enriched", 
+                                 "Not significant"),
                       values = unname(ev_pal[c(2,3,1)])) + 
   annotate("text", x = 8, y = 0.5, label = "bold('ATCC10231')", parse = TRUE) + 
-  annotate("text", x = 3.5, y = 7, label = "bold('55')", 
+  annotate("text", x = 3.5, y = 7, label = "bold('101')", 
            parse = TRUE, colour = unname(ev_pal[2])) + 
-  annotate("text", x = -3.5, y = 7, label = "bold('52')", 
+  annotate("text", x = -3.5, y = 7, label = "bold('105')", 
            parse = TRUE, colour = unname(ev_pal[3])) + 
-  annotate("text", x = 0, y = 6, label = "bold('567')", 
+  annotate("text", x = 0, y = 6, label = "bold('468')", 
            parse = TRUE, colour = unname(ev_pal[1]))
@@
                      axis_params = c("black", 10)) + 
-  scale_colour_manual(labels = c("EV enriched (95)", "WCL enriched (79)", 
-                                 "Not significant (484)"), 
+  scale_colour_manual(labels = c("EV enriched", "WCL enriched", 
+                                 "Not significant"), 
                       values = unname(ev_pal[c(2,1,3)]), 
@@
   annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 B')", parse = TRUE) + 
-  annotate("text", x = 3.5, y = 7, label = "bold('95')", 
+  annotate("text", x = 3.5, y = 7, label = "bold('105')", 
            parse = TRUE, colour = unname(ev_pal[2])) + 
-  annotate("text", x = -3.5, y = 7, label = "bold('79')", 
+  annotate("text", x = -3.5, y = 7, label = "bold('100')", 
            parse = TRUE, colour = unname(ev_pal[3])) + 
-  annotate("text", x = 0, y = 6, label = "bold('484')", 
+  annotate("text", x = 0, y = 6, label = "bold('453')", 
            parse = TRUE, colour = unname(ev_pal[1]))
@@
            enriched proteins were identified using a Benjamini-Hochberg 
-           adjusted p-value cut off of 0.01. Counts of significant and 
+           adjusted p-value cut off of 0.01 and log\\textsubscript{2}(FC) cutoff 
+           of 1. Counts of significant and 
            non-significant proteins are indicated on each graph. Proteins with 
@@
                 shape_size = 3, dim.plot = c(1,2)) + 
-  scale_x_continuous(limits = c(-1.5, 2.5), 
+  scale_x_continuous(limits = c(-1.5, 2), 
                      expand = c(0,0)) + 
-  scale_y_continuous(limits = c(-2.5, 1.5), 
+  scale_y_continuous(limits = c(-2, 1.5), 
                      expand = c(0,0)) + 
@@
                 shape_size = 3, dim.plot = c(3,2)) + 
-  scale_x_continuous(limits = c(-1.5, 2.5), 
+  scale_x_continuous(limits = c(-1.5, 2), 
                      expand = c(0,0)) + 
-  scale_y_continuous(limits = c(-2.5, 1.5), 
+  scale_y_continuous(limits = c(-2, 1.5), 
                      expand = c(0,0)) + 
@@
            \\@ref(fig:figure2) were compared to select those which were common 
-           to all 4 datasets. 39 proteins were identified as potential positive 
-           EV protein markers and 40 proteins as potential negative EV protein 
+           to all 4 datasets. 47 proteins were identified as potential positive 
+           EV protein markers and 62 proteins as potential negative EV protein 
            markers. The data tables underlying Figure 
            \\@ref(fig:figure6) are provided in supplemental File S4. Details of 
-           the 39 positive EV protein marker candidates and 40 negative 
+           the 47 positive EV protein marker candidates and 62 negative 
            candidates can be found in Table \\@ref(tab:table1) and supplemental 
@@
 ```{r figure7, fig.cap=f7_cap, fig.width=3.5, fig.height=2.8}
-f7_cap <- "\\textbf{Eighteen best potential \\textit{C. albicans} positive EV 
+f7_cap <- "\\textbf{Twenty-two best potential \\textit{C. albicans} positive EV 
            protein markers.} These proteins are those underlined in Table 

### 2019-07-15 inst/manuscript/components/protein_funs.R

@@ -1,124 +1,0 @@
-# Function descriptions for Table 1 and Table S2
-
-
-## @knitr fun_list1
-function_desc1 <- c("1,3-beta-glucanosyltransferase",
-                    "Rho family GTPase",
-                    "Multidrug transporter of ABC superfamily",
-                    "Major chitin synthase of yeast and hyphae",
-                    "GPI-anchored cell wall transglycosylase",
-                    "GPI-anchored cell wall protein",
-                    paste0("Predicted P-type ATPase sodium pump",
-                           footnote_marker_alphabet(1)),
-                    "ER oxidoreductin",
-                    "Multicopper feroxidase",
-                    "High-affinity S-adenosylmethionine permease",
-                    "1,3-beta-glucan synthase",
-                    "High-affinity MFS glucose transporter",
-                    "Putative high-affinity MFS glucose transporter",
-                    "Putative MFS glucose transporter",
-                    paste0("Putative mitochondrial phosphate transporter",
-                           footnote_marker_alphabet(1)),
-                    "Cell surface mannoprotein",
-                    "Mucin family adhesin-like protein",
-                    "Sphingolipid C9-methyltransferase",
-                    paste0("\\textit{S. cerevisiae} ortholog is Pom33, transmembrane nucleoporin",
-                           footnote_marker_alphabet(2)),
-                    paste0("\\textit{S. cerevisiae} ortholog is Yop1, reticulon-interacting protein",
-                           footnote_marker_alphabet(2)),
-                    paste0("\\textit{S. cerevisiae} ortholog is Rtn1, reticulon protein",
-                           footnote_marker_alphabet(2)),
-                    paste0("\\textit{S. cerevisiae} ortholog is Pun1, plasma membrane protein",
-                           footnote_marker_alphabet(2)),
-                    "1,3-beta-glucanosyltransferase",
-                    "GPI-anchored cell surface protein of unknown function",
-                    "Putative ion transporter",
-                    "Cell surface glycosidase",
-                    "Glycosidase",
-                    "Phospholipase B",
-                    "Plasma membrane ATPase",
-                    paste0("Mitochondrial outer membrane porin",
-                           footnote_marker_alphabet(1)),
-                    "G-protein of RAC subfamily",
-                    "Rho family GTPase",
-                    "Rho family GTPase",
-                    "Secreted aspartyl protease",
-                    paste0("Protein required for normal cell wall, plasma membrane",
[…]

### 2019-07-15 inst/manuscript/manuscript.Rmd
Update imputation method in supplement

@@
              subcellular localisation as annotated in the Candida Genome 
-             Database (candidagenome.org) (ref:footnote1) or in the 
-             \\textit{C. albicans} UniProt reference proteome (UP000000559) 
-             (ref:footnote2). The log\\textsubscript{2} ratio of the abundance 
+             Database (candidagenome.org) (ref:footnote1) unless otherwise 
+             indicated. The log\\textsubscript{2} ratio of the abundance 
              (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
@@
              escape = FALSE)  %>% 
-  row_spec(row = c(1,2, 6,7, 13,14,15, 18,19,20,21,22,23, 27, 32, 
-                   38,39,40, 42,43,44,45), underline = TRUE) %>% 
+  row_spec(row = c(1,2, 6,7, 13:15, 18:23, 27, 32, 38:40, 42:45), 
+           underline = TRUE) %>% 
   add_header_above(c(" " = 2, 
@@
   footnote(alphabet = c("Protein localisation was inferred from sequence 
-                         similarity with \\\\textit{S. cerevisiae} ortholog as 
+                         similarity with \\\\textit{S. cerevisiae} homolog as 
                          annotated in the Candida Genome Database 
@@
                         "Protein localisation was obtained from the GO Cellular
-                        Component annotation in UniProt (ref:footnote2).", 
+                        Component annotation in the \\\\textit{C. albicans} 
+                        UniProt reference proteome UP000000559 (ref:footnote2).", 
                         "Presence of transmembrane domains and absence of a 

### 2019-07-15 inst/manuscript/manuscript_supplement.Rmd
Update imputation method in supplement

@@
    **Supplement to: Protein markers for *Candida albicans* EVs include
-   claudin-like Sur7 family proteins and Rho GTPases**
+   claudin-like Sur7 family proteins and GTPases**
 author: | 
@@
 set.seed(1)
-
-# reference external R script with protein function lists
-knitr::read_chunk('components/protein_funs.R')
 ```
@@
 # create design matrix
-b_samp <- data.frame(T = (rep(c("EV", "WCL"), each = 5)))
+b_samp <- data.frame(T = rep(c("EV", "WCL"), each = 5))
 
@@
 wcl_longlist <- wcl_candidates %>% 
-  mutate(Function = match_id(Name, uniprot, "CGD_gene_name", 
-                             "Protein_name", concat = TRUE, str_split = FALSE),
-         DAY.Y = match_id(Name, yeast_res, "CGD_gene_name", 
+  mutate(DAY.Y = match_id(Name, yeast_res, "CGD_gene_name", 
                           "logFC", concat = TRUE, str_split = FALSE), 
@@
 
-# load vector of protein functions from external R script
-<<fun_list2>>
+# load .csv file with table S2 labels
+wcl_labels <- read.csv("components/tableS2.csv", stringsAsFactors = FALSE) %>% 
+  mutate(Function = case_when(Superscript == "a" ~ paste0(Function, 
+                                                          footnote_marker_alphabet(1)), 
+                              Superscript == "b" ~ paste0(Function, 
+                                                          footnote_marker_alphabet(2)),
+                              Superscript == "c" ~ paste0(Function, 
+                                                          footnote_marker_alphabet(3)), 
+                              TRUE ~ as.character(Function)), 
+         VDM = c(rep("", 62)))
 
-# add proper protein functions to table 1
+# add proper protein functions to table S2
 # also add vesicle depleted supernatant info and 
 # group proteins according to localisation
-wcl_longlist2 <- wcl_longlist %>% 
-  mutate(Function = function_desc2, 
-         VDM = c(rep("", 40)), 
-         pack_row = c(rep(4, 2), 3, rep(2, 2), 7, rep(1, 2), rep(7, 2), 1, 
-                      rep(2, 4), 7, 3, 2, 5, 1, 
-                      2, 6, 2, 1, 7, rep(1, 2), 2, 1, 5, 1, 
-                      1, 6, 2, 1, rep(8, 2), rep(1, 3))) %>% 
-  arrange(pack_row)
+wcl_longlist2 <- match_id_multi(df = wcl_longlist, 
+                                id = "Name", 
+                                ref = wcl_labels, 
+                                match = "Name", 
+                                new = c("Function", "Loc_num", "VDM"), 
+                                str_split = FALSE) %>% 
+  select(Name, Function, everything()) %>% 
+  arrange(Loc_num)
 ```
@@
 
-(ref:footnote2) [@almagroarmenteros2017]
-
-(ref:footnote3) [@savojardo2018]
+(ref:footnote2) [@theuniprotconsortium2019]
 
@@
               \\textit{C. albicans} strains examined in this study. Proteins 
-              are grouped according to their subcellular localisation as 
-              annotated in the Candida Genome Database (candidagenome.org) 
-              (ref:footnote1). The log\\textsubscript{2} ratio of the abundance 
+              are grouped according to their 
+              subcellular localisation as annotated in the Candida Genome 
+              Database (candidagenome.org) (ref:footnote1) unless otherwise 
+              indicated. The log\\textsubscript{2} ratio of the abundance 
               (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
@@
 # draw table S2
-knitr::kable(wcl_longlist2[, -10], 
+knitr::kable(wcl_longlist2[, -9], 
              caption = tabs2_cap, 
@@
              escape = FALSE) %>% 
-  row_spec(row = c(20, 25, 29, 36), underline = TRUE) %>% 
+  row_spec(row = c(26, 32, 36:38, 42, 58), underline = TRUE) %>% 
   add_header_above(c(" " = 2, 
@@
                 latex_options = c("HOLD_position")) %>% 
-  pack_rows("Cytoplasm", 1, 14) %>% 
-  pack_rows("Mitochondria", 15, 25) %>% 
-  pack_rows("Nucleus", 26, 27) %>% 
-  pack_rows("Vacuole", 28, 29) %>% 
-  pack_rows("Peroxisome", 30, 31) %>% 
-  pack_rows("Proteasome", 32, 33) %>% 
-  pack_rows("Cell wall, cell surface, fungal biofilm matrix", 34, 38) %>% 
-  pack_rows("Ribosome", 39, 40) %>% 
+  pack_rows("Cytoplasm", 1, 13) %>% 
+  pack_rows("Cytosol and mitochondria", 14, 16) %>% 
+  pack_rows("Mitochondria", 17, 32) %>% 
+  pack_rows("Nucleus", 33, 34) %>% 
+  pack_rows("Vacuole", 35, 38) %>% 
+  pack_rows("Cell wall, cell surface, fungal biofilm matrix", 39, 50) %>% 
+  pack_rows("Proteasome", 51, 54) %>% 
+  pack_rows("Cytoplasmic stress granule", 55, 56) %>% 
+  pack_rows("Peroxisome", 57, 57) %>% 
+  pack_rows("Actin cortical patch", 58, 58) %>% 
+  pack_rows("Unknown", 59, 62) %>% 
   footnote(alphabet = c("Protein localisation was inferred from sequence 
-                         similarity with \\\\textit{S. cerevisiae} ortholog as 
+                         similarity with \\\\textit{S. cerevisiae} homolog as 
                          annotated in the Candida Genome Database 
                          (ref:footnote1)", 
-                        "Protein localisation was predicted using DeepLoc-1.0 
-                         (ref:footnote2)", 
-                        "Protein localisation was predicted using BUSCA 
-                         (ref:footnote3)"), 
+                        "Protein localisation was obtained from the GO Cellular
+                        Component annotation in the \\\\textit{C. albicans} 
+                        UniProt reference proteome UP000000559 (ref:footnote2).", 
+                        "Protein and has no Cellular Component annotation in 
+                         the Candida Genome Database or UniProt reference 
+                        proteome."), 
            escape = FALSE, 

### 2019-07-16 inst/manuscript/manuscript.Rmd
Add more GO terms to Fig 3
Also increase heatmap splits from 5 to 7

@@
 # GO term bar plots
-f3_y <- plot_go_bar(f3_y_go_table, c(1:4, 49,52:53,55, 77,79:81), f3_pal) + 
-  annotate("text", x = 12, y = 65, label = "bold('DAY286 Y')", parse = TRUE) + 
+f3_y <- plot_go_bar(f3_y_go_table, c(1:4,6, 23,26:28,30, 42,44:46), f3_pal) + 
+  annotate("text", x = 14, y = 65, label = "bold('DAY286 Y')", parse = TRUE) + 
   labs(fill = "GO domain") + 
@@
 
-f3_b <- plot_go_bar(f3_b_go_table, c(1:4, 69,71:73, 96:97, 100, 102), f3_pal) + 
-  annotate("text", x = 12, y = 60, label = "bold('DAY286 B')", parse = TRUE)
-
-f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:3,6, 27,29,33,40, 46,49,51:52), f3_pal) + 
-  annotate("text", x = 12, y = 70, label = "bold('ATCC90028')", parse = TRUE)
-
-f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4, 62,65:66,76, 86:89), f3_pal) + 
-  annotate("text", x = 12, y = 70, label = "bold('ATCC10231')", parse = TRUE)
-```
-
-```{r figure3, fig.cap=f3_cap, fig.width=7.2, fig.height=5}
-# draw figure 4
+f3_b <- plot_go_bar(f3_b_go_table, c(1:4,6, 54:57,67, 73:75,77), f3_pal) + 
+  annotate("text", x = 14, y = 60, label = "bold('DAY286 B')", parse = TRUE)
+
+f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:5, 12,14,17,18,24, 26:29), f3_pal) + 
+  annotate("text", x = 14, y = 70, label = "bold('ATCC90028')", parse = TRUE)
+
+f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4,6, 31,33:35,45, 49:52), f3_pal) + 
+  annotate("text", x = 14, y = 70, label = "bold('ATCC10231')", parse = TRUE)
+```
+
+```{r figure3, fig.cap=f3_cap, fig.width=7.2, fig.height=6}
+# draw figure 3
 ggarrange(f3_y, f3_a9, 
@@
 f5_htmp <- plot_heatmap(mt = f5_table_filt, 
-                        plot = FALSE,
+                        plot = TRUE,
                         df = FALSE, 
@@
                         split_type = "cutree", 
-                        k = 5, 
+                        k = 7, 
                         cluster_split = FALSE, 
-                        split_order = c(2, 5, 1, 4, 3), 
+                        split_order = c(4, 1, 6, 2, 3, 5, 7), 
                         colour_lims = c(-4, 4),
@@
                         column_names_rot = 45, 
+                        row_title = c("1", "2", "3", "4", "5", "6", "7"), 
                         row_title_fontsize = 6, 
                         row_title_rot = 0, 
-                        row_title = c("1", "2", "3", "4", "5"), 
                         heatmap_legend_param = f5_params)
@@
                             split_type = "cutree", 
-                            k = 5, 
+                            k = 7, 
                             cluster_split = FALSE) %>% 
   mutate(cluster = recode(cluster, 
-                          "1" = 4, "2" = 1, "3" = 5, "4" = 2, "5" = 3)) %>% 
+                          "4" = 1, "1" = 2, "6" = 3, "2" = 4, 
+                          "3" = 5, "5" = 6, "7" = 7)) %>% 
   arrange(cluster)

### 2019-07-16 inst/manuscript/manuscript.Rmd
Update Figure 5

@@
 f5_htmp <- plot_heatmap(mt = f5_table_filt, 
-                        plot = TRUE,
+                        plot = FALSE,
                         df = FALSE, 
@@
 # extract identifiers from each cluster
-f5_clust1 <- f5_clusters %>% 
-  filter(cluster == 1) %>% 
+f5_clust1_2 <- f5_clusters %>% 
+  filter(cluster == 1 | cluster == 2) %>% 
   mutate(id = gsub("PEP1", "CaO19.3767", id)) %>% 
@@
 
-f5_clust2 <- f5_clusters %>% 
-  filter(cluster == 2) %>% 
-  pull(id)
-
 f5_clust3 <- f5_clusters %>% 
@@
   filter(cluster == 5) %>% 
+  mutate(id = gsub("RPS1", "CaO19.3002", id)) %>% 
+  pull(id) %>% 
+  stringr::str_extract_all(., "[^;]+") %>% 
+  unlist() %>% 
+  unique()
+
+f5_clust6 <- f5_clusters %>% 
+  filter(cluster == 6) %>% 
   mutate(id = gsub("ALA1", "CaO19.5746", id), 
          id = gsub("MDH1", "CaO19.7481", id), 
-         id = gsub("RPS1", "CaO19.3002", id), 
          id = gsub("TSA1", "CaO19.7417", id)) %>% 
@@
 
+f5_clust7 <- f5_clusters %>% 
+  filter(cluster == 7) %>% 
+  pull(id)
+
 # cluster 6 is proteins that could not be clustered
 # because all 4 log2FCs = NA
-f5_clust6 <- sort(rownames(f5_table_excl))
+f5_clust8 <- sort(rownames(f5_table_excl))
 
 # import FungiFun2 results
-f5_go1 <- process_fungifun("figures/f5_GO_clust1.csv") %>% 
+# issue with PEP1, ambiguous ID in FungiFun, used CaO19.3767 as identifier
+f5_go1_2 <- process_fungifun("figures/f5_GO_clust1_2.csv") %>% 
   mutate(Prot.found = gsub("CaO19.3767", "PEP1", Prot.found))
-
-# issue with PEP1, ambiguous ID in FungiFun, used CaO19.3767 as identifier
-f5_go2 <- process_fungifun("figures/f5_GO_clust2.csv")
 
@@
 f5_go5 <- process_fungifun("figures/f5_GO_clust5.csv") %>% 
+  mutate(Prot.found = gsub("CaO19.3002", "RPS1", Prot.found))
+
+f5_go6 <- process_fungifun("figures/f5_GO_clust6.csv") %>% 
   mutate(Prot.found = gsub("CaO19.5746", "ALA1", Prot.found), 
          Prot.found = gsub("CaO19.7481", "MDH1", Prot.found), 
-         Prot.found = gsub("CaO19.3002", "RPS1", Prot.found), 
          Prot.found = gsub("CaO19.7417", "TSA1", Prot.found))
 
-f5_go6 <- process_fungifun("figures/f5_GO_clust6.csv")
+f5_go7 <- process_fungifun("figures/f5_GO_clust7.csv")
+
+f5_go8 <- process_fungifun("figures/f5_GO_clust8.csv")
 ```
@@
            R package \\textit{cluster} [@maechler2019]. Proteins which were 
-           exclusive to EVs from all four strains could not be clustered and 
+           exclusive to EVs from all four strains and therefore had no valid 
+           log\\textsubscript{2}(FC) values
            were seperated prior to clustering, in the group designated 
-           \`\`cluster 6\". Functional enrichment analyses were performed on 
+           \`\`cluster 8\". Functional enrichment analyses were performed on 
            the heatmap protein clusters using the online tool FungiFun2 
            [@priebe2015]. A selection of significantly enriched GO terms are 
-           presented in the table inset. Lists of the proteins identified in 
-           each cluster are shown and are also available in supplemental 
-           File S5. \\textsuperscript{a} indicates where all proteins from 
-           each protein group in the cluster were used for the GO analysis."
+           presented in the table inset. Full lists of enriched GO terms are 
+           available in supplemental File S3. Full lists of the proteins 
+           in each cluster are available in supplemental File S5.
 ```

### 2019-07-16 inst/manuscript/manuscript.Rmd
Update Figure 7

@@
            [@priebe2015]. A selection of significantly enriched GO terms are 
-           presented in the table inset. Full lists of enriched GO terms are 
-           available in supplemental File S3. Full lists of the proteins 
-           in each cluster are available in supplemental File S5.
+           presented in the table inset. Full lists of enriched GO terms and 
+           proteins in each cluster are available in supplemental Files S3 and 
+           S5 respectively."
 ```
@@
 
-```{r figure7, fig.cap=f7_cap, fig.width=3.5, fig.height=2.8}
+```{r figure7, fig.cap=f7_cap, fig.width=4, fig.height=3.6}
 f7_cap <- "\\textbf{Twenty-two best potential \\textit{C. albicans} positive EV 

### 2019-07-16 inst/manuscript/manuscript.Rmd
Regenerate supplement files

@@
 
-# cluster 5 has too many proteins to fit in table
-# but GO enrichment still possible
 f5_clust5 <- f5_clusters %>% 
@@
 
-# cluster 6 is proteins that could not be clustered
+# cluster 8 is proteins that could not be clustered
 # because all 4 log2FCs = NA
@@
 
+# issue with CHS3, ambiguous ID in FungiFun, used CaO19.4937 as identifier
 f5_go3 <- process_fungifun("figures/f5_GO_clust3.csv") %>% 
@@
 
-# issue with CHS3, ambiguous ID in FungiFun, used CaO19.4937 as identifier
 f5_go4 <- process_fungifun("figures/f5_GO_clust4.csv")
 
-# issue with ALA1, MDH1, used CaO19.5746 and CaO19.7481 as identifiers
+# issue with RPS1, ambiguous ID in FungiFun, used CaO19.3002 as identifier
 f5_go5 <- process_fungifun("figures/f5_GO_clust5.csv") %>% 
@@
 
+# issue with ALA1, MDH1, TSA1
+# used CaO19.5746, CaO19.7481, CaO19.7417 as identifiers
 f5_go6 <- process_fungifun("figures/f5_GO_clust6.csv") %>% 

### 2019-07-17 inst/manuscript/manuscript.Rmd
Adjust Figure 3 and 5

@@
 
-```{r figure1Data, include=FALSE, cache=TRUE}
+```{r figure1Data, include=FALSE}
 # construct data.frame with nta experiment info
@@
 
-f3_b <- plot_go_bar(f3_b_go_table, c(1:4,6, 54:57,67, 73:75,77), f3_pal) + 
+f3_b <- plot_go_bar(f3_b_go_table, c(1:4,6, 54:57,67, 73,75,77,87), f3_pal) + 
   annotate("text", x = 14, y = 60, label = "bold('DAY286 B')", parse = TRUE)

### 2019-07-17 inst/manuscript/manuscript.Rmd
Remove text from manscript.Rmd

@@
    **Protein markers for *Candida albicans* EVs include claudin-like Sur7 
-   family proteins and Rho GTPases**
+   family proteins and GTPases**
 author: | 
@@
 mainfont: Times New Roman
-linestretch: 2
+linestretch: 1.5
 header-includes:
@@
   - \usepackage{fancyhdr}
-  - \usepackage{lipsum}
   - \pagestyle{fancy}
-  - \fancyhead[L]{Defining \textit{Candida albicans} EV protein markers}
   - \setlength{\headheight}{15pt}
@@
 
-**Running title:** Defining _Candida albicans_ EV protein markers
-
-\newpage
-
 ```{r setup, include=FALSE}
@@
 # normalise LFQ intensities
-yeast_norm2 <- normalizeCyclicLoess(yeast_filt2)
+yeast_norm2 <- limma::normalizeCyclicLoess(yeast_filt2)
 
@@
 # normalise LFQ intensities
-biofilm_norm <- normalizeCyclicLoess(biofilm_filt)
+biofilm_norm <- limma::normalizeCyclicLoess(biofilm_filt)
 
@@
 # normalise LFQ intensities
-atcc_norm <- normalizeCyclicLoess(atcc_filt)
+atcc_norm <- limma::normalizeCyclicLoess(atcc_filt)
 ```
@@
 ```
-
-# Abbreviations
-
-A1 - ATCC10231
-
-A9 - ATCC90028
-
-DAY B - DAY286 biofilm
-
-DAY Y - DAY286 yeast
-
-EV - extracellular vesicle
-
-Evp1 - extracellular vesicle protein 1 (orf19.6741)
-
-Log<sub>2</sub>(FC) - log<sub>2</sub> fold change
-
-MCC - membrane compartment of Can1
-
-MDS - multidimensional scaling
-
-MISEV - minimal information for studies of EVs
-
-sEVs - small EVs
-
-SP - signal peptide
-
-TEMs - tetraspanin enriched microdomains
-
-TM - transmembrane domain
-
-VDM - vesicle depleted medium
-
-WCL - whole cell lysate
-
-\newpage
-
-# Abstract
-
-\newpage
-
-# Introduction
-
-Fungal infections are ubiquitous and are estimated to affect over 20% of the 
-world’s population [@havlickova2008]. These infections range from 
-non-life-threatening mycoses of the skin and nails, to deadly systemic 
-infections. They represent a significant burden to healthcare systems, with the 
-direct medical cost of fungal disease in the United States in 2017 estimated to 
-be \$7.2 billion [@benedict2018]. The fungi responsible for most fungal 
-infections worldwide are the various species of _Candida_ [@pfaller2007]. 
-_Candida_ is primarily associated with relatively harmless superficial infections 
-[@brown2012], but infections of the bloodstream or internal organs are 
-associated with mortality rates as high as 75% [@guinea2014; @kullberg2015]. 
-Over 12,000 people were hospitalised for invasive candidiasis in the US in 2017 
-alone, at a cost of almost \$1.2 billion [@benedict2018]. The species 
-responsible for the majority of _Candida_ infections is _Candida albicans_ 
-[@guinea2014]. _C. albicans_ infections are most often treated with two classes 
-of antifungals, the azoles which target biosynthesis of the fungal-specific 
-sterol ergosterol, and the echinocandins, which target biosynthesis of the major
-cell wall polysaccharide 1,3-β-glucan [@pappas2016]. Resistance to these and 
-other antifungals has begun to emerge 
-[@fisher2018; @perlin2015; @perlin2017; @whaley2017] making the development of 
-new antifungals with novel mechanisms of action paramount. Understanding the 
-interface between the host and pathogen will help to identify new targets for 
-controlling _C. albicans_ infections.
-
-Extracellular vesicles (EVs) are key factors in the progression of many diseases 
-ranging from cancer [@xu2018] to neurodegenerative diseases [@quek2017] and 
-bacterial infections [@pathirana2016]. EVs are defined as “particles naturally 
-released from the cell that are delimited by a lipid bilayer and cannot 
-replicate” [@thery2018]. Packaging of cargo into EVs is a method for the 
-coordinated release of biological molecules via a non-classic method of 
-secretion.  This facilitates intercellular communication both within an 
-organism [@maas2017] and between organisms [@schorey2015].
-
-Recently, EVs have 
-been proposed to function in the pathogenesis of fungal disease, particularly 
-in yeast infections including those from the genera _Cryptococcus_ 
-[@bielska2018; @oliveira2010b; @rodrigues2008], _Paracoccidioides_ 
-[@dasilva2015a; @vallejo2011], and _Candida_ 
-[@joffe2016; @vargas2015; @wolf2015]. The cargo of fungal EVs comprises 
-proteins [@bleackley2019], nucleic acids [@dasilva2015], lipids 
-[@oliveira2009; @rodrigues2007; @vargas2015; @wolf2015] and carbohydrates 
-[@dasilva2015a; @rodrigues2007]. Fungal EVs activate innate immune cells in 
-vitro [@dasilva2016; @oliveira2010b; @vargas2015; @wolf2015] and are responsible 
-for the hypervirulence of a _Cryptococcus gattii_ strain that caused disease in 
-immunocompetent individuals [@bielska2018]. Given the potential roles for EVs in 
-host-pathogen interactions, there is significant motivation to better understand 
-the biology of fungal EVs.
-
-_C. albicans_ EVs are typical of fungal EVs. They contain proteins, lipids, 
-nucleic acids and carbohydrates 
-[@dasilva2015; @gil-bona2015b; @vargas2015; @wolf2015; @zarnowski2018]. 
-Activation of murine macrophages and dendritic cells by EVs from _C. albicans_ 
-indicates a potential role for EVs in modulating the innate immune response to 
-the fungus [@vargas2015; @wolf2015]. Formation of biofilms is a critical 
-component of _C. albicans_ pathogenesis [@nobile2015] and the biofilm matrix 
-provides a protective layer for the fungus against antifungal drugs [@taff2012]. 
-The cargo of EVs produced by _C. albicans_ biofilms includes key proteins and 
-carbohydrates for biofilm biogenesis, making EVs crucial contributors to the 
-establishment of biofilms [@zarnowski2018]. Furthermore, “add-back” of EVs from 
-wildtype biofilms restored the loss of azole resistance in biofilms formed by 
-strains with deletions in genes encoding important enzymes for matrix 
-generation [@zarnowski2018]. That is, EVs also function in antifungal drug 
-resistance.
-
-The tools and techniques for the study of fungal EVs have been adapted from 
-those established for mammalian systems, where EVs are most intensively 
-studied. Many of the cutting-edge experimental techniques for isolation, 
-tracking, and analysis of mammalian EVs are dependent on protein markers 
-[@lotvall2014]. They include identifying fractions containing EVs after density 
-gradient centrifugation [@greening2015] or size exclusion chromatography 
-[@gamez-valero2016], purification of EVs via immunoaffinity capture [@oksvold2015], 
-and imaging of EV release and uptake [@suetsugu2013]. Unfortunately, proteomic 
-analyses of fungal EVs have revealed that the markers that have been so useful 
-for the isolation and study of mammalian EVs are not present in fungal EVs 
-[@bleackley2019]. Thus, there are differences in the protein cargo and possibly 
-the biogenesis of EVs from fungi and mammalian cells, and _de novo_ 
-identification of fungal EV markers is essential. Inconsistencies between 
-published data sets on the protein content of fungal EVs [@bleackley2019] means 
-that a robust proteomic analysis of EVs from a particular species is required 
-to provide an adequate data set for EV marker identification. In this study, we 
-have addressed this problem by performing in-depth proteomic analyses on 
-multiple _C. albicans_ strains to define a set of broadly applicable 
-_C. albicans_ EV markers.
-
-We employed label-free quantitative proteomics to generate EV and whole cell 
-lysate (WCL) proteomes for a selection of different _C. albicans_ strains and 
-morphologies; DAY286 yeast, DAY286 biofilm, ATCC90028 yeast, and ATCC10231 
-yeast. By comparing the EV versus WCL data across all four strains we 
-identified 39 putative EV markers which are enriched in _C. albicans_ EVs 
-regardless of source, cell strain, or morphology. These candidate protein 
-markers include GTPases, enzymes crucial for cell wall synthesis, and 
-plasma membrane proteins resembling mammalian tetraspanins or claudins. 
-The “minimal information for studies of EVs” (MISEV) 2018 position statement 
-indicates that, in addition to demonstrating the enrichment of EV marker 
-proteins in EV preparations, a deficiency of non-EV proteins should also be 
-shown [@thery2018]. With this in mind, we identified 40 proteins that were 
-depleted in _C. albicans_ EVs compared to the WCL from the four strains. 
-Validation of these putative EV markers in vitro will allow future _C. albicans_ 
-EV research to align better with the recommendations set out in MISEV2018. 
-Furthermore, robust _C. albicans_ EV markers will allow adaptation of mammalian 
-EV analysis techniques for use in the study of EVs in _C. albicans_ pathogenesis 
-and will provide potential new targets for the development of novel antifungals.
-
-# Experimental procedures
-
-## _C. albicans_ strains and maintenance
-
-_C. albicans_ strains used in this study were DAY286 [@davis2002], ATCC90028, 
-and ATCC10231. All strains were maintained on YPD Agar plates (1% yeast extract, 
-2% peptone, 2% dextrose, 2% agar). Liquid starter cultures were grown overnight 
-in YPD medium (1% yeast extract, 2% peptone, 2% dextrose) at 30°C and 300 rpm.
-
-## Yeast culture conditions
-
-For isolation of EVs from yeast form _C. albicans_ (DAY286, ATCC90028, 
-ATCC10231), YPD starter cultures were used to inoculate 150 or 300 mL YPD at an 
-OD~600~ = 0.2 in a baffled flask. Cultures were incubated at 30°C overnight 
-(approximately 20h). The culture OD~600~ was measured immediately prior to EV 
-isolation.
-
-## Biofilm culture conditions
-
-Biofilms (DAY286) were generated based on the method described in [@ramage2002] 
-with modifications. Briefly, 500 mL pre-warmed ½ strength RPMI (250 mL RPMI 
-1640 (Sigma), 0.165 M MOPS (Sigma) and 250 mL 3.6% dextrose) was inoculated 
-using a liquid starter culture to 1.0 x 10^6^ cells/mL. Five 25 x 25 
-cm non-treated bioassay dishes (Thermo Fisher Scientific) were each filled with 
-100 mL of inoculated ½ RPMI and incubated statically for 4 h at 37°C to allow 
-for adhesion of cells to the dish. Following cell adhesion, the culture medium 
-and any non-adherent cells was decanted and replaced with 200 mL pre-warmed 
-full strength RPMI. Biofilms were formed by incubating the dishes for 54 h at 
-37°C with agitation at 28 rpm in an Incu-Shaker Mini (Benchmark Scientific).
-
-## EV isolation
-
-EVs were isolated according to the method described in [@rodrigues2007] with 
-minor modifications. In brief, yeast cells or biofilm fragments were separated 
-from the culture supernatants by centrifugation at 4,000 x g for 15 min 
-(75003607 rotor, Thermo Scientific), then 15,000 x g for 30 min 
-(JLA 16.250 rotor, Beckman Coulter). Supernatants were 0.45 μm (Millipore) 
-filtered then centrifuged twice at 100,000 x g for 1 h (45Ti rotor, 
-Beckman Coulter) to pellet EVs which were resuspended in phosphate buffered 
-saline (137 mM NaCl, 2.7 mM KCl, 10 mM Na~2~HPO~4~, 1.8 mM KH~2~PO~4~) (PBS). 
-An aliquot of yeast cells (250 µL) was reserved for preparation of yeast whole 
-cell lysate. Similarly, 250 μL of biofilm scrapings were resuspended in PBS for 
-preparation of biofilm lysate.
-
-## Preparation of whole cell lysate and protein quantification
-
-Samples were washed three times with PBS prior to the addition of approximately 
-400 µL of acid washed glass beads (Sigma). Cells were lysed using a TissueLyser 
-(Qiagen) at 30 bps for 3 x 1 min bursts with 1 min incubations on ice between 
-bursts. Debris and beads were pelleted by centrifugation for 5 min at 
-23,000 x g at 4 °C. The supernatant was retained as the respective lysate 
-sample. Protein concentration of EVs and whole cell lysates (WCL) was 
-determined using a Qubit^TM^ 4 fluorimeter (Life Technologies) and the 
-Qubit^TM^ protein assay kit according to the manufacturer’s instructions.
-
-## Nanoparticle tracking analysis
-
-The particle size and concentration of EV samples was determined using a 
-NanoSight NS300 equipped with a 405 nm (blue) laser (Malvern Instruments).  
-Immediately prior to injection, EVs were diluted between 1:250 and 1:6000 
-in 0.22 μm (Millipore) filtered PBS to bring the particle concentration within 
-the manufacturer’s recommended range (10^7^ – 10^9^ particles/mL). NTA software 
-version 3.2 was used to record data in 60 s reads in triplicate. Instrument 
-settings included: a syringe infusion rate of 70, temperature held at 25°C, 
-a camera level of 11, and a detection threshold of 6. The particle 
-concentrations and particle size parameters were recorded. Dilution 
-factor correction and averaging of data across biological replicates was 
-performed using the R package _tidyNano_ [@nguyen2019].
-
-## Transmission electron microscopy
-
-Carbon-coated 400-mesh copper grids (ProSciTech) were glow discharged for 1 
-min in a K950X turbo evaporator coupled to a K350 glow discharge unit 
-(Quorum Technologies Ltd). EVs (5 µL) were deposited onto the grid and 
-incubated for 1 min. Grids were then washed once with ultrapure water and 
-negatively stained three times with 2% (v/v) uranyl acetate (Agar Scientific). 
-Excess solution was blotted off and the grids were dried overnight. A JEM 2100 
-electron microscope (JEOL Ltd) operated at 200 kV was used for imaging.
-
-## Experimental design and statistical rationale
-
-A total of 14 EV and WCL samples from four different _C. albicans_ strains were 
-used for proteomics and NTA analyses; DAY286 yeast (n = 3), ATCC90028 yeast 
-(n = 3), ATCC10231 yeast (n = 3), and DAY286 biofilm (n = 5). The EV and WCL 
-samples from an individual biological replicate were paired as they were derived 
-from cells in the same culture or biofilm. Biofilm EVs and WCLs were obtained 
-from 5 independent biofilms on different days. Yeast EVs and WCLs were obtained 
-from 3 independent yeast cultures in parallel on different days for each strain. 
-Preparation of EV and WCL proteomics samples and MS data acquisition was 
-performed in three separate batches; DAY286 yeast, DAY286 biofilm, and then 
-both ATCC strains. Proteomics samples were randomised prior to injection and 
-each biological replicate was injected twice. The raw data from both injections 
-was combined into one sample during protein identification and quantification. 
-All proteomics statistical and data analyses were performed using R version 
-3.6.0 [@rcoreteam2018], Statistical tests, multiple comparison corrections and 
-important individual R and Bioconductor packages are referenced where they have 
-been used.
-
-## Sample preparation for mass spectrometry
-
-EVs or WCLs (15 μg protein) were boiled in LDS sample buffer (Life Technologies) 
-and TCEP (Thermo Fisher Scientific), then separated by short-range SDS-PAGE 
-[@greening2016]. The gel was fixed in 50% (v/v) methanol, 7% (v/v) acetic acid 
-for 30 min, and the samples were excised. The proteins were reduced (2 mM TCEP, 
-1 h) and alkylated (40 mM iodoacetamide, 30 min in the dark) before digestion 
-(1 μg trypsin, 18 h at 37°C). Peptides were then extracted from the gel pieces 
-with 85% (v/v) ACN, 0.5% (v/v) TFA, lyophilised and resuspended in 5% (v/v) 
-ACN, 0.5% (v/v) TFA.
-
-## Mass spectrometry (ESI-LC-MS/MS) of EVs and WCL proteins
-
-Peptides were analysed as described previously [@fingerhut2018] with 
-modifications. Using a nanoflow UPLC instrument (Scientific^TM^ 
-UltiMate^TM^ 3000 RSLCnano, Thermo Fisher Scientific), the 
-reconstituted peptides were loaded onto a precolumn (C18 PepMap 300 μm ID x 2 cm 
-trapping column, Thermo Fisher Scientific) and washed prior to separation using 
-a 90 min linear ACN gradient on an analytical column (BEH C18, 1.7 μm, 130 Å 
-and 75 μm ID x 25 cm, Waters). The nanoflow UPLC was coupled on-line to a 
-Q Exactive HF mass spectrometer (Thermo Fisher Scientific) with a 
-nanoelectrospray ion source (Thermo Fisher Scientific). The Orbitrap of the Q 
-Exactive HF was used for MS and the linear trap was used for MS/MS.
-
-Data were collected in data-dependent acquisition mode using an MS scan range 
-of m/z 350 – 1500 and resolution of 60,000. HCD MS/MS spectra were collected 
-for the 15 most intense ions per MS scan at 15,000 resolution with a normalised 
-collision energy of 28% and an isolation window of 1.4 m/z. Dynamic exclusion 
-parameters were set as follows: exclude isotope on, duration 30 sec and peptide 
-match preferred. Other Orbitrap instrument parameters included an MS maximum 
-injection time of 30 ms with AGC target 3 x 10^6^, for a maximum 
-injection time of 25 ms with an AGT target of 1 x 10^5^.
-
-## Database search and protein identification
-
-Tandem MS data collected for EVs and WCLs were processed in MaxQuant 
-version 1.6.0.16 [@tyanova2016]. Andromeda was used to search the data against 
-the UniProt _C. albicans_ reference proteome (UP000000559; downloaded 
-16/06/2018; 6035 entries) and the common contaminants and decoys list [@cox2011]. 
-Trypsin was selected as the digestion enzyme and up to 2 missed cleavages were 
-allowed. Carbamidomethylation of cysteine was set as a fixed modification and 
-oxidation of methionine and N-terminal acetylation were set as variable 
-modifications. Peptide mass tolerances were 20 ppm (first search) and 4.5 ppm 
-(main search), and false discovery rate (FDR) cut offs were 0.01 for both 
-proteins and peptides. Minimum and maximum peptide lengths were set to 8 and 25 
-respectively and match between runs was not selected. Label-free quantification 
-(LFQ) of protein abundances was performed using the MaxLFQ algorithm [@cox2014]. 
-Fast LFQ was selected and normalisation was skipped. The proteinGroups.txt 
-MaxQuant output was used for further analyses. Metadata for identified proteins 
-(localisation, topology, function) were obtained from the UniProt _C. albicans_ 
-reference proteome was well as the _C. albicans_ SC5314 Assembly 22 chromosomal 
-feature file available from the Candida Genome Database 
-(candidagenome.org/download/chromosomal_feature_files) 
-[@arnaud2005; @skrzypek2017].
-
-## Protein filtering and proteomics analysis
-
-Data processing and statistical analyses were all performed using R 
-version 3.6.0 and RStudio version 1.2.1335 [@rcoreteam2018; @rstudioinc]. 
-The DAY286 yeast, DAY286 biofilm, and ATCC proteinGroups.txt files were 
-initially processed and analysed separately. Analysis methodology and some 
-modified functions were derived from the Bioconductor package _DEP_ [@zhang2018]. 
-First, reversed and contaminant proteins as well as proteins identified by less 
-than 2 unique peptides were removed. The resulting proteins were filtered for 
-those quantified (LFQ intensity > 0) in minimum 2/3 yeast or 4/5 biofilm EV or 
-WCL biological replicates. The raw LFQ intensities, sequence coverage, 
-number of unique peptides, and MS/MS counts for these proteins can be found in 
-supplemental File S1. LFQ intensities were log~2~ transformed, then 
-normalised using the default cyclic loess normalisation method from the 
-Bioconductor package _limma_ [@ritchie2015]. Proteins were then separated into 
-two groups: those exclusive to EVs or WCL, and those quantified in both samples. 
-Missing LFQ values in the latter group were imputed using the QRILC method from 
-the R package _imputeLCMD_ [@lazar2015], while exclusive proteins were left 
-untouched. Finally, differential abundance analysis of proteins in EV versus 
-WCL was performed using empirical Bayes method from _limma_ 
-[@phipson2016; @ritchie2015]. Protein log~2~(fold changes) indicated 
-the difference in average log~2~ LFQ intensity values between EVs and 
-WCLs, this value is referred to as the log~2~(FC). The resulting 
-p-values were adjusted using the Benjamini-Hochberg approach [@benjamini1995] 
-and the significance threshold was set at an adjusted p-value of 0.01. Proteins 
-were considered significantly enriched or depleted in EVs if they had a p-value 
-less than 0.01 and a positive or negative log~2~(FC) respectively. 
-Results of the differential abundance analyses are available in supplemental 
-File S2.
-
-## Functional enrichment analysis and clustering
-
-The online tool FungiFun2 version 2.2.8 (sbi.hki-jena.de/fungifun) was used for 
-all GO term enrichment analyses [@priebe2015]. Enriched GO terms were those 
-with a Benjamini-Hochberg adjusted p-value less than 0.05. Multidimensional 
-scaling (MDS) plots were constructed using the plotMDS function from _limma_ 
-[@ritchie2015]. The top 500 proteins with the largest standard deviations 
-between the proteomics samples were used for the distance calculation. To 
-construct the heatmap in Figure 5, unsupervised clustering of log~2~(FC) 
-values for the proteins common to EVs from all strains was performed using 
-Gower’s formula via the daisy function from the R package _cluster_ [@maechler2019].
-
-## Protein localisation and attribute prediction
-
-Location information of proteins was obtained from the Candida Genome Database 
-(candidagenome.org) [@arnaud2005; @skrzypek2017]. When this information was not 
-available DeepLoc-1.0 (cbs.dtu.dk/services/DeepLoc) was used to predict 
-subcellular location [@almagroarmenteros2017]. Signal peptide and transmembrane 
-domain annotations for each protein were obtained from UniProtKB or were 
-predicted using TOPCONS2 (topcons.cbr.su.se) 
-[@theuniprotconsortium2019; @tsirigos2015]. Prediction of protein palmitoylation 
-sites was performed using CSS-PALM 4.0 (csspalm.biocuckoo.org) [@ren2008].
-
-## _C. albicans_ EV marker definition
-
-Lists of proteins significantly enriched and exclusive in EVs from each strain 
-were compared using the R package _VennDiagram_ [@chen2011]. Proteins common to 
-all four strains were selected as potential EV positive protein markers. This 
-was repeated for significantly enriched and exclusive proteins in WCL to define 
-potential EV negative protein markers. Initial candidate EV marker proteins 
-were refined using the following criteria to obtain a shortlist of the best 
-potential markers. Ideal positive EV markers were proteins that satisfied 
-MISEV2018 marker categories 1 and 2 [@thery2018] and had less than 5 transmembrane 
-domains, no recognisable signal peptide, and were not detected in 
-vesicle-depleted media [@gil-bona2015b]. Ideal negative EV marker proteins were 
-selected based on prior tagging with fluorescent proteins in literature, prior 
-detection via Western blot, and adherence to MISEV2018 marker categories
-3 or 4 [@thery2018].
-
-## Data availability
-
-The proteomics data have been deposited in the ProteomeXchange Consortium 
-database via the PRIDE partner repository [@deutsch2017; @perez-riverol2019] 
-with the data set identifiers PXD014367 (DAY286 yeast), PXD014388 (ATCC90028 
-and ATCC10231), and PXD014389 (DAY286 biofilm). These data include ‘RAW’ files, 
-peak list files, MaxQuant search engine txt output, and the UniProt C. albicans 
-reference proteome FASTA file. The proteinGroups.txt files and source code used 
-in this study is freely available in an online research compendium available at 
-github.com/csdaw/candidaev. It was constructed using the R package 
-_rrtools_ [@marwick2018] and is structured as an R package which can be used to 
-reproduce the results and manuscript as submitted. The compendium has also been 
-permanently archived at zenodo (url).
-
-# Results
-
-# Discussion
-
-# Acknowledgements
-
-# Data availability
-
-# Acknowledgements
-
-\newpage
-
-# References 
-\setstretch{1.5}
-<div id="refs"></div>
 
@@
 
-<!-- assign markdown references for table caption -->
-(ref:table1) [@gil-bona2015]
-(ref:footnote1) [@skrzypek2017]
-(ref:footnote2) [@theuniprotconsortium2019]
-(ref:footnote3) [@tsirigos2015]
+<!-- Ref (31) is Gil-Bona et al. 2015 -->
+<!-- Ref (48, 49) is Arnaud et al. 2005, Skrzypek et al. 2017 -->
+<!-- Ref (57) is The UniProt Consortium 2019 -->
+<!-- Ref (58) is Tsirigos et al. 2015 -->
 
@@
              culture media (i.e. the proteins may also be in the soluble secretome) 
-             (ref:table1). Underlined proteins are those identified as the 
+             (31). Underlined proteins are those identified as the 
              best candidates for positive EV markers according to the 
-             criteria depicted in supplemental Figure S1."
+             criteria depicted in Supplementary Figure S1."
 
@@
                          similarity with \\\\textit{S. cerevisiae} homolog as 
-                         annotated in the Candida Genome Database 
-                        (ref:footnote1).", 
+                         annotated in the Candida Genome Database (48, 49).", 
                         "Protein localisation was obtained from the GO Cellular
                         Component annotation in the \\\\textit{C. albicans} 
-                        UniProt reference proteome UP000000559 (ref:footnote2).", 
+                        UniProt reference proteome UP000000559 (57).", 
                         "Presence of transmembrane domains and absence of a 
-                        signal peptide was predicted using TOPCONS2 
-                        (ref:footnote3).",
+                        signal peptide was predicted using TOPCONS2 (58).",
                         "The name Evp1 for the protein encoded by orf19.6741 
@@
 # Figures
+
+## Figure 1
 
@@
 
-```{r figure1, fig.cap=f1_cap, fig.width=7.1, fig.height=4}
+```{r figure1, fig.width=7.1, fig.height=4}
 # draw figure 1
@@
           heights = c(1,1))
-
-f1_cap <- "\\textbf{Characterisation and quantification of EVs from different 
-           \\textit{C. albicans} strains.} \\textit{(A)} Representative TEM 
-           images of EVs isolated from 4 different \\textit{C. albicans} 
-           strains. Scale bar indicates 0.5 $\\mu$m. \\textit{(B)} Size 
-           distribution of DAY286 yeast (n = 3), ATCC90028 yeast (n = 3), 
-           ATCC10231 yeast (n = 3), and DAY286 biofilm (n = 5) EVs as measured 
-           by nanoparticle tracking analysis. Line plots shown are the average 
-           of the biological replicates and the dashed grey line indicates 100 
-           nm. Plots for the individual biological replicates are presented in 
-           supplemental Figure S2. \\textit{(C)} Comparison of the ratio of 
-           particle concentration to protein concentration of the EV fraction, 
-           (particles/mL) $\\div$ ($\\mu$g protein/mL), across the four EV 
-           sources. Each dot represents one biological replicate. Sample means 
-           were compared using ANOVA followed by Tukey's HSD \\textit{post-hoc} 
-           test. P-values indicating significant differences are shown. The 
-           particle and protein concentrations for each biological replicate 
-           are provided in supplemental Table S1."
 ```
@@
 \newpage
+
+## Figure 2
 
@@
 
-```{r figure2, fig.cap=f2_cap, fig.width=7.1, fig.height=6}
+```{r figure2, fig.width=7.1, fig.height=6}
 # draw figure 2
@@
           heights = c(1,2))
-
-f2_cap <- "\\textbf{Differential abundance analysis of proteins identified in 
-           \\textit{C. albicans} EVs and whole cell lysates (WCL).} 
-           \\textit{(A)} Venn diagrams comparing the EV and WCL proteomes from 
-           four \\textit{C. albicans} strains; DAY286 yeast (n = 3), ATCC90028 
-           yeast (n = 3), ATCC10231 yeast (n = 3), and DAY286 biofilm (n = 5). 
-           Whole cell lysates were prepared from the EV source cells. Proteins 
-           were quantified (MaxQuant LFQ intensity) in minimum 2/3 (yeast) and 
-           4/5 (biofilm) biological replicates of EV or WCL. \\textit{(B)} 
-           Volcano plots depicting significantly enriched EV or WCL proteins. 
-           Differential abundance analysis was performed by comparing the mean 
-           normalised LFQ intensities of proteins identified in both EV and 
-           WCL (i.e. proteins in the venn overlap) using the Bioconductor 
-           package \\textit{limma} [@cox2014; @ritchie2015]. Significantly 
-           enriched proteins were identified using a Benjamini-Hochberg 
-           adjusted p-value cut off of 0.01 and log\\textsubscript{2}(FC) cutoff 
-           of 1. Counts of significant and 
-           non-significant proteins are indicated on each graph. Proteins with 
-           a log\\textsubscript{2}(FC) greater than 8 are labelled. Data tables 
-           underlying the venn diagrams and volcano plots are provided in 
-           supplemental File S2."
 ```
@@
 \newpage
+
+## Figure 3
 
@@
 
-```{r figure3, fig.cap=f3_cap, fig.width=7.2, fig.height=6}
+```{r figure3, fig.width=7.2, fig.height=6}
 # draw figure 3
@@
           align = "hv")
-
-f3_cap <- "\\textbf{Functional enrichment analyses of the significantly 
-           enriched and exclusive \\textit{C. albicans} EV proteins.} The 
-           online tool FungiFun2 (elbe.hki-jena.de/fungifun) was used to 
-           identify enriched biological process (BP), cellular component (CC), 
-           and molecular function (MF) GO terms [@priebe2015]. A selection of 
-           the most significantly enriched terms for each GO domain are shown. 
-           They are presented top to bottom in order of increasing 
-           Benjamini-Hochberg adjusted p-value. Full lists of enriched GO 
-           terms can be found in supplemental File S3."
 ```
@@
 \newpage
+
+## Figure 4
 
@@
 
-```{r figure4, fig.cap=f4_cap, fig.width=7.1, fig.height=5}
+```{r figure4, fig.width=7.1, fig.height=5}
 ggarrange(ggarrange(f4a, f4b,
@@
           heights = c(2, 3))
-
-f4_cap <- "\\textbf{Combined comparison of \\textit{C. albicans} proteomes.} 
-           \\textit{(A)} Venn diagram comparing four \\textit{C. albicans} EV 
-           proteomes. Lists of proteins present in the centre and right 
-           partitions of each venn diagram in Figure \\@ref(fig:figure2)A were 
-           compared to identify proteins present in all four datasets. 
-           \\textit{(B)} Venn diagram comparing four \\textit{C. albicans} WCL 
-           proteomes. Lists of proteins present in the centre and left 
-           partitions of each venn diagram in Figure \\@ref(fig:figure2)A were 
-           compared to identify proteins present in all four datasets. The data 
-           tables underlying Figures \\@ref(fig:figure4)A and 
-           \\@ref(fig:figure4)B are provided in supplemental File S4. 
-           \\textit{(C)} Multidimensional scaling (MDS) plot of each LC-MS/MS 
-           biological replicate sample with the first 2 dimensions shown. 
-           Pairwise distance between samples approximately indicates the 
-           log\\textsubscript{2}(FC) between samples. \\textit{limma} was used 
-           to generate the MDS plots [@ritchie2015]. \\textit{(D)} MDS plot of 
-           each LC-MS/MS biological replicate sample with the second and third 
-           dimensions shown."
 ```
@@
 \newpage
+
+## Figure 5
 
@@
 
-```{r figure5, fig.cap=f5_cap, fig.height=6}
+```{r figure5, fig.height=6}
 f5 <- png::readPNG("figures/figure5.png")
@@
                              unit = "inches"))
-
-f5_cap <- "\\textbf{Identification of commonly enriched EV proteins across 
-           different \\textit{C. albicans} strains.} Heatmap of proteins 
-           (n = 396) identified in all four EV samples (venn overlap in Figure 
-           \\@ref(fig:figure4)A). Each column represents a 
-           \\textit{C. albicans} strain and each row represents a protein. The 
-           colours indicate the log\\textsubscript{2}(FC) of the protein for 
-           that particular strain; red is EV enriched, blue is EV depleted, and 
-           black is EV exclusive. Unsupervised clustering of rows and columns 
-           was performed using Gower's formula via the daisy function from the 
-           R package \\textit{cluster} [@maechler2019]. Proteins which were 
-           exclusive to EVs from all four strains and therefore had no valid 
-           log\\textsubscript{2}(FC) values
-           were seperated prior to clustering, in the group designated 
-           \`\`cluster 8\". Functional enrichment analyses were performed on 
-           the heatmap protein clusters using the online tool FungiFun2 
-           [@priebe2015]. A selection of significantly enriched GO terms are 
-           presented in the table inset. Full lists of enriched GO terms and 
-           proteins in each cluster are available in supplemental Files S3 and 
-           S5 respectively."
 ```
@@
 \newpage
+
+## Figure 6
 
@@
 
-```{r figure6, fig.cap=f6_cap, fig.width=2.5, fig.height=4}
+```{r figure6, fig.width=2.5, fig.height=4}
 ggarrange(f6a, f6b, 
@@
           nrow = 2)
-
-f6_cap <- "\\textbf{Identification of common signficantly enriched or exclusive 
-           \\textit{C. albicans} EV and WCL proteins.} Proteins identified as 
-           significantly enriched or exclusive to EVs in Figure 
-           \\@ref(fig:figure2) were compared to select those which were common 
-           to all 4 datasets. 47 proteins were identified as potential positive 
-           EV protein markers and 62 proteins as potential negative EV protein 
-           markers. The data tables underlying Figure 
-           \\@ref(fig:figure6) are provided in supplemental File S4. Details of 
-           the 47 positive EV protein marker candidates and 62 negative 
-           candidates can be found in Table \\@ref(tab:table1) and supplemental 
-           Table S2 respectively."
 ```
@@
 
-```{r figure7, fig.cap=f7_cap, fig.width=4, fig.height=3.6}
-f7_cap <- "\\textbf{Twenty-two best potential \\textit{C. albicans} positive EV 
-           protein markers.} These proteins are those underlined in Table 
-           \\@ref(tab:table1). They are are enriched or exclusive to EVs 
-           isolated from all of the \\textit{C. albicans} strains investigated 
-           in this study. The proteins fit within the EV biomarker categories 
-           1 and 2 from MISEV2018 which includes transmembrane, 
-           GPI-anchored, and cytosolic proteins that are EV enriched 
-           [@thery2018]."
-
+## Figure 7
+
+```{r figure7, fig.width=4, fig.height=3.6}
 f7 <- png::readPNG("figures/figure7.png")
@@
 
-```{r figure8, fig.cap=f8_cap, fig.width=7.2, fig.height=6}
-f8_cap <- "\\textbf{Predicted topology and palmitoylation sites of 
-           \\textit{C. albicans} MCC/eisosome proteins Sur7 and Evp1 
-           (orf19.6741) 
-           compared to the human tetraspanin CD81.} The presence of 
-           transmembrane (TM) domains and palmitoylation sites shown on the 
-           left side of the figure were predicted using the online tools 
-           TOPCONS2 (topcons.cbr.su.se) [@tsirigos2015] and CSS-PALM 4.0 
-           (csspalm.biocuckoo.org) [@ren2008] respectively. For CD81, 
-           palmitoylation sites experimentally determined in previous 
-           literature are shown [@delandre2009]. The right side of the figure 
-           shows a cartoon representation of the TOPCONS2 consensus topology 
-           prediction for the three proteins as well as the crystal structure 
-           of CD81 (PDB: 5TCX) [@zimmerman2016]."
-
+## Figure 8
+
+```{r figure8, fig.width=7.2, fig.height=6}
 f8 <- png::readPNG("figures/figure8.png")

### 2019-07-17 inst/manuscript/manuscript_supplement.Rmd
Remove text from manscript.Rmd

@@
 **Corresponding author:** Mark Bleackley, m.bleackley@latrobe.edu.au
-
-**Running title:** Defining _Candida albicans_ EV protein markers
 
@@
 
-(ref:footnote1) [@skrzypek2017]
+(ref:footnote1) [@arnaud2005; @skrzypek2017]
 
@@
               UniProtKB. \`\`SP\" indicates whether a protein is annotated as 
-              having a signal peptide according to UniProtKB. \`\`VDM\" shows 
+              having a signal peptide according to UniProt. \`\`VDM\" shows 
               whether a protein has previously been detected in 
@@
               those identified as the best candidates for negative
-              EV markers according to the criteria depicted in Figure S1."
+              EV markers according to the criteria depicted in 
+              Supplementary Figure S1."
 

### 2019-07-17 inst/manuscript/candidaev_figures.Rmd
Fix formatting of Supplementary Data

--- 2019-07-17 inst/manuscript/manuscript.Rmd
@@
 <!-- Ref (48, 49) is Arnaud et al. 2005, Skrzypek et al. 2017 -->
-<!-- Ref (57) is The UniProt Consortium 2019 -->
-<!-- Ref (58) is Tsirigos et al. 2015 -->
+<!-- Ref (58) is The UniProt Consortium 2019 -->
+<!-- Ref (59) is Tsirigos et al. 2015 -->
 
@@
                         Component annotation in the \\\\textit{C. albicans} 
-                        UniProt reference proteome UP000000559 (57).", 
+                        UniProt reference proteome UP000000559 (58).", 
                         "Presence of transmembrane domains and absence of a 
-                        signal peptide was predicted using TOPCONS2 (58).",
+                        signal peptide was predicted using TOPCONS2 (59).",
                         "The name Evp1 for the protein encoded by orf19.6741 

### 2019-07-18 README.Rmd
Remove text from manscript.Rmd
Update github READMEs

@@
 Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
-claudin-like Sur7 family proteins and Rho GTPases. _Molecular and Cellular_ 
-_Proteomics_, submitted.
+claudin-like Sur7 family proteins and GTPases. _Journal of Extracellular_ 
+_Vesicles_, submitted.
 
@@
 Bleackley, M. R. (2019) Research compendium for "Protein markers for 
-_Candida albicans_ EVs include claudin-like Sur7 family proteins and Rho 
-GTPases". version x.x.x. Zenodo. URL.
+_Candida albicans_ EVs include claudin-like Sur7 family proteins and GTPases". 
+version x.x.x. Zenodo. URL.
 
@@
     ├── /data                # Data tables installed with package
-    ├── /inst/manuscript     # Final submitted manuscript and supplemental files
+    ├── /inst/manuscript     # Final submitted manuscript, figures, and supplementary data
     ├── /man                 # Auto-generated documentation for functions and included data
@@
 GitHub using `devtools`. A full installation will include all the functions and 
-data included in the package as well as some HTML vignettes,
-and the manuscript `.Rmd` file which can be used to reproduce the manuscript as
-it was submitted.
+data included in the package as well as some HTML vignettes, the manuscript
+text, the figures `.Rmd` file which can be used to reproduce the analysis and 
+figures as submitted.
 
@@
 
-**Note:** the contents of `/data-raw` and `/inst/manuscript/supplement_files` 
+**Note:** the contents of `/data-raw` and `/inst/manuscript/supplementary_data` 
 are not installed when the package is 
@@
 [here](https://github.com/csdaw/candidaev/tree/master/data-raw) and 
-`/inst/manuscript/supplement_files` can be manually downloaded from 
+`/inst/manuscript/supplementary_data` can be manually downloaded from 
 [here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).
@@
 
-The manuscript `.pdf` file, as submitted, can be downloaded 
+The manuscript `.docx` file, as submitted, can be downloaded 
 [here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).
 
-#### Building the manuscript from scratch
+The figures for the manuscript were produced using the `candidaev_figures.Rmd` 
+file which can be downloaded
+[here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).
 
-To generate the reproducible manuscript, an installation of LaTeX is required. 
+#### Building the figures from scratch
+
+To generate the reproducible figures, an installation of LaTeX is required. 
 TinyTex is a good option for this and can be installed using:
@@
 
-Then the manuscript (and supplement) can be built using:
+Then the manuscript figures (and supplement) can be built using:
 
@@
 # requires LaTeX installation and full compendium installation
-rmarkdown::render(system.file("manuscript", "manuscript.Rmd", 
+rmarkdown::render(system.file("manuscript", "candidaev_figures.Rmd", 
                               package = "candidaev"))
-rmarkdown::render(system.file("manuscript", "manuscript_supplement.Rmd", 
+rmarkdown::render(system.file("manuscript", "candidaev_supplement.Rmd", 
                               package = "candidaev"))
@@
 
-```{r sessionInfo, echo=FALSE}
-sessionInfo()
+```{r sessionInfo, echo=FALSE, cache=FALSE}
+devtools::session_info()
 ```

### 2019-07-18 inst/manuscript/README.Rmd
Update github READMEs

@@
 
-This directory contains the submitted manuscript, supplemental figures and 
-tables, and supplemental files for our paper:
+This directory contains the submitted manuscript `.docx` file, main figures,
+supplementary figures, and supplementary data for our paper:
 
@@
 Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
-claudin-like Sur7 family proteins and Rho GTPases. Mol. Cell. Proteomics, 
-submitted.
+claudin-like Sur7 family proteins and GTPases. _Journal of Extracellular_ 
+_Vesicles_, submitted.
 
@@
     │         ├── /supplement_files           # Contains .R scripts used to generate supplemental files
-    │         ├── manuscript.Rmd              # R markdown file to produce manuscript.pdf
-    │         ├── manuscript.pdf              # Final submitted manuscript
-    │         ├── manuscript_supplement.Rmd   # R markdown file to produce manuscript_supplement.pdf
-    │         ├── manuscript_supplement.pdf   # Final submitted supplemental figures and tables
-    │         ├── README.Rmd                  # R markdown file to produce README.md
-    │         └── README.md                   # Description of /inst/manuscript directory
+    │         ├── README.Rmd                  # Rmarkdown file to produce README.md
+    │         ├── README.md                   # Description of /inst/manuscript directory
+    │         ├── candidaev_manuscript.docx   # Full manuscript text and figure legends as submitted
+    │         ├── candidaev_figures.pdf       # Main figures and table as submitted
+    │         ├── candidaev_figures.Rmd       # Rmarkdown file to produce candidaev_figures.pdf
+    │         ├── candidaev_supplement.pdf    # Supplementary figures and tables as submitted
+    │         └── candidaev_supplement.Rmd    # Rmarkdown file to produce candidaev_supplement.pdf
     └── ...

### 2019-07-18 inst/manuscript/candidaev_figures.Rmd
Change reference style .csl file

@@
 bibliography: "components/references.bib" 
-csl: "components/molecular-and-cellular-proteomics.csl"
+csl: "components/taylor-and-francis-acs.csl"
 link-citations: yes

### 2019-09-06 inst/manuscript/candidaev_supplement.Rmd
Export individual supplemental figures and tables
May require individual files for the supplementary figures and tables
for publication.

Export the supplementary figure .svg files as .eps files.

Export the supplementary tables as .txt files containing LaTeX code
to be imported into excel and saved as .xlsx.

@@
 library(kableExtra)
-
-# set seed for random number generation
-set.seed(1)
 ```
@@
 
-```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5}
+```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript')}
 fS2_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 
@@
 # construct a table of metadata for each EV biological replicate
-nta_total %>% 
+tabS1 <- nta_total %>% 
   select(-strain) %>% 
@@
   pack_rows("DAY286 biofilm", 10, 14)
+
+# export table S2 LaTeX code with \\ line endings removed in a text file
+tabS1_clean <- gsub("\\\\\\\\\n", "\n", tabS1)
+
+cat(tabS1_clean, file = "tables/table_S1.txt", sep = "\n")
+
+# show table S1 in PDF output
+tabS1
 ```
@@
 
-(ref:table1) [@gil-bona2015]
+(ref:table1) [@gil-bona2015b]
 
@@
 # draw table S2
-knitr::kable(wcl_longlist2[, -9], 
+tabS2 <- knitr::kable(wcl_longlist2[, -9], 
                       caption = tabs2_cap, 
@@
            threeparttable = TRUE)
+
+# export table S2 LaTeX code with \\ line endings removed in a text file
+tabS2_clean <- gsub("\\\\\\\\\n", "\n", tabS2)
+
+cat(tabS2_clean, file = "tables/table_S2.txt", sep = "\n")
+
+# show table S2 in PDF output
+tabS2
 ```

### 2019-09-06 inst/manuscript/candidaev_figures.Rmd
Update figures Rmarkdown and PDF

@@
 # draw table 1
-knitr::kable(marker_longlist2[ ,-9],
+tab1 <- knitr::kable(marker_longlist2[ ,-9],
                      caption = tab1_cap, 
@@
            threeparttable = TRUE)
+
+# export table 1 LaTeX code with \\ line endings removed in a text file
+tab1_clean <- gsub("\\\\\\\\\n", "\n", tab1)
+
+cat(tab1_clean, file = "tables/table_1.txt", sep = "\n")
+
+# show table 1 in PDF output
+tab1
 ```
@@
                               "DAY286" = "Y"))
-```
-
-```{r figure1, fig.width=7.1, fig.height=4}
+
+# arguments for figure 1 export
+f1_args <- list(tiff = list(type = "cairo"))
+```
+
+```{r figure1, fig.width=7.1, fig.height=4, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=f1_args, dpi=600}
 # draw figure 1
@@
            parse = TRUE, colour = unname(ev_pal[1]))
-```
-
-```{r figure2, fig.width=7.1, fig.height=6}
+
+# arguments for figure 2 export
+f2_args <- list(tiff = list(type = "cairo"))
+```
+
+```{r figure2, fig.width=7.1, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f2_args, dpi=600}
 # draw figure 2
@@
   annotate("text", x = 14, y = 70, label = "bold('ATCC10231')", parse = TRUE)
-```
-
-```{r figure3, fig.width=7.2, fig.height=6}
+
+# arguments for figure 3 export
+f3_args <- list(tiff = list(type = "cairo"))
+```
+
+```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f3_args, dpi=600}
 # draw figure 3
@@
   ylab(label = "Dimension 2")
-```
-
-```{r figure4, fig.width=7.1, fig.height=5}
+
+# arguments for figure 4 export
+f4_args <- list(tiff = list(type = "cairo"))
+```
+
+```{r figure4, fig.width=7.1, fig.height=5, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f4_args, dpi=600}
 ggarrange(ggarrange(f4a, f4b,
@@
 f5_go8 <- process_fungifun("figures/f5_GO_clust8.csv")
-```
-
-```{r figure5, fig.height=6}
+
+# arguments for figure 5 export
+f5_args <- list(tiff = list(type = "cairo"))
+```
+
+```{r figure5, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f5_args, dpi=600}
 f5 <- png::readPNG("figures/figure5.png")
@@
   theme(plot.margin = unit(c(1.2,0,0,0), "lines"))
-```
-
-```{r figure6, fig.width=2.5, fig.height=4}
+
+# arguments for figure 6 export
+f6_args <- list(tiff = list(type = "cairo"))
+```
+
+```{r figure6, fig.width=2.5, fig.height=4, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=f6_args, dpi=600}
 ggarrange(f6a, f6b, 
@@
           nrow = 2)
+
+# arguments for figure 7 export
+f7_args <- list(tiff = list(type = "cairo"))
 ```
@@
 
-```{r figure7, fig.width=4, fig.height=3.6}
+```{r figure7, fig.width=4, fig.height=3.6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f7_args, dpi=600}
 f7 <- png::readPNG("figures/figure7.png")
@@
   background_image(f7)
+
+# arguments for figure 8 export
+f8_args <- list(tiff = list(type = "cairo"))
 ```
@@
 
-```{r figure8, fig.width=7.2, fig.height=6}
+```{r figure8, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f8_args, dpi=600}
 f8 <- png::readPNG("figures/figure8.png")

### 2019-09-06 inst/manuscript/candidaev_supplement.Rmd
Update figures Rmarkdown and PDF

@@
                       type = "individual")[[1]]
+
+# arguments for figure S1 export
+fS1_args <- list(tiff = list(type = "cairo"))
 ```
@@
 
-```{r figureS1, fig.cap=fs1_cap, fig.width=5.45, fig.height=6}
+```{r figureS1, fig.cap=fS1_cap, fig.width=5.45, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=fS1_args, dpi=600}
 # construct figure 1
-fs1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
+fS1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
            proteomic analysis of \\textit{C. albicans} EVs and the selection 
@@
 
-fs1 <- png::readPNG("figures/figures1.png")
+fS1 <- png::readPNG("figures/figures1.png")
 
@@
 ggplot() + 
-  background_image(fs1)
+  background_image(fS1)
+
+# arguments for figure S2 export
+fS2_args <- list(tiff = list(type = "cairo"))
 ```
 
-```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript')}
+```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=fS2_args, dpi=600}
 fS2_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 

### 2019-09-06 inst/manuscript/candidaev_supplement.Rmd
Track compressed supplementary .tiff files
Supplementary figure .tiff files with lzw compression are
a more manageable size, therefore track with git.

@@
 # arguments for figure S1 export
-fS1_args <- list(tiff = list(type = "cairo"))
+fS1_args <- list(tiff = list(type = "cairo", compression = "lzw"))
 ```
@@
 # arguments for figure S2 export
-fS2_args <- list(tiff = list(type = "cairo"))
+fS2_args <- list(tiff = list(type = "cairo", compression = "lzw"))
 ```

### 2019-09-06 inst/manuscript/candidaev_figures.Rmd
Track compressed manuscript figure .tiff files
Manuscript figure .tiff files with lzw compression are
a more manageable size, therefore track with git.

@@
 # arguments for figure 1 export
-f1_args <- list(tiff = list(type = "cairo"))
+f1_args <- list(tiff = list(type = "cairo", compression = "lzw"))
 ```
@@
 # arguments for figure 2 export
-f2_args <- list(tiff = list(type = "cairo"))
+f2_args <- list(tiff = list(type = "cairo", compression = "lzw"))
 ```
@@
 # arguments for figure 3 export
-f3_args <- list(tiff = list(type = "cairo"))
+f3_args <- list(tiff = list(type = "cairo", compression = "lzw"))
 ```
@@
 # arguments for figure 4 export
-f4_args <- list(tiff = list(type = "cairo"))
+f4_args <- list(tiff = list(type = "cairo", compression = "lzw"))
 ```
@@
 # arguments for figure 5 export
-f5_args <- list(tiff = list(type = "cairo"))
+f5_args <- list(tiff = list(type = "cairo", compression = "lzw"))
 ```
@@
 # arguments for figure 6 export
-f6_args <- list(tiff = list(type = "cairo"))
+f6_args <- list(tiff = list(type = "cairo", compression = "lzw"))
 ```
@@
 # arguments for figure 7 export
-f7_args <- list(tiff = list(type = "cairo"))
+f7_args <- list(tiff = list(type = "cairo", compression = "lzw"))
 ```
@@
 # arguments for figure 8 export
-f8_args <- list(tiff = list(type = "cairo"))
+f8_args <- list(tiff = list(type = "cairo", compression = "lzw"))
 ```

### 2019-09-06 inst/manuscript/candidaev_figures.Rmd
Switch CairoPDF back to grDevices pdf

@@
 
-```{r figure1, fig.width=7.1, fig.height=4, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=f1_args, dpi=600}
+```{r figure1, fig.width=7.1, fig.height=4, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=f1_args, dpi=600}
 # draw figure 1
@@
 
-```{r figure2, fig.width=7.1, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f2_args, dpi=600}
+```{r figure2, fig.width=7.1, fig.height=6, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f2_args, dpi=600}
 # draw figure 2
@@
 
-```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f3_args, dpi=600}
+```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f3_args, dpi=600}
 # draw figure 3
@@
 
-```{r figure4, fig.width=7.1, fig.height=5, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'),  dev.args=f4_args, dpi=600}
+```{r figure4, fig.width=7.1, fig.height=5, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f4_args, dpi=600}
 ggarrange(ggarrange(f4a, f4b,
@@
 
-```{r figure5, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f5_args, dpi=600}
+```{r figure5, fig.height=6, fig.path='figures/', dev=c('pdf', 'tiff'), dev.args=f5_args, dpi=600}
 f5 <- png::readPNG("figures/figure5.png")
@@
 
-```{r figure6, fig.width=2.5, fig.height=4, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=f6_args, dpi=600}
+```{r figure6, fig.width=2.5, fig.height=4, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=f6_args, dpi=600}
 ggarrange(f6a, f6b, 
@@
 
-```{r figure7, fig.width=4, fig.height=3.6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f7_args, dpi=600}
+```{r figure7, fig.width=4, fig.height=3.6, fig.path='figures/', dev=c('pdf', 'tiff'), dev.args=f7_args, dpi=600}
 f7 <- png::readPNG("figures/figure7.png")
@@
 
-```{r figure8, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=f8_args, dpi=600}
+```{r figure8, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('pdf', 'tiff'), dev.args=f8_args, dpi=600}
 f8 <- png::readPNG("figures/figure8.png")

### 2019-09-06 inst/manuscript/candidaev_supplement.Rmd
Switch CairoPDF back to grDevices pdf

@@
 
-```{r figureS1, fig.cap=fS1_cap, fig.width=5.45, fig.height=6, fig.path='figures/', dev=c('CairoPDF', 'tiff'), dev.args=fS1_args, dpi=600}
+```{r figureS1, fig.cap=fS1_cap, fig.width=5.45, fig.height=6, fig.path='figures/', dev=c('pdf', 'tiff'), dev.args=fS1_args, dpi=600}
 # construct figure 1
@@
 
-```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('CairoPDF', 'CairoPS', 'tiff'), dev.args=fS2_args, dpi=600}
+```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=fS2_args, dpi=600}
 fS2_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 

### 2019-09-06 inst/manuscript/candidaev_figures.Rmd
Switch CairoPS back to grDevices postscript
Also remove Cairo from Suggests

@@
 # arguments for figure 1 export
-f1_args <- list(tiff = list(type = "cairo", compression = "lzw"))
-```
-
-```{r figure1, fig.width=7.1, fig.height=4, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=f1_args, dpi=600}
+f1_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
+                postscript = list(bg = "white", fonts = "sans"))
+```
+
+```{r figure1, fig.width=7.1, fig.height=4, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=f1_args, dpi=600}
 # draw figure 1
@@
 # arguments for figure 2 export
-f2_args <- list(tiff = list(type = "cairo", compression = "lzw"))
-```
-
-```{r figure2, fig.width=7.1, fig.height=6, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f2_args, dpi=600}
+f2_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
+                postscript = list(bg = "white", fonts = "sans"))
+```
+
+```{r figure2, fig.width=7.1, fig.height=6, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'),  dev.args=f2_args, dpi=600}
 # draw figure 2
@@
 # arguments for figure 3 export
-f3_args <- list(tiff = list(type = "cairo", compression = "lzw"))
-```
-
-```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f3_args, dpi=600}
+f3_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
+                postscript = list(bg = "white", fonts = "sans"))
+```
+
+```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'),  dev.args=f3_args, dpi=600}
 # draw figure 3
@@
 # arguments for figure 4 export
-f4_args <- list(tiff = list(type = "cairo", compression = "lzw"))
-```
-
-```{r figure4, fig.width=7.1, fig.height=5, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f4_args, dpi=600}
+f4_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
+                postscript = list(bg = "white", fonts = "sans"))
+```
+
+```{r figure4, fig.width=7.1, fig.height=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'),  dev.args=f4_args, dpi=600}
 ggarrange(ggarrange(f4a, f4b,
@@
 # arguments for figure 6 export
-f6_args <- list(tiff = list(type = "cairo", compression = "lzw"))
-```
-
-```{r figure6, fig.width=2.5, fig.height=4, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=f6_args, dpi=600}
+f6_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
+                postscript = list(bg = "white", fonts = "sans"))
+```
+
+```{r figure6, fig.width=2.5, fig.height=4, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=f6_args, dpi=600}
 ggarrange(f6a, f6b, 

### 2019-09-06 inst/manuscript/candidaev_supplement.Rmd
Switch CairoPS back to grDevices postscript
Also remove Cairo from Suggests

@@
 # arguments for figure S2 export
-fS2_args <- list(tiff = list(type = "cairo", compression = "lzw"))
+fS2_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
+                postscript = list(bg = "white", fonts = "sans"))
 ```
 
-```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=fS2_args, dpi=600}
+```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS2_args, dpi=600}
 fS2_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 

### 2019-12-26 inst/manuscript/candidaev_figures.Rmd
Address reviewer 2 comment 3
Figure 1B hard to read because ATCC10231 particle concentration a lot
lower than the others.

Changed Figure 1B to percentage of total bar chart which shows
differences in size distribution better. Old Figure 1B should be
moved to supplementary material.

@@
 # construct figure 1b
-f1b <- nta_bioavg %>% 
-  ggplot(aes(x = particle_size, y = Bio_rep_mean, colour = Strain)) + 
-  scale_colour_manual(values = st_pal[c(3, 2, 4, 1)], 
-                      breaks = c("DAY286", "ATCC90028", 
-                                 "ATCC10231", "Biofilm"), 
-                      labels = c("DAY286 Y", "ATCC90028", 
-                                 "ATCC10231", "DAY286 B")) + 
-  geom_vline(xintercept = 100, colour = "#999999", linetype = "dashed") +
-  geom_line(size = 0.5) + 
-  facet_wrap(~ facet, scales = "free", ncol = 2, nrow = 1) + 
+nta_binned <- nta_techavg %>% 
+  ungroup() %>% 
+  mutate(bin = ntile(particle_size, 10)) %>% 
+  nanocount(Strain, Bio_rep, bin, 
+            param_var = Tech_rep_mean)
+
+test <- nta_binned %>% 
+  mutate(bin = as.factor(bin))
+
+test2 <- aov(Particle_count ~ Strain * bin, data = test)
+summary(test2)
+
+TukeyHSD(test2, which = "Strain")
+
+nta_binned_bio <- nta_binned %>% 
+  nanolyze(Strain, bin, 
+           name = "Bio_rep", 
+           param_var = Particle_count)
+
+nta_percent <- nta_binned_bio %>% 
+  group_by(Strain) %>% 
+  summarise(Total_particles = sum(Bio_rep_mean)) %>% 
+  left_join(nta_binned_bio, by = "Strain") %>% 
+  select(-Total_particles, Total_particles) %>% 
+  mutate(Percentage_total = Bio_rep_mean / Total_particles * 100, 
+         Percentage_se = Bio_rep_se / Total_particles * 100) %>% 
+  filter(bin %in% c(1, 2, 3, 4, 5, 6))
+
+nta_percent$Strain <- factor(nta_percent$Strain, 
+                             levels = c("DAY286", "ATCC90028", 
+                                        "ATCC10231", "Biofilm"))
+
+f1b_x_labs <- c("0-100", "100-200", "200-300", "300-400", "400-500", "500-600")
+
+f1b <- ggplot(data = nta_percent, aes(x = as.factor(bin), 
+                               y = Percentage_total, 
+                               fill = Strain)) + 
+  geom_bar(stat = "identity", position = "dodge") + 
+  geom_errorbar(aes(ymin = Percentage_total - Percentage_se, 
+                    ymax = Percentage_total + Percentage_se), 
+                width = 0.2, 
+                position = position_dodge(0.9)) + 
+  scale_fill_manual(values = st_pal) + 
+  scale_x_discrete(labels = f1b_x_labs) + 
+  labs(x = "Particle size (nm)", 
+       y = "% of total particles   ") + 
   theme_classic() + 
-  theme(strip.background = element_blank(), 
-        strip.text = element_blank(), 
-        legend.position = c(0.88, 0.6), 
-        legend.title = element_blank(), 
-        plot.margin = margin(t = 0.2, l = 0, r = 0.2, b = 0, unit = "inches"), 
-        axis.text.x = element_text(colour = "black")) + 
-  xlab(label = "Particle size (nm)") + 
-  ylab(label = "Particles / mL")
+  theme(legend.position = c(0.8, 0.6), 
+        axis.text = element_text(colour = "black"), 
+        legend.title = element_blank())
 
@@
                               "Biofilm" = "B", 
-                              "DAY286" = "Y"))
+                              "DAY286" = "Y")) + 
+  coord_cartesian(clip = "off")
 

### 2019-12-30 inst/manuscript/candidaev_supplement.Rmd
Add Supplementary Figure S3
Boxplots comparing mode EV size and EV particle
concentration for each 'strain'.

@@
 library(kableExtra)
+
+# define colour palette to distinguish between strains
+# colours = yellow, blue, green, pink
+# levels = yeast, ATCC90028, ATCC10231, biofilm
+st_pal <- c("#E69F00", "#56B4E9", "#009E73", "#CC79A7")
 ```
@@
                                            rep(300, 3)), 
-                           protein_yield = c(19.2, 28.2, 28.7, 
-                                             42.4, 71.6, 58.4, 
-                                             20.4, 19.8, 29.7, 19.3, 41.6, 
-                                             21.9, 18.0, 22.4), 
+                           ev_vol = c(100, 100, 100, 
+                                      100, 100, 100, 
+                                      100, 100, 100, 100, 100, 
+                                      50, 50, 50), 
                            protein_conc = c(0.192, 0.282, 0.287, 
@@
                                           rep(4, 5), rep(1, 3)), 
-                           stringsAsFactors = FALSE)
+                           stringsAsFactors = FALSE) %>% 
+  mutate(protein_yield = ev_vol * protein_conc) %>% 
+  select(id, strain, replicate, OD600, culture_vol, ev_vol, 
+         protein_yield, everything())
 
@@
   arrange(sort_order) %>% 
-  select(strain, replicate, OD600, culture_vol, protein_yield, protein_conc, 
-         Particle_count, mean, mode, sd) %>% 
+  select(strain, replicate, OD600, culture_vol, ev_vol, protein_yield, 
+         protein_conc, Particle_count, mean, mode, sd) %>% 
   mutate(OD600 = case_when(is.na(OD600) == TRUE ~ "NA", 
@@
 tabS1 <- nta_total %>% 
-  select(-strain) %>% 
+  select(-strain, -ev_vol) %>% 
   mutate_all(linebreak) %>% 
@@
 tabS1
+```
+
+\newpage
+
+```{r figureS3data}
+## Compare mode size of EVs from each strain
+# Use ANOVA for comparison
+mode_aov <- aov(mode ~ strain, data = nta_total)
+
+# Check assumptions of normality and homogeneous variances
+# Plot residuals vs fitted values. Variances seem homogeneous
+# plot(mode_aov, 1)
+
+# Check assumption of normality with Shapiro-Wilk test
+# Non-significant result indicates data is normal
+# shapiro.test(x = residuals(object = mode_aov))
+
+# Check ANOVA is significant (it is) and do TukeyHSD post-hoc
+mode_result <- mode_aov %>% 
+  tukey_hsd()
+
+# Plot mode size comparison
+fs3a <- nta_total %>% 
+  ggboxplot(x = "strain", y = "mode", 
+            color = "strain", palette = st_pal, add = "jitter", 
+            add.params = list(color = "black"), 
+            shape = 15, 
+            ylab = "Mode particle size (nm)") + 
+  scale_y_continuous(expand = c(0, 0), 
+                     limits = c(0, 210)) + 
+  theme(axis.title.x = element_blank(), 
+        legend.position = "none") + 
+  stat_compare_means(method = "anova", 
+                     label.x = 0.7, 
+                     label.y = 205) + 
+  stat_pvalue_manual(mode_result[c(2:5), ], label = "p.adj", 
+                     y.position = c(180, 190, 205, 170)) + 
+  coord_cartesian(clip = "off")
+
+## Compare EV concentration from each strain
+# Use ANOVA for comparison
+conc_aov <- aov(mode ~ strain, data = nta_total)
+
+# Check assumptions of normality and homogeneous variances
+# Plot residuals vs fitted values. Variances seem homogeneous
+# plot(conc_aov, 1)
+
+# Check assumption of normality with Shapiro-Wilk test
+# Data is non-normal. Therefore use Kruskall-Wallis instead.
+# shapiro.test(x = residuals(object = mode_aov))
+
+# Check Kruskall-Wallis is significant (it is) and do Dunn's test post-hoc
+conc_kruskall <- kruskal.test(Particle_count ~ strain, data = nta_total)
+conc_dunns <- FSA::dunnTest(Particle_count ~ strain, data = nta_total, 
+                            method = "bh")[[2]] %>% 
+  tidyr::separate(col = Comparison, 
+                  into = c("group1", "group2"), 
+                  sep = " - ") %>% 
+  mutate(p.adj = round(P.adj, digits = 3))
+
+fs3b <- nta_total %>% 
+  ggboxplot(x = "strain", y = "Particle_count", 
+            color = "strain", palette = st_pal, add = "jitter", 
+            add.params = list(color = "black"), 
+            shape = 15, 
+            ylab = "Total particle concentration / mL") + 
+  scale_y_continuous(expand = c(0, 0), 
+                     limits = c(0, 1e13)) + 
+  theme(axis.title.x = element_blank(), 
+        legend.position = "none") + 
+  stat_compare_means(method = "kruskal.test", 
+                     label.x = 0.82, 
+                     label.y = 9.7e12) +
+  stat_pvalue_manual(conc_dunns[c(2), ], label = "p.adj", 
+                     y.position = 8.8e12) + 
+  coord_cartesian(clip = "off")
+
+# arguments for figure S3 export
+fS3_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
+                postscript = list(bg = "white", fonts = "sans"))
+```
+
+```{r figureS3, fig.cap=fS3_cap, fig.height=7, fig.width=5.5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS3_args, dpi=600}
+fS3_cap <- c("\\textbf{MAIN} Sub.")
+
+ggarrange(fs3a, fs3b, 
+          labels = c("A", "B"), 
+          nrow = 2, 
+          ncol = 1, 
+          heights = c(1,1), 
+          align = "v")
 ```

### 2019-12-31 inst/manuscript/candidaev_figures.Rmd
Make minute change to candidaev_figures.Rmd

@@
 
-test <- nta_binned %>% 
-  mutate(bin = as.factor(bin))
-
-test2 <- aov(Particle_count ~ Strain * bin, data = test)
-summary(test2)
-
-TukeyHSD(test2, which = "Strain")
-
 nta_binned_bio <- nta_binned %>% 
@@
 
-# construct figure 2c
+# construct figure 1c
 nta_total$Strain <- factor(nta_total$Strain, 

### 2020-01-09 inst/manuscript/candidaev_supplement.Rmd
Add supplementary figures S4 S5
Figure S4A is a venn diagram comparing yeast EV proteins with biofilm
EV proteins.

Figure S4B is a volcano plot showing enrichment of proteins common to
yeast and biofilm EVs.

Data underlying figure S4 are given in supplementary data S6.

Figure S5A is a GO enrichment analysis performed on yeast EV proteins
that are exclusive or enriched compared to biofilm EVs.

Figure S5B is  a GO enrichment analysis performed on biofilm EV
proteins that are exclusive or enriched compared to yeast EVs.

Data underlying figure S5 are given in supplmentary data S7

@@
 
+```{r figureS4Data}
+#### DAY286 yeast EV proteins ####
+# filter for proteins quantified in min 2/3 reps of yeast EV or WCL
+# then convert to a data.frame and extract protein acessions from row names
+yeast_filt3 <- filter_na2(yeast_lfq2, logic = "or", op = "<=",
+                          pat1 = "EV", val1 = 1,
+                          pat2 = "W", val2 = 1) %>%
+  as.data.frame() %>%
+  mutate(id = stringr::str_extract(rownames(.), "[^;]+")) %>%
+  select(id, everything())
+
+#### DAY286 biofilm EV proteins ####
+# filter for proteins quantified in min 4/5 reps of biofilm EV or WCL
+# then convert to a data.frame and extract protein acessions from row names
+biofilm_filt2 <- filter_na2(biofilm_lfq, logic = "or", op = "<=",
+                           pat1 = "EV", val1 = 1,
+                           pat2 = "W", val2 = 1) %>%
+  as.data.frame() %>%
+  mutate(id = stringr::str_extract(rownames(.), "[^;]+")) %>%
+  select(id, everything())
+
+#### Combine yeast EV and biofilm EV data ####
+# Combine the yeast and biofilm datasets by matching Uniprot accessions
+# Remove the WCL columns
+# Filter for proteins with at least 1 valid LFQ value
+# Convert to numeric matrix
+ev_comb <- full_join(yeast_filt3, biofilm_filt2, by = "id") %>%
+  select(id, contains("EV")) %>%
+  tibble::column_to_rownames(var = "id") %>%
+  filter_na(op = "<=", pat = "EV", val = 7) %>%
+  as.matrix()
+
+# Rename the columns to something useful
+colnames(ev_comb) <- c("Y_EV1", "Y_EV2", "Y_EV3",
+                       "B_EV1", "B_EV2", "B_EV3", "B_EV4", "B_EV5")
+
+# Check the yeast EV and biofilm EV proteins match the counts in Figure 2A
+b_ev2 <- filter_na(ev_comb, op = "<=", pat = "B_EV", val = 4)
+y_ev2 <- filter_na(ev_comb, op = "<=", pat = "Y_EV", val = 2)
+
+# check_venn <- plot_venn(list("Y_EV" = y_ev, "B_EV" = b_ev),
+#                         use_uniprot = TRUE, type = "plot",
+#                         fontfamily = "sans",
+#                         cex = 0.8,
+#                         cat.fontfamily = "sans",
+#                         cat.just = list(c(0.5,1.7), c(0.5,1.5)),
+#                         margin = 0.05)
+
+# Import the yeast EV vs biofilm EV experimental design required for limma
+ev_exp <- read.table("supplementary_data/Y_EV_vs_B_EV_expdesign.txt",
+                     sep = "\t", header = TRUE, stringsAsFactors = FALSE)
+
+#### Data processing ####
+# Normalise log2 LFQ data
+ev_norm <- normalizeCyclicLoess(ev_comb)
+
+# Won't impute with so many missing values
+# Separate EV/WCL exclusive proteins (don't impute) from
+# EV/WCL common proteins (impute)
+ev_excl <- filter_na2(ev_norm, logic = "or", op = "==",
+                      pat1 = "Y_EV", val1 = 3,
+                      pat2 = "B_EV", val2 = 5)
+
+ev_both <- filter_na2(ev_norm, logic = "and", op = "<=",
+                      pat1 = "Y_EV", val1 = 2,
+                      pat2 = "B_EV", val2 = 4)
+
+# Use bpca method from pcaMethods for missing value imputation
+ev_imp <- pcaMethods::pca(ev_both, method = "bpca")
+ev_imp <- pcaMethods::completeObs(ev_imp)
+
+ev_de <- rbind(ev_excl, ev_imp)
+
+# see limma user guide section 9.2 for more info about DE
+# create design matrix
+ev_samp <- data.frame(T = c(rep("Y_EV", 3), rep("B_EV", 5)))
+
+ev_design <- stats::model.matrix(~ 0 + T, data = ev_samp)
+colnames(ev_design) <- c("B_EV", "Y_EV")
+
+# define sample comparisons of interest
+ev_contrasts <- c("Y_EV - B_EV")
+
+# make all pair-wise comparisons between EV and WCL
+# and perform limma::eBayes()
+ev_efit <- limma_eBayes(ev_de, design = ev_design, contrasts = ev_contrasts)
+
+# extract DE results
+# adj.p.val cutoff is 0.01, log2FC cutoff is 1
+ev_res <- get_results(efit = ev_efit,
+                      mat = ev_de,
+                      p_val = 0.01,
+                      lfc = 1,
+                      type = "individual")[[1]]
+
+## Construct figure S4 components
+# Fig S4A = compare DAY286 yeast EV and biofilm EV proteins via venn diagram
+fS4_a <- plot_venn(list("DAY286\nYeast EV" = y_ev2, 
+                             "DAY286\nBiofilm EV" = b_ev2),
+                        use_uniprot = TRUE, type = "plot",
+                        fontfamily = "sans",
+                        cex = 0.8,
+                        cat.fontfamily = "sans",
+                        cat.just = list(c(0.5,1.7), c(0.5,1.5)),
+                        margin = 0.05) %>% 
+  as_ggplot() + 
+  theme(plot.margin = unit(c(0,1.5,0,1.5), "cm"))
+
+# Fig S4B = compare compare enrichment of common proteins to DAYY286 yeast EVs
+# and DAY286 biofilm EVs via volcano plot
+fS4_b <- plot_volcano(data = ev_res, 
+                        p_val = adj.P.Val, 
+                        log2fc = logFC,
+                        group = group, 
+                        use_labels = TRUE,
+                        label_fun = ifelse(logFC >= 5 | logFC <= -5, 
+                                           CGD_gene_name, ""), 
+                        point_size = 0.6, 
+                        label_size = 2, 
+                        x_lim = c(-8, 8), 
+                        y_lim = c(0, 8), 
+                        legend_params = c("left", 11, 8), 
+                        axis_params = c("black", 10)) + 
+  scale_colour_manual(labels = c("Yeast EV enriched", 
+                                 "Biofilm EV enriched", 
+                                 "Not significant"), 
+                      values = c("#0072B2", 
+                                 "#999999", 
+                                 "#D55E00"), 
+                      breaks = c("Y_EV up", "B_EV up", "not sig"), 
+                      name = element_blank()) + 
+  annotate("text", x = 5.5, y = 0.5, label = "bold('DAY286')", parse = TRUE) + 
+  annotate("text", x = 3.5, y = 7, label = "bold('136')", 
+           parse = TRUE, colour = "#D55E00") + 
+  annotate("text", x = -3.5, y = 7, label = "bold('129')", parse = TRUE, 
+           colour = "#0072B2") + 
+  annotate("text", x = 0, y = 6, label = "bold('168')", parse = TRUE, 
+           colour = "#999999") + 
+  theme(legend.position = "right")
+
+# arguments for figure S4 export
+fS4_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
+                postscript = list(bg = "white", fonts = "sans"))
+```
+
+```{r figureS4, fig.cap=fS4_cap, fig.height=6, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS4_args, dpi=600}
+fS4_cap <- c("\\textbf{MAIN} Sub.")
+
+# draw figure S4
+ggarrange(fS4_a, fS4_b, 
+          labels = c("A", "B"), 
+          ncol = 1, 
+          nrow = 2)
+```
+
+\newpage
+
+```{r figureS5Data}
+#### Fig S5A = DAY286 yeast EV enr and ex proteins GO enrichment ####
+# Copy protein names for pasting into FungiFun2 online GO enrichment tool
+# FungiFun2 parameters:
+# 1. Strain = Candida albicans (strain SC5314/ATCC MYA-2876)
+# 2. Classification ontology = GO
+# 3. Input IDs = paste protein names here
+# 4. Advanced options = default except significance level = 0.01
+
+# Yeast EV exclusive proteins
+# Write to clipboard, paste into FungiFun2, and submit
+yev_ex <- ev_res %>%
+  filter(group == "Y_EV ex") %>%
+  pull(CGD_gene_name)
+
+# Yeast EV enriched proteins
+# Write to clipboard, paste into FungiFun2, and submit
+yev_up <- ev_res %>%
+  filter(group == "Y_EV up") %>%
+  pull(CGD_gene_name) %>%
+  stringi::stri_replace_all_regex(.,
+                                  c("MDH1"),
+                                  c("CaO19.7481"),
+                                  vectorize_all = FALSE)
+
+# Import FungiFun2 functional (GO) enrichment results
+
+# Yeast EV exclusive and enriched proteins
+yev_go <- process_fungifun("supplementary_data/GO_supplementary/yev_ex_up.csv") %>%
+  mutate(Prot.found = stringi::stri_replace_all_regex(.$Prot.found,
+                                                      c("CaO19.7481"),
+                                                      c("MDH1"),
+                                                      vectorize_all = FALSE))
+
+# define the colour palette
+fS5_pal <- c("#6D2077", "#E4002B", "#FFB81C")
+
+# define figure S5A
+fs5_a <- plot_go_bar(yev_go, c(1:10, 17:26, 31:40), fS5_pal) + 
+  facet_grid(rows = vars(GO.type), scales = "free") + 
+  theme(legend.position = "none")
+
+#### Fig S5B = DAY286 biofilm EV enr and ex proteins GO enrichment ####
+# Copy protein names for pasting into FungiFun2 online GO enrichment tool
+# FungiFun2 parameters:
+# 1. Strain = Candida albicans (strain SC5314/ATCC MYA-2876)
+# 2. Classification ontology = GO
+# 3. Input IDs = paste protein names here
+# 4. Advanced options = default except significance level = 0.01
+
+# Biofilm EV exclusive proteins
+# Write to clipboard, paste into FungiFun2, and submit
+bev_ex <- ev_res %>%
+  filter(group == "B_EV ex") %>%
+  pull(CGD_gene_name) %>%
+  stringi::stri_replace_all_regex(.,
+                                  c("ALS3", "ARO2", "HOM3",
+                                    "OSM1", "PLB3", "FBP1",
+                                    "PST2", "STE23"),
+                                  c("CaO19.1816", "CaO19.1986", "CaO19.1235",
+                                    "CaO19.6882", "CaO19.6594", "CaO19.6178",
+                                    "CaO19.3612", "CaO19.5561"),
+                                  vectorize_all = FALSE)
+
+# Biofilm EV enriched proteins
+# Write to clipboard, paste into FungiFun2, and submit
+bev_up <- ev_res %>%
+  filter(group == "B_EV up") %>%
+  pull(CGD_gene_name) %>%
+  stringi::stri_replace_all_regex(.,
+                                  c("PEP1"),
+                                  c("CaO19.3767"),
+                                  vectorize_all = FALSE)
+
+# Import FungiFun2 functional (GO) enrichment results
+
+# Biofilm EV exclusive and enriched proteins
+bev_go <- process_fungifun("supplementary_data/GO_supplementary/bev_ex_up.csv") %>%
+  mutate(Prot.found = stringi::stri_replace_all_regex(.$Prot.found,
+                                                      c("CaO19.1816", "CaO19.1986", "CaO19.1235",
+                                                        "CaO19.6882", "CaO19.6594", "CaO19.6178",
+                                                        "CaO19.3612", "CaO19.5561", "CaO19.3767"),
+                                                      c("ALS3", "ARO2", "HOM3",
+                                                        "OSM1", "PLB3", "FBP1",
+                                                        "PST2", "STE23", "PEP1"),
+                                                      vectorize_all = FALSE))
+
+# define figure S5B
+fs5_b <- plot_go_bar(bev_go, c(1:10, 35:44, 54:63), fS5_pal) + 
+  facet_grid(rows = vars(GO.type), scales = "free") + 
+  theme(legend.position = "none")
+
+# arguments for figure S5 export
+fS5_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
+                postscript = list(bg = "white", fonts = "sans"))
+```
+
+```{r figureS5, fig.cap=fS5_cap, fig.height=7, fig.width=7, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS5_args, dpi=600}
+fS5_cap <- c("\\textbf{MAIN} Sub.")
+
+# draw figure S5
+ggarrange(fs5_a, fs5_b, 
+          labels = c("A\nYeast EV", 
+                     "B\nBiofilm EV"), 
+          ncol = 1, 
+          nrow = 2, 
+          align = "hv")
+```
+
+\newpage
+
 # References

### 2020-01-09 inst/manuscript/supplementary_data/sdata_S6_S7.R

@@ -83,7 +83,7 @@ check_venn <- plot_venn(list("Y_EV" = y_ev, "B_EV" = b_ev),
                         margin = 0.05)
 
 # Import the yeast EV vs biofilm EV experimental design required for limma
-ev_exp <- read.table("inst/manuscript/supplementary_data/yEV_vs_bEV_expdesign",
+ev_exp <- read.table("inst/manuscript/supplementary_data/Y_EV_vs_B_EV_expdesign",
                      sep = "\t", header = TRUE, stringsAsFactors = FALSE)
 
 #### Data processing ####
@@ -192,18 +192,75 @@ yev_ex <- ev_res %>%
 # Write to clipboard, paste into FungiFun2, and submit
 yev_up <- ev_res %>%
   filter(group == "Y_EV up") %>%
-  pull(CGD_gene_name)
+  pull(CGD_gene_name) %>%
+  stringi::stri_replace_all_regex(.,
+                                  c("MDH1"),
+                                  c("CaO19.7481"),
+                                  vectorize_all = FALSE)
 
 # Biofilm EV exclusive proteins
 # Write to clipboard, paste into FungiFun2, and submit
 bev_ex <- ev_res %>%
   filter(group == "B_EV ex") %>%
-  pull(CGD_gene_name)
+  pull(CGD_gene_name) %>%
+  stringi::stri_replace_all_regex(.,
+                                  c("ALS3", "ARO2", "HOM3",
+                                    "OSM1", "PLB3", "FBP1",
+                                    "PST2", "STE23"),
+                                  c("CaO19.1816", "CaO19.1986", "CaO19.1235",
+                                    "CaO19.6882", "CaO19.6594", "CaO19.6178",
+                                    "CaO19.3612", "CaO19.5561"),
+                                  vectorize_all = FALSE)
 
 # Biofilm EV enriched proteins
 # Write to clipboard, paste into FungiFun2, and submit
 bev_up <- ev_res %>%
   filter(group == "B_EV up") %>%
-  pull(CGD_gene_name)
+  pull(CGD_gene_name) %>%
+  stringi::stri_replace_all_regex(.,
+                                  c("PEP1"),
+                                  c("CaO19.3767"),
+                                  vectorize_all = FALSE)
+
+# Define function to rename FungiFun2 columns
+rnm_cols <- function(df) {
+  df <- df %>%
+    rename("GO ID" = GO.ID,
+           "GO term" = GO.term,
[…]

### 2020-01-12 inst/manuscript/candidaev_figures.Rmd
Finish responses to reviewer comments
Add Supplementary Data S8.

Modify Figure 5. Fix typo in Supplementary Figure S1.

Add headings to Supplementary Data S6 S7 and S8

@@
 f3_y_go_table <- process_fungifun("figures/f3_GO_DAY_Y.csv")
+f3_y_go_table[43,2] <- "d-p-m-protein mannosyltransferase activity"
 f3_b_go_table <- process_fungifun("figures/f3_GO_DAY_B.csv")
@@
 # GO term bar plots
-f3_y <- plot_go_bar(f3_y_go_table, c(1:4,6, 23,26:28,30, 42,44:46), f3_pal) + 
-  annotate("text", x = 14, y = 65, label = "bold('DAY286 Y')", parse = TRUE) + 
-  labs(fill = "GO domain") + 
-  theme(legend.text = element_text(size = 10), 
-        legend.title = element_text(size = 10))
-
-f3_b <- plot_go_bar(f3_b_go_table, c(1:4,6, 54:57,67, 73,75,77,87), f3_pal) + 
-  annotate("text", x = 14, y = 60, label = "bold('DAY286 B')", parse = TRUE)
-
-f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:5, 12,14,17,18,24, 26:29), f3_pal) + 
-  annotate("text", x = 14, y = 70, label = "bold('ATCC90028')", parse = TRUE)
-
-f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4,6, 31,33:35,45, 49:52), f3_pal) + 
-  annotate("text", x = 14, y = 70, label = "bold('ATCC10231')", parse = TRUE)
+f3_y <- plot_go_bar(f3_y_go_table, c(1:8, 23:30, 42:49), f3_pal) +
+  theme(legend.position = "none") + 
+  facet_grid(rows = vars(GO.type), scales = "free")
+
+f3_b <- plot_go_bar(f3_b_go_table, c(1:8, 53:60, 73:80), f3_pal) +
+  theme(legend.position = "none") + 
+  facet_grid(rows = vars(GO.type), scales = "free")
+
+f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:8, 12:19, 26:29), f3_pal) +
+  theme(legend.position = "none") + 
+  facet_grid(rows = vars(GO.type), scales = "free")
+
+f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:8, 31:38, 48:55), f3_pal) +
+  theme(legend.position = "none") + 
+  facet_grid(rows = vars(GO.type), scales = "free")
 
@@
 
-```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'),  dev.args=f3_args, dpi=600}
+```{r figure3, fig.width=7.2, fig.height=7, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'),  dev.args=f3_args, dpi=600}
 # draw figure 3
@@
           f3_a1, f3_b, 
-          labels = NULL, 
+          labels = c("A", "B", "C", "D"), 
           ncol = 2, 
           nrow = 2, 
-          common.legend = TRUE, 
-          legend = "bottom", 
           align = "hv")

### 2020-01-12 inst/manuscript/candidaev_supplement.Rmd
Finish responses to reviewer comments
Add Supplementary Data S8.

Modify Figure 5. Fix typo in Supplementary Figure S1.

Add headings to Supplementary Data S6 S7 and S8

@@
 ```{r figureS3, fig.cap=fS3_cap, fig.height=7, fig.width=5.5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS3_args, dpi=600}
-fS3_cap <- c("\\textbf{MAIN} Sub.")
+fS3_cap <- c("\\textbf{Statistical comparisons of \\textit{C. albicans} EV 
+              isolations.} \\textit{(A)} Boxplot showing EV mode diameter 
+              measured using NTA. Differences in average EV mode diameters
+              were compared using One-way ANOVA followed by Tukey's HSD 
+              \\textit{post-hoc} test. Adjusted p-values indicating 
+              significant differences are shown. \\textit{(B)} Boxplot showing 
+              total particle concentration for each EV preparation as measured 
+              by NTA. Differences in average total particle concentration 
+              were compared by Kruskal-Wallis test followed by Dunn's Test.
+              Adjusted p-values indicating significant differences are shown.")
 
@@
   as_ggplot() + 
-  theme(plot.margin = unit(c(0,1.5,0,1.5), "cm"))
+  theme(plot.margin = unit(c(0,2,0,2), "cm"))
 
@@
 
+(ref:limma) [@cox2014; @ritchie2015]
+
 ```{r figureS4, fig.cap=fS4_cap, fig.height=6, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS4_args, dpi=600}
-fS4_cap <- c("\\textbf{MAIN} Sub.")
+fS4_cap <- c("\\textbf{Differential abundance analysis of proteins identified 
+              in EVs isolated from two different morphologies of the DAY286 
+              \\textit{C. albicans} strain.} \\textit{(A)} Venn diagram 
+              comparing the biofilm EV and yeast EV proteome data sets shown 
+              in Figure 2A. \\textit{(B)} Volcano plot depicting significantly 
+              enriched biofilm EV or yeast EV proteins. Differential abundance 
+              analysis was performed by comparing the mean normalised LFQ
+              intensities of common DAY286 EV proteins (i.e. proteins in the 
+              Venn overlap) using the package \\textit{limma} (ref:limma). 
+              Significantly enriched proteins were identified using a 
+              Benjamini-Hochberg adjusted p-value cut-off of 0.01 and a 
+              log\\textsubscript{2}(FC) cut-off of 1. Counts of significant and 
+              non-significant proeins are indicated. Proteins with a
+              log\\textsubscript{2}(FC) greater than 5 or less than -5 are 
+              labelled. Data underlying this plot are provided in 
+              Supplementary Data S6.")
 
@@
 
-```{r figureS5, fig.cap=fS5_cap, fig.height=7, fig.width=7, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS5_args, dpi=600}
-fS5_cap <- c("\\textbf{MAIN} Sub.")
+(ref:fungifun) [@priebe2015]
+
+```{r figureS5, fig.cap=fS5_cap, fig.height=7, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS5_args, dpi=600}
+fS5_cap <- c("\\textbf{Functional enrichment analyses of EVs from two DAY286 
+              morphologies.} Top 10 signficantly enriched biological process 
+              (BP), cellular component (CC), and molecular function (MF) GO 
+              terms for the \\textit{(A)} yeast EV enriched and exclusive proteins or
+              \\textit{(B)} biofilm EV enriched or exclusive proteins shown in 
+              Supplementary Figure S4. GO analyses were performed using 
+              the online tool FungiFun2 (elbe.hki-jena.de/fungifun) 
+              (Hypergeometric distribution, Benjamini-Hochberg adjusted 
+              p-value < 0.01)
+              (ref:fungifun). The GO terms are presented top to bottom in order 
+              of increasing adjusted p-value. Full lists of enriched GO terms
+              can be found in Supplementary Data S7.")
 

### 2020-01-12 inst/manuscript/supplementary_data/sdata_S6_S7.R

@@ -83,7 +83,7 @@ check_venn <- plot_venn(list("Y_EV" = y_ev, "B_EV" = b_ev),
                         margin = 0.05)
 
 # Import the yeast EV vs biofilm EV experimental design required for limma
-ev_exp <- read.table("inst/manuscript/supplementary_data/Y_EV_vs_B_EV_expdesign",
+ev_exp <- read.table("inst/manuscript/supplementary_data/Y_EV_vs_B_EV_expdesign.txt",
                      sep = "\t", header = TRUE, stringsAsFactors = FALSE)
 
 #### Data processing ####
@@ -133,8 +133,8 @@ ev_res <- get_results(efit = ev_efit,
 
 
 s6 <- ev_res %>%
-  mutate(group = case_when(group == "EV up" ~ "EV sig",
-                           group == "WCL up" ~ "WCL sig",
+  mutate(group = case_when(group == "Y_EV up" ~ "Y_EV sig",
+                           group == "B_EV up" ~ "B_EV sig",
                            TRUE ~ as.character(group)),
          CGDID = match_id(UP_accession, uniprot,
                           "UP_accession", "CGDID"),
@@ -260,7 +260,7 @@ bev_go <- process_fungifun("inst/manuscript/supplementary_data/GO_supplementary/
                                                       vectorize_all = FALSE))
   rnm_cols()
 
-sheets <- list("Fig S5 DAY286 yeast" = yev_go,
-                  "Fig S6 DAY286 biofilm" = bev_go)
+sheets <- list("Fig S5A DAY286 yeast" = yev_go,
+                  "Fig S5B DAY286 biofilm" = bev_go)
 writexl::write_xlsx(sheets,
                     "inst/manuscript/supplementary_data/supplementary_data_S7.xlsx")

### 2020-01-12 inst/manuscript/supplementary_data/sdata_S8.R

@@ -1,0 +1,69 @@
+#### Setup ####
+# need writexl package to write output to .xlsx
+requireNamespace("writexl", quietly = TRUE)
+
+# load packages
+library(dplyr)
+library(candidaev)
+
+# define column rename function
+rnm_cols <- function(df) {
+  df <- df %>%
+    rename("Accession" = UP_accession,
+           "CGDID" = CGDID,
+           "Gene name" = UP_gene_name,
+           "CGD Gene name" = CGD_gene_name,
+           "CGD Feature name" = CGD_feature_name,
+           "CGD systematic name" = CGD_systematic_name,
+           "Protein name" = Protein_name,
+           "CGD description" = CGD_description,
+           "Function" = Function,
+           "Location" = Subcellular_location,
+           "Mass (kDa)" = "Mass_(kDa)",
+           "Length (aa)" = "Length_(aa)",
+           "Sequence" = Sequence,
+           "TM domain" = Transmembrane,
+           "Topology" = Topology,
+           "Signal peptide" = Signal_peptide,
+           "GO all" = "GO_all",
+           "GO CC" = GO_CC,
+           "GO MF" = GO_MF,
+           "GO BP" = GO_BP,
+           "GO IDs" = GO_IDs,
+           "UP status" = UP_status)
+}
+
+#### Supplementary Data S8 ####
+# Table of 22 C. albicans EV marker candidates
+# Metadata for these proteins
+
+marker_22 <- c("ARF3",
+               "CDC42",
+               "FAA4",
+               "FET34",
+               "MTS1",
+               "NCE102",
+               "orf19.6741",
+               "RAC1",
+               "RHO1",
+               "RHO3",
+               "SSO2",
+               "SUR7",
+               "YCK2",
+               "GPD2",
+               "PHR1",
+               "orf19.1054",
+               "orf19.2168.3",
+               "orf19.3799",
+               "SEC4",
+               "YKT6",
+               "YPT31",
+               "VAC8")
+
+metadata <- candidaev::uniprot %>%
+  filter(CGD_gene_name %in% marker_22) %>%
+  rnm_cols
+
+sheets <- list("22 markers" = metadata)
+writexl::write_xlsx(sheets,
+                    "inst/manuscript/supplementary_data/supplementary_data_S8.xlsx")

### 2020-01-21 inst/manuscript/candidaev_figures.Rmd
Finalise manuscript for resubmission

@@
    **Protein markers for *Candida albicans* EVs include claudin-like Sur7 
-   family proteins and GTPases**
+   family proteins**
 author: | 
@@
      Pierre Faou^b^,
-   | Marilyn Anderson^a^, Mark Bleackley^a^
+   | Mark Bleackley^a^, Marilyn Anderson^a^
 date: | 
@@
 
-**Corresponding author:** Mark Bleackley, m.bleackley@latrobe.edu.au
+**Corresponding author:** Marilyn Anderson, m.anderson@latrobe.edu.au
 

### 2020-01-21 inst/manuscript/candidaev_supplement.Rmd
Finalise manuscript for resubmission

@@
    **Supplement to: Protein markers for *Candida albicans* EVs include
-   claudin-like Sur7 family proteins and GTPases**
+   claudin-like Sur7 family proteins**
 author: | 

### 2020-01-21 README.Rmd
Update manuscript title in README

@@
 
-> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
-Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
-claudin-like Sur7 family proteins and GTPases. _Journal of Extracellular_ 
+> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Bleackley, M. R., 
+Anderson, M. A. (2019) Protein markers for _Candida albicans_ EVs include 
+claudin-like Sur7 family proteins. _Journal of Extracellular_ 
 _Vesicles_, submitted.
@@
 
-> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Anderson, M. A., 
-Bleackley, M. R. (2019) Research compendium for "Protein markers for 
-_Candida albicans_ EVs include claudin-like Sur7 family proteins and GTPases". 
+> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Bleackley, M. R., 
+Anderson, M. A. (2019) Research compendium for "Protein markers for 
+_Candida albicans_ EVs include claudin-like Sur7 family proteins". 
 version x.x.x. Zenodo. URL.

### 2020-03-24 README.Rmd
Update root README

@@
 
-![GitHub last commit](https://img.shields.io/github/last-commit/csdaw/candidaev.svg?style=popout)
-
 This repository contains the research compendium for our paper:
@@
 > Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Bleackley, M. R., 
-Anderson, M. A. (2019) Protein markers for _Candida albicans_ EVs include 
+Anderson, M. A. (2020) Protein markers for _Candida albicans_ EVs include 
 claudin-like Sur7 family proteins. _Journal of Extracellular_ 
@@
 > Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Bleackley, M. R., 
-Anderson, M. A. (2019) Research compendium for "Protein markers for 
+Anderson, M. A. (2020) Research compendium for "Protein markers for 
 _Candida albicans_ EVs include claudin-like Sur7 family proteins". 

### 2020-03-24 inst/manuscript/candidaev_figures.Rmd
Update affiliation in figures pdf

@@
 author: | 
-   | Charlotte Dawson^a^, Donovan Garcia Ceron^a^, Harinda Rajapaksha^b^, 
+   | Charlotte Dawson^ac^, Donovan Garcia Ceron^a^, Harinda Rajapaksha^b^, 
      Pierre Faou^b^,
@@
      3086, Victoria, Australia*
+   | *^c^Cambridge Centre for Proteomics, Milner Therapeutics Institute, 
+     Jeffrey Cheah Biomedical Centre, University of Cambridge, 
+     Puddicombe Way, Cambridge CB2 0AW, United Kingdom*
 output: 
@@
                                  "Not significant"), 
-                      values = unname(ev_pal[c(2,1,3)]), 
+                      values = unname(ev_pal[c(2,3,1)]), 
                       breaks = c("EV up", "WCL up", "not sig"), 
@@
                                  "Not significant"), 
-                      values = unname(ev_pal[c(2,1,3)]), 
+                      values = unname(ev_pal[c(2,3,1)]), 
                       breaks = c("EV up", "WCL up", "not sig")) + 

### 2020-03-24 inst/manuscript/candidaev_supplement.Rmd
Update affiliation in supplementary
Also, fix typo in Table S2.

@@
             shape = 15, 
-            ylab = "Total particle concentration / mL") + 
+            ylab = "Total particle concentration / mL", 
+            outlier.shape = NA) + 
   scale_y_continuous(expand = c(0, 0), 
@@
                                  "Not significant"), 
-                      values = c("#0072B2", 
-                                 "#999999", 
-                                 "#D55E00"), 
+                      values = c("#D55E00", 
+                                 "#0072B2", 
+                                 "#999999"), 
                       breaks = c("Y_EV up", "B_EV up", "not sig"), 

### 2020-03-30 inst/manuscript/tables/table_1.tex
Make docx files for tables

\begingroup\fontsize{8}{10}\selectfont

\begin{ThreePartTable}
\begin{TableNotes}
\item[a] Protein localisation was inferred from sequence 
                         similarity with \textit{S. cerevisiae} homolog as 
                         annotated in the Candida Genome Database (48, 49).
\item[b] Protein localisation was obtained from the GO Cellular
                        Component annotation in the \textit{C. albicans} 
                        UniProt reference proteome UP000000559 (58).
\item[c] Presence of transmembrane domains and absence of a 
                        signal peptide was predicted using TOPCONS2 (59).
\item[d] The name Evp1 for the protein encoded by orf19.6741 
                        was proposed in the present study.
\end{TableNotes}
\begin{longtable}[t]{lllllllll}
\caption{\label{tab:}\textbf{Candidate positive protein markers for 
             \textit{C. albicans} EVs.} This list of proteins consists of 
             those that were found to be exclusive to EVs or significantly 
             enriched in EVs across the four \textit{C. albicans} strains 
             examined in this study. Proteins are grouped according to their 
             subcellular localisation as annotated in the Candida Genome 
             Database (candidagenome.org) (ref:footnote1) unless otherwise 
             indicated. The log\textsubscript{2} ratio of the abundance 
             (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
             whole cell lysate (WCL) for each strain is listed. ``ex" 
             indicates where a protein was only quantified in the EV fraction 
             and not the WCL for that strain. The ``TM" column indicates the 
             number of transmembrane domains for each protein as annotated in 
             UniProt. ``SP" indicates whether a protein is annotated as 
             having a signal peptide according to UniProt. ``VDM" shows 
             whether a protein has previously been detected in vesicle-depleted 
             culture media (i.e. the proteins may also be in the soluble secretome) 
             (31). Underlined proteins are those identified as the 
             best candidates for positive EV markers according to the 
             criteria depicted in Supplementary Figure S1.}\\
\toprule
\multicolumn{2}{c}{ } & \multicolumn{4}{c}{log\textsubscript{2}(fold change) EV vs WCL} & \multicolumn{2}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){3-6}
Name & Function & DAY Y & A9 & A1 & DAY B & TM & SP & VDM\\
\midrule
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Plasma membrane}}\\
\hspace{1em}\underline{ARF3} & \underline{Arf family GTPase<sup>a</sup>} & \underline{ex} & \underline{1.69} & \underline{ex} & \underline{3.45} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}\underline{CDC42} & \underline{Rho family GTPase} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}CDR1;CDR2 & Multidrug transporter of ABC superfamily & ex & ex & ex & 11.19 & 12;12 &  & \\
\hspace{1em}CHS3 & Major chitin synthase of yeast and hyphae & ex & 4.12 & ex & ex & 5 &  & \\
\hspace{1em}ENA21 & Predicted P-type ATPase sodium pump<sup>a</sup> & ex & ex & ex & ex & 9 &  & \\
\hspace{1em}\underline{FAA4} & \underline{Long-chain fatty acid-CoA ligase<sup>a</sup>} & \underline{2.89} & \underline{2.24} & \underline{2.28} & \underline{1.45} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}\underline{FET34} & \underline{Multicopper feroxidase} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{6.18} & \underline{1} & \underline{Y} & \underline{}\\
\hspace{1em}GAP4 & High-affinity S-adenosylmethionine permease & ex & ex & ex & 4.28 & 12 &  & \\
\hspace{1em}GSC1 & 1,3-beta-glucan synthase & 2.57 & 3.45 & 5.97 & 8.01 & 15 &  & \\
\hspace{1em}HGT1 & High-affinity MFS glucose transporter & ex & ex & ex & ex & 12 &  & \\
\hspace{1em}HGT6 & Putative high-affinity MFS glucose transporter & 4.04 & 4.78 & 6.53 & 5.68 & 11 &  & \\
\hspace{1em}HGT7 & Putative MFS glucose transporter & ex & 5.95 & ex & ex & 11 &  & \\
\hspace{1em}\underline{MTS1} & \underline{Sphingolipid C9-methyltransferase} & \underline{2.20} & \underline{1.86} & \underline{1.41} & \underline{2.13} & \underline{2} & \underline{} & \underline{}\\
\hspace{1em}\underline{NCE102} & \underline{Non-classical protein export protein} & \underline{3.34} & \underline{2.20} & \underline{ex} & \underline{5.32} & \underline{4} & \underline{} & \underline{}\\
\hspace{1em}\underline{EVP1<sup>d</sup>} & \underline{\textit{S. cerevisiae} ortholog is Pun1, plasma membrane protein<sup>a</sup>} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{3} & \underline{} & \underline{Y}\\
\hspace{1em}PHM7 & Putative ion transporter & ex & ex & ex & ex & 11 &  & \\
\hspace{1em}PMA1 & Plasma membrane ATPase & 5.65 & 4.38 & 5.60 & 6.46 & 8 &  & \\
\hspace{1em}\underline{RAC1} & \underline{G-protein of RAC subfamily} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{3.92} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}\underline{RHO1} & \underline{Rho family GTPase} & \underline{2.81} & \underline{3.68} & \underline{3.74} & \underline{4.03} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}\underline{RHO3} & \underline{Rho family GTPase} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}\underline{SSO2} & \underline{Plasma membrane t-SNARE<sup>a</sup>} & \underline{ex} & \underline{1.88} & \underline{3.57} & \underline{ex} & \underline{1} & \underline{} & \underline{}\\
\hspace{1em}\underline{SUR7} & \underline{Protein required for normal cell wall, plasma membrane<sup>c</sup>} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{7.04} & \underline{4} & \underline{} & \underline{}\\
\hspace{1em}\underline{YCK2} & \underline{\textit{S. cerevisiae} ortholog is Yck2, casein kinase} & \underline{ex} & \underline{4.42} & \underline{ex} & \underline{ex} & \underline{} & \underline{} & \underline{}\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Cell wall, cell surface}}\\
\hspace{1em}BGL2 & 1,3-beta-glucanosyltransferase & 7.26 & 9.44 & 11.08 & ex &  & Y & Y\\
\hspace{1em}CRH11 & GPI-anchored cell wall transglycosylase & ex & ex & ex & ex &  & Y & Y\\
\hspace{1em}ECM33 & GPI-anchored cell wall protein & 4.39 & 5.28 & 8.31 & 7.03 &  & Y & Y\\
\hspace{1em}\underline{GPD2} & \underline{Glycerol-3-phosphate dehydrogenase} & \underline{ex} & \underline{3.48} & \underline{2.39} & \underline{1.30} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}MP65 & Cell surface mannoprotein & ex & ex & ex & ex &  & Y & Y\\
\hspace{1em}MSB2 & Mucin family adhesin-like protein & ex & ex & ex & ex & 1 & Y & Y\\
\hspace{1em}PGA4 & 1,3-beta-glucanosyltransferase & ex & ex & ex & ex &  & Y & Y\\
\hspace{1em}PGA52 & GPI-anchored cell surface protein of unknown function & ex & ex & ex & ex &  & Y & Y\\
\hspace{1em}\underline{PHR1} & \underline{Cell surface glycosidase} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{5.65} & \underline{} & \underline{Y} & \underline{}\\
\hspace{1em}PHR2 & Glycosidase & ex & 3.51 & 6.44 & ex &  & Y & Y\\
\hspace{1em}PLB4.5 & Phospholipase B & ex & ex & ex & ex &  & Y & Y\\
\hspace{1em}SAP9 & Secreted aspartyl protease & ex & ex & ex & ex & 1 & Y & Y\\
\hspace{1em}YWP1 & Secreted yeast cell wall protein & 2.37 & 3.51 & 6.17 & ex &  & Y & Y\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Endoplasmic reticulum}}\\
\hspace{1em}ERO1 & ER oxidoreductin & ex & ex & 2.32 & 1.68 &  & Y & Y\\
\hspace{1em}\underline{orf19.1054} & \underline{\textit{S. cerevisiae} ortholog is Pom33, transmembrane nucleoporin<sup>b</sup>} & \underline{5.66} & \underline{ex} & \underline{ex} & \underline{2.51} & \underline{4} & \underline{} & \underline{}\\
\hspace{1em}\underline{orf19.2168.3} & \underline{\textit{S. cerevisiae} ortholog is Yop1, reticulon-interacting protein<sup>a</sup>} & \underline{4.77} & \underline{1.98} & \underline{2.29} & \underline{1.81} & \underline{4} & \underline{} & \underline{}\\
\hspace{1em}\underline{orf19.3799} & \underline{\textit{S. cerevisiae} ortholog is Rtn1, reticulon protein<sup>b</sup>} & \underline{2.24} & \underline{1.40} & \underline{3.00} & \underline{1.29} & \underline{2} & \underline{} & \underline{}\\
\hspace{1em}SEC61 & ER protein-translocation complex subunit & 2.53 & 2.16 & 2.10 & 1.46 & 8 &  & \\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Endosome, Golgi, transport vesicle}}\\
\hspace{1em}\underline{SEC4} & \underline{Rab family GTPase<sup>a</sup>} & \underline{1.88} & \underline{1.20} & \underline{1.86} & \underline{2.90} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}\underline{YKT6} & \underline{Palmitoyltransferase, putative vacuolar SNARE complex protein<sup>a</sup>} & \underline{ex} & \underline{4.01} & \underline{5.46} & \underline{3.20} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}\underline{YPT31} & \underline{Rab family GTPase<sup>a</sup>} & \underline{ex} & \underline{1.57} & \underline{1.33} & \underline{3.33} & \underline{} & \underline{} & \underline{}\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Vacuole}}\\
\hspace{1em}\underline{VAC8} & \underline{Protein involved in vacuolar inheritance<sup>a</sup>} & \underline{2.79} & \underline{ex} & \underline{ex} & \underline{3.83} & \underline{} & \underline{} & \underline{}\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Mitochondrion}}\\
\hspace{1em}MIR1 & Putative mitochondrial phosphate transporter<sup>a</sup> & 3.68 & 4.38 & 4.24 & 1.60 &  &  & \\
\hspace{1em}POR1 & Mitochondrial outer membrane porin<sup>a</sup> & 3.44 & 2.51 & 3.69 & 1.38 &  &  & \\
\bottomrule
\insertTableNotes
\end{longtable}
\end{ThreePartTable}
\endgroup{}

### 2020-03-30 inst/manuscript/tables/table_S2.tex
Make docx files for tables

\begingroup\fontsize{8}{10}\selectfont

\begin{ThreePartTable}
\begin{TableNotes}
\item[a] Protein localisation was inferred from sequence 
                         similarity with \textit{S. cerevisiae} homolog as 
                         annotated in the Candida Genome Database 
                         (ref:footnote1)
\item[b] Protein localisation was obtained from the GO Cellular
                        Component annotation in the \textit{C. albicans} 
                        UniProt reference proteome UP000000559 (ref:footnote2).
\item[c] Protein and has no Cellular Component annotation in 
                         the Candida Genome Database or UniProt reference 
                        proteome.
\end{TableNotes}
\begin{longtable}[t]{lllllllll}
\caption{\label{tab:}\textbf{Candidate negative protein markers for 
              \textit{C. albicans} EVs.} This list of proteins consists of 
              those that were found to be exclusive to whole cell lysate (WCL) 
              or significantly enriched in WCL across the four 
              \textit{C. albicans} strains examined in this study. Proteins 
              are grouped according to their 
              subcellular localisation as annotated in the Candida Genome 
              Database (candidagenome.org) (ref:footnote1) unless otherwise 
              indicated. The log\textsubscript{2} ratio of the abundance 
              (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
              WCL for each strain is listed. A negative value indicates that a 
              protein was enriched in WCL compared to EV. ``ex" indicates 
              where a protein was only quantified in the WCL fraction and not 
              in EVs for that strain. The ``TM" column indicates the number 
              of transmembrane domains for each protein as annotated in 
              UniProtKB. ``SP" indicates whether a protein is annotated as 
              having a signal peptide according to UniProt. ``VDM" shows 
              whether a protein has previously been detected in 
              vesicle-depleted culture media (i.e. the proteins may also be in 
              the soluble secretome) (ref:table1). Underlined proteins are 
              those identified as the best candidates for negative
              EV markers according to the criteria depicted in 
              Supplementary Figure S1.}\\
\toprule
\multicolumn{2}{c}{ } & \multicolumn{4}{c}{log\textsubscript{2}(fold change) EV vs WCL} & \multicolumn{3}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){3-6}
Name & Function & DAY Y & A9 & A1 & DAY B & TM & SP & VDM\\
\midrule
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Cytoplasm}}\\
\hspace{1em}ARO3 & Phospho-2-dehydro-3-deoxyheptonate aldolase<sup>b</sup> & -1.28 & -2.55 & -1.51 & -1.46 &  &  & \\
\hspace{1em}ARO8 & Aromatic transaminase of the Ehrlich fusel oil pathway<sup>a</sup> & -2.37 & -1.81 & ex & -2.36 &  &  & \\
\hspace{1em}GDB1 & Putative glycogen debranching enzyme & ex & ex & ex & -1.99 &  &  & \\
\hspace{1em}HOM2 & Aspartate-semialdehyde dehydrogenase<sup>b</sup> & ex & -3.41 & ex & ex &  &  & \\
\hspace{1em}orf19.1889 & Putative phosphoglycerate mutase family protein<sup>b</sup> & ex & -1.60 & ex & ex &  &  & \\
\hspace{1em}orf19.5943.1 & \textit{S. cerevisiae} ortholog is Stm1, regulates translation<sup>a</sup> & ex & -3.98 & -4.57 & ex &  &  & \\
\hspace{1em}orf19.6596 & Putative esterase<sup>a</sup> & ex & ex & ex & -2.90 &  &  & \\
\hspace{1em}orf19.7263 & Putative X-Pro aminopeptidase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}SBP1 & \textit{S. cerevisiae} ortholog is Sbp1, eIF4G binding protein<sup>a</sup> & ex & -4.30 & -3.80 & -2.15 &  &  & \\
\hspace{1em}STI1 & HSP90 co-chaperone<sup>a</sup> & ex & -2.20 & ex & ex &  &  & \\
\hspace{1em}URA4 & Predicted succinate semialdehyde dehydrogenase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}XKS1 & Putative xylulokinase<sup>b</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}YNK1 & Nucleoside disphosphate kinase & -3.07 & -2.57 & -2.17 & -1.40 &  &  & \\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Cytosol and mitochondria}}\\
\hspace{1em}ACH1 & Acetyl-CoA hydrolase<sup>b</sup> & -3.24 & -5.09 & -2.79 & -4.03 &  &  & \\
\hspace{1em}GLR1 & Glutathione reductase<sup>b</sup> & ex & ex & ex & -3.28 &  &  & \\
\hspace{1em}HSP60 & Heat shock protein 60<sup>b</sup> & -4.66 & -1.59 & -4.22 & -4.06 &  &  & \\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Mitochondria}}\\
\hspace{1em}AAT1 & Aspartate aminotransferase<sup>a</sup> & ex & -2.11 & -1.48 & -5.70 &  &  & \\
\hspace{1em}BAT22 & Putative branched chain amino acid aminotransferase<sup>b</sup> & ex & -3.57 & -1.44 & -3.12 &  &  & \\
\hspace{1em}ETR1 & Putative 2-enoyl thioester reductase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}GCV2 & Glycine decarboxylase P subunit<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}IDH1 & Isocitrate dehydrogenase subunit<sup>a</sup> & -2.67 & -2.48 & -1.85 & -2.22 &  &  & \\
\hspace{1em}IDH2 & Isocitrate dehydrogenase<sup>a</sup> & -3.21 & -2.88 & -3.54 & -3.37 &  &  & \\
\hspace{1em}IDP1 & Putative isocitrate dehydrogenase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}ILV5 & Ketol-acid reductoisomerase<sup>b</sup> & -3.68 & -2.62 & -2.27 & -5.48 &  &  & \\
\hspace{1em}KGD2 & Putative dihydrolipoamide S-succinyltransferase<sup>a</sup> & ex & -2.20 & -2.04 & ex &  &  & \\
\hspace{1em}\underline{LPD1} & \underline{Dihydrolipoamide dehydrogenase} & \underline{ex} & \underline{-7.49} & \underline{-4.08} & \underline{-7.91} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}NIF3 & \textit{S. cerevisiae} ortholog is Nif3, mitochondrial protein<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}orf19.2966 & Predicted dienelactone hydrolase domain<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}orf19.449 & Putative phosphatidyl synthase<sup>b</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}orf19.7215.3 & \textit{S. cerevisiae} ortholog is Hsp10, mitochondrial co-chaperonin<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}PDX3 & Pyridoxamine-phosphate oxidase<sup>a</sup> & ex & -1.85 & ex & ex &  &  & \\
\hspace{1em}\underline{SOD2} & \underline{Superoxide dismutase} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{} & \underline{} & \underline{}\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Nucleus}}\\
\hspace{1em}DOT5 & Thioredoxin peroxidase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}NHP6A & Non-histone chromosomal protein 6<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Vacuole}}\\
\hspace{1em}AMS1 & Putative alpha-mannosidase<sup>a</sup> & ex & ex & ex & -2.23 &  &  & \\
\hspace{1em}\underline{APR1} & \underline{Vacuolar aspartic proteinase} & \underline{-1.83} & \underline{ex} & \underline{ex} & \underline{-1.07} & \underline{} & \underline{Y} & \underline{}\\
\hspace{1em}\underline{CPY1} & \underline{Carboxypeptidase Y} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{-1.59} & \underline{} & \underline{Y} & \underline{}\\
\hspace{1em}\underline{LAP41} & \underline{Putative aminopeptidase yscI precursor} & \underline{ex} & \underline{-3.96} & \underline{-1.80} & \underline{-2.64} & \underline{} & \underline{} & \underline{}\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Cell wall, cell surface, fungal biofilm matrix}}\\
\hspace{1em}CPR3 & Putative peptidyl-prolyl cis-trans isomerase & ex & -2.59 & ex & ex &  &  & \\
\hspace{1em}GCY1 & Glycerol 2-dehydrogenase & ex & ex & ex & ex &  &  & \\
\hspace{1em}GLX3 & Glutathione-independent glyoxalase & ex & -6.21 & ex & -1.49 &  &  & \\
\hspace{1em}\underline{GPM1} & \underline{Phosphoglycerate mutase} & \underline{-6.84} & \underline{-4.93} & \underline{-3.80} & \underline{-2.78} & \underline{} & \underline{} & \underline{}\\
\hspace{1em}GRP2 & NAD(H)-linked methylglyoxal oxidoreductase & ex & -7.45 & -2.46 & -1.42 &  &  & \\
\hspace{1em}HSP21 & Small heat shock protein & ex & -4.97 & ex & -2.24 &  &  & \\
\hspace{1em}MET15 & O-acetylhomoserine O-acetylserine sulfhydrylase & ex & -2.91 & -2.00 & -2.72 &  &  & \\
\hspace{1em}orf19.3053 & Protein of unknown function & ex & -4.71 & -2.35 & -3.02 &  &  & \\
\hspace{1em}orf19.590 & Putative thiamine biosynthesis enzyme & ex & ex & ex & ex &  &  & \\
\hspace{1em}PGI1 & Glucose-6-phosphate isomerase & -6.91 & -5.44 & -4.14 & -1.68 &  &  & \\
\hspace{1em}PST2 & Flavodoxin-like protein & ex & ex & ex & -2.07 &  &  & \\
\hspace{1em}RIB3 & 3,4-Dihydroxy-2-butanone 4-phosphate synthase & ex & -1.06 & -1.23 & -2.11 &  &  & \\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Proteasome}}\\
\hspace{1em}orf19.2755 & \textit{S. cerevisiae} ortholog is Pre7, Beta 6 subunit of 20S proteasome<sup>a</sup> & ex & -2.34 & ex & ex &  &  & \\
\hspace{1em}orf19.4230 & 20S proteasome subunit (beta7)<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}PUP2 & Alpha5 subunit of the 20S proteasome & ex & -4.13 & -2.53 & ex &  &  & \\
\hspace{1em}SCL1 & Proteasome subunit YC7alpha<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Cytoplasmic stress granule}}\\
\hspace{1em}TIF11 & Translation initiation factor eIF1a<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}TMA19 & \textit{S. cerevisiae} ortholog is Tma19, ribosome associated protein<sup>a</sup> & ex & -3.05 & -2.74 & ex &  &  & \\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Peroxisome}}\\
\hspace{1em}orf19.1433 & \textit{S. cerevisiae} ortholog is Lpx1, peroxisomal lipase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Actin cortical patch}}\\
\hspace{1em}\underline{ABP1} & \underline{Actin-binding protein} & \underline{ex} & \underline{-1.47} & \underline{ex} & \underline{ex} & \underline{} & \underline{} & \underline{}\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Unknown}}\\
\hspace{1em}orf19.2125 & Protein of unknown function<sup>c</sup> & ex & ex & ex & ex & 1 &  & \\
\hspace{1em}orf19.2737 & Carbohydrate kinase domain-containing protein<sup>c</sup> & ex & ex & ex & -1.48 &  &  & \\
\hspace{1em}orf19.5620 & Stationary phase enriched protein<sup>c</sup> & ex & ex & ex & -3.43 &  &  & \\
\hspace{1em}OYE32 & NADPH oxidoreductase family protein<sup>c</sup> & ex & ex & ex & -2.90 &  &  & \\
\bottomrule
\insertTableNotes
\end{longtable}
\end{ThreePartTable}
\endgroup{}

### 2020-03-30 inst/manuscript/candidaev_supplement.Rmd
Fix minor typos in supplement

@@
            ATCC10231 yeast, and DAY286 biofilm. The results from the four 
-           seperate analyses were combined (step 7) to identify proteins which 
+           separate analyses were combined (step 7) to identify proteins which 
            commonly appeared as EV marker candidates. The MISEV2018 criteria 
@@
 
-# export table S2 LaTeX code with \\ line endings removed in a text file
-tabS1_clean <- gsub("\\\\\\\\\n", "\n", tabS1)
-
-cat(tabS1_clean, file = "tables/table_S1.txt", sep = "\n")
-
 # show table S1 in PDF output
@@
 
-# export table S2 LaTeX code with \\ line endings removed in a text file
-tabS2_clean <- gsub("\\\\\\\\\n", "\n", tabS2)
-
-cat(tabS2_clean, file = "tables/table_S2.txt", sep = "\n")
+# export table S2 LaTeX code (to be converted to docx with Pandoc)
+cat(tabS2, file = "tables/table_S2.tex", sep = "\n")
 
@@
               log\\textsubscript{2}(FC) cut-off of 1. Counts of significant and 
-              non-significant proeins are indicated. Proteins with a
+              non-significant proteins are indicated. Proteins with a
               log\\textsubscript{2}(FC) greater than 5 or less than -5 are 
@@
 fS5_cap <- c("\\textbf{Functional enrichment analyses of EVs from two DAY286 
-              morphologies.} Top 10 signficantly enriched biological process 
+              morphologies.} Top 10 significantly enriched biological process 
               (BP), cellular component (CC), and molecular function (MF) GO 

### 2020-03-30 inst/manuscript/tables/table_S2.tex
Fix minor typos in supplement

@@
 \begin{longtable}[t]{lllllllll}
-\caption{\label{tab:}\textbf{Candidate negative protein markers for 
+\caption{(\#tab:tableS2)\textbf{Candidate negative protein markers for 
               \textit{C. albicans} EVs.} This list of proteins consists of 
@@
 \multicolumn{9}{l}{\textbf{Cytoplasm}}\\
-\hspace{1em}ARO3 & Phospho-2-dehydro-3-deoxyheptonate aldolase<sup>b</sup> & -1.28 & -2.55 & -1.51 & -1.46 &  &  & \\
-\hspace{1em}ARO8 & Aromatic transaminase of the Ehrlich fusel oil pathway<sup>a</sup> & -2.37 & -1.81 & ex & -2.36 &  &  & \\
+\hspace{1em}ARO3 & Phospho-2-dehydro-3-deoxyheptonate aldolase\textsuperscript{b} & -1.28 & -2.55 & -1.51 & -1.46 &  &  & \\
+\hspace{1em}ARO8 & Aromatic transaminase of the Ehrlich fusel oil pathway\textsuperscript{a} & -2.37 & -1.81 & ex & -2.36 &  &  & \\
 \hspace{1em}GDB1 & Putative glycogen debranching enzyme & ex & ex & ex & -1.99 &  &  & \\
-\hspace{1em}HOM2 & Aspartate-semialdehyde dehydrogenase<sup>b</sup> & ex & -3.41 & ex & ex &  &  & \\
-\hspace{1em}orf19.1889 & Putative phosphoglycerate mutase family protein<sup>b</sup> & ex & -1.60 & ex & ex &  &  & \\
-\hspace{1em}orf19.5943.1 & \textit{S. cerevisiae} ortholog is Stm1, regulates translation<sup>a</sup> & ex & -3.98 & -4.57 & ex &  &  & \\
-\hspace{1em}orf19.6596 & Putative esterase<sup>a</sup> & ex & ex & ex & -2.90 &  &  & \\
-\hspace{1em}orf19.7263 & Putative X-Pro aminopeptidase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
-\hspace{1em}SBP1 & \textit{S. cerevisiae} ortholog is Sbp1, eIF4G binding protein<sup>a</sup> & ex & -4.30 & -3.80 & -2.15 &  &  & \\
-\hspace{1em}STI1 & HSP90 co-chaperone<sup>a</sup> & ex & -2.20 & ex & ex &  &  & \\
-\hspace{1em}URA4 & Predicted succinate semialdehyde dehydrogenase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
-\hspace{1em}XKS1 & Putative xylulokinase<sup>b</sup> & ex & ex & ex & ex &  &  & \\
+\hspace{1em}HOM2 & Aspartate-semialdehyde dehydrogenase\textsuperscript{b} & ex & -3.41 & ex & ex &  &  & \\
+\hspace{1em}orf19.1889 & Putative phosphoglycerate mutase family protein\textsuperscript{b} & ex & -1.60 & ex & ex &  &  & \\
+\hspace{1em}orf19.5943.1 & \textit{S. cerevisiae} ortholog is Stm1, regulates translation\textsuperscript{a} & ex & -3.98 & -4.57 & ex &  &  & \\
+\hspace{1em}orf19.6596 & Putative esterase\textsuperscript{a} & ex & ex & ex & -2.90 &  &  & \\
+\hspace{1em}orf19.7263 & Putative X-Pro aminopeptidase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
+\hspace{1em}SBP1 & \textit{S. cerevisiae} ortholog is Sbp1, eIF4G binding protein\textsuperscript{a} & ex & -4.30 & -3.80 & -2.15 &  &  & \\
+\hspace{1em}STI1 & HSP90 co-chaperone\textsuperscript{a} & ex & -2.20 & ex & ex &  &  & \\
+\hspace{1em}URA4 & Predicted succinate semialdehyde dehydrogenase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
+\hspace{1em}XKS1 & Putative xylulokinase\textsuperscript{b} & ex & ex & ex & ex &  &  & \\
 \hspace{1em}YNK1 & Nucleoside disphosphate kinase & -3.07 & -2.57 & -2.17 & -1.40 &  &  & \\
@@
 \multicolumn{9}{l}{\textbf{Cytosol and mitochondria}}\\
-\hspace{1em}ACH1 & Acetyl-CoA hydrolase<sup>b</sup> & -3.24 & -5.09 & -2.79 & -4.03 &  &  & \\
-\hspace{1em}GLR1 & Glutathione reductase<sup>b</sup> & ex & ex & ex & -3.28 &  &  & \\
-\hspace{1em}HSP60 & Heat shock protein 60<sup>b</sup> & -4.66 & -1.59 & -4.22 & -4.06 &  &  & \\
+\hspace{1em}ACH1 & Acetyl-CoA hydrolase\textsuperscript{b} & -3.24 & -5.09 & -2.79 & -4.03 &  &  & \\
+\hspace{1em}GLR1 & Glutathione reductase\textsuperscript{b} & ex & ex & ex & -3.28 &  &  & \\
+\hspace{1em}HSP60 & Heat shock protein 60\textsuperscript{b} & -4.66 & -1.59 & -4.22 & -4.06 &  &  & \\
 \addlinespace[0.3em]
 \multicolumn{9}{l}{\textbf{Mitochondria}}\\
-\hspace{1em}AAT1 & Aspartate aminotransferase<sup>a</sup> & ex & -2.11 & -1.48 & -5.70 &  &  & \\
-\hspace{1em}BAT22 & Putative branched chain amino acid aminotransferase<sup>b</sup> & ex & -3.57 & -1.44 & -3.12 &  &  & \\
-\hspace{1em}ETR1 & Putative 2-enoyl thioester reductase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
-\hspace{1em}GCV2 & Glycine decarboxylase P subunit<sup>a</sup> & ex & ex & ex & ex &  &  & \\
-\hspace{1em}IDH1 & Isocitrate dehydrogenase subunit<sup>a</sup> & -2.67 & -2.48 & -1.85 & -2.22 &  &  & \\
-\hspace{1em}IDH2 & Isocitrate dehydrogenase<sup>a</sup> & -3.21 & -2.88 & -3.54 & -3.37 &  &  & \\
-\hspace{1em}IDP1 & Putative isocitrate dehydrogenase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
-\hspace{1em}ILV5 & Ketol-acid reductoisomerase<sup>b</sup> & -3.68 & -2.62 & -2.27 & -5.48 &  &  & \\
-\hspace{1em}KGD2 & Putative dihydrolipoamide S-succinyltransferase<sup>a</sup> & ex & -2.20 & -2.04 & ex &  &  & \\
+\hspace{1em}AAT1 & Aspartate aminotransferase\textsuperscript{a} & ex & -2.11 & -1.48 & -5.70 &  &  & \\
+\hspace{1em}BAT22 & Putative branched chain amino acid aminotransferase\textsuperscript{b} & ex & -3.57 & -1.44 & -3.12 &  &  & \\
+\hspace{1em}ETR1 & Putative 2-enoyl thioester reductase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
+\hspace{1em}GCV2 & Glycine decarboxylase P subunit\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
+\hspace{1em}IDH1 & Isocitrate dehydrogenase subunit\textsuperscript{a} & -2.67 & -2.48 & -1.85 & -2.22 &  &  & \\
+\hspace{1em}IDH2 & Isocitrate dehydrogenase\textsuperscript{a} & -3.21 & -2.88 & -3.54 & -3.37 &  &  & \\
+\hspace{1em}IDP1 & Putative isocitrate dehydrogenase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
+\hspace{1em}ILV5 & Ketol-acid reductoisomerase\textsuperscript{b} & -3.68 & -2.62 & -2.27 & -5.48 &  &  & \\
+\hspace{1em}KGD2 & Putative dihydrolipoamide S-succinyltransferase\textsuperscript{a} & ex & -2.20 & -2.04 & ex &  &  & \\
 \hspace{1em}\underline{LPD1} & \underline{Dihydrolipoamide dehydrogenase} & \underline{ex} & \underline{-7.49} & \underline{-4.08} & \underline{-7.91} & \underline{} & \underline{} & \underline{}\\
-\hspace{1em}NIF3 & \textit{S. cerevisiae} ortholog is Nif3, mitochondrial protein<sup>a</sup> & ex & ex & ex & ex &  &  & \\
-\hspace{1em}orf19.2966 & Predicted dienelactone hydrolase domain<sup>a</sup> & ex & ex & ex & ex &  &  & \\
-\hspace{1em}orf19.449 & Putative phosphatidyl synthase<sup>b</sup> & ex & ex & ex & ex &  &  & \\
-\hspace{1em}orf19.7215.3 & \textit{S. cerevisiae} ortholog is Hsp10, mitochondrial co-chaperonin<sup>a</sup> & ex & ex & ex & ex &  &  & \\
-\hspace{1em}PDX3 & Pyridoxamine-phosphate oxidase<sup>a</sup> & ex & -1.85 & ex & ex &  &  & \\
+\hspace{1em}NIF3 & \textit{S. cerevisiae} ortholog is Nif3, mitochondrial protein\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
+\hspace{1em}orf19.2966 & Predicted dienelactone hydrolase domain\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
+\hspace{1em}orf19.449 & Putative phosphatidyl synthase\textsuperscript{b} & ex & ex & ex & ex &  &  & \\
+\hspace{1em}orf19.7215.3 & \textit{S. cerevisiae} ortholog is Hsp10, mitochondrial co-chaperonin\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
+\hspace{1em}PDX3 & Pyridoxamine-phosphate oxidase\textsuperscript{a} & ex & -1.85 & ex & ex &  &  & \\
 \hspace{1em}\underline{SOD2} & \underline{Superoxide dismutase} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{} & \underline{} & \underline{}\\
@@
 \multicolumn{9}{l}{\textbf{Nucleus}}\\
-\hspace{1em}DOT5 & Thioredoxin peroxidase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
-\hspace{1em}NHP6A & Non-histone chromosomal protein 6<sup>a</sup> & ex & ex & ex & ex &  &  & \\
+\hspace{1em}DOT5 & Thioredoxin peroxidase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
+\hspace{1em}NHP6A & Non-histone chromosomal protein 6\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
 \addlinespace[0.3em]
 \multicolumn{9}{l}{\textbf{Vacuole}}\\
-\hspace{1em}AMS1 & Putative alpha-mannosidase<sup>a</sup> & ex & ex & ex & -2.23 &  &  & \\
+\hspace{1em}AMS1 & Putative alpha-mannosidase\textsuperscript{a} & ex & ex & ex & -2.23 &  &  & \\
 \hspace{1em}\underline{APR1} & \underline{Vacuolar aspartic proteinase} & \underline{-1.83} & \underline{ex} & \underline{ex} & \underline{-1.07} & \underline{} & \underline{Y} & \underline{}\\
@@
 \multicolumn{9}{l}{\textbf{Proteasome}}\\
-\hspace{1em}orf19.2755 & \textit{S. cerevisiae} ortholog is Pre7, Beta 6 subunit of 20S proteasome<sup>a</sup> & ex & -2.34 & ex & ex &  &  & \\
-\hspace{1em}orf19.4230 & 20S proteasome subunit (beta7)<sup>a</sup> & ex & ex & ex & ex &  &  & \\
+\hspace{1em}orf19.2755 & \textit{S. cerevisiae} ortholog is Pre7, Beta 6 subunit of 20S proteasome\textsuperscript{a} & ex & -2.34 & ex & ex &  &  & \\
+\hspace{1em}orf19.4230 & 20S proteasome subunit (beta7)\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
 \hspace{1em}PUP2 & Alpha5 subunit of the 20S proteasome & ex & -4.13 & -2.53 & ex &  &  & \\
-\hspace{1em}SCL1 & Proteasome subunit YC7alpha<sup>a</sup> & ex & ex & ex & ex &  &  & \\
+\hspace{1em}SCL1 & Proteasome subunit YC7alpha\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
 \addlinespace[0.3em]
 \multicolumn{9}{l}{\textbf{Cytoplasmic stress granule}}\\
-\hspace{1em}TIF11 & Translation initiation factor eIF1a<sup>a</sup> & ex & ex & ex & ex &  &  & \\
-\hspace{1em}TMA19 & \textit{S. cerevisiae} ortholog is Tma19, ribosome associated protein<sup>a</sup> & ex & -3.05 & -2.74 & ex &  &  & \\
+\hspace{1em}TIF11 & Translation initiation factor eIF1a\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
+\hspace{1em}TMA19 & \textit{S. cerevisiae} ortholog is Tma19, ribosome associated protein\textsuperscript{a} & ex & -3.05 & -2.74 & ex &  &  & \\
 \addlinespace[0.3em]
 \multicolumn{9}{l}{\textbf{Peroxisome}}\\
-\hspace{1em}orf19.1433 & \textit{S. cerevisiae} ortholog is Lpx1, peroxisomal lipase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
+\hspace{1em}orf19.1433 & \textit{S. cerevisiae} ortholog is Lpx1, peroxisomal lipase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
 \addlinespace[0.3em]
@@
 \multicolumn{9}{l}{\textbf{Unknown}}\\
-\hspace{1em}orf19.2125 & Protein of unknown function<sup>c</sup> & ex & ex & ex & ex & 1 &  & \\
-\hspace{1em}orf19.2737 & Carbohydrate kinase domain-containing protein<sup>c</sup> & ex & ex & ex & -1.48 &  &  & \\
-\hspace{1em}orf19.5620 & Stationary phase enriched protein<sup>c</sup> & ex & ex & ex & -3.43 &  &  & \\
-\hspace{1em}OYE32 & NADPH oxidoreductase family protein<sup>c</sup> & ex & ex & ex & -2.90 &  &  & \\
+\hspace{1em}orf19.2125 & Protein of unknown function\textsuperscript{c} & ex & ex & ex & ex & 1 &  & \\
+\hspace{1em}orf19.2737 & Carbohydrate kinase domain-containing protein\textsuperscript{c} & ex & ex & ex & -1.48 &  &  & \\
+\hspace{1em}orf19.5620 & Stationary phase enriched protein\textsuperscript{c} & ex & ex & ex & -3.43 &  &  & \\
+\hspace{1em}OYE32 & NADPH oxidoreductase family protein\textsuperscript{c} & ex & ex & ex & -2.90 &  &  & \\
 \bottomrule

### 2020-03-30 inst/manuscript/candidaev_figures.Rmd
Fix Figure 4C 4D colours
Also, fix minor typos.

@@
              subcellular localisation as annotated in the Candida Genome 
-             Database (candidagenome.org) (ref:footnote1) unless otherwise 
+             Database (candidagenome.org) (48, 49) unless otherwise 
              indicated. The log\\textsubscript{2} ratio of the abundance 
@@
 
-# export table 1 LaTeX code with \\ line endings removed in a text file
-tab1_clean <- gsub("\\\\\\\\\n", "\n", tab1)
-
-cat(tab1_clean, file = "tables/table_1.txt", sep = "\n")
+# export table 1 LaTeX code (to be converted to docx with Pandoc)
+cat(tab1, file = "tables/table_1.tex", sep = "\n")
 
@@
   scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
-                    values = st_pal[c(3, 2, 4, 1)], 
+                    values = st_pal[c(1, 2, 3, 4)], 
                     labels = c("DAY Y", "A90028", "A10231", "DAY B"), 

### 2020-03-30 inst/manuscript/tables/table_1.tex
Fix Figure 4C 4D colours
Also, fix minor typos.

@@
 \begin{longtable}[t]{lllllllll}
-\caption{\label{tab:}\textbf{Candidate positive protein markers for 
+\caption{(\#tab:table1)\textbf{Candidate positive protein markers for 
              \textit{C. albicans} EVs.} This list of proteins consists of 
@@
              subcellular localisation as annotated in the Candida Genome 
-             Database (candidagenome.org) (ref:footnote1) unless otherwise 
+             Database (candidagenome.org) (48, 49) unless otherwise 
              indicated. The log\textsubscript{2} ratio of the abundance 
@@
 \multicolumn{9}{l}{\textbf{Plasma membrane}}\\
-\hspace{1em}\underline{ARF3} & \underline{Arf family GTPase<sup>a</sup>} & \underline{ex} & \underline{1.69} & \underline{ex} & \underline{3.45} & \underline{} & \underline{} & \underline{}\\
+\hspace{1em}\underline{ARF3} & \underline{Arf family GTPase\textsuperscript{a}} & \underline{ex} & \underline{1.69} & \underline{ex} & \underline{3.45} & \underline{} & \underline{} & \underline{}\\
 \hspace{1em}\underline{CDC42} & \underline{Rho family GTPase} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{} & \underline{} & \underline{}\\
@@
 \hspace{1em}CHS3 & Major chitin synthase of yeast and hyphae & ex & 4.12 & ex & ex & 5 &  & \\
-\hspace{1em}ENA21 & Predicted P-type ATPase sodium pump<sup>a</sup> & ex & ex & ex & ex & 9 &  & \\
-\hspace{1em}\underline{FAA4} & \underline{Long-chain fatty acid-CoA ligase<sup>a</sup>} & \underline{2.89} & \underline{2.24} & \underline{2.28} & \underline{1.45} & \underline{} & \underline{} & \underline{}\\
+\hspace{1em}ENA21 & Predicted P-type ATPase sodium pump\textsuperscript{a} & ex & ex & ex & ex & 9 &  & \\
+\hspace{1em}\underline{FAA4} & \underline{Long-chain fatty acid-CoA ligase\textsuperscript{a}} & \underline{2.89} & \underline{2.24} & \underline{2.28} & \underline{1.45} & \underline{} & \underline{} & \underline{}\\
 \hspace{1em}\underline{FET34} & \underline{Multicopper feroxidase} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{6.18} & \underline{1} & \underline{Y} & \underline{}\\
@@
 \hspace{1em}\underline{NCE102} & \underline{Non-classical protein export protein} & \underline{3.34} & \underline{2.20} & \underline{ex} & \underline{5.32} & \underline{4} & \underline{} & \underline{}\\
-\hspace{1em}\underline{EVP1<sup>d</sup>} & \underline{\textit{S.
-cerevisiae} ortholog is Pun1, plasma membrane protein<sup>a</sup>} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{3} & \underline{} & \underline{Y}\\
+\hspace{1em}\underline{EVP1\textsuperscript{d}} & \underline{\textit{S.
+cerevisiae} ortholog is Pun1, plasma membrane protein\textsuperscript{a}} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{3} & \underline{} & \underline{Y}\\
 \hspace{1em}PHM7 & Putative ion transporter & ex & ex & ex & ex & 11 &  & \\
@@
 \hspace{1em}\underline{RHO3} & \underline{Rho family GTPase} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{} & \underline{} & \underline{}\\
-\hspace{1em}\underline{SSO2} & \underline{Plasma membrane t-SNARE<sup>a</sup>} & \underline{ex} & \underline{1.88} & \underline{3.57} & \underline{ex} & \underline{1} & \underline{} & \underline{}\\
-\hspace{1em}\underline{SUR7} & \underline{Protein required for normal cell wall, plasma membrane<sup>c</sup>} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{7.04} & \underline{4} & \underline{} & \underline{}\\
+\hspace{1em}\underline{SSO2} & \underline{Plasma membrane t-SNARE\textsuperscript{a}} & \underline{ex} & \underline{1.88} & \underline{3.57} & \underline{ex} & \underline{1} & \underline{} & \underline{}\\
+\hspace{1em}\underline{SUR7} & \underline{Protein required for normal cell wall, plasma membrane\textsuperscript{c}} & \underline{ex} & \underline{ex} & \underline{ex} & \underline{7.04} & \underline{4} & \underline{} & \underline{}\\
 \hspace{1em}\underline{YCK2} & \underline{\textit{S.
@@
 \hspace{1em}\underline{orf19.1054} & \underline{\textit{S.
-cerevisiae} ortholog is Pom33, transmembrane nucleoporin<sup>b</sup>} & \underline{5.66} & \underline{ex} & \underline{ex} & \underline{2.51} & \underline{4} & \underline{} & \underline{}\\
+cerevisiae} ortholog is Pom33, transmembrane nucleoporin\textsuperscript{b}} & \underline{5.66} & \underline{ex} & \underline{ex} & \underline{2.51} & \underline{4} & \underline{} & \underline{}\\
 \hspace{1em}\underline{orf19.2168.3} & \underline{\textit{S.
-cerevisiae} ortholog is Yop1, reticulon-interacting protein<sup>a</sup>} & \underline{4.77} & \underline{1.98} & \underline{2.29} & \underline{1.81} & \underline{4} & \underline{} & \underline{}\\
+cerevisiae} ortholog is Yop1, reticulon-interacting protein\textsuperscript{a}} & \underline{4.77} & \underline{1.98} & \underline{2.29} & \underline{1.81} & \underline{4} & \underline{} & \underline{}\\
 \hspace{1em}\underline{orf19.3799} & \underline{\textit{S.
-cerevisiae} ortholog is Rtn1, reticulon protein<sup>b</sup>} & \underline{2.24} & \underline{1.40} & \underline{3.00} & \underline{1.29} & \underline{2} & \underline{} & \underline{}\\
+cerevisiae} ortholog is Rtn1, reticulon protein\textsuperscript{b}} & \underline{2.24} & \underline{1.40} & \underline{3.00} & \underline{1.29} & \underline{2} & \underline{} & \underline{}\\
 \hspace{1em}SEC61 & ER protein-translocation complex subunit & 2.53 & 2.16 & 2.10 & 1.46 & 8 &  & \\
@@
 \multicolumn{9}{l}{\textbf{Endosome, Golgi, transport vesicle}}\\
-\hspace{1em}\underline{SEC4} & \underline{Rab family GTPase<sup>a</sup>} & \underline{1.88} & \underline{1.20} & \underline{1.86} & \underline{2.90} & \underline{} & \underline{} & \underline{}\\
-\hspace{1em}\underline{YKT6} & \underline{Palmitoyltransferase, putative vacuolar SNARE complex protein<sup>a</sup>} & \underline{ex} & \underline{4.01} & \underline{5.46} & \underline{3.20} & \underline{} & \underline{} & \underline{}\\
-\hspace{1em}\underline{YPT31} & \underline{Rab family GTPase<sup>a</sup>} & \underline{ex} & \underline{1.57} & \underline{1.33} & \underline{3.33} & \underline{} & \underline{} & \underline{}\\
+\hspace{1em}\underline{SEC4} & \underline{Rab family GTPase\textsuperscript{a}} & \underline{1.88} & \underline{1.20} & \underline{1.86} & \underline{2.90} & \underline{} & \underline{} & \underline{}\\
+\hspace{1em}\underline{YKT6} & \underline{Palmitoyltransferase, putative vacuolar SNARE complex protein\textsuperscript{a}} & \underline{ex} & \underline{4.01} & \underline{5.46} & \underline{3.20} & \underline{} & \underline{} & \underline{}\\
+\hspace{1em}\underline{YPT31} & \underline{Rab family GTPase\textsuperscript{a}} & \underline{ex} & \underline{1.57} & \underline{1.33} & \underline{3.33} & \underline{} & \underline{} & \underline{}\\
 \addlinespace[0.3em]
 \multicolumn{9}{l}{\textbf{Vacuole}}\\
-\hspace{1em}\underline{VAC8} & \underline{Protein involved in vacuolar inheritance<sup>a</sup>} & \underline{2.79} & \underline{ex} & \underline{ex} & \underline{3.83} & \underline{} & \underline{} & \underline{}\\
+\hspace{1em}\underline{VAC8} & \underline{Protein involved in vacuolar inheritance\textsuperscript{a}} & \underline{2.79} & \underline{ex} & \underline{ex} & \underline{3.83} & \underline{} & \underline{} & \underline{}\\
 \addlinespace[0.3em]
 \multicolumn{9}{l}{\textbf{Mitochondrion}}\\
-\hspace{1em}MIR1 & Putative mitochondrial phosphate transporter<sup>a</sup> & 3.68 & 4.38 & 4.24 & 1.60 &  &  & \\
-\hspace{1em}POR1 & Mitochondrial outer membrane porin<sup>a</sup> & 3.44 & 2.51 & 3.69 & 1.38 &  &  & \\
+\hspace{1em}MIR1 & Putative mitochondrial phosphate transporter\textsuperscript{a} & 3.68 & 4.38 & 4.24 & 1.60 &  &  & \\
+\hspace{1em}POR1 & Mitochondrial outer membrane porin\textsuperscript{a} & 3.44 & 2.51 & 3.69 & 1.38 &  &  & \\
 \bottomrule

### 2020-04-10 R/README.Rmd
Update README files

@@
 This directory contains R script files used throughout the project. Each file 
-contains one custom function or one data.frame which has been
-documented using an roxygen2 skeleton.
+should only contain 1 function or dataset. Many of these functions have been
+taken from the _Bioconductor_ package 
+**[DEP](https://doi.org/10.18129/B9.bioc.DEP)**^1^, and adapted for use on
+basic matrices instead of `SummarizedExperiment` objects.
 
 After installing `candidaev`, an index of all the included 
-functions/data.frames can be viewed in R using:
+functions/datasets can be viewed in R using:
 
@@
 ```
+
+### References
+
+1. Zhang, X., Smits, A., van Tilburg, G., Ovaa, H., Huber, W., Vermeulen, 
+   M. (2018). Proteome-wide identification of ubiquitin interactions using UbIA-MS. 
+   _Nature Protocols_, **13**, 530-550. 
+   [doi:10.1038/nprot.2017.147](https://doi.org/10.1038/nprot.2017.147)

### 2020-04-10 README.Rmd
Accepted
Update README files

@@
 
-> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Bleackley, M. R., 
-Anderson, M. A. (2020) Protein markers for _Candida albicans_ EVs include 
+> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
+Bleackley, M. R. (2020) Protein markers for _Candida albicans_ EVs include 
 claudin-like Sur7 family proteins. _Journal of Extracellular_ 
-_Vesicles_, submitted.
+_Vesicles_, x(x): 1750810. DOI: 
+[10.1080/20013078.2020.1750810](https://doi.org/10.1080/20013078.2020.1750810)
 
-It has been permanently archived at Zenodo with the DOI shown above. The raw 
+It has been permanently archived at Zenodo with the DOI shown below. The raw 
 MS data has been deposited in the ProteomeXchange Consortium database via 
@@
 ```
-    .
-    ├── /R                   # Script files for functions and included data
-    ├── /data-raw            # Raw data used (but not modified) in analyses
-    ├── /data                # Data tables installed with package
-    ├── /inst/manuscript     # Final submitted manuscript, figures, and supplementary data
-    ├── /man                 # Auto-generated documentation for functions and included data
-    ├── /vignettes           # Detailed examples of how analyses were performed
+    ./
+    ├── R                    # Script files for functions and included datasets
+    ├── data-raw             # Raw data used (but not modified) in analyses
+    ├── data                 # Datasets included with package
+    ├── inst/manuscript      # Final accepted manuscript, figures, and supplementary data
+    ├── man                  # Auto-generated documentation for functions and included data
+    ├── vignettes            # Detailed examples of how analyses were performed
     ├── .Rbuildignore        # List of files and directories to ignore during R package build
@@
 
-A partial installation will only install functions and data, which can be
-used to analyse other MaxQuant `.txt` files.
+A partial installation will only install functions, datasets, which can be
+used to analyse other MaxQuant `.txt` files with _Candida albicans_ LFQ data.
+The manuscript will also be installed, but the vignettes won't be available.
 
@@
 
-# install partial compendium (functions, data)
+# install partial compendium (functions, datasets, manuscript)
 devtools::install_github("csdaw/candidaev", 
@@
 
-# install full compendium (functions, data, vignettes, manuscript) 
+# install full compendium (functions, datasets, manuscript, vignettes) 
 # and other packages required to build vignettes and manuscript
@@
 
-The manuscript `.docx` file, as submitted, can be downloaded 
+The manuscript `.docx` file, as accepted, can be downloaded 
 [here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).

### 2020-04-10 data-raw/README.Rmd
Update README files

@@
 
-# /data-raw
+# data-raw
 
 ## Description
+
 This directory contains all of the raw data files used in this project. 
@@
     ├── ...
-    ├── /data-raw
-    │    ├── /lcms           # proteinGroups.txt files output by MaxQuant
-    │    ├── /nta            # Nanosight NS300 .csv summary tables
-    │    ├── /reference      # UniProt and Candida Genome Database reference tables
+    ├── data-raw
+    │    ├── lcms            # proteinGroups.txt files output by MaxQuant
+    │    ├── nta             # Nanosight NS300 .csv summary tables
+    │    ├── reference       # UniProt and Candida Genome Database reference tables
     │    ├── README.Rmd      # R markdown file to produce README.md
-    │    └── README.md       # Description of /data-raw directory
+    │    └── README.md       # Description of data-raw directory
     └── ...

### 2020-04-10 inst/manuscript/README.Rmd
Update README files

--- 2019-07-03 inst/manuscript/README.Rmd
@@
 
-# /inst/manuscript
+# inst/manuscript
 
@@
 
-This directory contains the submitted manuscript, supplemental figures and 
-tables, and supplemental files for our paper:
+This directory contains the submitted manuscript and supplement `.docx` files, 
+main figures, supplementary figures, supplementary data for our paper:
 
 > Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
-Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
-claudin-like Sur7 family proteins and Rho GTPases. Mol. Cell. Proteomics, 
-submitted.
+Bleackley, M. R. (2020) Protein markers for _Candida albicans_ EVs include 
+claudin-like Sur7 family proteins. _Journal of Extracellular_ 
+_Vesicles_, x(x): 1750810. DOI: 
+[10.1080/20013078.2020.1750810](https://doi.org/10.1080/20013078.2020.1750810)
 
-The Rmarkdown (`.Rmd`), `.svg`, and `.R` files used to generate these 
-documents are provided along with the derived `.pdf` and `.csv` files.
+The scripts used to generate the figures, tables, and supplementary data are
+also present. This directory is automatically installed when the `candidaev`
+package is installed.
 
@@
 ├── ...
-    ├── /inst
-    │    ├── /manuscript
-    │         ├── /components                 # Contains required components for building the manuscript
-    │         ├── /figures                    # Contains .svg and .csv files used to make some figures
-    │         ├── /supplement_files           # Contains .R scripts used to generate supplemental files
-    │         ├── manuscript.Rmd              # R markdown file to produce manuscript.pdf
-    │         ├── manuscript.pdf              # Final submitted manuscript
-    │         ├── manuscript_supplement.Rmd   # R markdown file to produce manuscript_supplement.pdf
-    │         ├── manuscript_supplement.pdf   # Final submitted supplemental figures and tables
-    │         ├── README.Rmd                  # R markdown file to produce README.md
-    │         └── README.md                   # Description of /inst/manuscript directory
+├── inst
+│    ├── manuscript
+│         ├── components                        # Required components for building the manuscript
+│         ├── figures                           # Individual high resolution files for each figure
+|         ├── tables                            # Tables as .docx files
+│         ├── supplementary_data                # Supplementary data and scripts to generate them
+│         ├── README.Rmd                        # Rmarkdown file to produce README.md
+│         ├── README.md                         # Description of inst/manuscript directory
+│         ├── candidaev_manuscript_FINAL.docx   # Manuscript as accepted
+│         ├── candidaev_supplement_FINAL.docx   # Supplement figure and table legends
+│         ├── candidaev_figures.pdf             # Main figures and table as accepted
+│         ├── candidaev_figures.Rmd             # Script to produce main figures and table
+│         ├── candidaev_supplement.pdf          # Supplementary figures and tables as accepted
+│         └── candidaev_supplement.Rmd          # Script to produce supplementary figures and tables
 └── ...

### 2020-04-10 R/zzz.R
Fix various typos so check runs successfully

@@ -38,7 +38,12 @@
 
         # tukey_hsd.R
         "comparison", "comparison2", "p.adj", "term", "group1", "group2",
-        "adj.p.value")
+        "adj.p.value",
+
+        # sum_table.R
+        "median", "std.dev", "coeff.var", "n.valid.val", "n.na.val",
+        "prcnt.na"
+        )
       )
   invisible()
 }

### 2020-04-17 R/atcc_exp.R
Update volume and issue number

@@ -21,6 +21,6 @@
 #' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
 #' M. A., Bleackley, M. R. (2020) Protein markers for \emph{Candida albicans}
 #' EVs include claudin-like Sur7 family proteins.
-#' \emph{Journal of Extracellular Vesicles}, x(x): 1750810. DOI:
+#' \emph{Journal of Extracellular Vesicles}, 9(1): 1750810. DOI:
 #' \href{https://doi.org/10.1080/20013078.2020.1750810}{10.1080/20013078.2020.1750810}
 "atcc_exp"

### 2020-04-17 R/biofilm.R

@@ -64,6 +64,6 @@
 #' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
 #' M. A., Bleackley, M. R. (2020) Protein markers for \emph{Candida albicans}
 #' EVs include claudin-like Sur7 family proteins.
-#' \emph{Journal of Extracellular Vesicles}, x(x): 1750810. DOI:
+#' \emph{Journal of Extracellular Vesicles}, 9(1): 1750810. DOI:
 #' \href{https://doi.org/10.1080/20013078.2020.1750810}{10.1080/20013078.2020.1750810}
 "biofilm"

### 2020-04-17 R/biofilm_exp.R

@@ -21,6 +21,6 @@
 #' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
 #' M. A., Bleackley, M. R. (2020) Protein markers for \emph{Candida albicans}
 #' EVs include claudin-like Sur7 family proteins.
-#' \emph{Journal of Extracellular Vesicles}, x(x): 1750810. DOI:
+#' \emph{Journal of Extracellular Vesicles}, 9(1): 1750810. DOI:
 #' \href{https://doi.org/10.1080/20013078.2020.1750810}{10.1080/20013078.2020.1750810}
 "biofilm_exp"

### 2020-04-17 R/nta.R

@@ -44,6 +44,6 @@
 #' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
 #' M. A., Bleackley, M. R. (2020) Protein markers for \emph{Candida albicans}
 #' EVs include claudin-like Sur7 family proteins.
-#' \emph{Journal of Extracellular Vesicles}, x(x): 1750810. DOI:
+#' \emph{Journal of Extracellular Vesicles}, 9(1): 1750810. DOI:
 #' \href{https://doi.org/10.1080/20013078.2020.1750810}{10.1080/20013078.2020.1750810}
 "nta"

### 2020-04-17 R/yeast.R

@@ -68,6 +68,6 @@
 #' @source Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson,
 #' M. A., Bleackley, M. R. (2020) Protein markers for \emph{Candida albicans}
 #' EVs include claudin-like Sur7 family proteins.
-#' \emph{Journal of Extracellular Vesicles}, x(x): 1750810. DOI:
+#' \emph{Journal of Extracellular Vesicles}, 9(1): 1750810. DOI:
 #' \href{https://doi.org/10.1080/20013078.2020.1750810}{10.1080/20013078.2020.1750810}
 "yeast"
